### 2021-03-31 draft.tex
original

\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\include{snippets}

\newtheorem{theorem}{Theorem}

\begin{document}
\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
\author{Chenran Lin \and Lok-Ming Lui}
\date{}

\maketitle

\begin{abstract}
    There is a growing interest in shape analysis in recent years and in this paper we present a novel contour-based shape representation named Beltrami signature for 2D bounded simple connected domain. The proposed representation is based on conformal welding. With suitable normalization, the uniqueness of welding is guaranteed up to a rotation. Then it can be extended to a harmonic function and finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension. The benifits of the proposed signature is it keeps invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformation and distortion. Experiments demonstrates the above properties and also shows the excellent classification performance.
\end{abstract}

\keywords{Shape representation, conformal welding, simple connected,invariance}

\section{Introduction}
    The outline of the shape contains very important information and it can be used in many applications, such as segementation, recognition, registration and so on. However, even for the simplest situation, 2D simple connected shapes, it is a big challenge to describe clearly what the shape contour looks like. Because of the complexity of the image, there is an urgent demand to find a common, simple and robust shape representation for further mining and utilizing of shapes' geometric information. Therefore, many different presentations and measures have been widly studied and proposed recently \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.

    Considering 2D simple connected shapes, conformal welding is a kind of well-known shape signature. Given 2D simple connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$. This gives a simple but wonderful representation of $\Omega$ as Fig. \ref{fig1} shows. However, it has two fatal defects. First is that such representation is not unique. Because of the arbitrary of Riemann conformal mapping, $\Phi_1$ and $\Phi_2$ can only be determined up to a Mobious transformation, so such conformal welding is not unique. Generally speaking, some assumption is required to remove this uncertainty. For example, Sharon \etal \cite{sharon20062d} need to select a base point $P$ inside the given domain $\Omega$ artificially, then let $\Phi_1$ maps $0$ to this point $P$. The work of Mcenteggart \etal \cite{mcenteggart2018uniqueness} is based on Schramm-Loewner evolution(SLE) on random surfaces called Liouville quantum gravity, they proved the equivalence between uniqueness of conformal welding and conformal removable and conculded that if the boundary curve $\eta$ is an $\text{SLE}_k$ for $k \in (0, 4)$ and satisifies some other requirements, the corresponding conformal welding is unique. Some may not that care the uniqueness itself, they used equivalent class to guarantee uniqueness in a broader sense or evne just ignored it \cite{katznelson1990conformal,marshall2012conformal,lui2013shape,astala2010random}.

    Another thing is that even the conformal welding is very easy to be changed by simple transformations like rotation, scaling and translation. Such a unstable representation is hard to apply in practical applications since these transformations are inevitable in the real world.

    The contribution of this paper is that we propose a brand new presentation for 2D simple connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Beltrami signature. Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points. Under suitable normalization, conformal welding $f: \partial \D \rightarrow \partial \D$ can be determined up to a rotation. Such conformal welding can be extended to the whole unit disk and get a harmonic function $F: \D \rightarrow \D$ and the Beltrami coefficient of $F$ is our Beltrami signature.

    The proposed shape representation, Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain. The Beltrami signature is based on computational quasiconformal geometry. Computational quasiconformal geometry has been widely used in image processing and image analysis. Applications can be found in image segmentation 
    \cite{siu2020image,chan2018topology,zhang2020topology}
    , image registration
    \cite{lam2014landmark,lui2014teichmuller,ng2014computing,lui2012optimization,lam2014genus,zhang2012registration,lee2016landmark,lui2010optimized,lui2013texture,lui2010shape,lui2010optimizedc,lui2014geometric,choi2015flash}
     and image analysis 
    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shapec,lui2010shape3}
    . What's more worth mentioning is that Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape. It means the proposed representation has high practical value and can be applied in computer vision work like classification, segementation and so on.

    The paper is organized as follows: Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem and how Beltrami signature is obtained from given domain; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results. The paper is concluded in Section \ref{conclusion} and we point out future directions.

    \begin{figure}
        \begin{center}
        \includegraphics[width=\textwidth]{src/fig1.png}
        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simple connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
        \end{center}
        \label{fig1}
    \end{figure}

\section{Theoretical basis}\label{background}
    \subsection{Quasi-conformal mapping and Beltrami equation}
        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
        \[
            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
        \]

        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
        \begin{equation}\label{beltrami eq}
            \Part{f}{\overline{z}} = \mu(z) \Part{f}{z}
        \end{equation}
        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$. More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
        \begin{equation}
            \mu = \frac{f_{\overline{z}}}{f_{z}}
        \end{equation}
        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
        \begin{equation}
            f^*(ds^2_E) = \abs{\Part{f}{z}}^2 \abs{dz + \mu(z)d\overline{z}}^2
        \end{equation}
        which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$. $\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality. In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$. Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
        \begin{equation}\label{local f}
            f(z) = f(p)+f_z(p)z+f_{\overline{z}}(p)\overline{z} = f(p)+f_z(p)(z+\mu(p)\overline{z}).
        \end{equation}

        \begin{figure}
            \begin{center}
                \includegraphics[width=8cm]{src/fig2.jpg}
            \end{center}
            \caption{(a) Shows the original hippocampus. (b) Shows the parameter domain with circle packing pattern. Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
            \label{fig2}
        \end{figure}

        If $\mu(z)=0$ everywhere, then $f$ us called \textit{conformal} or \textit{holomorphic}. A conformal map satisfies the following well-known Cauchy-Riemann equation:
        \begin{equation}\label{cr eq}
            \Part{f}{\overline{z}} = 0.
        \end{equation}
        Inside the local parameter domain, $f$ may be considered as a map composed of a translation to $f(p)$ together with a stretch map $S(z) = z + \mu(p)\overline{z}$, which is postcomposed by multiplication of $f_z(p)$, which is conformal. All the conformal distortion of $S(z)$ is caused by $\mu(p)$. $S(z)$ is the map that causes $f$ to map a small circle to a small ellipse (see Fig. \ref{fig2}). Form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well. Specially, the angle of maximal magnification is $\arg(\mu(p))/2$ with magnifying factor $1+\abs{\mu(p)}$; the angle of maximal shrinkage is the orthogonal angle $\arg(\mu(p))/2 - \pi/2$ with shrinkage factor $1-\abs{\mu(p)}$. The distortion or dilation is given by:
        \begin{equation}
            K = \frac{1+\abs{\mu(p)}}{1-\abs{\mu(p)}}.
        \end{equation}
        Thus, the Beltrami coefficient $\mu$ gives us important information about the properties of the map (see Fig. \ref{fig3}).

        \begin{figure}
            \begin{center}
                \includegraphics[width=8cm]{src/fig3.jpg}
            \end{center}
            \caption{Quasi-conformal maps infinitesimal circles to ellipses. The Beltrami coefficient measure the distortion or dilation of the ellipse under the QC map.}
            \label{fig3}
        \end{figure}

        Suppose $f, g: \C \rightarrow \C$ are complex-valued function with Beltrami coefficient $\mu_f, \mu_g$ respectively. Then the Beltrami coefficient for the composition $g \circ f$ is given by
        \begin{equation}\label{mu of composition}
            \mu_{g \circ f} = \frac{\mu_f+(\mu_g \circ f) \tau}{1+\overline{\mu_f}(\mu_g \circ f) \tau},
        \end{equation}
        where $\tau = \frac{\overline{f_z}}{f_z}$. Note that when $g$ is conformal, $\mu_g = 0$ and 
        \begin{equation}\label{mu of conformal composition}
            \mu_{g \circ f} = \mu_f.
        \end{equation}

    \subsection{Conformal welding}
        Given 2D bounded simple connected shape, we can treat it as a boundary simple connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$. $\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobious transformation}:
        \begin{equation}
            M(z) = e^{i \theta} \frac{z - a}{1 - \overline{a}z}.
        \end{equation}
        Then we can define \textit{conformal welding} as:
        \begin{equation}
            f = \Phi_1^{-1} \circ \Phi_2.
        \end{equation}
        Such $f: \partial \D \rightarrow \partial \D$ is a diffeomorphism from $\partial \D$ to itself, which can be also thought as a periodic, real-valued monotone increasing function $f_\R: [0, 2\pi) \rightarrow [0, 2\pi)$ such that $f(e^{i \theta}) = e^{i f_\R(\theta)}$ (see Fig. \ref{fig1}).

    % \subsection{Reconstruction from conformal welding}
    %     Another important thing is that how we reconstruct the original domain $\Omega$ when we know the shape signature $f: \partial \D \rightarrow \partial \D$. Firstly, we can define $F: \D \rightarrow \D$ as
    %     \begin{equation}
    %         F(re^{i\theta}) = rf(e^{i \theta}) = r \Phi_1^{-1} \circ \Phi_2(e^{i\theta}),
    %     \end{equation}
    %     then we define
    %     \begin{equation}
    %         G(z) = \begin{cases}
    %             \Phi_1 \circ F, & z \in \D\\
    %             \Phi_2, & z \notin \D
    %         \end{cases}.
    %     \end{equation}
    %     It is easy to check such a $G$ is well-defined. For all $z \in \partial \D$, 
    %     $$\Phi_1 \circ F(z) = \Phi_1 \circ \Phi_1^{-1} \circ \Phi_2(z) = \Phi_2(z).$$
    %     Now we consider the Beltrami coefficient of G
    %     \begin{equation}\label{PDE reconstruct conformal welding}
    %         \mu_G = \frac{G_{\overline{z}}}{G_z} = \begin{cases}
    %             \mu_{\Phi_1 \circ F} = \mu_F,& z \in \D\\
    %             \mu_{\Phi_2} = 0, & z \notin \D
    %         \end{cases},
    %     \end{equation}
    %     and the map $G$ is the solution of above PDE (\ref{PDE reconstruct conformal welding}), which can be solved out by LBS method. Therefore, $\Phi_1 = G|_\D \circ F^{-1}$, $\Phi_2 = G|_{\D^c}$ and $\Omega = G \circ F^{-1}(\D)$ or $\Omega = G(\D^c)^c$.
    \subsection{Harmonic function and Poisson integral}
        A complex-valued function $f$ defined on $\Omega \subset \C$ is called \textit{harmonic} if it satisfies the \textit{Laplace's equation}:
        \begin{equation}
            \Delta f = 4 \frac{\partial^2 f}{\partial z \partial \overline{z}} = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2} = 0,
        \end{equation}
        where $z = x + iy$, $x$, $y$ is the real and imaginary value.

        Chen \etal prove following theorem in \cite{chen2010compositions}, which tells us that the composition of harmonic mappings and other mappings can inherit such harmonicity in some condition.
        \begin{theorem}\label{composition of harmonic}
            Let $f$ be a harmonic mapping, $f \circ g$ is harmonic if and only if $g(z) = az + b \overline{z} + c$, where $a$, $b$ and $c$ are constaants and $g \circ f$ is harmonic if and only if $g$ is analytic or anti-analytic.
        \end{theorem}

        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}. For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $F : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
            \begin{equation}\label{poisson integral}
                F(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
            \end{equation}
        Such $F$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e. $F(e^{i\theta}) = f(e^{i\theta})$ (see Fig. \ref{harmonic}). Of course, this $F$ is unique.

        \begin{figure}
            \begin{center}
                \includegraphics[width=\textwidth]{src/fig4.png}
            \end{center}
            \caption{(a) Continious function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$. (b) The corresponding harmonic function $F$ generated from $f$ by the equation (\ref{poisson integral}). Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
            \label{harmonic}
        \end{figure}

    \section{Beltrami signature}\label{main}
        In this chapter, we will propose a new signature, Beltrami signature, to representation boundary simple connected domain $\Omega$. Our proposed signature is based on conformal welding. But with some normalization.

        \subsection{Beltrami signature based on conformal welding}
            Here we give a brief explaination of how to create our new signature. Given the boundary simple connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it. Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $f$ is determined up to a rotation. Then $f$ can be extended to harmonic function $F$ defined on $\D$ by Poisson integral. At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
            \begin{equation}
                B:= \mu_F = \frac{F_{\overline{z}}}{F_z}.
            \end{equation}

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/fig5.png}
                \end{center}
                \caption{Illustration of Beltrami signature. (a) The input shape, a dolphin. (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b). (c) The Beltrami signature of original shape. Remark that the harmonic funcion and Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
                \label{illu of BS}
            \end{figure}

        \subsection{Analysis of uniqueness of Beltrami signature}
            According to Riemann mapping theorem, the conformal mapings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique. Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobious transformations. Therefore, the corresponding conformal welding is
            \begin{equation}
                \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = M_1^{-1} \circ \Phi_1^{-1} \circ \Phi_2 \circ M_2 = M_1^{-1} \circ f \circ M_2.
            \end{equation}

            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{F}$. The following theorem show the relationship between $F$ and $\tilde{F}$.

            \begin{theorem}
                Suppose $f$ and $\tilde{f}$ are continious map from $\partial \D$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations. $F$ and $\tilde{F}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{F} = M_1^{-1} \circ F \circ M_2$ iff $M_1$ is a rotation.
            \end{theorem}

            \begin{proof}
                Since $M_1$ is a Mobious transformations, $M_1^{-1}$ is also a Mobious transformation, so it can be written as $M_1^{-1}(z) = e^{i \theta}\frac{z - p}{1 - \overline{p}z}$, where $\theta \in [0, 2\pi)$ and $p \in \D$.

                $\Rightarrow :$ When $\tilde{F} = M_1^{-1} \circ F \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $F \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal. $\tilde{F}$ and $F \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$. Therefore, we have $$e^{i \theta}\frac{z - p}{1 - \overline{p}z} = az + b \overline{z} + c,$$ which means $p = b = c = 0$, $a = e^{i \theta}$ and so $M_1$ is a rotation.

                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ F \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}. It's easy to check that
                \[
                    M_1^{-1} \circ F \circ M_2 (e^{i \theta}) = M_1^{-1} \circ f \circ M_2(e^{i \theta}) = \tilde{f}(e^{i \theta}) = \tilde{F} (e^{i \theta}),
                \]
                which means $M_1^{-1} \circ F \circ M_2$ and $\tilde{F}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ F \circ M_2 = \tilde{F}$.
            \end{proof}

            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{F}$
            \begin{equation}
                \tilde{B} = \mu_{\tilde{F}} = \mu_{M_1^{-1} \circ F \circ M_2} = \mu_{F \circ M_2}.
            \end{equation}
            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{F \circ M_2} = \mu_{F} = B$, then we get $M_2$ is identity. Therefore, we know that the uniqueness of Beltrami signature is equivalent to following restrictions:
            \begin{enumerate}
                \item $\Phi_1: \D \rightarrow \Omega$ should be determined up to a rotation.
                \item $\Phi_2: \D^c \rightarrow \Omega^c$ should be uniquely determined.
            \end{enumerate}

        \subsection{Normalization to $\Phi_1$}\label{norm1}
            We hope $\Phi_1$ is determined up to a rotation. It is not that hard, for example, we can normalize $\Phi_1$ by restricting $\Phi_1(0) = 0$. But it need a hypothesis that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold. Here we want to show a new approach which can determine $\Phi_1$ up to a rotation without any additional assumption.

            In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n$ of $\Omega$. Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, we claims that $\Phi_1$ can be normalized by restricting the center of $p_i$ to $0$.

            \begin{theorem}\label{unique up to a rotation}
                Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
                \begin{align}\label{norm phi1}
                    \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
                \end{align}
                then such $\Phi_1$ is unique up to a rotation.
            \end{theorem}

            Before proving theorem \ref{unique up to a rotation}, we can consider following problem. Given boundary points $p_i$ on unit circle, can we find a Mobious transformation $M$ satisfies the following equation (\ref{fz})?
            \begin{equation}\label{fz}
                \sum_{k=1}^n M(p_k) = \sum_{k=1}^n e^{i\theta} \frac{p_k - a}{1 - \overline{a}p_k}= 0
            \end{equation}

            Without lose of generality, we ignore the rotation of $M$ and let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$. So $F_a$ is also a Mobius transformation and it's sufficient to find $a \in \D$ such that
            \begin{equation}\label{eq}
                f(a) = \sum_{k=1}^n F_a(p_k) = \sum_{k=1}^n \frac{p_k - a}{1 - \overline{a}p_k} = 0
            \end{equation}
            to show the equation (\ref{fz}) holds for some $M$. Intuitively, we believe that there is always a unique solution to this equation (\ref{eq}) (see Fig \ref{fasolvable}).

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/fig6.png}
                \end{center}
                \caption{The first row are some randomly generated points in $\partial \D$. The second row are the corresponding $\abs{f(a)}$, where $a \in \D$. The third row are also $\abs{f(a)}$ but is in top view. }
                \label{fasolvable}
            \end{figure}

            \subsubsection{The solvability of equation (\ref{eq})}
            First thing we want to do is to check whether this equation (\ref{eq}) is always solvable. According to Brouwer fixed point theorem, we have

            \begin{theorem}\label{existence}
                Given $\{p_1, p_2, \cdots, p_n\} \subset \partial \D$ and $n \ge 3$, let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$. The solution of equation (\ref{eq}) always exists.
            \end{theorem}

            \begin{proof}
                Note that when $e^{i \theta} \neq p_k$ for any $k$, we have
                \begin{equation*}
                    f(e^{i \theta}) = \sum_{k=1}^n \frac{p_k - e^{i \theta}}{1 - e^{-i\theta}p_k} = - n e^{i\theta},
                \end{equation*}
                so $\frac{1}{n} f(e^{i\theta}) + e^{i \theta} = 0$. Let 
                $$g(a) = \begin{cases}
                \frac{1}{n} f(a) + a, a \in \D,\\
                0, a \in \partial \D,
                \end{cases}
                $$
                such $g$ is defined on $\overline{\D}$ and is continuous. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.

                Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, then define
                $$
                h(a) = \begin{cases}
                    g(a), &a \in  \overline{\D} \setminus M,\\
                    \frac{g(a)}{\norm{g(a)}}, &a \in  M.
                \end{cases}
                $$
                $h$ is a continuous map from $\overline{\D}$ to itself, so there exists some $a$ let $h(a) = a$.

                If $a \in \partial \D$, $\norm{a} = 1$, but $\norm{h(a)} = 0 \neq \norm{a}$. If $a \in M$, we know $a \notin \partial \D$, so $\norm{a} < 1$, but $\norm{h(a)} = \frac{\norm{g(a)}}{\norm{g(a)}} = 1 \neq \norm{a}$. So when $h(a) = a$, $a$ is inside $\D \setminus M$. Therefore, such $a$ satisfies $g(a) = a$ and then $f(a) = 0$.
            \end{proof}

            Therefore, there must be some $a \in \D$ to be the solution of equation (\ref{fz}).

            \subsubsection{The uniqueness of the solution of equation (\ref{eq})}
            With solvability proved, we naturally want to know if this solution is unique. Let's consider a special case when $\sum_{k=1}^n p_k = 0$, we have
            \begin{theorem}\label{uniqueness when 0}
                Suppose $\sum_{k=1}^n p_k = 0$, equation (\ref{eq}) holds if and only if $a = 0$.
            \end{theorem}

            \begin{proof}
                If $a = 0$, it's obvious $F_0$ is identity, so $f(0) = \sum_{k=1}^n p_k = 0$.

                If $a \neq 0$, WLOG, we can assume that $0 < a < 1$, then $F_a(1) = 1$ and $F_a(-1) = -1$. For any $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$,
                \begin{equation*}
                    F_a(p_k) = F_a(\cos \theta_k + \sin \theta_k i) = \frac{\cos \theta_k + \sin \theta_k i - a}{1 - a \cos \theta_k - a \sin \theta_k i} = \frac{(a^2 + 1) \cos \theta_k -2a - (a^2 - 1) \sin \theta_k i}{a^2 + 1 - 2a \cos \theta_k},
                \end{equation*}
                so
                \begin{equation*}
                    \Re(F_a(p_k)) = \frac{(a^2 + 1) \cos \theta_k -2a}{a^2 + 1 - 2a \cos \theta_k} = \cos \theta_k - \frac{2a(1-\cos^2 \theta_k)}{(a-1)^2 + 2a(1-\cos \theta_k)} < \cos \theta_k = \Re(p_k).
                \end{equation*}

                Therefore, if $n \ge 3$, there must be at least one $p_k \neq \pm 1$ and so
                \begin{equation*}
                    \Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) < \sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
                \end{equation*}
                which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
            \end{proof}

            In the fact, no matter how these $p_i$ distribute, we can reduce it to the special mentioned above.

            \begin{theorem}\label{uniqueness}
                The solution of equation (\ref{eq}) is unique.
            \end{theorem}

            \begin{proof}
                Assume that $a_0, a_1$ are two different solutions, then we have that
                \begin{align*}
                    \sum_{k=1}^n F_{a_0}(p_k) = 0,\sum_{k=1}^n F_{a_1}(p_k) = 0
                \end{align*}

                Let $p_k' = F_{a_0}(p_k)$, then
                \begin{equation*}
                    \sum_{k=1}^n F_{a_1} \circ F_{a_0}^{-1} \circ F_{a_0}(p_k) = \sum_{k=1}^n (F_{a_1} \circ F_{-a_0})(F_{a_0}(p_k))= \frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}}\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0.
                \end{equation*}
                Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$. According to the above claim, $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, so $a_0 = a_1$, which contradicts to the assumption.
            \end{proof}

            \subsubsection{Unque $\Phi_1$ up to a rotation}

            Above theorems show that there is alway an unique solution $a \in \D$ of equation (\ref{eq}), so we can come back to theorem (\ref{unique up to a rotation}),

            \begin{proof}
                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$, then $\tilde{\Phi}_1 = \Phi_1 \circ M$, where $M$ is a Mobious transformation. Let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M^{-1} (p_k) = 0$. $M^{-1}$ is also a Mobious transformation so let $M^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
                \begin{equation*}
                    e^{i \theta} \sum_{k=1}^n F_a(p_k) = 0.
                \end{equation*}

                From theorem \ref{uniqueness when 0} we can know $a = 0$, then $M^{-1}(z) = e^{i \theta} z$ and so $\Phi_1$ is unique up to a rotation.
            \end{proof}

        \subsection{Normalization to $\Phi_2$}\label{norm2}
            As for $\Phi_2$, we hope it is uniquely determined. Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this and derivative to guarantee uniqueness of $\Phi_2$.

            \begin{theorem}
                If $\Phi_2: \D^c \rightarrow \Omega^c$ satisifies that
                \begin{align}
                    \Phi_2(\infty) = &\infty\label{norm phi2 1}\\
                    1 = \argmax{z \in \partial \D} &\abs{\Phi_2'(z)},\label{norm phi2 2}
                \end{align}
                then such $\Phi_2$ is uniquely determined.
            \end{theorem}

            \begin{proof}
                $\Phi_2$ and $\tilde{\Phi}_2$ are two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi}_2 = \Phi_2 \circ M$, where $M(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$ is a Mobious transformation. $\Phi_2$ and $\tilde{\Phi}_2$ both satisify (\ref{norm phi2 1}), then\[
                    \tilde{\Phi}_2(\infty) = \Phi_2(M(\infty)) = \infty \text{~and~} \Phi_2(\infty) = \infty.
                \]
                Therefore, $M(\infty) = e^{i \theta} \frac{\infty - a}{1- \overline{a} \infty} = \infty$, which means that $a = 0$ and $M(z) = e^{i \theta} z$.

                Consider the derivative of $\tilde{\Phi}_2$,
                \begin{equation}
                    \tilde{\Phi}_2'(z) = \Phi_2' \circ M(z) \cdot M'(z) = e^{i\theta} \Phi_2' (e^{i \theta}z),
                \end{equation}
                then we know that $\abs{\tilde{\Phi}_2'(z)} = \abs{\Phi_2'(e^{i \theta}z)}$. Suppose $a = \argmin{z \in \partial \D} |\Phi_2'(z)|$ and $a e^{-i \theta} = \argmin{z \in \partial \D} |\tilde{\Phi}_2'(z)|$. If condition (\ref{norm phi2 2}) holds for both $\Phi_2$ and $\tilde{\Phi}_2$, then $a = a e^{-i \theta} = 1$, so $a = 1$, $\theta = 0$ and $M$ is an identity, which shows that $\Phi_2 = \tilde{\Phi}_2$.
            \end{proof}

        \subsection{Invariance under simple transformation}
            With the normalization mentioned above, we can get unique Beltrami signature $B$ corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$. Now we want to prove that if we do some simple transformation like rotation, scaling and translation to $\Omega$, the Beltrami signature is invariant.

            \begin{theorem}
                Given a boundary simple connected domain $\Omega$ and transformation $T$ which is composed by rotation, scaling and transformation. Let $B_\Omega$ and $B_{T(\Omega)}$ be the Beltrami signature of $\Omega$ and $T(\Omega)$, then $B_\Omega = B_{T(\Omega)}$
            \end{theorem}

            \begin{proof}
                Suppose $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, $\tilde{\Phi}_1: \D \rightarrow T(\Omega)$ and $\tilde{\Phi}_2 : \D^c \rightarrow T(\Omega)$ are conformal. Since $T$ is composed by rotation, scaling and translation, $T$ can be written as $T(z) = ke^{i\theta} z + b$. Such $T$ is absolutely invertible and conformal.

                Let $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1 : \D \rightarrow \Omega$, $\hat{\Phi}_1$ is conformal. Given the boundary points $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$, then $\{T(z_1), T(z_2), \cdots, T(z_n)\} \subset \partial T(\Omega)$. Since $\tilde{\Phi}_1$ satisifies condition (\ref{norm phi1}), we have
                \[
                    \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0.
                \]
                Therefore
                \[
                    \sum_{i=1}^n \hat{\Phi}_1^{-1}(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1} \circ T(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0,
                \]
                which means $\hat{\Phi}_1$ also satisifies condition (\ref{norm phi1}). Hence $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1= \Phi_1 \circ R$, which equals to
                \begin{equation}
                    \tilde{\Phi}_1 = T \circ \Phi_1 \circ R,
                \end{equation}
                where $R$ is a rotation.

                Similarly, let $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2: \D^c \rightarrow \Omega^c$, $\hat{\Phi}_2$ is conformal. Since $\tilde{\Phi}_2(\infty) = \infty$, we have
                $$\hat{\Phi}_2(\infty) = T \circ \tilde{\Phi}_2(\infty) = \infty,$$
                which means $\hat{\Phi}_2$ satisifies condition (\ref{norm phi2 1}).

                As for condition (\ref{norm phi2 2}), we know that $T'(z) = k e^{i \theta}$, so
                \begin{equation}
                    \hat{\Phi}_2'(z) = T' \circ \tilde{\Phi}_2(z) \cdot \tilde{\Phi}_2'(z) = k e^{i \theta} \tilde{\Phi}_2'(z).
                \end{equation}
                Hence $\abs{\hat{\Phi}_2'} = \abs{k}\abs{\tilde{\Phi}_2'}$, which means $\hat{\Phi}_2$ also satisifies condition (\ref{norm phi2 2}). Therefore, $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2 = \Phi_2$ and then
                \begin{equation}
                    \tilde{\Phi}_2 = T \circ \Phi_2.
                \end{equation}

                We have the conformal welding
                \begin{equation}
                    \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = R^{-1} \circ \Phi_1^{-1} \circ T^{-1} \circ T \circ \Phi_2 = R^{-1} \circ f.
                \end{equation}
                Then the harmonic extension $\tilde{F} = R^{-1} \circ F$ and 
                \begin{equation}
                    B_{T(\Omega)} = \mu_{\tilde{F}} = \mu_{R^{-1} \circ F} = \mu_F = B_\Omega.
                \end{equation}
            \end{proof}

    % \section{Reconstruction from Beltrami signature}
    %     Given the Beltrami signature $B: \D \rightarrow \C$, we know that $B$ is Beltrami coefficient of some harmonic function $F: \overline{\D} \rightarrow \C$ and $F = f = \Phi_1^{-1} \circ \Phi_2$ in $\partial \D$. Define
    %     \begin{equation}
    %         G(z) = \begin{cases}
    %             \Phi_1 \circ F, & z \in \D\\
    %             \Phi_2, & z \notin \D
    %         \end{cases}.
    %     \end{equation}
    %     It is easy to check such a $G$ is well-defined. For all $z \in \partial \D$, 
    %     $$\Phi_1 \circ F(z) = \Phi_1 \circ \Phi_1^{-1} \circ \Phi_2(z) = \Phi_2(z).$$
    %     Then we compute the Beltrami coefficient of $G$,
    %     \begin{equation}\label{PDE beltrami signature}
    %         \mu_G = \frac{G_{\overline{z}}}{G_z} \begin{cases}
    %             \mu_{\Phi_1 \circ F} = \mu_F = B, &z \in \D\\
    %             \mu_{\Phi_2} = 0, & z \notin \D
    %         \end{cases}.
    %     \end{equation}
    %     The map $G$ is the solution of PDE (\ref{PDE beltrami signature}), which can be solved by LBS method. Therefore, $\Phi_2 = G|_{\D^c}$ and $\Omega = G(\D^c)^c$.
    \section{Implementation detail}\label{implementation}
        \subsection{Zipper algorithm}
            In oder to find an unique and stable Beltrami signature, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk. As metioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.

            Marshall \etal demonstrates the zipper algorithm detailedly with clear diagrams in \cite{marshall2007convergence}. For the convenience of readers, we gives a very brief review here. Given $N$ clockwise boundary points $z_1, z_2, \cdots, z_N \in \partial \Omega$, this algorithm use a series of linear fractional transformations $g_1, g_2, \cdots, g_N$ to map $z_1, z_2,\cdots, z_N$ to real axis one-by-one, and finally transfrom the upper half plane to unit disk by $g_{N+1}(z) = \frac{z-i}{z+i}$. Therefore, $g = g_{N+1} \circ g_N \circ \cdots \circ g_2 \circ g_1$ is a conformal mapping undisputedly and maps all these boundary points to unit circle and the domain $\Omega$ to $\D$. Remark that zipper algorithm is sensitive to the order of points. If we input the points anti-clockwise, i.e. $z_N, z_{N-1}, \cdots, z_1$, the zipper will give us a conformal mapping from $\Omega^c$ to $\D$.

            For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputing points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$. For $\Phi_2 : \D^c \rightarrow \Omega^c$, we can input anti-clockwise points and get $g_{\Phi_2} : \Omega^c \rightarrow \D$. At the result $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$. Because of the invariance of scaling, the number of boundary points $N$ is fixed as $200$ here and they are picked uniformly from the shape contour.

            \begin{algorithm}[H]                           % HERE!!!!!!!!!
            \caption{Zipper}          % give the algorithm a caption
            \label{zipper}      % and a label for \ref{} commands later in the document
            \begin{algorithmic}  % enter the algorithmic environment
                \STATE \textbf{Inputs:} $z_i \in \partial \Omega$ for $i=1, 2, \cdots, N$, $N=200$. %, $\epsilon = 10^{-10}$(any very small value)
                \STATE \textbf{Initialize:} Let $r=2$, $g_1(z) = \sqrt{\frac{z-z_2}{z-z_1}}$, $g= g_1$ and compute $p_{i,2}=g(z_i)$.
                \WHILE{$r < N$}
                    \STATE Pick $q = p_{r+1, r} = a + b i$, then compute $c = \frac{a}{\abs{q}^2}$, $d = \frac{b}{\abs{q}^2}$.
                    \STATE Let $g_r(z) = \sqrt{\frac{cz}{1+dzi}}$, then $g = g_r \circ g$ and compute $p_{i, r+1} = g_r(p_{i, k})$.
                    \STATE Let $r = r+1$.
                \ENDWHILE
                \STATE Let $g_{N}(z) = \left(\frac{z}{1-\frac{z}{p_{1,N}}}\right)^2$ and $g_{N+1}(z) = \frac{z-i}{z+i}$, then $g = g_{N+1} \circ g_N \circ g$ and $p_i = g_{N+1} \circ g_N(p_{i,N})$.
                \RETURN Conformal mapping $g: \Omega \rightarrow \D$ and boundary points $p_i \in \partial \D$.
            \end{algorithmic}
            \end{algorithm}

        \subsection{Normalization}
            To normalization $\Phi_1$, we need to solve equation (\ref{eq}). Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concerntrate around a point. At that time, $\abs{f(a)} \approx 1$ almost everywhere and the solution of (\ref{eq}) is also very close to the point. This means the solution is quite unstable and hard to converge for common algorithms(see Fig \ref{original distribution}).

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/fig7.png}
                \end{center}
                \caption{(a) The $p_i \in \partial \D$ gather in a small neiborhood around their arithmetic mean $p_c$, which is labeled in red. (b) The corresponding $\abs{f(a)}$ for these $p_i$. It's worth to metion that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
                \label{original distribution}
            \end{figure}

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/fig8.png}
                \end{center}
                \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment. (b) The $\abs{f(a)}$.}
            \end{figure}

            Instead of proposed a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobious transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform. For the $r$-th iteration, let $$p_{c,r} = \frac{\sum_{i=1}^k p_{i,r}}{k} \in \D$$ as the arithmetic center of $p_{i,r} \in \partial \D$, then the Mobious transformation $M_{p_{c,r}}$ gives new boundary points on unit disk as $$p_{i,r+1} = M_{p_{c,r}}(p_{i,r}) = \frac{p_{i,r} - p_{c,r}}{1 - \overline{p_{c,r}}p_{i,r}}.$$
            Note that we set $p_{i,0} = p_{i}$ at the beginning. Repeat this iteration for $r$ times until the center of boundary points is close to $0$, then the distribution is sufficiently regular and $\Phi_1$ becomes
            \begin{equation}
                \tilde{\Phi}_1 = \Phi_1 \circ M_{p_{c,0}}^{-1} \circ M_{p_{c,1}}^{-1} \circ \cdots \circ M_{p_{c,r}}^{-1}.
            \end{equation}
            Now equation (\ref{eq}) can be solved without much effort by Newtown's method. Suppose $a \in \D$ is the optimal solution and the final mapping is
            \begin{equation}
                \hat{\Phi}_1 = \tilde{\Phi}_1 \circ M_{a}^{-1}
            \end{equation}

            \begin{algorithm}[H]
            \caption{Normalize $\Phi_1$}
            \label{alg norm phi1}
            \begin{algorithmic}
                \STATE \textbf{Inputs:} $\Phi_1$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $\epsilon=0.2$.
                \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$. %and $M_{p_{c,0}}(z) = \frac{z-p_{c,0}}{1- \overline{p_{c, 0}}z}$
                \WHILE{$\abs{p_c,r} > \epsilon$}
                    \STATE Let $M_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $\Phi_1 = \Phi_1 \circ M_{p_{c,r}}^{-1}$.
                    \STATE Compute $p_{i, r+1} = M_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
                    \STATE Let $r = r+1$.
                \ENDWHILE
                \STATE Solve equation (\ref{eq}) by Newtown's method and get solution $a \in \D$.
                \STATE Let $M_a(z) = \frac{z-a}{1- \overline{a}z}$ and $\hat{\Phi}_1 = \Phi_1 \circ M^{-1}_{a}$.
                \STATE Compute $p_i = M_a(p_{i,r})$.
                \RETURN Conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfied (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
            \end{algorithmic}
            \end{algorithm}

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/fig9.png}
                \end{center}
                \caption{The iteration of distribution adjustment. The boundary points are blue and their arithmetic center is red in each picture. (a)-(d) The 1st, 3rd, 7th, 12th iteration.}
            \end{figure}

            As for the normalization of $\Phi_2$, it's much easier since we only need to map $\infty$ to $\infty$ by replace $\Phi_2$ with $\tilde{\Phi}_2(z)=\Phi_2 \circ M^{-1}_{b}(\frac{1}{z})$, where $b = \Phi_2^{-1}(\infty)$. Another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$. Since we know each linear fractional transformation composing $\Phi_2$, the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule. Here we select $10^5$ points from $[0, 2\pi)$ as $\theta_j$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}). Therefore, the maximal solution $\theta_{\max} = \argmax{j \in [1,10^5]} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ can be used to normalize the rotation and the final mapping is 
            \begin{equation}
                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z).
            \end{equation}
            This grid can generate a triangluar mesh $M$ and we will calculate the Beltrami coefficient on $M$.

            \begin{algorithm}[H]
            \caption{Normalize $\Phi_2$}
            \label{alg norm phi2}
            \begin{algorithmic}
                \STATE \textbf{Inputs:} $\Phi_2$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $M=10^5$.
                \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$.
                \STATE Let $M_b(z) = \frac{z-b}{1-\overline{b}z}$ and $\tilde{\Phi}_2(z)=\Phi_2 \circ M^{-1}_{b}(\frac{1}{z})$.
                \STATE Calculate $\abs{\tilde{\Phi}_2'}$ by chain derative rule.
                \STATE Let $\theta_j = \frac{2\pi}{M}(j-1)$ for $j=1,2, \cdots, M$.
                \STATE Compute $\abs{\tilde{\Phi}_2'}(e^{i \theta_j})$.
                \STATE Find maximal value and corresponding $\theta_{max}$.
                \STATE Let $\hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z)$ and compute $p_i = \frac{e^{-i \theta_{max}}}{M_b(p_i)}$.
                \RETURN Conformal mapping $\Phi_1: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
            \end{algorithmic}
            \end{algorithm}

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/fig10.png}
                \end{center}
                \caption{The change of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ for different $\theta_j \in [0, 2\pi)$. It shows this function has a significant maximum and $\theta_{max}$ is about $1.25\pi$.}
                \label{derative}
            \end{figure}

        \subsection{Harmonic extension}\label{detail harmonic}
            After obtaining the normalized $\hat{\Phi}_1$ and $\hat{\Phi}_2$, the conformal welding can be represented as a series points $(\varphi_i, \omega_i) = \left(\arg(\hat{\Phi}_2^{-1}(z_i)), \arg(\hat{\Phi}_1^{-1}(z_i))\right)$, where $\varphi_i, \omega_i \in [0, 2\pi)$. So in fact we should use discrete form Poisson integral to extend $f$ to a harmonic mapping $F$ on the unit disk.
            \begin{equation}\label{discrete poisson integral}
                F(re^{i\theta}) = \frac{1}{2\pi} \sum_{j=1}^k \frac{(1-r^2) e^{i \omega_j}}{1 - 2 r cos (\varphi_j - \theta) + r^2} \left((\varphi_{j} - \varphi_{j-1}) \bmod{ 2\pi}\right),
            \end{equation}
            where $\varphi_0 = \varphi_k$ and this $\bmod$ can solve some critical value problem, for example, $\varphi_j = 0$ but $\varphi_{j-1} = 6$. For the convenience of computation, we only calculate the value of $F$ on a grid
            \begin{equation}
                G = \{z=x+iy \mid \abs{z} \le 1, x=\frac{j}{100}, y=\frac{k}{100}, j,k=-100,-99,\cdots,99,100 \}.
            \end{equation}

        \subsection{Summary of the Algorithm}
            The totally algorithm is as following.
            \begin{algorithm}[H]
            \caption{Calculate Beltrami signature}
            \label{alg all}
            \begin{algorithmic}
                \STATE \textbf{Inputs:} Bounded simple connected shape $\Omega \subset \C$, $N=200$.
                \STATE Pick $N$ clockwise points $z_1, z_2, \cdots, z_N$ from $\partial \Omega$ uniformly.
                \STATE Input $z_1, z_2, \cdots, z_N$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_1}: \D \rightarrow \Omega$ and $p_{i,1} \in \partial\D$.
                \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and input it and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get normalized $\hat{\Phi}_1$ and $p_{i,1}$.
                \STATE Input $z_N, \cdots, z_2, z_1$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_2}: \D \rightarrow \Omega^c$ and $p_{i,2} \in \partial\D$.
                \STATE Let $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$ and input it and $p_{i,2}$ to Algorithm \ref{alg norm phi2}, then get normalized $\hat{\Phi}_2$ and $p_{i,2}$.
                \STATE Let $f = \hat{\Phi}_1^{-1} \circ \hat{\Phi}_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
                \STATE Extend $f$ to $F$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
                \STATE Calculate Beltrami coefficient $B$ of $F$ on $M$.
                \RETURN Beltrami signature $B$.
            \end{algorithmic}
            \end{algorithm}
    \section{Experimental result}\label{result}
        In this section, we will validate key properties of our proposed Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification. Besides that, a good shape representation should keep the similarity with the same kind shape and is significantly different from different kinds of shape.

        Before showing results, what needs illustration is that the distance we used to measure the difference of Beltrami signature is based on $L^2$ norm,
        \begin{equation}\label{bs dis}
            d(B_1, B_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{B_1(z_i) - B_2(z_i)}^2},
        \end{equation}
        where $B_1, B_2$ are two different Beltrami signature, $z_i \in \D$ is the face center of triangluar mesh $M$ metioned in Section \ref{detail harmonic} and $N=60962$ here.
        \subsection{Invariance}\label{sec inv}
            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate Beltrami signature after sacling, translation and rotation and compare them with the original shape's Beltrami signature. The result is displayed in Fig \ref{inv}. In this figure, the first column are the sets of boundary points and we remark them as $\Omega_a$ to $\Omega_f$. The second column are the corresponding Beltrami signatures $B_a$ to $B_f$. Note that all the Beltrami signatures are shown in modulus, i.e. $\abs{B_n}$ for row $n$, and in top view. And the third column(if have) are the histograms of the difference between original shape's Beltrami signature, i.e. $\abs{B_n - B_a}$ for row $n$.

            Row b and c are about scaling, the shapes are $\Omega_b = \{z \mid z = 1.5 z_a, z_a \in \Omega_a \}$ and $\Omega_c = \{z \mid z = 0.5 z_a, z_a \in \Omega_a \}$ and the distance are $d(B_a, B_b) = 5.5647 \times 10^{-8}$ and $d(B_a, B_c) = 5.3476 \times 10^{-8}$. Row d is about translation, the shape $\Omega_d = \{z \mid z = z_a+100+20i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_d) = 4.7817 \times 10^{-8}$. Row e is about rotation, the shape is $\Omega_e = \{z \mid z = e^{0.2\pi i} z_a, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.2144 \times 10^{-8}$. Row f is the combination of scaling, tanslation and rotation, the shape is $\Omega_e = \{z \mid z = 3e^{-0.85\pi i} z_a+350+600i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.7635 \times 10^{-8}$. These confirm the invariance of Beltrami signature and scaling, translation and rotation.

            \begin{figure}
                \begin{center}
                    \includegraphics[width=10.5cm]{src/inv.png}
                \end{center}
                \caption{Beltrami signature under scaling, translation and rotation.}
                \label{inv}
            \end{figure}

        \subsection{Robustness}
            Similar with Section \ref{sec inv}, here we still treat the dolphin as the original shape and modify some small parts of it and Fig \ref{robust} is the result. It shows that the proposed signature is robust and stable and will not have a big mutation cauesd by small disturbance.

            Row g, h and i are result about modification. These shapes are generated by removing or adding something, which is in the red circle. We can see that Beltrami signatures have slight differences from $B_a$ but are still similar in general. And this figure also demonstrates that the bigger the modification part is, the more different the Beltrami signature is. For example in row i, losing a half of the tail makes the signature has a marked change. Quantitatively, $d(B_a, B_g) = 0.0132$, $d(B_a, B_h) = 0.0316$ and $d(B_a, B_i) = 0.1761$.

            Row j is for distortion. This dolphin is only enlarged in horizontally and becomes fatter, then the $B_j$ moves a little bit and $d(B_a, B_j) = 0.0724$.

            \begin{figure}
                \begin{center}
                    \includegraphics[width=10.5cm]{src/robust.png}
                \end{center}
                \caption{Beltrami signature under small modification}
                \label{robust}
            \end{figure}

        \subsection{Classification with Beltrami signature}
            Above properties ensure the proposed signature having the ablity to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.

            To compare the classification performance, we also use conformal welding directly to classify, and the distance is defined as
            \begin{equation}\label{welding dis}
                d_c(f_1, f_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{f_1(z_i) - f_2(z_i)}^2},
            \end{equation}
            where $f_1, f_2$ are two different conformal welding, $N=200$ here.

            We prepare 3 kinds of animals, fish, giraffe and elephant. There are 3 images for each group so 9 images in total. From Fig \ref{classification images}, we can find that each class share similar Beltrami signatures and conformal welding. From Fig \ref{dis matrix}, the inter-class distance of Beltrami signature is awlays less than 0.2 while the intra-class distance is greater than 0.2. But for conformal welding, the data is messy, for example, fish 3 thinks itself is very different from other fishes but looks most like giraffe 2. After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the Beltrami signature shows powerful classification ablity.

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/figs.png}
                \end{center}
                \caption{These 3 rows are elephant, fish and giraffe. In each subfigure, the top left is the input shape, bottom left is the conformal welding and the right is Beltrami signature.}
                \label{classification images}
            \end{figure}

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/distance.png}
                \end{center}
                \caption{(a) The distance matrix of Beltrami signatures of above 9 shapes by equation (\ref{bs dis}). (b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
                \label{dis matrix}
            \end{figure}

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/mds.png}
                \end{center}
                \caption{(a) The MDS result of Beltrami signature. (b) The MDS result of conformal welding.}
                \label{mds1}
            \end{figure}

            \begin{figure}
                \begin{center}
                    \includegraphics[width=\textwidth]{src/mds2.png}
                \end{center}
                \caption{(a) The MDS result of Beltrami signature. (b) The MDS result of conformal welding. (c) The clustering result of Beltrami signature. (d) The clustering results of conformal welding.}
                \label{mds2}
            \end{figure}

        \subsection{Classification for more classes}
            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabit. We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes. The MDS and clustering results based on Beltrami signature and conformal welding are displayed in Fig \ref{mds2}. The classification accuracy based on Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.

    \section{Conclusion}\label{conclusion}
        In this paper, we propose a novel shape representation for 2D bounded simple connected objects called Beltrami signature. The proposed signature is based on conformal welding but overcome a key shortcoming that it can be uniquely determined by the given shape. What's more exciting is that the proposed representation is invariance under scaling, translation and rotation. For slight deformation and distortion, Beltrami signature keeps roubost and only changes within a reasonable small range. Therefore, there are reasons to believe the it does have ablity to represent some invariant geometrical features. The experimental results also confirm that the Beltrami signature has excellent performance in multi-classification tasks.

        Although our work has achieved relatively good results, the proposed representation still have some limitations. Firstly, the Beltrami signature is only applicable to simple connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world. So we are eager for a feasible method to extend our Beltrami signature to multi connected situation. Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangluar mesh, which consumes a lot of time. Therefore, a fast algorithm to obatin this signature avoiding dense mesh is of high priority in our future work. Thirdly, when normalizing the conformal mapping $\Phi_2$ from exterior of unit disk to exterior of the domain, the position where the derivation of $\Phi_2$ reaches the maximum value is used to adjust the rotation. We trust this point in the original image has a certain geometric meaning, whereas it is not clear at present.

        In summary, we will focus on third marjor directions in the future. One is that the deeper meaning of Beltrami signature is worth digging and then a multi-connected version of representation based on this work can be proposed. Another is that if the Beltrami signature contains some geometrical features of shapes, we can also extract them directly from images and generate the Beltrami signature again. Hence the deep learning theory may help us to compute this signature from given images immediately, which is very likely to improve algorithm speed performance greatly. A third direction is this representation can be used in more applications like segementation, registration and so on.

    \bibliographystyle{IEEEtran}
    \bibliography{cite}
\end{document}

### 2021-04-07 template.tex
normalize H

--- 2021-03-31 draft.tex
@@
-\documentclass[12pt]{article}
+\RequirePackage{fix-cm}
+%
+%\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+% \smartqed  % flush right qed marks, e.g. at end of proof
+%
+% \let\equation\relax
+% \let\endequation\relax
+\let\proof\relax
+\let\endproof\relax
+\let\example\relax
+\let\endexample\relax
 
+\usepackage{graphicx}
 \usepackage[margin=1in]{geometry} 
-\usepackage{amsmath,amsthm,amssymb}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amssymb}
 \usepackage{hyperref}
-\usepackage{graphicx}
 \usepackage{algorithm}
@@
 \include{snippets}
+%
+% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
+%
+% insert here the call for the packages your document requires
+%\usepackage{latexsym}
+% etc.
+%
+% please place your own definitions here and don't use \def but
+% \newcommand{}{}
+%
+% Insert the name of "your journal" with
+% \journalname{myjournal}
+%
+\begin{document}
 
-\newtheorem{theorem}{Theorem}
+\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
+% \subtitle{Do you have a subtitle?\\ If so, write it here}
 
-\begin{document}
-\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
-\author{Chenran Lin \and Lok-Ming Lui}
-\date{}
+%\titlerunning{Short form of title}        % if too long for running head
+
+\author{Chenran Lin \and Lok Ming Lui}
+
+%\authorrunning{Short form of author list} % if too long for running head
+
+\institute{Chenran Lin \at
+              Department of Mathematics, The Chinese University of Hong Kong \\
+              \email{crlin@math.cuhk.edu.hk}           %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+           \and
+           Lok Ming Lui \at
+              Department of Mathematics, The Chinese University of Hong Kong\\
+              \email{lmlui@math.cuhk.edu.hk}           %  \\
+}
+
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
 
@@
 \begin{abstract}
-    There is a growing interest in shape analysis in recent years and in this paper we present a novel contour-based shape representation named Beltrami signature for 2D bounded simple connected domain.
-The proposed representation is based on conformal welding.
-With suitable normalization, the uniqueness of welding is guaranteed up to a rotation.
-Then it can be extended to a harmonic function and finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension.
+  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simple connected domain in this paper, named Beltrami signature.
+The proposed signature is based on conformal welding.
+We extended the welding mapping to a harmonic function.
+With suitable normalization, the uniqueness of this harmonic function is guaranteed up to a rotation.
+And finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension.
 The benifits of the proposed signature is it keeps invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformation and distortion.
-Experiments demonstrates the above properties and also shows the excellent classification performance.
+Experiments demonstrate the above properties and also show the excellent classification performance.
+\keywords{
+  Shape representation \and conformal welding \and simple connected \and invariance}
+% \PACS{PACS code1 \and PACS code2 \and more}
+% \subclass{MSC code1 \and MSC code2 \and more}
 \end{abstract}
 
-\keywords{Shape representation, conformal welding, simple connected,invariance}
-
 \section{Introduction}
+\label{intro}
     The outline of the shape contains very important information and it can be used in many applications, such as segementation, recognition, registration and so on.
@@
 Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points.
-Under suitable normalization, conformal welding $f: \partial \D \rightarrow \partial \D$ can be determined up to a rotation.
-Such conformal welding can be extended to the whole unit disk and get a harmonic function $F: \D \rightarrow \D$ and the Beltrami coefficient of $F$ is our Beltrami signature.
+Such conformal welding can be extended to the whole unit disk and get a harmonic function $H: \D \rightarrow \D$.
+Under suitable normalization, harmonic extension $H$ can be determined up to a rotation and the Beltrami coefficient of $H$ is then unique and becomes our Beltrami signature.
 
@@
         \begin{center}
-        \includegraphics[width=\textwidth]{src/fig1.png}
+        \includegraphics[width=7.6cm]{src/fig1_down.png}
         \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simple connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
@@
         Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
-        \[
+        \begin{equation*}
             \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
-        \]
+        \end{equation*}
 
@@
         \begin{equation}\label{local f}
-            f(z) = f(p)+f_z(p)z+f_{\overline{z}}(p)\overline{z} = f(p)+f_z(p)(z+\mu(p)\overline{z}).
+            f(z) = f(p)+f_z(p)(z+\mu(p)\overline{z}).
         \end{equation}
@@
             \begin{center}
-                \includegraphics[width=8cm]{src/fig2.jpg}
+                \includegraphics[width=7.6cm]{src/fig2.jpg}
             \end{center}
@@
             \begin{center}
-                \includegraphics[width=8cm]{src/fig3.jpg}
+                \includegraphics[width=7.6cm]{src/fig3.jpg}
             \end{center}
@@
 
-    % \subsection{Reconstruction from conformal welding}
-    %     Another important thing is that how we reconstruct the original domain $\Omega$ when we know the shape signature $f: \partial \D \rightarrow \partial \D$.
-Firstly, we can define $F: \D \rightarrow \D$ as
-    %     \begin{equation}
-    %         F(re^{i\theta}) = rf(e^{i \theta}) = r \Phi_1^{-1} \circ \Phi_2(e^{i\theta}),
-    %     \end{equation}
-    %     then we define
-    %     \begin{equation}
-    %         G(z) = \begin{cases}
-    %             \Phi_1 \circ F, & z \in \D\\
-    %             \Phi_2, & z \notin \D
-    %         \end{cases}.
-    %     \end{equation}
-    %     It is easy to check such a $G$ is well-defined. For all $z \in \partial \D$, 
-    %     $$\Phi_1 \circ F(z) = \Phi_1 \circ \Phi_1^{-1} \circ \Phi_2(z) = \Phi_2(z).$$
-    %     Now we consider the Beltrami coefficient of G
-    %     \begin{equation}\label{PDE reconstruct conformal welding}
-    %         \mu_G = \frac{G_{\overline{z}}}{G_z} = \begin{cases}
-    %             \mu_{\Phi_1 \circ F} = \mu_F,& z \in \D\\
-    %             \mu_{\Phi_2} = 0, & z \notin \D
-    %         \end{cases},
-    %     \end{equation}
-    %     and the map $G$ is the solution of above PDE (\ref{PDE reconstruct conformal welding}), which can be solved out by LBS method.
-Therefore, $\Phi_1 = G|_\D \circ F^{-1}$, $\Phi_2 = G|_{\D^c}$ and $\Omega = G \circ F^{-1}(\D)$ or $\Omega = G(\D^c)^c$.
     \subsection{Harmonic function and Poisson integral}
@@
         The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}.
-For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $F : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
+For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
             \begin{equation}\label{poisson integral}
-                F(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
+                H(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
             \end{equation}
-        Such $F$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
-$F(e^{i\theta}) = f(e^{i\theta})$ (see Fig.
+        Such $H$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
+$H(e^{i\theta}) = f(e^{i\theta})$ (see Fig.
 \ref{harmonic}).
-Of course, this $F$ is unique.
+Of course, this $H$ is unique.
 
@@
             \begin{center}
-                \includegraphics[width=\textwidth]{src/fig4.png}
+                \includegraphics[width=7.6cm]{src/fig4_down.png}
             \end{center}
             \caption{(a) Continious function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$.
-(b) The corresponding harmonic function $F$ generated from $f$ by the equation (\ref{poisson integral}).
+(b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
 Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
@@
     \section{Beltrami signature}\label{main}
-        In this chapter, we will propose a new signature, Beltrami signature, to representation boundary simple connected domain $\Omega$.
-Our proposed signature is based on conformal welding.
-But with some normalization.
+        In this chapter, we will propose a new representation, Beltrami signature, to discribe boundary simple connected domain $\Omega$.
+Our proposed signature is based on conformal welding and quasi-conformal theory.
 
@@
 Given the boundary simple connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it.
-Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $f$ is determined up to a rotation.
-Then $f$ can be extended to harmonic function $F$ defined on $\D$ by Poisson integral.
+Then $f$ can be extended to harmonic function $H$ defined on $\D$ by Poisson integral (\ref{poisson integral}).
 At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
             \begin{equation}
-                B:= \mu_F = \frac{F_{\overline{z}}}{F_z}.
+                B:= \mu_H = \frac{H_{\overline{z}}}{H_z}.
             \end{equation}
+            Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $B$ is determined.
 
-            \begin{figure}
+            \begin{figure*}
                 \begin{center}
@@
 (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b).
-(c) The Beltrami signature of original shape.
+(c) The Beltrami signature of (a).
 Remark that the harmonic funcion and Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
                 \label{illu of BS}
-            \end{figure}
+            \end{figure*}
 
@@
 
-            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{F}$. The following theorem show the relationship between $F$ and $\tilde{F}$.
+            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{H}$. The following theorem show the relationship between $H$ and $\tilde{H}$.
 
@@
                 Suppose $f$ and $\tilde{f}$ are continious map from $\partial \D$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
-$F$ and $\tilde{F}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{F} = M_1^{-1} \circ F \circ M_2$ iff $M_1$ is a rotation.
+$H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
             \end{theorem}
@@
 
-                $\Rightarrow :$ When $\tilde{F} = M_1^{-1} \circ F \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $F \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
-$\tilde{F}$ and $F \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
-Therefore, we have $$e^{i \theta}\frac{z - p}{1 - \overline{p}z} = az + b \overline{z} + c,$$ which means $p = b = c = 0$, $a = e^{i \theta}$ and so $M_1$ is a rotation.
+                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
+$\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
+Therefore, we have
+                \begin{equation*}
+                    e^{i \theta}\frac{z - p}{1 - \overline{p}z} = az + b \overline{z} + c,
+                \end{equation*}
+                which means $p = b = c = 0$, $a = e^{i \theta}$ and so $M_1$ is a rotation.
 
-                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ F \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}.
+                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ H \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}.
 It's easy to check that
-                \[
-                    M_1^{-1} \circ F \circ M_2 (e^{i \theta}) = M_1^{-1} \circ f \circ M_2(e^{i \theta}) = \tilde{f}(e^{i \theta}) = \tilde{F} (e^{i \theta}),
-                \]
-                which means $M_1^{-1} \circ F \circ M_2$ and $\tilde{F}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ F \circ M_2 = \tilde{F}$.
+                \begin{align*}
+                    M_1^{-1} \circ H \circ M_2 (e^{i \theta})
+                    &= M_1^{-1} \circ f \circ M_2(e^{i \theta})\\
+                    &= \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
+                \end{align*}
+                which means $M_1^{-1} \circ H \circ M_2$ and $\tilde{H}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ H \circ M_2 = \tilde{H}$.
             \end{proof}
 
-            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{F}$
+            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{H}$
             \begin{equation}
-                \tilde{B} = \mu_{\tilde{F}} = \mu_{M_1^{-1} \circ F \circ M_2} = \mu_{F \circ M_2}.
+                \tilde{B} = \mu_{\tilde{H}} = \mu_{M_1^{-1} \circ H \circ M_2} = \mu_{H\circ M_2}.
             \end{equation}
-            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{F \circ M_2} = \mu_{F} = B$, then we get $M_2$ is identity.
+            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, then we get $M_2$ is identity.
 Therefore, we know that the uniqueness of Beltrami signature is equivalent to following restrictions:
             \begin{enumerate}
-                \item $\Phi_1: \D \rightarrow \Omega$ should be determined up to a rotation.
-                \item $\Phi_2: \D^c \rightarrow \Omega^c$ should be uniquely determined.
+                \item $M_1$ should be a rotation.
+                \item $M_2$ should be identity.
             \end{enumerate}
 
-        \subsection{Normalization to $\Phi_1$}\label{norm1}
-            We hope $\Phi_1$ is determined up to a rotation.
-It is not that hard, for example, we can normalize $\Phi_1$ by restricting $\Phi_1(0) = 0$.
+        \subsection{Normalization to $M_1$}\label{norm1}
+            We hope $M_1$ is a rotation.
+It is not that hard, for example, we can achieve it by restricting $\Phi_1(0) = 0$.
 But it need a hypothesis that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold.
-Here we want to show a new approach which can determine $\Phi_1$ up to a rotation without any additional assumption.
+Here we want to show a new approach without any additional assumption.
 
-            In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n$ of $\Omega$.
-Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, we claims that $\Phi_1$ can be normalized by restricting the center of $p_i$ to $0$.
+            In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$.
+Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, where $\Phi_1 : \D \rightarrow \Omega$.
+We claims that $M_1$ can be normalized by restricting the center of $p_i$ to $0$.
 
@@
                 \end{align}
-                then such $\Phi_1$ is unique up to a rotation.
+                then such $\Phi_1$ is unique up to a rotation $M_1$.
             \end{theorem}
@@
 
-            \begin{figure}
+            \begin{figure*}
                 \begin{center}
@@
                 \label{fasolvable}
-            \end{figure}
+            \end{figure*}
 
@@
                 so $\frac{1}{n} f(e^{i\theta}) + e^{i \theta} = 0$. Let 
-                $$g(a) = \begin{cases}
+                \begin{equation*}
+                    g(a) = \begin{cases}
                 \frac{1}{n} f(a) + a, a \in \D,\\
@@
                 \end{cases}
-                $$
+                \end{equation*}
                 such $g$ is defined on $\overline{\D}$ and is continuous. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.
@@
                 Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, then define
-                $$
+                \begin{equation*}
                     h(a) = \begin{cases}
@@
                 \end{cases}
-                $$
+                \end{equation*}
                 $h$ is a continuous map from $\overline{\D}$ to itself, so there exists some $a$ let $h(a) = a$.
@@
 For any $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$,
-                \begin{equation*}
-                    F_a(p_k) = F_a(\cos \theta_k + \sin \theta_k i) = \frac{\cos \theta_k + \sin \theta_k i - a}{1 - a \cos \theta_k - a \sin \theta_k i} = \frac{(a^2 + 1) \cos \theta_k -2a - (a^2 - 1) \sin \theta_k i}{a^2 + 1 - 2a \cos \theta_k},
-                \end{equation*}
+                \begin{align*}
+                    &F_a(p_k) \\
+                    = &F_a(\cos \theta_k + \sin \theta_k i) \\
+                    = &\frac{\cos \theta_k + \sin \theta_k i - a}{1 - a \cos \theta_k - a \sin \theta_k i} \\
+                    = &\frac{(a^2 + 1) \cos \theta_k -2a - (a^2 - 1) \sin \theta_k i}{a^2 + 1 - 2a \cos \theta_k},
+                \end{align*}
                 so
-                \begin{equation*}
-                    \Re(F_a(p_k)) = \frac{(a^2 + 1) \cos \theta_k -2a}{a^2 + 1 - 2a \cos \theta_k} = \cos \theta_k - \frac{2a(1-\cos^2 \theta_k)}{(a-1)^2 + 2a(1-\cos \theta_k)} < \cos \theta_k = \Re(p_k).
-                \end{equation*}
+                \begin{align*}
+                    &\Re(F_a(p_k)) \\
+                    = &\frac{(a^2 + 1) \cos \theta_k -2a}{a^2 + 1 - 2a \cos \theta_k} \\
+                    = &\cos \theta_k - \frac{2a(1-\cos^2 \theta_k)}{(a-1)^2 + 2a(1-\cos \theta_k)} \\
+                    < &\cos \theta_k = \Re(p_k).
+                \end{align*}
 
                 Therefore, if $n \ge 3$, there must be at least one $p_k \neq \pm 1$ and so
-                \begin{equation*}
-                    \Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) < \sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
-                \end{equation*}
-                which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
+                \begin{align*}
+                    &\Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) \\
+                    < &\sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
+                \end{align*}
+                which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $a=0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
             \end{proof}
 
-            In the fact, no matter how these $p_i$ distribute, we can reduce it to the special mentioned above.
+            This theorem confirms the uniqueness for a special situation $\sum_{k=1}^n p_k = 0$ and actually this conclusion is universal no matter how $p_i$ distribute.
 
@@
                 Let $p_k' = F_{a_0}(p_k)$, then
-                \begin{equation*}
-                    \sum_{k=1}^n F_{a_1} \circ F_{a_0}^{-1} \circ F_{a_0}(p_k) = \sum_{k=1}^n (F_{a_1} \circ F_{-a_0})(F_{a_0}(p_k))= \frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}}\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0.
-                \end{equation*}
-                Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$.
-According to the above claim, $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, so $a_0 = a_1$, which contradicts to the assumption.
+                \begin{align*}
+                    &\sum_{k=1}^n F_{a_1} \circ F_{a_0}^{-1} \circ F_{a_0}(p_k)\\
+                    = &\sum_{k=1}^n (F_{a_1} \circ F_{-a_0})(F_{a_0}(p_k))\\
+                    = &\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}}\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0.
+                \end{align*}
+
+                Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so \\
+                $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$. According to theorem \ref{uniqueness when 0},\\
+                $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, then $a_0 = a_1$, which contradicts to the assumption.
             \end{proof}
@@
 
-            Above theorems show that there is alway an unique solution $a \in \D$ of equation (\ref{eq}), so we can come back to theorem (\ref{unique up to a rotation}),
+            Above theorems show that there is alway an unique solution $a \in \D$ for equation (\ref{eq}), so we can come back to theorem \ref{unique up to a rotation}.
 
             \begin{proof}
-                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$, then $\tilde{\Phi}_1 = \Phi_1 \circ M$, where $M$ is a Mobious transformation.
-Let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M^{-1} (p_k) = 0$.
-$M^{-1}$ is also a Mobious transformation so let $M^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
+                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobious transformation.
+If $\Phi_1$, $\tilde{\Phi_1} $ satisfy equation (\ref{norm phi1}), let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M_1^{-1} (p_k) = 0$.
+$M_1^{-1}$ is also a Mobious transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
                 \begin{equation*}
@@
 
-                From theorem \ref{uniqueness when 0} we can know $a = 0$, then $M^{-1}(z) = e^{i \theta} z$ and so $\Phi_1$ is unique up to a rotation.
+                From theorem \ref{uniqueness when 0} we can know $a = 0$, then $M_1^{-1}(z) = e^{i \theta} z$ and $\Phi_1$ is unique up to a rotation $M_1$.
             \end{proof}
 
-        \subsection{Normalization to $\Phi_2$}\label{norm2}
-            As for $\Phi_2$, we hope it is uniquely determined.
-Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this and derivative to guarantee uniqueness of $\Phi_2$.
+        \subsection{Normalization to $M_2$}\label{norm2}
+            As for $M_2$, we hope it is identity, which is equivalent with the uniqueness of $\Phi_2: \D^c \rightarrow \Omega^c$.
+Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this and derivative to guarantee the uniqueness.
 
             \begin{theorem}
-                If $\Phi_2: \D^c \rightarrow \Omega^c$ satisifies that
+                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobious transformation.
+If $\tilde{\Phi_2}, \Phi_2$ satisifies that
                 \begin{align}
-                    \Phi_2(\infty) = &\infty\label{norm phi2 1}\\
-                    1 = \argmax{z \in \partial \D} &\abs{\Phi_2'(z)},\label{norm phi2 2}
+                    &\tilde{\Phi_2}(\infty) = \Phi_2(\infty) = \infty\label{norm phi2 1}\\
+                    &\argmax{z \in \partial \D} \abs{\Phi_2'(z)} = \argmax{z \in \partial \D} \abs{\tilde{\Phi_2'}(z)} = 1,\label{norm phi2 2}
                 \end{align}
-                then such $\Phi_2$ is uniquely determined.
+                then such $M_2$ is identity.
             \end{theorem}
@@
             \begin{proof}
-                $\Phi_2$ and $\tilde{\Phi}_2$ are two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi}_2 = \Phi_2 \circ M$, where $M(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$ is a Mobious transformation.
-$\Phi_2$ and $\tilde{\Phi}_2$ both satisify (\ref{norm phi2 1}), then\[
-                    \tilde{\Phi}_2(\infty) = \Phi_2(M(\infty)) = \infty \text{~and~} \Phi_2(\infty) = \infty.
-                \]
-                Therefore, $M(\infty) = e^{i \theta} \frac{\infty - a}{1- \overline{a} \infty} = \infty$, which means that $a = 0$ and $M(z) = e^{i \theta} z$.
+                Suppose Mobious transformation $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$. Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisify (\ref{norm phi2 1}), then
+                \begin{align*}
+                    &\tilde{\Phi}_2(\infty) = \Phi_2(M_2(\infty)) = \infty, \\
+                    &\Phi_2(\infty) = \infty.
+                \end{align*}
+                Therefore, $M_2(\infty) = e^{i \theta} \frac{\infty - a}{1- \overline{a} \infty} = \infty$, which means that $a = 0$ and $M_2(z) = e^{i \theta} z$.
 
@@
                 \begin{equation}
-                    \tilde{\Phi}_2'(z) = \Phi_2' \circ M(z) \cdot M'(z) = e^{i\theta} \Phi_2' (e^{i \theta}z),
+                    \tilde{\Phi}_2'(z) = \Phi_2' \circ M_2(z) \cdot M_2'(z) = e^{i\theta} \Phi_2' (e^{i \theta}z),
                 \end{equation}
                 then we know that $\abs{\tilde{\Phi}_2'(z)} = \abs{\Phi_2'(e^{i \theta}z)}$.
-Suppose $a = \argmin{z \in \partial \D} |\Phi_2'(z)|$ and $a e^{-i \theta} = \argmin{z \in \partial \D} |\tilde{\Phi}_2'(z)|$.
-If condition (\ref{norm phi2 2}) holds for both $\Phi_2$ and $\tilde{\Phi}_2$, then $a = a e^{-i \theta} = 1$, so $a = 1$, $\theta = 0$ and $M$ is an identity, which shows that $\Phi_2 = \tilde{\Phi}_2$.
+Suppose $a = \argmax{z \in \partial \D} |\Phi_2'(z)|$, then we will have that $ae^{-i \theta} = \argmax{z \in \partial \D} |\tilde{\Phi}_2'(z)|$.
+                If condition (\ref{norm phi2 2}) holds for both $\tilde{\Phi}_2$ and $\Phi_2$, it means $a = a e^{-i \theta} = 1$, so $a = 1$, $\theta = 0$ and $M_2$ is identity.
             \end{proof}
@@
 Since $\tilde{\Phi}_1$ satisifies condition (\ref{norm phi1}), we have
-                \[
+                \begin{equation*}
                     \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0.
-                \]
+                \end{equation*}
+
                 Therefore
-                \[
+                \begin{equation*}
                     \sum_{i=1}^n \hat{\Phi}_1^{-1}(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1} \circ T(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0,
-                \]
+                \end{equation*}
                 which means $\hat{\Phi}_1$ also satisifies condition (\ref{norm phi1}). Hence $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1= \Phi_1 \circ R$, which equals to
@@
                 Similarly, let $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2: \D^c \rightarrow \Omega^c$, $\hat{\Phi}_2$ is conformal. Since $\tilde{\Phi}_2(\infty) = \infty$, we have
-                $$\hat{\Phi}_2(\infty) = T \circ \tilde{\Phi}_2(\infty) = \infty,$$
+                \begin{equation*}
+                    \hat{\Phi}_2(\infty) = T \circ \tilde{\Phi}_2(\infty) = \infty,
+                \end{equation*}
                 which means $\hat{\Phi}_2$ satisifies condition (\ref{norm phi2 1}).
@@
                 \end{equation}
-                Then the harmonic extension $\tilde{F} = R^{-1} \circ F$ and 
+                Then the harmonic extension $\tilde{H} = R^{-1} \circ H$ and 
                 \begin{equation}
-                    B_{T(\Omega)} = \mu_{\tilde{F}} = \mu_{R^{-1} \circ F} = \mu_F = B_\Omega.
+                    B_{T(\Omega)} = \mu_{\tilde{H}} = \mu_{R^{-1} \circ H} = \mu_H = B_\Omega.
                 \end{equation}
@@
 
-    % \section{Reconstruction from Beltrami signature}
-    %     Given the Beltrami signature $B: \D \rightarrow \C$, we know that $B$ is Beltrami coefficient of some harmonic function $F: \overline{\D} \rightarrow \C$ and $F = f = \Phi_1^{-1} \circ \Phi_2$ in $\partial \D$.
-Define
-    %     \begin{equation}
-    %         G(z) = \begin{cases}
-    %             \Phi_1 \circ F, & z \in \D\\
-    %             \Phi_2, & z \notin \D
-    %         \end{cases}.
-    %     \end{equation}
-    %     It is easy to check such a $G$ is well-defined. For all $z \in \partial \D$, 
-    %     $$\Phi_1 \circ F(z) = \Phi_1 \circ \Phi_1^{-1} \circ \Phi_2(z) = \Phi_2(z).$$
-    %     Then we compute the Beltrami coefficient of $G$,
-    %     \begin{equation}\label{PDE beltrami signature}
-    %         \mu_G = \frac{G_{\overline{z}}}{G_z} \begin{cases}
-    %             \mu_{\Phi_1 \circ F} = \mu_F = B, &z \in \D\\
-    %             \mu_{\Phi_2} = 0, & z \notin \D
-    %         \end{cases}.
-    %     \end{equation}
-    %     The map $G$ is the solution of PDE (\ref{PDE beltrami signature}), which can be solved by LBS method. Therefore, $\Phi_2 = G|_{\D^c}$ and $\Omega = G(\D^c)^c$.
     \section{Implementation detail}\label{implementation}
@@
 
+        \subsection{Harmonic extension}\label{detail harmonic}
+            After obtaining the output of zipper algorithm, $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$, the conformal welding can be represented as a series points
+            \begin{equation*}
+                (\varphi_i, \omega_i) = \left(\arg(\hat{\Phi}_2^{-1}(z_i)), \arg(\hat{\Phi}_1^{-1}(z_i))\right),
+            \end{equation*}
+            where $\varphi_i, \omega_i \in [0, 2\pi)$. So in fact we should use discrete form Poisson integral to extend $f$ to a harmonic mapping $H$ on the unit disk
+            \begin{equation}\label{discrete poisson integral}
+                H(re^{i\theta}) = \frac{1}{2\pi} \sum_{j=1}^k \frac{(1-r^2) e^{i \omega_j} \gamma_j}{1 - 2 r cos (\varphi_j - \theta) + r^2} ,
+            \end{equation}
+            where $\gamma_j = (\varphi_{j} - \varphi_{j-1}) \bmod{ 2\pi}$ and $\varphi_0 = \varphi_k$ and this $\bmod$ can solve some critical value problem, for example, $\varphi_j = 0$ but $\varphi_{j-1} = 6$.
+For the convenience of computation, we only calculate the value of $H$ on a grid
+            \begin{align*}
+                G = \{z=x+iy \mid &\abs{z} \le 1, x=\frac{j}{100}, y=\frac{k}{100},\\
+                &j,k=-100,-99,\cdots,99,100 \}.
+            \end{align*}
+
         \subsection{Normalization}
-            To normalization $\Phi_1$, we need to solve equation (\ref{eq}).
+            Because of the arbitrariness of the comformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
+            \begin{equation*}
+                \tilde{H} = M_1 \circ H \circ M_2.
+            \end{equation*}
+            Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then Beltrami signature $B$ can be unique.
+This section will tells how to satisfy equation (\ref{norm phi1}), (\ref{norm phi2 1}) and (\ref{norm phi2 2}) from the output of zipper algorithm.
+
+            To normalization $M_1$, we need to solve equation (\ref{eq}).
 Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concerntrate around a point.
@@
                 \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig7.png}
+                    \includegraphics[width=7.6cm]{src/fig7_down.png}
                 \end{center}
@@
                 \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig8.png}
+                    \includegraphics[width=7.6cm]{src/fig8_down.png}
                 \end{center}
@@
 
-            Instead of proposed a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobious transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
-For the $r$-th iteration, let $$p_{c,r} = \frac{\sum_{i=1}^k p_{i,r}}{k} \in \D$$ as the arithmetic center of $p_{i,r} \in \partial \D$, then the Mobious transformation $M_{p_{c,r}}$ gives new boundary points on unit disk as $$p_{i,r+1} = M_{p_{c,r}}(p_{i,r}) = \frac{p_{i,r} - p_{c,r}}{1 - \overline{p_{c,r}}p_{i,r}}.$$
+            Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobious transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
+For the $r$-th iteration, let
+            \begin{equation*}
+                p_{c,r} = \frac{\sum_{i=1}^k p_{i,r}}{k} \in \D
+            \end{equation*}
+            as the arithmetic center of $p_{i,r} \in \partial \D$.
+Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobious transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
+            \begin{equation*}
+                p_{i,r+1} = F_{p_{c,r}}(p_{i,r}) = \frac{p_{i,r} - p_{c,r}}{1 - \overline{p_{c,r}}p_{i,r}}.
+            \end{equation*}
             Note that we set $p_{i,0} = p_{i}$ at the beginning.
@@
             \begin{equation}
-                \tilde{\Phi}_1 = \Phi_1 \circ M_{p_{c,0}}^{-1} \circ M_{p_{c,1}}^{-1} \circ \cdots \circ M_{p_{c,r}}^{-1}.
+                \tilde{\Phi}_1 = \Phi_1 \circ F_{p_{c,0}}^{-1} \circ F_{p_{c,1}}^{-1} \circ \cdots \circ F_{p_{c,r}}^{-1}.
             \end{equation}
-            Now equation (\ref{eq}) can be solved without much effort by Newtown's method. Suppose $a \in \D$ is the optimal solution and the final mapping is
+            Now equation (\ref{eq}) can be solved without much effort by Newtown's method. Suppose $a \in \D$ is the optimal solution and let 
+            \begin{equation*}
+                F_{\Phi_1} = F_a \circ F_{p_{c,r}} \circ F_{p_{c,r-1}} \circ \cdots \circ F_{p_{c, 0}}
+            \end{equation*}
+            and the final conformal mapping satisfying (\ref{norm phi1}) is
             \begin{equation}
-                \hat{\Phi}_1 = \tilde{\Phi}_1 \circ M_{a}^{-1}
+                \hat{\Phi}_1 = \tilde{\Phi}_1 \circ F_{a}^{-1} = \Phi_1 \circ F_{\Phi_1}^{-1}
             \end{equation}
@@
             \begin{algorithm}[H]
-            \caption{Normalize $\Phi_1$}
+            \caption{Normalize $M_1$}
             \label{alg norm phi1}
@@
                 \STATE \textbf{Inputs:} $\Phi_1$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $\epsilon=0.2$.
-                \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$. %and $M_{p_{c,0}}(z) = \frac{z-p_{c,0}}{1- \overline{p_{c, 0}}z}$
+                \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$, $F_{\Phi_1} = id$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$.
+%and $M_{p_{c,0}}(z) = \frac{z-p_{c,0}}{1- \overline{p_{c, 0}}z}$
                 \WHILE{$\abs{p_c,r} > \epsilon$}
-                    \STATE Let $M_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $\Phi_1 = \Phi_1 \circ M_{p_{c,r}}^{-1}$.
-                    \STATE Compute $p_{i, r+1} = M_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
+                    \STATE Let $F_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $\Phi_1 = \Phi_1 \circ F_{p_{c,r}}^{-1}$.
+                    \STATE Compute $F_{\Phi_1} = F_{p_{c,r}} \circ F_{\Phi_1}$, $p_{i, r+1} = F_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
                     \STATE Let $r = r+1$.
@@
                 \STATE Solve equation (\ref{eq}) by Newtown's method and get solution $a \in \D$.
-                \STATE Let $M_a(z) = \frac{z-a}{1- \overline{a}z}$ and $\hat{\Phi}_1 = \Phi_1 \circ M^{-1}_{a}$.
-                \STATE Compute $p_i = M_a(p_{i,r})$.
-                \RETURN Conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfied (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
+                \STATE Let $F_a(z) = \frac{z-a}{1- \overline{a}z}$, $F_{\Phi_1} = F_a \circ F_{\Phi_1}$ and $\hat{\Phi}_1 = \Phi_1 \circ F^{-1}_{a}$.
+                \STATE Compute $p_i = F_a(p_{i,r})$.
+                \RETURN Mobious transformation $F_{\Phi_1}$, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
             \end{algorithmic}
@@
                 \caption{The iteration of distribution adjustment. The boundary points are blue and their arithmetic center is red in each picture. (a)-(d) The 1st, 3rd, 7th, 12th iteration.}
-            \end{figure}
+            \end{figure*}
 
-            As for the normalization of $\Phi_2$, it's much easier since we only need to map $\infty$ to $\infty$ by replace $\Phi_2$ with $\tilde{\Phi}_2(z)=\Phi_2 \circ M^{-1}_{b}(\frac{1}{z})$, where $b = \Phi_2^{-1}(\infty)$.
+            As for the normalization of $M_2$, it's much easier.
+For requirement (\ref{norm phi2 1}), we only need to map $\infty$ to $\infty$ by replace $\Phi_2$ with $\tilde{\Phi}_2(z)=\Phi_2 \circ F^{-1}_{b}(\frac{1}{z})$, where $b = \Phi_2^{-1}(\infty)$.
 Another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
-Since we know each linear fractional transformation composing $\Phi_2$, the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
-Here we select $10^5$ points from $[0, 2\pi)$ as $\theta_j$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}).
-Therefore, the maximal solution $\theta_{\max} = \argmax{j \in [1,10^5]} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ can be used to normalize the rotation and the final mapping is
+According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
+Here we select $M = 10^5$ points uniformly from $[0, 2\pi)$ as $\theta_j = \frac{2 j \pi}{M}$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}).
+Therefore, the maximal solution $\theta_{\max} = \argmax{j \in [0,10^5)} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ can be used to normalize the rotation and the final mapping is
             \begin{equation}
-                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z).
+                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
             \end{equation}
-            This grid can generate a triangluar mesh $M$ and we will calculate the Beltrami coefficient on $M$.
+            where $M_{\Phi_2}(z) = e^{i \theta_{max}} \frac{z-b}{1 - \overline{b}z}$.
 
             \begin{algorithm}[H]
-            \caption{Normalize $\Phi_2$}
+            \caption{Normalize $M_2$}
             \label{alg norm phi2}
@@
                 \STATE Let $\hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z)$ and compute $p_i = \frac{e^{-i \theta_{max}}}{M_b(p_i)}$.
-                \RETURN Conformal mapping $\Phi_1: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
+                \RETURN Conformal mapping $\hat{\Phi}_2: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
             \end{algorithmic}
@@
                 \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig10.png}
+                    \includegraphics[width=.76cm]{src/fig10.png}
                 \end{center}
@@
 
-        \subsection{Harmonic extension}\label{detail harmonic}
-            After obtaining the normalized $\hat{\Phi}_1$ and $\hat{\Phi}_2$, the conformal welding can be represented as a series points $(\varphi_i, \omega_i) = \left(\arg(\hat{\Phi}_2^{-1}(z_i)), \arg(\hat{\Phi}_1^{-1}(z_i))\right)$, where $\varphi_i, \omega_i \in [0, 2\pi)$.
-So in fact we should use discrete form Poisson integral to extend $f$ to a harmonic mapping $F$ on the unit disk.
-            \begin{equation}\label{discrete poisson integral}
-                F(re^{i\theta}) = \frac{1}{2\pi} \sum_{j=1}^k \frac{(1-r^2) e^{i \omega_j}}{1 - 2 r cos (\varphi_j - \theta) + r^2} \left((\varphi_{j} - \varphi_{j-1}) \bmod{ 2\pi}\right),
-            \end{equation}
-            where $\varphi_0 = \varphi_k$ and this $\bmod$ can solve some critical value problem, for example, $\varphi_j = 0$ but $\varphi_{j-1} = 6$.
-For the convenience of computation, we only calculate the value of $F$ on a grid
-            \begin{equation}
-                G = \{z=x+iy \mid \abs{z} \le 1, x=\frac{j}{100}, y=\frac{k}{100}, j,k=-100,-99,\cdots,99,100 \}.
-            \end{equation}
+            After obatining Mobious transformations $F_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
+            \begin{align*}
+                \hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}
+            \end{align*}
+            and it is unique up to a rotation.
 
@@
                 \STATE Input $z_1, z_2, \cdots, z_N$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_1}: \D \rightarrow \Omega$ and $p_{i,1} \in \partial\D$.
-                \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and input it and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get normalized $\hat{\Phi}_1$ and $p_{i,1}$.
+                \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$. %and 
                 \STATE Input $z_N, \cdots, z_2, z_1$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_2}: \D \rightarrow \Omega^c$ and $p_{i,2} \in \partial\D$.
-                \STATE Let $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$ and input it and $p_{i,2}$ to Algorithm \ref{alg norm phi2}, then get normalized $\hat{\Phi}_2$ and $p_{i,2}$.
-                \STATE Let $f = \hat{\Phi}_1^{-1} \circ \hat{\Phi}_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
-                \STATE Extend $f$ to $F$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
-                \STATE Calculate Beltrami coefficient $B$ of $F$ on $M$.
+                \STATE Let $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
+                \STATE Let $f = \Phi_1^{-1} \circ \Phi_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
+                \STATE Extend $f$ to $H$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
+                \STATE Input $\Phi_1$ and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get $F_{\Phi_1}$.
+                \STATE Input $\Phi_2$ and $p_{i,2}$ to Algorithm \ref{alg norm phi2}, then get $M_{\Phi_2}$.
+                \STATE Calculate normalized harmonic extension $\hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}$.
+                \STATE Calculate Beltrami coefficient $B$ of $\hat{H}$.
                 \RETURN Beltrami signature $B$.
@@
                 \label{inv}
-            \end{figure}
+            \end{figure*}
 
@@
                 \label{robust}
-            \end{figure}
+            \end{figure*}
 
@@
                 \label{classification images}
-            \end{figure}
+            \end{figure*}
 
@@
                 \begin{center}
-                    \includegraphics[width=\textwidth]{src/distance.png}
+                    \includegraphics[width=7.6cm]{src/distance_down.png}
                 \end{center}
@@
                 \begin{center}
-                    \includegraphics[width=\textwidth]{src/mds.png}
+                    \includegraphics[width=7.6cm]{src/mds_down.png}
                 \end{center}
@@
                 \label{mds2}
-            \end{figure}
+            \end{figure*}
 
@@
 A third direction is this representation can be used in more applications like segementation, registration and so on.
+%\begin{acknowledgements}
+%If you'd like to thank anyone, place your comments here
+%and remove the percent signs.
+%\end{acknowledgements}
 
-    \bibliographystyle{IEEEtran}
+% Authors must disclose all relationships or interests that 
+% could have direct or potential influence or impart bias on 
+% the work: 
+%
+% \section*{Conflict of interest}
+%
+% The authors declare that they have no conflict of interest.
+
+% BibTeX users please use one of
+% \bibliographystyle{spbasic}      % basic style, author-year citations
+\bibliographystyle{spmpsci}      % mathematics and physical sciences
+%\bibliographystyle{spphys}       % APS-like style for physics
+%\bibliography{}   % name your BibTeX data base
 \bibliography{cite}
+% Non-BibTeX users please use
+% \begin{thebibliography}{}
+% %
+% % and use \bibitem to create references. Consult the Instructions
+% % for authors for reference list style.
+% %
+% \bibitem{RefJ}
+% % Format for Journal Reference
+% Author, Article title, Journal, Volume, page numbers (year)
+% % Format for books
+% \bibitem{RefB}
+% Author, Book title, page numbers. Publisher, place (year)
+% % etc
+% \end{thebibliography}
+
 \end{document}
+% end of file template.tex

### 2021-04-08 paper.tex
share

--- 2021-04-07 template.tex
@@
             \begin{equation*}
-                F_{\Phi_1} = F_a \circ F_{p_{c,r}} \circ F_{p_{c,r-1}} \circ \cdots \circ F_{p_{c, 0}}
+                M_{\Phi_1} = F_a \circ F_{p_{c,r}} \circ F_{p_{c,r-1}} \circ \cdots \circ F_{p_{c, 0}}
             \end{equation*}
@@
             \begin{equation}
-                \hat{\Phi}_1 = \tilde{\Phi}_1 \circ F_{a}^{-1} = \Phi_1 \circ F_{\Phi_1}^{-1}
+                \hat{\Phi}_1 = \tilde{\Phi}_1 \circ F_{a}^{-1} = \Phi_1 \circ M_{\Phi_1}^{-1}
             \end{equation}
@@
                 \STATE \textbf{Inputs:} $\Phi_1$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $\epsilon=0.2$.
-                \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$, $F_{\Phi_1} = id$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$.
+                \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$, $M_{\Phi_1} = id$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$.
 %and $M_{p_{c,0}}(z) = \frac{z-p_{c,0}}{1- \overline{p_{c, 0}}z}$
                 \WHILE{$\abs{p_c,r} > \epsilon$}
-                    \STATE Let $F_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $\Phi_1 = \Phi_1 \circ F_{p_{c,r}}^{-1}$.
-                    \STATE Compute $F_{\Phi_1} = F_{p_{c,r}} \circ F_{\Phi_1}$, $p_{i, r+1} = F_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
+                    \STATE Let $F_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $M_{\Phi_1} = F_{p_{c,r}} \circ M_{\Phi_1}$.%and $\Phi_1 = \Phi_1 \circ F_{p_{c,r}}^{-1}$.
+                    \STATE Compute $p_{i, r+1} = F_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
                     \STATE Let $r = r+1$.
@@
                 \STATE Solve equation (\ref{eq}) by Newtown's method and get solution $a \in \D$.
-                \STATE Let $F_a(z) = \frac{z-a}{1- \overline{a}z}$, $F_{\Phi_1} = F_a \circ F_{\Phi_1}$ and $\hat{\Phi}_1 = \Phi_1 \circ F^{-1}_{a}$.
-                \STATE Compute $p_i = F_a(p_{i,r})$.
-                \RETURN Mobious transformation $F_{\Phi_1}$, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
+                \STATE Let $F_a(z) = \frac{z-a}{1- \overline{a}z}$ and $M_{\Phi_1} = F_a \circ M_{\Phi_1}$.% and $\hat{\Phi}_1 = \Phi_1 \circ F^{-1}_{a}$.
+                %\STATE Compute $p_i = F_a(p_{i,r})$.
+                \RETURN Mobious transformation $M_{\Phi_1}$.%, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
             \end{algorithmic}
@@
 
-            As for the normalization of $M_2$, it's much easier.
-For requirement (\ref{norm phi2 1}), we only need to map $\infty$ to $\infty$ by replace $\Phi_2$ with $\tilde{\Phi}_2(z)=\Phi_2 \circ F^{-1}_{b}(\frac{1}{z})$, where $b = \Phi_2^{-1}(\infty)$.
-Another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
+            As for the normalization of $M_2$, it's much easier. For requirement (\ref{norm phi2 1}), let $b = \Phi_2^{-1}(\infty)$ and $c = -\frac{1}{\bar{b}}$, from
+            \begin{equation*}
+                F_{c}(\infty) = \lim_{z \rightarrow \infty} \frac{z -c}{1 - \bar{c}z} = -\frac{1}{\overline{c}} = b
+            \end{equation*} we have 
+            \begin{equation*}
+                \tilde{\Phi}_2(\infty) = \Phi_2 \circ F_{c}(\infty) = \Phi_2(b) = \infty.
+            \end{equation*}
+            So we only need replace $\Phi_2$ with $\tilde{\Phi}_2 =\Phi_2 \circ F_{c}$ to map $\infty$ to $\infty$.
+
             According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
-Here we select $M = 10^5$ points uniformly from $[0, 2\pi)$ as $\theta_j = \frac{2 j \pi}{M}$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}).
-Therefore, the maximal solution $\theta_{\max} = \argmax{j \in [0,10^5)} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ can be used to normalize the rotation and the final mapping is
+And another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
+Here we select $M = 10^5$ points uniformly from $[0, 2\pi)$ as $\theta_j = \frac{2\pi}{M}(j-1)$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}).
+
+            Therefore, the maximal solution
             \begin{equation}
-                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
+                \theta_{\max} = \argmax{j \in [1,10^5]} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}
             \end{equation}
-            where $M_{\Phi_2}(z) = e^{i \theta_{max}} \frac{z-b}{1 - \overline{b}z}$.
+            can be used to normalize the rotation and the final mapping is 
+            \begin{equation}
+                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{\max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
+            \end{equation}
+            where $M_{\Phi_2} = e^{i \theta_{\max}} F_{ce^{-i \theta_{\max}}}$.
 
@@
                 \STATE \textbf{Inputs:} $\Phi_2$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $M=10^5$.
-                \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$.
-                \STATE Let $M_b(z) = \frac{z-b}{1-\overline{b}z}$ and $\tilde{\Phi}_2(z)=\Phi_2 \circ M^{-1}_{b}(\frac{1}{z})$.
-                \STATE Calculate $\abs{\tilde{\Phi}_2'}$ by chain derative rule.
+                \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$ and $c = -\frac{1}{\bar{b}}$.
+                \STATE Let $F_c(z) = \frac{z-c}{1-\overline{c}z}$ and $\tilde{\Phi}_2(z)=\Phi_2 \circ F_{c}(z)$.
                 \STATE Let $\theta_j = \frac{2\pi}{M}(j-1)$ for $j=1,2, \cdots, M$.
-                \STATE Compute $\abs{\tilde{\Phi}_2'}(e^{i \theta_j})$.
-                \STATE Find maximal value and corresponding $\theta_{max}$.
-                \STATE Let $\hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z)$ and compute $p_i = \frac{e^{-i \theta_{max}}}{M_b(p_i)}$.
-                \RETURN Conformal mapping $\hat{\Phi}_2: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
+                \STATE Find maximal value of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ and corresponding $\theta_{\max}$.
+                \STATE Let $M_{\Phi_2} = e^{i \theta_{\max}} F_{ce^{-i \theta_{\max}}}$.
+                \RETURN Mobious transformation $M_{\Phi_2}$
+                % \RETURN Conformal mapping $\hat{\Phi}_2: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
             \end{algorithmic}
@@
                 \begin{center}
-                    \includegraphics[width=.76cm]{src/fig10.png}
+                    \includegraphics[width=7.6cm]{src/fig10.png}
                 \end{center}
                 \caption{The change of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ for different $\theta_j \in [0, 2\pi)$.
-It shows this function has a significant maximum and $\theta_{max}$ is about $1.25\pi$.}
+It shows this function has a significant maximum and $\theta_{\max}$ is about $1.25\pi$.}
                 \label{derative}
@@
 
-            After obatining Mobious transformations $F_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
+            After obatining Mobious transformations $M_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
             \begin{align*}
-                \hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}
+                \hat{H} = M_{\Phi_1} \circ H \circ M_{\Phi_2}
             \end{align*}
@@
             \begin{algorithmic}
-                \STATE \textbf{Inputs:} Bounded simple connected shape $\Omega \subset \C$, $N=200$.
-                \STATE Pick $N$ clockwise points $z_1, z_2, \cdots, z_N$ from $\partial \Omega$ uniformly.
+                \STATE \textbf{Inputs:} Simple connected shape $\Omega \subset \C$, $N=200$.
+                \STATE Pick clockwise points $z_1, \cdots, z_N \in \partial \Omega$ uniformly.
                 \STATE Input $z_1, z_2, \cdots, z_N$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_1}: \D \rightarrow \Omega$ and $p_{i,1} \in \partial\D$.
-                \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$. %and 
                 \STATE Input $z_N, \cdots, z_2, z_1$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_2}: \D \rightarrow \Omega^c$ and $p_{i,2} \in \partial\D$.
-                \STATE Let $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
+                \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
                 \STATE Let $f = \Phi_1^{-1} \circ \Phi_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
                 \STATE Extend $f$ to $H$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
-                \STATE Input $\Phi_1$ and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get $F_{\Phi_1}$.
+                \STATE Input $\Phi_1$ and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get $M_{\Phi_1}$.
                 \STATE Input $\Phi_2$ and $p_{i,2}$ to Algorithm \ref{alg norm phi2}, then get $M_{\Phi_2}$.
-                \STATE Calculate normalized harmonic extension $\hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}$.
+                \STATE Calculate normalized harmonic extension $\hat{H} = M_{\Phi_1} \circ H \circ M_{\Phi_2}$.
                 \STATE Calculate Beltrami coefficient $B$ of $\hat{H}$.

### 2021-05-24 paper.tex
v3

@@
 
-\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
+\title{Harmonic Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
 % \subtitle{Do you have a subtitle?\\ If so, write it here}
@@
 \begin{abstract}
-  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simple connected domain in this paper, named Beltrami signature.
-The proposed signature is based on conformal welding.
-We extended the welding mapping to a harmonic function.
+  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simply-connected domains in this paper, named the Harmonic Beltrami signature.
+The proposed signature is based on the extension of the conformal welding map of a unit circle $S^1$ to a harmonic function of a unit disk $\D$.
 With suitable normalization, the uniqueness of this harmonic function is guaranteed up to a rotation.
-And finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension.
-The benifits of the proposed signature is it keeps invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformation and distortion.
+And finally quasi-conformal theory helps get rid of the only uncertainty by computing the Beltrami coefficient of harmonic extension.
+The benifit of the proposed signature is that it keeps to be invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformations and distortions.
 Experiments demonstrate the above properties and also show the excellent classification performance.
 \keywords{
-  Shape representation \and conformal welding \and simple connected \and invariance}
+  Shape representation \and conformal welding \and simply-connected \and invariance}
 % \PACS{PACS code1 \and PACS code2 \and more}
@@
 \label{intro}
-    The outline of the shape contains very important information and it can be used in many applications, such as segementation, recognition, registration and so on.
-However, even for the simplest situation, 2D simple connected shapes, it is a big challenge to describe clearly what the shape contour looks like.
-Because of the complexity of the image, there is an urgent demand to find a common, simple and robust shape representation for further mining and utilizing of shapes' geometric information.
-Therefore, many different presentations and measures have been widly studied and proposed recently \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.
-
-    Considering 2D simple connected shapes, conformal welding is a kind of well-known shape signature.
-Given 2D simple connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$.
+    The outline of a shape contains important information, which can be used in many applications, such as medical image analysis, image segmentation, recognition, registration and so on.
+Nevertheless, it is a big challenge to define a robust descriptor for the space of shapes, even for the simplest situation of 2D simply-connected objects.
+In order to manipulate shapes and utilize their geometric information, there is an urgent demand to find a simple and robust representation to mathematically describe shape contours.
+The shape representation should also inherits a natural metric to measure geometric differences between two shape representations.
+With the geometric dissimilarity metric, two shapes can be quantitatively compared and prior shape information can be incorporated into various imaging models by adding a penalty term to further improve the accuracy.
+Due to its significance, this problem has been widely studied and different models to build the metric shape space have been proposed.
+    % \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.
+
+    Considering 2D simply-connected shapes, conformal welding is a kind of well-known shape signature.
+Given 2D simply-connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$.
 This gives a simple but wonderful representation of $\Omega$ as Fig.
@@
 For example, Sharon \etal \cite{sharon20062d} need to select a base point $P$ inside the given domain $\Omega$ artificially, then let $\Phi_1$ maps $0$ to this point $P$.
-The work of Mcenteggart \etal \cite{mcenteggart2018uniqueness} is based on Schramm-Loewner evolution(SLE) on random surfaces called Liouville quantum gravity, they proved the equivalence between uniqueness of conformal welding and conformal removable and conculded that if the boundary curve $\eta$ is an $\text{SLE}_k$ for $k \in (0, 4)$ and satisifies some other requirements, the corresponding conformal welding is unique.
+The work of Mcenteggart \etal \cite{mcenteggart2018uniqueness} is based on Schramm-Loewner evolution(SLE) on random surfaces called Liouville quantum gravity, they proved the equivalence between uniqueness of conformal welding and conformal removable and conculded that if the boundary curve $\eta$ is an $\text{SLE}_k$ for $k \in (0, 4)$ and satisfies some other requirements, the corresponding conformal welding is unique.
 Some may not that care the uniqueness itself, they used equivalent class to guarantee uniqueness in a broader sense or evne just ignored it \cite{katznelson1990conformal,marshall2012conformal,lui2013shape,astala2010random}.
@@
 
-    The contribution of this paper is that we propose a brand new presentation for 2D simple connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Beltrami signature.
+    The contribution of this paper is that we propose a novel presentation for 2D simply-connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Harmonic Beltrami signature.
 Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points.
 Such conformal welding can be extended to the whole unit disk and get a harmonic function $H: \D \rightarrow \D$.
-Under suitable normalization, harmonic extension $H$ can be determined up to a rotation and the Beltrami coefficient of $H$ is then unique and becomes our Beltrami signature.
-
-    The proposed shape representation, Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
-The Beltrami signature is based on computational quasiconformal geometry.
-Computational quasiconformal geometry has been widely used in image processing and image analysis.
+Under suitable normalization, harmonic extension $H$ can be determined up to a rotation and the Beltrami coefficient of $H$ is then unique and becomes our Harmonic Beltrami signature.
+
+    The proposed shape representation, Harmonic Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
+The Harmonic Beltrami signature is based on computational quasi-conformal geometry.
+Computational quasi-conformal geometry has been widely used in image processing and image analysis.
 Applications can be found in image segmentation
@@
      and image analysis 
-    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shapec,lui2010shape3}
+    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shape,lui2010shape3}
     .
-What's more worth mentioning is that Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape.
-It means the proposed representation has high practical value and can be applied in computer vision work like classification, segementation and so on.
-
-    The paper is organized as follows: Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem and how Beltrami signature is obtained from given domain; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
+What's more worth mentioning is that Harmonic Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape.
+It means the proposed representation has high practical value and can be applied in computer vision work like classification, segmentation and so on.
+
+    The paper is organized as follows: Section \ref{related work} reviews some related topics about shape representation; Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem and how Harmonic Beltrami signature is obtained from given domain; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
 The paper is concluded in Section \ref{conclusion} and we point out future directions.
@@
         \includegraphics[width=7.6cm]{src/fig1_down.png}
-        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simple connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
+        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simply-connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
         \end{center}
@@
     \end{figure}
+
+\section{Contributions}
+The contributions of this paper can be summarized as follows.
+\begin{enumerate}
+    \item Firstly, we propose a new shape signature, called the Harmonic Beltrami signature, to effectively represent 2D simply-connected shapes.
+Every shape has a unique Harmonic Beltrami signature.
+Conversely, given a Harmonic Beltrami signature, its corresponding shape can be determined up to a translation, rotation and scaling.
+    \item Secondly, the proposed Harmonic Beltrami signature solves the issue of conformal ambiguities facing the conformal welding signature.
+    \item Thirdly, we propose a practical procedure to normalize the Harmonic Beltrami signature to handle the non-uniqueness issue, with rigorous theoretical justifications.
+    \item Fourthly, we propose a reconstruction algorithm to construct the corresponding shape from the Harmonic Beltrami signature up to a rotation, translation and scaling.
+This allows us to go back and fro between shapes and Beltrami signatures in the imaging model.
+    \item Finally, the proposed Harmonic Beltrami signature inherits a simple metric, namely, the $L^2$ distance, to measure the geometric dissimilarity between shapes.
+We have applied the shape distance to shape classification and shown satisfactory results.
+\end{enumerate}
+
+\section{Related works}\label{related work}
+    Shape representation and description is an enduring field and there have been extensive and in-depth discussions in the past several decades.
+Demisse \etal \cite{demisse2017deformation} proposed a method to represent an ordered set of points sampled from a curved shape as an element of a finite dimensional matrix Lie group.
+Mokhtarian \etal \cite{mokhtarian1997efficient} use the maxima of curvature zero-crossing contours of Curvature Scale Space image to represent the shapes of object boundary contours.
+Lui \etal \cite{lui2013shape} extracted each component of a 2D multi-connected shape, then the conformal weldings represent all components and conformal modules describe relationships between components.
+
+    A more meticulous survery about shape representations can be found in \cite{zhang2004review}.
+Generally speaking, all of these representation techniques can be divided into two major categories, \textit{contour-based} methods and \textit{region-based} methods, depending on whether shape features are extracted from the contour only or from the whole shape region.
+
+    \subsection{Contour-based methods}
+        As its name suggests, this kind of representations only exploits the information providing by shape boundary.
+A very natural idea is that the boundary can be taken as a whole, from which a multi-dimensional numeric feature vector can be calculated and becomes the demanded representation.
+
+        The simplest features are area, circularity, curvature and so on and their combination can be used as shape representation.
+Peura \etal \cite{peura1997efficiency} proposed such descriptor including convexity, ratio of principle axis, circular variance and elliptic variance.
+Belongie \etal \cite{belongie2002shape} tried in a different way and build a representation based on Hausdorff distance, called shape contexts.
+For any boundary point $p$, they calculated the Hausdorff distance $d_{pq}$ and the orientation $\theta_{pq}$ with any other boundary point $q$, then these $d_{pq}$ and $\theta_{pq}$ are quantized to create a histogram map $H_p$ which is used to represent the point $p$.
+All the histogram $H_p$ is flattened and concatenated to form the context of the shape.
+Asada \etal \cite{asada1986curvature} attempted to smooth the boundary by Gaussian filter and second derivatives of Gaussian filter and the inflection points that remain are expected to be significant object characteristics.
+
+        Some other contour-based representations pay more attention to local boundary information and broke the shape down into many pieces.
+Chain code describes an object by a sequence of unit-size line segments with a given orientation, which was introduced by Freeman \etal \cite{freeman1961encoding}.
+Berretti \etal \cite{berretti2000retrieval} extended the model.
+The curvature zero-crossing points from a Gaussian smoothed boundary are used to obtain smooth curve, called tokens.
+The feature for each token is its maximum curvature and its orientation, and the similarity between two tokens is measured by the weighted Euclidean distance.
+
+    \subsection{Region-based methods}
+        Different from the previous category, region-based representations make the best use of all the pixels within the given shape region.
+Geometric moment is a classical and representative region-based shape description with form
+        \begin{equation*}
+            m_{pq} = \sum_x \sum_y x^p y^q f(x, y),
+        \end{equation*}
+        where $p, q = 0, 1, 2, \cdots$ and $f$ is the given shape.
+Hu published the first significant paper about geometric moment and applied it in pattern recognition \cite{hu1962visual}.
+Taubin \etal \cite{taubin1991object,taubin1991recognition} proposed algebraic moment, which is computed from the first $m$ central moments and is given as the eigenvalues of predefined matrices, $M_{[j; k]}$, whose elements are scaled factors of the central moments.
+Zhang \etal \cite{zhang2002generic} proposed Generic Fourier descriptor which is acquired by applying a 2D Fourier transform on a polar-raster sampled image
+        \begin{equation*}
+            PF_2(\rho, \phi) = \sum_r \sum_k f(r, \theta_k) e^{2 \pi i (\frac{r}{R} \rho + \theta_k \phi)},
+        \end{equation*}
+        where $0 \le r < R$, $0 \le \rho < R$, $0 \le k < T$, $0 \le \phi < T$, $\theta_k = \frac{2\pi k}{T}$ and $R, T$ are the radial frequency resolution and angular frequency resolution respectively
 
@@
 
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig2.jpg}
-            \end{center}
-            \caption{(a) Shows the original hippocampus.
+        % \begin{figure}
+        %     \begin{center}
+        %         \includegraphics[width=7.6cm]{src/fig2.jpg}
+        %     \end{center}
+        %     \caption{(a) Shows the original hippocampus.
 (b) Shows the parameter domain with circle packing pattern.
 Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
-            \label{fig2}
-        \end{figure}
+        %     \label{fig2}
+        % \end{figure}
 
@@
 All the conformal distortion of $S(z)$ is caused by $\mu(p)$.
-$S(z)$ is the map that causes $f$ to map a small circle to a small ellipse (see Fig.
-\ref{fig2}).
+$S(z)$ is the map that causes $f$ to map a small circle to a small ellipse.
 Form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well.
@@
             \begin{center}
-                \includegraphics[width=7.6cm]{src/fig3.jpg}
+                \includegraphics[width=7.6cm]{src/fig3.png}
             \end{center}
@@
 
+        Note that there is a one-to-one correspondence between the quasi-conformal mapping f and its Beltrami coefficient $\mu$.
+Given $f$, there exists a Beltrami coefficient $\mu$ satisfying the Beltrami equation.
+Conversely, the following theorem states that given an admissible Beltrami coefficient $\mu$, there always exists an quasi-conformal mapping $f$ associating with this $\mu$.
+
+        \begin{theorem}[Measurable Riemannian Mapping Theorem]\label{Measurable Riemannian Mapping Theorem}
+            Suppose $\mu : \C \rightarrow \C$ is Lebesgue measurable satisfying $\abs{\mu}_\infty <1$; then, there exists a quasi-conformal homeomorphism $f$ from $\C$ onto itself, which is in the Sobolev space $W_{1,2}(\C)$ and satisfies the Beltrami equation in the distribution sense.
+The associated quasi-conformal homeomorphism $f$ is unique up to a Mobious transformation.
+Furthermore, by fixing $0$, $1$ and $\infty$, the $f$ is uniquely determined.
+        \end{theorem}
+
         Suppose $f, g: \C \rightarrow \C$ are complex-valued function with Beltrami coefficient $\mu_f, \mu_g$ respectively. Then the Beltrami coefficient for the composition $g \circ f$ is given by 
@@
 
-    \subsection{Conformal welding}
-        Given 2D bounded simple connected shape, we can treat it as a boundary simple connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
+    \subsection{Conformal welding}\label{welding}
+        Given 2D bounded simply-connected shape, we can treat it as a boundary simply-connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
 $\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobious transformation}:
@@
 
+        However, such welding mappings are not unique because of the arbitrariness of Riemann mappings, as shown in Fig. \ref{unsatble}.
+
+        \begin{figure}
+            \begin{center}
+                \includegraphics[width=7.6cm]{src/unstable welding.png}
+            \end{center}
+            \caption{Different conformal welding mappings (b), (c) and (d) of the same shape (a)}
+            \label{unsatble}
+        \end{figure}
+
     \subsection{Harmonic function and Poisson integral}
@@
         \begin{theorem}\label{composition of harmonic}
-            Let $f$ be a harmonic mapping, $f \circ g$ is harmonic if and only if $g(z) = az + b \overline{z} + c$, where $a$, $b$ and $c$ are constaants and $g \circ f$ is harmonic if and only if $g$ is analytic or anti-analytic.
+            Let $f$ be a harmonic mapping, $f \circ g$ is harmonic if and only if $g(z) = az + b \overline{z} + c$, where $a$, $b$ and $c$ are constants and $g \circ f$ is harmonic if and only if $g$ is analytic or anti-analytic.
         \end{theorem}
@@
         The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}.
-For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
+For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continuous $f$ on $\partial \D$
             \begin{equation}\label{poisson integral}
@@
             \end{equation}
-        Such $H$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
+        Such $H$ is harmonic on $\D$ and continuous on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
 $H(e^{i\theta}) = f(e^{i\theta})$ (see Fig.
@@
             \end{center}
-            \caption{(a) Continious function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$.
+            \caption{(a) Continuous function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$.
 (b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
@@
 
-    \section{Beltrami signature}\label{main}
-        In this chapter, we will propose a new representation, Beltrami signature, to discribe boundary simple connected domain $\Omega$.
-Our proposed signature is based on conformal welding and quasi-conformal theory.
-
-        \subsection{Beltrami signature based on conformal welding}
-            Here we give a brief explaination of how to create our new signature.
-Given the boundary simple connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it.
+    \section{Harmonic Beltrami signature (HBS)}\label{main}
+        In this section, we describe our proposed shape signature, called the {\it Harmonic Beltrami signature (HBS)}, to represent a simply-connected domain $\Omega$.
+The space of HBS inherits a natural metric, so that geometric distance between two shapes can be easily measured.
+In the following subsection, the definition of HBS and some of its theoretical analysis are addressed.
+
+        \subsection{Definition of Harmonic Beltrami Signature}
+        Consider a bounded simply-connected domain $\Omega\subset \mathbb{C}$.
+Suppose $\Omega$ is a quasicircle, which is the image of the unit disk under a quasiconformal map.
+Let $f = \Phi_1^{-1} \circ \Phi_2$ be the conformal welding of $\Omega$, where  $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are the conformal mappings as described in Section \ref{welding}.
+Denote the harmonic extension of $f$ by $H:\mathbb{D}\to \mathbb{D}$.
+
+         \begin{definition}
+         The {\it Harmonic Beltrami Signature (HBS)} is a complex-valued function $B:\mathbb{D}\to \mathbb{D}$ with $||B||_{\infty}<1$ defined as
+         \begin{equation}
+                B:= \mu_H = \frac{H_{\overline{z}}}{H_z}.
+        \end{equation}
+         \end{definition}
+
+        Note that the HBS is not unique without suitable normalizations of the conformal mappings.
+More precisely, the conformal welding of $\Omega$ is unique up to a pre- and post-composition of Mobi\"us transformations.
+Suppose $f_1$ and $f_2$ are both conformal weldings of $\Omega$.
+Then, $f_2 = M_1\circ f\circ M_2$.
+The harmonic extension and hence the HBS are not unique due to conformal ambiguities.
+This motivates us to give the following definition of equivalence.
+
+        \begin{definition}
+        Two HBS $B$ and $\tilde{B}$ are said to be {\it equivalent} if $B=\mu_H$ and $\tilde{B} = \mu_{\tilde{H}}$, where $H$ and $\tilde{H}$ are respectively the harmonic extensions of a diffeomorphism $f:\mathbb{S}^1\to \mathbb{S}^1$ and $\tilde{f} = M_1\circ f \circ M_2$ for some Mobi\"us transformations $M_1$ and $M_2$.
+In this case, we denote $B \sim \tilde{B}$.
+Also, the equivalence class of $B$ is denoted by $[B]$.
+        \end{definition}
+
+        In this work, we consider the quotient space of HBS $\mathcal{B} = \{B:\mathbb{D}\to \mathbb{D}:B \text{ is a HBS} \} /\sim$ to study the space of bounded simply-connected shapes.
+The following theorem illustrates that $\mathcal{B}$ is indeed an effective representation for the space of shapes.
+
+        \begin{theorem}
+        There is a one-to-one correspondence between $\mathcal{B}$ and $\mathcal{S}$.
+In particular, given $[B]\in \mathcal{B}$, its associated shape $\Omega$ can be determined up to a Mobi\"us transformation.
+Also, if $\Phi_2$ is chosen such that $\Phi_2(\infty) = \infty$, $\Omega$ is determined up to a translation, rotation and scaling.
+        \end{theorem}
+
+        \begin{proof}
+        Given $\Omega$, there exist a unique $[B]\in \mathcal{B}$ corresponding to $\Omega$ follows from the definition of HBS.
+Conversely, let $[B]\in \mathcal{B}$.
+Define $\mu:\mathbb{C}\to \mathbb{C}$ as
+        \[
+        \mu := \begin{cases}
+        B \text{ on }\mathbb{D}\\
+        0 \text{ on }\mathbb{D}^c.
+        \end{cases}
+        \]
+        According to Quasiconformal Teichm\"uller theory, there exists $G:\mathbb{C}\to \mathbb{C}$ such that $G_{\bar{z}}/G_z = \mu$.
+$G$ is unique up to a Mobi\"us transformation.
+In other words, if $G_1$ and $G_2$ are two quasiconformal maps satisfying the above requirement, then $G_2=M\circ G_1$, where $M$ is a Mobi\"us transformation.
+In particular, $G$ is uniquely determined if we fix $0, 1$ and $\infty$.
+Let $\Omega = G(\mathbb{D})$.
+We claim that the HBS of $\Omega$ is $B$.
+To see this, let $\Phi_1: \mathbb{D}\to \Omega$ be the conformal parameterization of $\Omega$.
+By construction, $G|_{\mathbb{D}^c}: \mathbb{D}^c\to \Omega^c$ is conformal.
+The conformal welding of $\Omega$ is $\Phi_1^{-1}\circ G|_{\partial\mathbb{D}}$.
+As $\Phi_1$ is conformal and $G$ is harmonic, $\Phi_1^{-1}\circ G$ is the harmonic extension of the welding map.
+Thus, the HBS of $\Omega$ is: $\mu_{\Phi_1^{-1}\circ G}=\mu_G = B$.
+
+        Now, $\Omega$ is uniquely determined up to a Mobi\"us transformation $M=\frac{az+b}{cz+d}$.
+If $G(\infty) = \infty$, then $M$ is of the form: $M = az+b= re^{i\theta}z +b$, $r\in \mathbb{R}^+$, $\theta \in [0,2\pi)$ and $b\in \mathbb{C}$.
+Hence, $\Omega$ is uniquely determined up to a scaling, rotation and translation, which are reflected by $r, \theta$ and $b$ respectively.
+        \end{proof}
+
+\bigskip
+
+The above theorem demonstrates that the HBS is indeed an effective geometric representation or ``fingerprint" of a shape. It determines a shape up to a scaling, rotation and translation.
+
+            %Here we give a brief explanation of how to create our new signature.
+Given the boundary simply-connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it.
 Then $f$ can be extended to harmonic function $H$ defined on $\D$ by Poisson integral (\ref{poisson integral}).
 At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
-            \begin{equation}
-                B:= \mu_H = \frac{H_{\overline{z}}}{H_z}.
-            \end{equation}
-            Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $B$ is determined.
+           % \begin{equation}
+          %      B:= \mu_H = %\frac{H_{\overline{z}}}{H_z}.
+       %     \end{equation}
+        %    Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $B$ is determined.
 
@@
                 \end{center}
-                \caption{Illustration of Beltrami signature.
+                \caption{Illustration of Harmonic Beltrami signature.
 (a) The input shape, a dolphin.
 (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b).
-(c) The Beltrami signature of (a).
-Remark that the harmonic funcion and Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
+(c) The Harmonic Beltrami signature of (a).
+Remark that the harmonic function and Harmonic Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
                 \label{illu of BS}
@@
 
-        \subsection{Analysis of uniqueness of Beltrami signature}
-            According to Riemann mapping theorem, the conformal mapings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
+        \subsection{Unique representative of $[B]$}
+            As discussed, every shape can be represented by its associated HBS, which is an equivalence class.
+In order to measure the geometric difference between shapes based on HBS, it is necessary to find a unique representative in the equivalence class $[B]$.
+Once the unique representatives of two shapes are determined, the geometric difference between them can be easily measured, such as the $L^2$ distance.
+
+            According to Riemann mapping theorem, the conformal mappings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
 Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobious transformations.
@@
             \begin{theorem}
-                Suppose $f$ and $\tilde{f}$ are continious map from $\partial \D$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
+                Suppose $f$ and $\tilde{f}$ are continuous map from $\mathbb{S}^1$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
 $H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
@@
 
-            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{H}$
-            \begin{equation}
+            Suppose HBS $B$ is the representative of given equivalence class $[B]$ and $H$ is the corresponding Harmonic extension.
+Because of above theorem, we assume $M_1$ is a rotation, then some other $\tilde{B} \in [B]$ of $\tilde{H}$ is
+            \begin{equation}\label{tildeB}
                 \tilde{B} = \mu_{\tilde{H}} = \mu_{M_1^{-1} \circ H \circ M_2} = \mu_{H\circ M_2}.
             \end{equation}
-            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, then we get $M_2$ is identity.
-Therefore, we know that the uniqueness of Beltrami signature is equivalent to following restrictions:
-            \begin{enumerate}
-                \item $M_1$ should be a rotation.
-                \item $M_2$ should be identity.
-            \end{enumerate}
+            If we want to find a unique $B$, it means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, hence some pre- and post-normalizations are required.
 
@@
 
-            \subsubsection{Unque $\Phi_1$ up to a rotation}
-
-            Above theorems show that there is alway an unique solution $a \in \D$ for equation (\ref{eq}), so we can come back to theorem \ref{unique up to a rotation}.
+            \subsubsection{Unique $\Phi_1$ up to a rotation}
+
+            Above theorems show that there is always a unique solution $a \in \D$ for equation (\ref{eq}), so we can come back to theorem \ref{unique up to a rotation}.
 
@@
         \subsection{Normalization to $M_2$}\label{norm2}
-            As for $M_2$, we hope it is identity, which is equivalent with the uniqueness of $\Phi_2: \D^c \rightarrow \Omega^c$.
-Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this and derivative to guarantee the uniqueness.
+            As for $M_2$, we also hope it is also a rotation here, which is equivalent with that $\Phi_2$ is uniquely determined up to a rotation.
+Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this guarantee this uniqueness.
 
             \begin{theorem}
-                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobious transformation.
-If $\tilde{\Phi_2}, \Phi_2$ satisifies that
-                \begin{align}
-                    &\tilde{\Phi_2}(\infty) = \Phi_2(\infty) = \infty\label{norm phi2 1}\\
-                    &\argmax{z \in \partial \D} \abs{\Phi_2'(z)} = \argmax{z \in \partial \D} \abs{\tilde{\Phi_2'}(z)} = 1,\label{norm phi2 2}
-                \end{align}
-                then such $M_2$ is identity.
+                Let $\Phi_2$ be a conformal map from $\D^c$ to $\Omega^c$ satisfying that
+                \begin{equation}
+                    \Phi_2(\infty) = \infty\label{norm phi2 1}
+                \end{equation}
+                then such $\Phi_2$ is uniquely determined a rotation.
             \end{theorem}
@@
             \begin{proof}
-                Suppose Mobious transformation $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$. Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisify (\ref{norm phi2 1}), then
+                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobious transformation, $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$.
+Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisfy (\ref{norm phi2 1}), then
                 \begin{align*}
@@
                 Therefore, $M_2(\infty) = e^{i \theta} \frac{\infty - a}{1- \overline{a} \infty} = \infty$, which means that $a = 0$ and $M_2(z) = e^{i \theta} z$.
-
-                Consider the derivative of $\tilde{\Phi}_2$,
-                \begin{equation}
-                    \tilde{\Phi}_2'(z) = \Phi_2' \circ M_2(z) \cdot M_2'(z) = e^{i\theta} \Phi_2' (e^{i \theta}z),
-                \end{equation}
-                then we know that $\abs{\tilde{\Phi}_2'(z)} = \abs{\Phi_2'(e^{i \theta}z)}$.
-Suppose $a = \argmax{z \in \partial \D} |\Phi_2'(z)|$, then we will have that $ae^{-i \theta} = \argmax{z \in \partial \D} |\tilde{\Phi}_2'(z)|$.
-                If condition (\ref{norm phi2 2}) holds for both $\tilde{\Phi}_2$ and $\Phi_2$, it means $a = a e^{-i \theta} = 1$, so $a = 1$, $\theta = 0$ and $M_2$ is identity.
             \end{proof}
 
+        \subsection{Post-normalization for $B$}\label{post norm B}
+            After normalizing $M_1$ and $M_2$, where $M_1, M_2$ are both rotation, for $B, \tilde{B} \in [B]$ with harmonic extensions $H, \tilde{H}$, according to equations (\ref{mu of conformal composition}) and (\ref{tildeB}), we have
+            \begin{equation}\label{arg integral B is 0}
+                \tilde{B}(z) = \mu_{H \circ M_2}(z) = e^{-2i\theta} \mu_H \circ M_2(z) = e^{-2 i \theta} B(e^{i\theta} z),
+            \end{equation}
+            where $M_2(z) = e^{i \theta}z$. This equation tells us the uniqueness of $B$ can be achieved by following theorem.
+            \begin{theorem}\label{unique B}
+                Suppose $B$ is HBS in given equivalence class $[B]$ and satisfies requirements (\ref{norm phi1}) and (\ref{norm phi2 1}). If
+                \begin{equation}
+                    \arg \int_\D B(z) dz = 0,
+                \end{equation}
+                then $B$ is unique representative of $[B]$.
+            \end{theorem}
+
+            \begin{proof}
+                Suppose $B, \tilde{B}$ are both HBS in the same equivalence class $[B]$ with harmonic extensions $H$ and $\tilde{H}$ respectively, where $\tilde{H} = M_1^{-1} \circ H \circ M_2$ and $\int_D B(z)dz = r e^{i \tau}$.
+According to requirements (\ref{norm phi1}) and (\ref{norm phi2 1}), $M_1, M_2$ are rotation.
+Let $M_2(z) = e^{i\theta}z$, then we have
+                \begin{eqnarray}
+                    \int_B \tilde{B}(z) dz
+                    &=& \int_D e^{-2i\theta} B(e^{i\theta} z) dz \nonumber \\
+                    &=& e^{-2i\theta} \int_D B(z) dz \nonumber \\
+                    &=& r e^{i(\tau-2\theta)}.
+                \end{eqnarray}
+                If equation (\ref{arg integral B is 0}) holds,
+                \begin{equation*}
+                    \tau = \tau-2\theta  = 0,
+                \end{equation*}
+                hence $\theta = 0$, $M_2$ is identity and so$\tilde{B} = \mu_{H \circ I} = \mu_H = B$.
+            \end{proof}
+
+            Note that the unique representative $B$ of $[B]$ can be easily generated from any HBS $B_0 \in [B]$. If $\tau_0 =\arg \int_\D \tilde{B}(z) dz  \neq 0$, then
+            \begin{equation}\label{normaled B}
+                B(z) = e^{i\tau_0}B_0(e^{-\frac{\tau_0}{2}i}z)
+            \end{equation}
+            is just the desired representative.
+
         \subsection{Invariance under simple transformation}
-            With the normalization mentioned above, we can get unique Beltrami signature $B$ corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$.
-Now we want to prove that if we do some simple transformation like rotation, scaling and translation to $\Omega$, the Beltrami signature is invariant.
-
-            \begin{theorem}
-                Given a boundary simple connected domain $\Omega$ and transformation $T$ which is composed by rotation, scaling and transformation.
-Let $B_\Omega$ and $B_{T(\Omega)}$ be the Beltrami signature of $\Omega$ and $T(\Omega)$, then $B_\Omega = B_{T(\Omega)}$
+            With the normalization mentioned above, we can get a unique Harmonic Beltrami signature $B$ as the representative corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$.
+Now we want to prove that if we do some simple transformation like rotation, scaling and translation to $\Omega$, the HBS is invariant.
+
+            \begin{theorem}\label{invariance theorem}
+                Given a boundary simply-connected domain $\Omega$ and transformation $T$ which is composed by rotation, scaling and transformation.
+Let $B_\Omega$ and $B_{T(\Omega)}$ be the HBS of $\Omega$ and $T(\Omega)$, then $B_\Omega = B_{T(\Omega)}$
             \end{theorem}
@@
 Given the boundary points $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$, then $\{T(z_1), T(z_2), \cdots, T(z_n)\} \subset \partial T(\Omega)$.
-Since $\tilde{\Phi}_1$ satisifies condition (\ref{norm phi1}), we have
+Since $\tilde{\Phi}_1$ satisfies condition (\ref{norm phi1}), we have
                 \begin{equation*}
@@
                 \end{equation*}
-                which means $\hat{\Phi}_1$ also satisifies condition (\ref{norm phi1}). Hence $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1= \Phi_1 \circ R$, which equals to
-                \begin{equation}
-                    \tilde{\Phi}_1 = T \circ \Phi_1 \circ R,
-                \end{equation}
-                where $R$ is a rotation.
+                which means $\hat{\Phi}_1$ also satisfies condition (\ref{norm phi1}). Hence $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1= \Phi_1 \circ M_1$, which equals to
+                \begin{equation}
+                    \tilde{\Phi}_1 = T \circ \Phi_1 \circ M_1,
+                \end{equation}
+                where $M_1$ is a rotation.
 
@@
                 \end{equation*}
-                which means $\hat{\Phi}_2$ satisifies condition (\ref{norm phi2 1}).
-
-                As for condition (\ref{norm phi2 2}), we know that $T'(z) = k e^{i \theta}$, so
-                \begin{equation}
-                    \hat{\Phi}_2'(z) = T' \circ \tilde{\Phi}_2(z) \cdot \tilde{\Phi}_2'(z) = k e^{i \theta} \tilde{\Phi}_2'(z).
-                \end{equation}
-                Hence $\abs{\hat{\Phi}_2'} = \abs{k}\abs{\tilde{\Phi}_2'}$, which means $\hat{\Phi}_2$ also satisifies condition (\ref{norm phi2 2}).
-Therefore, $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2 = \Phi_2$ and then
-                \begin{equation}
-                    \tilde{\Phi}_2 = T \circ \Phi_2.
-                \end{equation}
+                which means $\hat{\Phi}_2$ satisfies condition (\ref{norm phi2 1}). Therefore, $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2 = \Phi_2 \circ M_2$ and then
+                \begin{equation}
+                    \tilde{\Phi}_2 = T \circ \Phi_2 \circ M_2,
+                \end{equation}
+                where $M_2$ is also a rotation.
 
                 We have the conformal welding
-                \begin{equation}
-                    \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = R^{-1} \circ \Phi_1^{-1} \circ T^{-1} \circ T \circ \Phi_2 = R^{-1} \circ f.
-                \end{equation}
-                Then the harmonic extension $\tilde{H} = R^{-1} \circ H$ and 
-                \begin{equation}
-                    B_{T(\Omega)} = \mu_{\tilde{H}} = \mu_{R^{-1} \circ H} = \mu_H = B_\Omega.
-                \end{equation}
+                \begin{eqnarray}
+                    \tilde{f}
+                    &=& \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 \\
+                    &=& M_1^{-1} \circ \Phi_1^{-1} \circ T^{-1} \circ T \circ \Phi_2 \circ M_2 \\
+                    &=& M_1^{-1} \circ f \circ M_2.
+                \end{eqnarray}
+                Then the harmonic extension $\tilde{H} = M_1^{-1} \circ H \circ M_2$ and so $B_\Omega = \mu_H$ and $B_{T(\Omega)} = \mu_{\tilde{H}}$ are both the representative of the same equivalence class.
+Therefore, $B_\Omega = B_{T(\Omega)}$ because of theorem \ref{unique B}.
             \end{proof}
+
+    \section{Reconstruction}\label{reconstruction}
+
+        The above theorems show that our Harmonic Beltrami signature can be uniquely defined by the given shape and is invariant under translation, scaling and rotation.
+Conversely, we will further demonstrate the method to reconstruct the original shape when given a Beltrami signature in this section.
+
+        If $B_\Omega$ is the HBS of some simply-connected domain $\Omega$, according to the process we mentioned in Section \ref{main}, there exists conformal mappings $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, conformal welding $f: \partial \D \rightarrow \partial \D $ and harmonic extension $H$ of $f$, where $\Phi_1$ satisfies equation (\ref{norm phi1}), $\Phi_2$ satisfies equations (\ref{norm phi2 1}), $f = \Phi_1^{-1} \circ \Phi_2$, $\mu_H = B_\Omega$ and $B_\Omega$ satisfies (\ref{arg integral B is 0}).
+
+        Given a Harmonic Beltrami signature $B_\Omega$, define
+        \begin{equation}
+            g(z) = \begin{cases}
+                B_\Omega(z), z \in \D \\
+                0, z \in \D^c
+            \end{cases}
+        \end{equation}
+        According to Theorem \ref{Measurable Riemannian Mapping Theorem}, we can find mapping $G: \overline{\C} \rightarrow \overline{\C}$ such that
+        \begin{align}
+            &\mu_G = \frac{G_{\overline{z}}}{G_z} = g \nonumber\\
+            &G(\infty) = \infty\label{Ginfty}
+        \end{align}
+        where $G$ is uniquely determined up to Mobious transformation $M$.
+
+        Claim that $\Omega' = G(\D)$ is the reconstructed domain satisfying $\Omega' = T(\Omega)$, where $T$ is composed by rotation, scaling and translation. Note that
+        \begin{equation}
+            G_0(z) = \begin{cases}
+                \Phi_1 \circ H(z), z \in \D\\
+                \Phi_2(z), z \in \D^c
+            \end{cases}
+        \end{equation}
+        is one solution of (\ref{Ginfty}) since $\mu_{\Phi_1 \circ H} = \mu_H = B_\Omega$ inside $\D$, $\mu_{\Phi_2} = 0$ outside $\D$ and $\Phi_2(\infty) = \infty$. Therefore, we have 
+        \begin{equation}
+            G = M \circ G_0 \text{ and } M(\infty) = \infty.
+        \end{equation}
+        By the properties of Mobious transformation, we have $M(z) = az+b$ where $a, b \in \C$.
+
+        On the other side, $H$ is a harmonic mapping from $\D$ onto itself, so $G_0(\D) = \Phi_1 \circ H(\D) = \Omega$, then $\Omega' = G(\D) = M(\Omega) = a \Omega + b$, which show the claim is correct.
+
+        That means the relationship between Harmonic Beltrami signatures and shapes is a bijection, up to transformation, scaling and rotation. 
+        \begin{theorem}
+            Let $\Omega_1, \Omega_2$ be two different simply-connected domains and $B_{\Omega_1}, B_{\Omega_2}$ are the corresponding HBS, then $B_{\Omega_1} = B_{\Omega_2}$ if and only is $\Omega_1 = T(\Omega_2)$, where $T$ is composed by rotation, scaling and translation.
+        \end{theorem}
+
+        \begin{proof}
+            The direction from signatures to shapes is proved in this section, and another direction is derived from theorem \ref{invariance theorem}.
+        \end{proof}
+
+        Hence, following powerful theorem about Beltrami holomorphic flow tells that if two HBS are similar, their corresponding shapes must be very alike.
+
+        \begin{theorem}[Beltrami holomorphic flow on $\mathbb{S}^2$]\label{BHF}
+            There is a one-to-one correspondence between the set of quasiconformal diffeomorphisms of $\mathbb{S}^2$ that fix the points 0, 1, and $\infty$ and the set of smooth complex-valued functions $\mu$ on $\mathbb{S}^2$ with $\norm{\mu}_\infty = k < 1$.
+Here, we have identified $\mathbb{S}^2$ with the extended complex plane $\overline{\C}$.
+Furthermore, the solution $f^\mu$ to the Beltrami equation depends holomorphically on $\mu$.
+Let $\{\mu(t)\}$ be a family of Beltrami coefficients depending on a real or complex parameter $t$.
+Suppose also that $\mu(t)$ can be written in the form
+            \begin{equation}
+                \mu(t)(z) = \mu(z) + tv(z) + t \epsilon(t)(z)
+            \end{equation}
+            for $z \in \C$, with suitable $\mu$ in the unit ball of $C^\infty(\C)$, $v, \epsilon(t) \in L^\infty(\C)$ such that $\lim_{t \rightarrow 0} \norm{\epsilon(t)}_\infty = 0$.
+Then for all $w \in \C$,
+            \begin{equation}
+                f^{\mu(t)}(w) = f^{\mu}(w) + tV(f^\mu, v)(w) + o(\abs{t})
+            \end{equation}
+            locally uniformly on $\C$ as $t \rightarrow 0$, where
+            \begin{align}
+                &V(f^\mu, v)(w) = -\frac{f^\mu(w)(f^\mu(w)-1)}{\pi}W(f^\mu, v)(w)\\
+                &W(f^\mu, v)(w) = \int_\C \frac{v(z)(f^\mu)^2_z(z)}{f^\mu(z)(f^\mu(z)-1)(f^\mu(z) - f^\mu(w))}dz.
+            \end{align}
+        \end{theorem}
+
+        \begin{proof}
+            This theorem is due to Bojarski. For detailed proof, please refer to \cite{durrleman2007measuring}.
+        \end{proof}
+
+        Given HBS $B_1, B_2$, we can solve PDE (\ref{Ginfty}) and get solutions $G_1, G_2$, then the corresponding original simply-connected domains $\Omega_1 = G_1(\D), \Omega_2 = G_2(\D)$. Let
+        \begin{equation}
+            g(t)(z) = \begin{cases}
+                B_1(z) + t v(z), z \in \D \\
+                0, z \in \D^c
+            \end{cases}
+        \end{equation}
+        where $v(z) = B_2(z) - B_1(z)$ if $z \in \D$ and $v(z) = 0$ if $z \notin \D$, so $G(t)(z) = G_1(z) + tV(G_1, v)(z)$. When $t=1$, we have $G(1)(z) = G_2(z)$ and
+        \begin{align*}
+            &\norm{G_2 - G_1}_\infty = \norm{V(G_1, v)}_\infty \\
+            &\le \frac{1}{\pi}\norm{G_1}_\infty \norm{G_1 - 1}_\infty \norm{W(G_1, v)}\\
+            &\le \frac{2}{\pi} \norm{W(G_1, v)}_\infty.
+        \end{align*}
+        Since $G_1$ is continuous and bounded, the integral $\int_\D \frac{(G_1)_z^2(z)}{G_1(z)(G_1(z)-1)(G_1(z)-G_1(w)}dz$ is bounded for any $w \in \D$.
+Therefore, there exists some $M > 0$ such that
+        \begin{equation}
+            \norm{G_2 - G_1}_\infty \le \frac{2M}{\pi} \norm{B_2-B_1}_\infty.
+        \end{equation}
+
+        This illustrates that if the difference between HBS is small enough, their corresponding domains is almost the same, which means our Harmonic Beltrami signature is a good indicator similarity of shapes.
 
@@
         \subsection{Zipper algorithm}
-            In oder to find an unique and stable Beltrami signature, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
-As metioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
+            In order to find a unique and stable HBS, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
+As mentioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
 
@@
 For the convenience of readers, we gives a very brief review here.
-Given $N$ clockwise boundary points $z_1, z_2, \cdots, z_N \in \partial \Omega$, this algorithm use a series of linear fractional transformations $g_1, g_2, \cdots, g_N$ to map $z_1, z_2,\cdots, z_N$ to real axis one-by-one, and finally transfrom the upper half plane to unit disk by $g_{N+1}(z) = \frac{z-i}{z+i}$.
-Therefore, $g = g_{N+1} \circ g_N \circ \cdots \circ g_2 \circ g_1$ is a conformal mapping undisputedly and maps all these boundary points to unit circle and the domain $\Omega$ to $\D$.
+Given $N$ clockwise boundary points $z_1, z_2, \cdots, z_N \in \partial \Omega$, this algorithm use a series of linear fractional transformations $g_1, g_2, \cdots, g_N$ to map $z_1, z_2,\cdots, z_N$ to real axis one-by-one, and finally transform the upper half plane to unit disk by $g_{N+1}(z) = \frac{z-i}{z+i}$.
+Therefore, $g = g_{N+1} \circ g_N \circ \cdots \circ g_2 \circ g_1$ is a conformal mapping indisputably and maps all these boundary points to unit circle and the domain $\Omega$ to $\D$.
 Remark that zipper algorithm is sensitive to the order of points.
@@
 
-            For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputing points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$.
+            For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputting points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$.
 For $\Phi_2 : \D^c \rightarrow \Omega^c$, we can input anti-clockwise points and get $g_{\Phi_2} : \Omega^c \rightarrow \D$.
@@
         \subsection{Normalization}
-            Because of the arbitrariness of the comformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
+            Because of the arbitrariness of the conformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
             \begin{equation*}
@@
             \end{equation*}
-            Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then Beltrami signature $B$ can be unique.
-This section will tells how to satisfy equation (\ref{norm phi1}), (\ref{norm phi2 1}) and (\ref{norm phi2 2}) from the output of zipper algorithm.
+            Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then HBS $B$ can be unique.
+This section will tells how to satisfy equation (\ref{norm phi1}) and (\ref{norm phi2 1}) from the output of zipper algorithm.
 
             To normalization $M_1$, we need to solve equation (\ref{eq}).
-Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concerntrate around a point.
+Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concentrate around a point.
 At that time, $\abs{f(a)} \approx 1$ almost everywhere and the solution of (\ref{eq}) is also very close to the point.
@@
                 \end{center}
-                \caption{(a) The $p_i \in \partial \D$ gather in a small neiborhood around their arithmetic mean $p_c$, which is labeled in red.
+                \caption{(a) The $p_i \in \partial \D$ gather in a small neighborhood around their arithmetic mean $p_c$, which is labeled in red.
 (b) The corresponding $\abs{f(a)}$ for these $p_i$.
-It's worth to metion that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
+It's worth to mention that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
                 \label{original distribution}
@@
 
-            According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
+            % According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
 And another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
@@
 
-            Therefore, the maximal solution
-            \begin{equation}
-                \theta_{\max} = \argmax{j \in [1,10^5]} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}
-            \end{equation}
-            can be used to normalize the rotation and the final mapping is 
-            \begin{equation}
-                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{\max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
-            \end{equation}
-            where $M_{\Phi_2} = e^{i \theta_{\max}} F_{ce^{-i \theta_{\max}}}$.
+            % Therefore, the maximal solution
+            % \begin{equation}
+            %     \theta_{\max} = \argmax{j \in [1,10^5]} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}
+            % \end{equation}
+            % can be used to normalize the rotation and the final mapping is 
+            % \begin{equation}
+            %     \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{\max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
+            % \end{equation}
+            % where $M_{\Phi_2} = e^{i \theta_{\max}} F_{ce^{-i \theta_{\max}}}$.
 
@@
                 \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$ and $c = -\frac{1}{\bar{b}}$.
-                \STATE Let $F_c(z) = \frac{z-c}{1-\overline{c}z}$ and $\tilde{\Phi}_2(z)=\Phi_2 \circ F_{c}(z)$.
-                \STATE Let $\theta_j = \frac{2\pi}{M}(j-1)$ for $j=1,2, \cdots, M$.
-                \STATE Find maximal value of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ and corresponding $\theta_{\max}$.
-                \STATE Let $M_{\Phi_2} = e^{i \theta_{\max}} F_{ce^{-i \theta_{\max}}}$.
+                \STATE Let $F_c(z) = \frac{z-c}{1-\overline{c}z}$ and $M_{\Phi_2} = F_{c}$.
                 \RETURN Mobious transformation $M_{\Phi_2}$
@@
 
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig10.png}
-                \end{center}
-                \caption{The change of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ for different $\theta_j \in [0, 2\pi)$.
-It shows this function has a significant maximum and $\theta_{\max}$ is about $1.25\pi$.}
-                \label{derative}
-            \end{figure}
-
-            After obatining Mobious transformations $M_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
+            After obtaining Mobious transformations $M_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
             \begin{align*}
@@
             \end{align*}
-            and it is unique up to a rotation.
+            and it is unique up to rotation. Finally, the desired HBS can be generated from $\mu_{\hat{H}}$ according to equation (\ref{normaled B}).
 
@@
             \begin{algorithm}[H]
-            \caption{Calculate Beltrami signature}
+            \caption{Calculate HBS}
             \label{alg all}
             \begin{algorithmic}
-                \STATE \textbf{Inputs:} Simple connected shape $\Omega \subset \C$, $N=200$.
+                \STATE \textbf{Inputs:} Simply-connected shape $\Omega \subset \C$, $N=200$.
                 \STATE Pick clockwise points $z_1, \cdots, z_N \in \partial \Omega$ uniformly.
@@
                 \STATE Calculate normalized harmonic extension $\hat{H} = M_{\Phi_1} \circ H \circ M_{\Phi_2}$.
-                \STATE Calculate Beltrami coefficient $B$ of $\hat{H}$.
-                \RETURN Beltrami signature $B$.
+                \STATE Calculate Beltrami coefficient $\mu_{\hat{H}}$.
+                \STATE Calculate $\theta = \arg \int_\D \mu_{\hat{H}}(z) dz$.
+                \STATE Let $B(z) = e^{i \theta} \mu_{\hat{H}}(e^{-\frac{1}{2}i\theta} z)$.
+                \RETURN Harmonic Beltrami signature $B$.
             \end{algorithmic}
@@
     \section{Experimental result}\label{result}
-        In this section, we will validate key properties of our proposed Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
+        In this section, we will validate key properties of our proposed Harmonic Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
 Besides that, a good shape representation should keep the similarity with the same kind shape and is significantly different from different kinds of shape.
 
-        Before showing results, what needs illustration is that the distance we used to measure the difference of Beltrami signature is based on $L^2$ norm,
+        Before showing results, what needs illustration is that the distance we used to measure the difference of HBS is based on $L^2$ norm,
         \begin{equation}\label{bs dis}
@@
         \end{equation}
-        where $B_1, B_2$ are two different Beltrami signature, $z_i \in \D$ is the face center of triangluar mesh $M$ metioned in Section \ref{detail harmonic} and $N=60962$ here.
+        where $B_1, B_2$ are two different Harmonic Beltrami signatures, $z_i \in \D$ is the face center of triangular mesh $M$ mentioned in Section \ref{detail harmonic} and $N=60962$ here.
         \subsection{Invariance}\label{sec inv}
-            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate Beltrami signature after sacling, translation and rotation and compare them with the original shape's Beltrami signature.
+            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate HBS after scaling, translation and rotation and compare them with the original shape's HBS.
 The result is displayed in Fig \ref{inv}.
 In this figure, the first column are the sets of boundary points and we remark them as $\Omega_a$ to $\Omega_f$.
-The second column are the corresponding Beltrami signatures $B_a$ to $B_f$.
-Note that all the Beltrami signatures are shown in modulus, i.e.
+The second column are the corresponding Harmonic Beltrami signatures $B_a$ to $B_f$.
+Note that all the Harmonic Beltrami signatures are shown in modulus, i.e.
 $\abs{B_n}$ for row $n$, and in top view.
-And the third column(if have) are the histograms of the difference between original shape's Beltrami signature, i.e.
+And the third column(if have) are the histograms of the difference between original shape's Harmonic Beltrami signature, i.e.
 $\abs{B_n - B_a}$ for row $n$.
@@
 Row e is about rotation, the shape is $\Omega_e = \{z \mid z = e^{0.2\pi i} z_a, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.2144 \times 10^{-8}$.
-Row f is the combination of scaling, tanslation and rotation, the shape is $\Omega_e = \{z \mid z = 3e^{-0.85\pi i} z_a+350+600i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.7635 \times 10^{-8}$.
-These confirm the invariance of Beltrami signature and scaling, translation and rotation.
+Row f is the combination of scaling, translation and rotation, the shape is $\Omega_e = \{z \mid z = 3e^{-0.85\pi i} z_a+350+600i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.7635 \times 10^{-8}$.
+These confirm the invariance of HBS and scaling, translation and rotation.
 
@@
                 \end{center}
-                \caption{Beltrami signature under scaling, translation and rotation.}
+                \caption{Harmonic Beltrami signature under scaling, translation and rotation.}
                 \label{inv}
@@
             Similar with Section \ref{sec inv}, here we still treat the dolphin as the original shape and modify some small parts of it and Fig \ref{robust} is the result.
-It shows that the proposed signature is robust and stable and will not have a big mutation cauesd by small disturbance.
+It shows that the proposed signature is robust and stable and will not have a big mutation caused by small disturbance.
 
@@
 These shapes are generated by removing or adding something, which is in the red circle.
-We can see that Beltrami signatures have slight differences from $B_a$ but are still similar in general.
-And this figure also demonstrates that the bigger the modification part is, the more different the Beltrami signature is.
+We can see that Harmonic Beltrami signatures have slight differences from $B_a$ but are still similar in general.
+And this figure also demonstrates that the bigger the modification part is, the more different the Harmonic Beltrami signature is.
 For example in row i, losing a half of the tail makes the signature has a marked change.
@@
                 \end{center}
-                \caption{Beltrami signature under small modification}
+                \caption{Harmonic Beltrami signature under small modification}
                 \label{robust}
@@
 
-        \subsection{Classification with Beltrami signature}
-            Above properties ensure the proposed signature having the ablity to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.
+        \subsection{Classification with HBS}
+            Above properties ensure the proposed signature having the ability to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.
 
@@
 There are 3 images for each group so 9 images in total.
-From Fig \ref{classification images}, we can find that each class share similar Beltrami signatures and conformal welding.
-From Fig \ref{dis matrix}, the inter-class distance of Beltrami signature is awlays less than 0.2 while the intra-class distance is greater than 0.2.
+From Fig \ref{classification images}, we can find that each class share similar HBS and conformal welding.
+From Fig \ref{dis matrix}, the intraclass distance of HBS is always less than 0.2 while the interclass distance is greater than 0.2.
 But for conformal welding, the data is messy, for example, fish 3 thinks itself is very different from other fishes but looks most like giraffe 2.
-After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the Beltrami signature shows powerful classification ablity.
+After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the HBS shows powerful classification ability.
 
@@
                 \end{center}
-                \caption{These 3 rows are elephant, fish and giraffe. In each subfigure, the top left is the input shape, bottom left is the conformal welding and the right is Beltrami signature.}
+                \caption{These 3 rows are elephant, fish and giraffe.
+In each subfigure, the top left is the input shape, bottom left is the conformal welding and the right is Harmonic Beltrami signature.}
                 \label{classification images}
@@
                 \end{center}
-                \caption{(a) The distance matrix of Beltrami signatures of above 9 shapes by equation (\ref{bs dis}). (b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
+                \caption{(a) The distance matrix of Harmonic Beltrami signatures of above 9 shapes by equation (\ref{bs dis}).
+(b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
                 \label{dis matrix}
@@
                 \end{center}
-                \caption{(a) The MDS result of Beltrami signature. (b) The MDS result of conformal welding.}
+                \caption{(a) The MDS result of Harmonic Beltrami signature. (b) The MDS result of conformal welding.}
                 \label{mds1}
@@
                 \end{center}
-                \caption{(a) The MDS result of Beltrami signature.
+                \caption{(a) The MDS result of Harmonic Beltrami signature.
 (b) The MDS result of conformal welding.
-(c) The clustering result of Beltrami signature.
+(c) The clustering result of Harmonic Beltrami signature.
 (d) The clustering results of conformal welding.}
@@
         \subsection{Classification for more classes}
-            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabit.
+            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabbit.
 We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes.
-The MDS and clustering results based on Beltrami signature and conformal welding are displayed in Fig \ref{mds2}.
-The classification accuracy based on Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
+The MDS and clustering results based on Harmonic Beltrami signature and conformal welding are displayed in Fig \ref{mds2}.
+The classification accuracy based on Harmonic Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
 
     \section{Conclusion}\label{conclusion}
-        In this paper, we propose a novel shape representation for 2D bounded simple connected objects called Beltrami signature.
+        In this paper, we propose a novel shape representation for 2D bounded simply-connected objects called Harmonic Beltrami signature.
 The proposed signature is based on conformal welding but overcome a key shortcoming that it can be uniquely determined by the given shape.
 What's more exciting is that the proposed representation is invariance under scaling, translation and rotation.
-For slight deformation and distortion, Beltrami signature keeps roubost and only changes within a reasonable small range.
-Therefore, there are reasons to believe the it does have ablity to represent some invariant geometrical features.
-The experimental results also confirm that the Beltrami signature has excellent performance in multi-classification tasks.
+For slight deformation and distortion, HBS keeps robust and only changes within a reasonable small range.
+Therefore, there are reasons to believe the it does have ability to represent some invariant geometrical features.
+The experimental results also confirm that the HBS has excellent performance in multi-classification tasks.
 
         Although our work has achieved relatively good results, the proposed representation still have some limitations.
-Firstly, the Beltrami signature is only applicable to simple connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world.
-So we are eager for a feasible method to extend our Beltrami signature to multi connected situation.
-Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangluar mesh, which consumes a lot of time.
-Therefore, a fast algorithm to obatin this signature avoiding dense mesh is of high priority in our future work.
+Firstly, the HBS is only applicable to simply-connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world.
+So we are eager for a feasible method to extend our HBS to multi connected situation.
+Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangular mesh, which consumes a lot of time.
+Therefore, a fast algorithm to obtain this signature avoiding dense mesh is of high priority in our future work.
 Thirdly, when normalizing the conformal mapping $\Phi_2$ from exterior of unit disk to exterior of the domain, the position where the derivation of $\Phi_2$ reaches the maximum value is used to adjust the rotation.
@@
 
-        In summary, we will focus on third marjor directions in the future.
-One is that the deeper meaning of Beltrami signature is worth digging and then a multi-connected version of representation based on this work can be proposed.
-Another is that if the Beltrami signature contains some geometrical features of shapes, we can also extract them directly from images and generate the Beltrami signature again.
+        In summary, we will focus on three major directions in the future.
+One is that the deeper meaning of HBS is worth digging and then a multi-connected version of representation based on this work can be proposed.
+Another is that if the HBS contains some geometrical features of shapes, we can also extract them directly from images and generate the HBS again.
 Hence the deep learning theory may help us to compute this signature from given images immediately, which is very likely to improve algorithm speed performance greatly.
-A third direction is this representation can be used in more applications like segementation, registration and so on.
+A third direction is this representation can be used in more applications like segmentation, registration and so on.
 %\begin{acknowledgements}

### 2021-06-11 Background/background.tex
final thesis

\chapter{Mathematical background} \label{background}
In this chapter, we will provide some essential mathematical backgrounds required for this thesis. Some of these contents were included in previous works, for example, conformal welding part was first introduced in \cite{parallel} and \cite{Yusan}, and the contents in quasi-conformal map can be traced back to \cite{nDregistration}.

\section{Conformal maps}
Conformal maps are nice in preserving geometric properties, in a way that the angles are well-preserved under such transformations, geometrically transforming infinitesimal circles to infinitesimal circles.

Mathematically, let $U\subset \C$ be any open subset. Then $f: U\rightarrow\C$ is conformal if $f$ is holomorphic and bijective. By definition of being holomorphic, $f = u+iv$ satisfies the Cauchy-Riemann equations:
\begin{align}
    \dfrac{\partial u}{\partial x} &= \dfrac{\partial v}{\partial y} \nonumber\\
    \dfrac{\partial u}{\partial y} &= -\dfrac{\partial v}{\partial y}
    \label{eqn: CauchyRiemann}
\end{align}
This is equivalent to having 
\begin{align*}
    \dfrac{\partial u}{\partial x} - \dfrac{\partial v}{\partial y} = 0,\hspace{3pt} \dfrac{\partial u}{\partial y}+\dfrac{\partial v}{\partial x} = 0
\end{align*}{}
Consequently, conformal maps can be obtained by minimizing the following energy:
\begin{equation}
    E_C(f)=\dfrac{1}{2}\int_U(\dfrac{\partial u}{\partial x}-\dfrac{\partial v}{\partial y})^2 + (\dfrac{\partial u}{\partial y}+\dfrac{\partial v}{\partial x})^2dA
    \label{eqn: conformal energy}
\end{equation}{}
To see that conformal maps preserves angles, let $\gamma_i: [-\epsilon,\epsilon]\rightarrow U, \epsilon>0$ with $i=1,2$ be two curves satisfying that $\gamma_i(0) = z$ with $\gamma_i'(0) = v_i, i=1,2$. The angle preserving property in the case on complex plane can be easily verified by:
\begin{equation}
    \dfrac{(f\circ\gamma_1)'(0)(f\circ\gamma_2)'(0)}{(\|f\circ\gamma_1)'(0)(f\circ\gamma_2)'(0)\|} = \dfrac{[f'(z)]^2\gamma_1'(0)\gamma_2'(0)}{\|f'(z)\|^2\|\gamma_1'(0)\gamma_2'(0)\|} = \dfrac{v_1v_2}{\|v_1v_2\|}.
\end{equation}
There are a lot of conformal maps in practice, we will introduce an important kind of them, namely Mobi\"us transformation here.

\section{Mobi\"us transformation}
A Mobi\"us transformation, is one kind of linear fractional transformation on the (extended) complex plane $M: \C \rightarrow \C$, with the general expression:
\begin{equation}
    M(z) = \dfrac{az+b}{cz+d}
\end{equation}{}
$a,b,c,d \in \C$ with $ad-bc\neq 0$ for the invertibility and hence conformality.

In the fact, the automorphism of the unit disk $\D$ is special kind of Mobi\"us transformations, which can be written as:
\begin{equation}
    M(z) = e^{i \theta} \frac{z - a}{1 - \overline{a}z}.
\end{equation}
where $a \in \D$, $\theta \in [0, 2\pi)$.

There are a few key properties of Mobi\"us transformation: It has typical correspondence of points: $(0, -\frac{d}{c}, \infty)\mapsto(\frac{b}{d}, \infty, \frac{a}{c})$ whenever these points are well-defined on the extended complex plane. Besides, all conformal maps are known to be equivalent up to a Mobi\"us transformation.

And for this reason, to obtain a unique conformal map, one still needs to provide a three-point correspondence. Also, later on we will make use of Mobi\"us transformation in many place.

\section{Conformal welding}
Conformal welding is a problem that occurs in complex analysis: Given 2D bounded simply-connected shape, we can treat it as a boundary simply-connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, where $\D^c $ and $\Omega^c$ are the exterior part of $\D, \Omega$ respectively. $\Phi_1$ and $\Phi_2$ are unique up to a Mobi\"us transformation.

Then we can define \textit{conformal welding} as:
\begin{equation}
    f = \Phi_1^{-1} \circ \Phi_2.
\end{equation}
Such $f: \partial \D \rightarrow \partial \D$ is a diffeomorphism from $\partial \D$ to itself, which can be also thought as a periodic, real-valued monotone increasing function $f_\R: [0, 2\pi) \rightarrow [0, 2\pi)$ such that $f(e^{i \theta}) = e^{i f_\R(\theta)}$ (see Fig. \ref{ill of cw}).

Conformal welding is a kind of contour-based shape representation but it's easy to find that such welding mapping $f$ is not unique because of the arbitrariness of Riemann mappings $\Phi_1$ and $\Phi_2$, as shown in Fig. \ref{unsatble}.

On the other side, for general homeomorphism $f$, there may be no domain $\Omega$ such that $f$ is just the corresponding Conformal welding. However, if $f$ satisfies certain conditions, this problem is solvable. Before that we need to define \textit{quasisymmetric function}:

\begin{definition}
    Let $f$ be a continuous, strictly increasing function defined on an interval $I$, we call $f$ is quasisymmetric on $I$ if there exists a positive constant $k$ such that
    \begin{equation}
        \frac{1}{k} \le \frac{f(x+t) - f(x)}{f(x)-f(x-t)} \le k
    \end{equation}
    for all $x, x-t, x+t \in I$ with $t>0$.
\end{definition}

Pfluger proved the following Sewing theorem based on the existence of solution to the Beltrami equation \cite{pfluger1960ueber}. This theorem tells us if $f$ is a quasisymmetric function, we can reconstruct the original domain as well as the conformal mappings.

\begin{theorem}[Sewing theorem]
    Let $f$ be a quasisymmetric function, then there is a Jordan domain $\Omega$ and conformal mappings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ such that 
    \begin{equation}
        f = \Phi_1^{-1} \circ \Phi_2.
    \end{equation}
    The domain $\Omega$ is unique up to Mobi\"us transformations.
\end{theorem}

\begin{figure}
    \begin{center}
        \includegraphics[width=7cm]{./src/unstable_welding.png}
    \end{center}
    \caption{Different conformal welding mappings (b), (c) and (d) of the same shape (a)}
    \label{unsatble}
\end{figure}

\section{Harmonic maps}
A complex-valued map $f$ defined on $\Omega \subset \C$ is called \textit{harmonic} if it satisfies the \textit{Laplace's equation}:
\begin{equation}
    \Delta f = 4 \frac{\partial^2 f}{\partial z \partial \overline{z}} = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2} = 0,
\end{equation}
where $z = x + iy$, $x$, $y$ is the real and imaginary value.

Chen \etal prove following theorem in \cite{chen2010compositions}, which tells us that the composition of harmonic mappings and other mappings can inherit such harmonicity in some condition.
\begin{theorem}\label{composition of harmonic}
    Let $f$ be a harmonic mapping, $f \circ g$ is harmonic if and only if $g(z) = az + b \overline{z} + c$, where $a$, $b$ and $c$ are constants and $g \circ f$ is harmonic if and only if $g$ is analytic or anti-analytic.
\end{theorem}

When $\Omega$ is a compact set, the harmonic function $f$ defined on it satisfies the following maximum principle:
\begin{theorem}[Maximum principle]\label{Maximum principle}
    If $\Omega$ is a nonempty compact subset of $\C$, then harmonic function $f: \Omega \rightarrow \C$ attains its maximum on the boundary of $\Omega$.
\end{theorem}
If we apply maximum principle to $-f$, we can know that the minimun also must be on the boundary of $\Omega$. Futhermore, $f$ cannot have local maxima or minima, other than the exceptional case where $f$ is constant.

\section{Dirichlet problem and Poisson integral}
A harmonic function on a compact set is determined by its restriction to the boundary. The progress of finding a harmonic function defined on the given domain with the same value with a given continuous function on the domain boundary is call \textit{Dirichlet problem}, i.e. finding $H: \Omega \rightarrow \C$ such that
\begin{equation}\label{direchlet PDE}
    \begin{split}
        &\Delta H(z) = 0, \text{ } z \in \Omega,\\
        &H(z) = f(z), \text{ } z \in \partial \Omega,
    \end{split}
\end{equation}
where $\Omega$, $f: \partial \D \rightarrow \C$ are given. The existence of solution for PDE (\ref{direchlet PDE}) is proved by Hilbert in 1900 and the uniqueness can be easily checked by using the maximum principle.

However, it's still a hard job to calculate such $H$. Luckily, for a special case, where the domain is unit disk $\D$ on complex plane, the \textit{Poisson integral} shows a explicit method to obtain the desired harmonic function $H$ as
    \begin{equation}\label{poisson integral}
        H(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
    \end{equation}
Such $H$ is harmonic on $\D$ and continuous on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e. $H(e^{i\theta}) = f(e^{i\theta})$. Of course, this $H$ is unique. Fig. \ref{harmonic} displays an example of Poisson integral.

The Poisson integral is a stable method to extend the continuous function on unit circle to a unique harmonic function on unit disk, and we call it \textit{harmonic extension}.

\begin{figure}
    \begin{center}
        \includegraphics[width=14cm]{fig4_down.png}
    \end{center}
    \caption{(a) Continuous function $f(e^{i \theta}) = \sin(10 \theta) + \cos(10 \theta) + 1.5$ defined on $\partial \D$; (b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}). Note that we used absolute value to illustrate the progress of harmonic extension for the convenience of demonstration.}
    \label{harmonic}
\end{figure}

\section{Quasi-conformal mapping and Beltrami equation}
        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
        \begin{equation*}
            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
        \end{equation*}

        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
        \begin{equation}\label{beltrami eq}
            \Part{f}{\overline{z}} = \mu(z) \Part{f}{z}
        \end{equation}
        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$. More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
        \begin{equation}
            \mu_f = \frac{f_{\overline{z}}}{f_{z}}
        \end{equation}
        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
        \begin{equation}
            f^*(ds^2_E) = \abs{\Part{f}{z}}^2 \abs{dz + \mu(z)d\overline{z}}^2
        \end{equation}
        which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$. $\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality. In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$. Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
        \begin{equation}\label{local f}
            f(z) = f(p)+f_z(p)(z+\mu(p)\overline{z}).
        \end{equation}

        % \begin{figure}
        %     \begin{center}
        %         \includegraphics[width=7.6cm]{fig2.jpg}
        %     \end{center}
        %     \caption{(a) Shows the original hippocampus; (b) Shows the parameter domain with circle packing pattern. Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
        %     \label{fig2}
        % \end{figure}

        If $\mu(z)=0$ everywhere, then $f$ us called \textit{conformal} or \textit{holomorphic}. A conformal map satisfies the following well-known Cauchy-Riemann equation:
        \begin{equation}\label{cr eq}
            \Part{f}{\overline{z}} = 0.
        \end{equation}
        Inside the local parameter domain, $f$ may be considered as a map composed of a translation to $f(p)$ together with a stretch map $S(z) = z + \mu(p)\overline{z}$, which is postcomposed by multiplication of $f_z(p)$, which is conformal. All the conformal distortion of $S(z)$ is caused by $\mu(p)$. $S(z)$ is the map that causes $f$ to map a small circle to a small ellipse. Form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well. Specially, the angle of maximal magnification is $\arg(\mu(p))/2$ with magnifying factor $1+\abs{\mu(p)}$; the angle of maximal shrinkage is the orthogonal angle $\arg(\mu(p))/2 - \pi/2$ with shrinkage factor $1-\abs{\mu(p)}$. The distortion or dilation is given by:
        \begin{equation}
            K = \frac{1+\abs{\mu(p)}}{1-\abs{\mu(p)}}.
        \end{equation}
        Thus, the Beltrami coefficient $\mu$ gives us important information about the properties of the map (see Fig. \ref{fig3}).

        \begin{figure}
            \begin{center}
                \includegraphics[width=6cm]{fig3.png}
            \end{center}
            \caption{Quasi-conformal maps infinitesimal circles to ellipses. The Beltrami coefficient measure the distortion or dilation of the ellipse under the QC map.}
            \label{fig3}
        \end{figure}

        Then we put eyes on the Beltrami coefficient of composition of two different maps. Suppose $f, g: \C \rightarrow \C$ are complex-valued function with Beltrami coefficient $\mu_f, \mu_g$ respectively. Then the Beltrami coefficient for the composition $g \circ f$ is given by 
        \begin{equation}\label{mu of composition}
            \mu_{g \circ f} = \frac{\mu_f+(\mu_g \circ f) \tau}{1+\overline{\mu_f}(\mu_g \circ f) \tau},
        \end{equation}
        where $\tau = \frac{\overline{f_z}}{f_z}$. This equation can be derived directly from the definition of Beltrami coefficient. Note that when $g$ is conformal, $\mu_g = 0$ and 
        \begin{equation}\label{mu of conformal composition}
            \mu_{g \circ f} = \mu_f.
        \end{equation}
        Conversely, when $f$ is conformal, we have $\mu_f = 0$ and
        \begin{equation}\label{mu of conformal composition 2}
            \mu_{g \circ f} = (\mu_g \circ f) \tau.
        \end{equation}
        It means similar relationship with equation (\ref{mu of conformal composition}) does not always holds, i.e. $\mu_{g \circ f} \neq \mu_g$.

        Note that there is a one-to-one correspondence between the quasi-conformal mapping f and its Beltrami coefficient $\mu$. Given $f$, there exists a Beltrami coefficient $\mu$ satisfying the Beltrami equation. Conversely, the following theorem states that given an admissible Beltrami coefficient $\mu$, there always exists an quasi-conformal mapping $f$ associating with this $\mu$.

        \begin{theorem}[Measurable Riemannian Mapping Theorem]\label{Measurable Riemannian Mapping Theorem}
            Suppose $\mu : \C \rightarrow \C$ is Lebesgue measurable satisfying $\abs{\mu}_\infty <1$; then, there exists a quasi-conformal homeomorphism $f$ from $\C$ onto itself, which is in the Sobolev space $W_{1,2}(\C)$ and satisfies the Beltrami equation in the distribution sense. The associated quasi-conformal homeomorphism $f$ is unique up to a Mobi\"us transformation. Furthermore, by fixing $0$, $1$ and $\infty$, the $f$ is uniquely determined.
        \end{theorem}

        By reflection, the above theorem can be further extended to Beltrami coefficients defined on the unit disk $\D$.

        \begin{theorem}
            Suppose $\mu : \D \rightarrow \D$ is Lebesgue measurable satisfying $\abs{\mu}_\infty <1$; then, there exists a quasi-conformal homeomorphism $f$ from $\D$ onto itself, which is in the Sobolev space $W_{1,2}(\D)$ and satisfies the Beltrami equation in the distribution sense. The associated quasi-conformal homeomorphism $f$ is unique up to a Mobi\"us transformation. Furthermore, by fixing $0$ and $1$, the $f$ is uniquely determined.
        \end{theorem}

        Above 2 theorems suggest that under suitable normalization, a homeomorphism from $\C$ or $\D$ onto itself can be uniquely determined by its associated Beltrami coefficient. We can study the way to obtain maps from Beltrami Coefficient. Let $f(x, y) = u(x, y)+iv(x, y)$. Then, by Beltrami equation (\ref{beltrami eq}), we have
        \begin{equation}\label{beltrami eq with u v}
            \mu = \frac{f_{\overline{z}}}{f_z} = \frac{(u_x-vy)+i(v_x+u_y)}{(u_x+v_y)+i(v_x-u_y)}.
        \end{equation}
        Suppose $\mu_f = \alpha + i \beta$, then we can rewrite equation (\ref{beltrami eq with u v}) and get two systems of linear equations that are:
        \begin{equation}
            \begin{cases}
                v_y = \gamma_1 u_x + \gamma_2 u_y\\
                -v_x = \gamma_2 u_x + \gamma_3 u_y
            \end{cases}
        \end{equation}
        and
        \begin{equation}
            \begin{cases}
                u_y = \gamma_1 v_x + \gamma_2 v_y\\
                -u_x = \gamma_2 v_x + \gamma_3 v_y
            \end{cases}
        \end{equation}
        where
        \begin{equation}
            \gamma_1 = \frac{(1-\alpha)^2 + \beta^2}{1-\alpha^2-\beta^2}, \gamma_2 = -\frac{2\beta}{1-\alpha^2-\beta^2}, \gamma_3 = \frac{(1+\alpha)^2 + \beta^2}{1-\alpha^2-\beta^2}.
        \end{equation}
        Since 
        \begin{equation}
            \begin{split}
                &\left\langle \nabla ,  \begin{pmatrix}
                    v_y \\ -v_x
                \end{pmatrix} \right\rangle = v_{xy} -v_{xy} = 0 \\
                &\left\langle \nabla ,  \begin{pmatrix}
                    u_y \\ -u_x
                \end{pmatrix} \right\rangle = u_{xy} -u_{xy} = 0,
            \end{split}
        \end{equation}
        it yields
        \begin{equation}\label{LBS}
            \begin{split}
                &\left\langle \nabla ,  A\begin{pmatrix}
                    v_y \\ -v_x
                \end{pmatrix} \right\rangle = v_{xy} -v_{xy} = 0 \\
                &\left\langle \nabla ,  A\begin{pmatrix}
                    u_y \\ -u_x
                \end{pmatrix} \right\rangle = u_{xy} -u_{xy} = 0,
            \end{split}
        \end{equation}
        with $A = \begin{pmatrix}
            \gamma_1 & \gamma_2\\\gamma_2 & \gamma_3
        \end{pmatrix}$. It is obvious that $\det(A) > 0$ and $A$ is symmetric, so A is symmetric positive definite. It has been shown that a quasiconformal map could be uniquely determined up to Mobi\"us transformation in theorem \ref{Measurable Riemannian Mapping Theorem}, and Mobi\"us transformation can be fixed by three points. It means that we need only three points as boundary condition to solve the systems of equation (\ref{LBS}). Indeed, this process was invented by Lui \etal \cite{lui2012beltrami} which is called the Linear Beltrami Solver(LBS).

### 2021-06-11 Conclusion/Conclusion.tex
final thesis

--- 2021-04-07 template.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-% \smartqed  % flush right qed marks, e.g. at end of proof
-%
-% \let\equation\relax
-% \let\endequation\relax
-\let\proof\relax
-\let\endproof\relax
-\let\example\relax
-\let\endexample\relax
+\chapter{Conclusion and Future works} \label{conclusion}
 
-\usepackage{graphicx}
-\usepackage[margin=1in]{geometry} 
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{hyperref}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\include{snippets}
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
-\begin{document}
-
-\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
-% \subtitle{Do you have a subtitle?\\ If so, write it here}
-
-%\titlerunning{Short form of title}        % if too long for running head
-
-\author{Chenran Lin \and Lok Ming Lui}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{Chenran Lin \at
-              Department of Mathematics, The Chinese University of Hong Kong \\
-              \email{crlin@math.cuhk.edu.hk}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           Lok Ming Lui \at
-              Department of Mathematics, The Chinese University of Hong Kong\\
-              \email{lmlui@math.cuhk.edu.hk}           %  \\
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simple connected domain in this paper, named Beltrami signature.
-The proposed signature is based on conformal welding.
-We extended the welding mapping to a harmonic function.
-With suitable normalization, the uniqueness of this harmonic function is guaranteed up to a rotation.
-And finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension.
-The benifits of the proposed signature is it keeps invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformation and distortion.
-Experiments demonstrate the above properties and also show the excellent classification performance.
-\keywords{
-  Shape representation \and conformal welding \and simple connected \and invariance}
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
-\end{abstract}
-
-\section{Introduction}
-\label{intro}
-    The outline of the shape contains very important information and it can be used in many applications, such as segementation, recognition, registration and so on.
-However, even for the simplest situation, 2D simple connected shapes, it is a big challenge to describe clearly what the shape contour looks like.
-Because of the complexity of the image, there is an urgent demand to find a common, simple and robust shape representation for further mining and utilizing of shapes' geometric information.
-Therefore, many different presentations and measures have been widly studied and proposed recently \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.
-
-    Considering 2D simple connected shapes, conformal welding is a kind of well-known shape signature.
-Given 2D simple connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$.
-This gives a simple but wonderful representation of $\Omega$ as Fig.
-\ref{fig1} shows.
-However, it has two fatal defects.
-First is that such representation is not unique.
-Because of the arbitrary of Riemann conformal mapping, $\Phi_1$ and $\Phi_2$ can only be determined up to a Mobious transformation, so such conformal welding is not unique.
-Generally speaking, some assumption is required to remove this uncertainty.
-For example, Sharon \etal \cite{sharon20062d} need to select a base point $P$ inside the given domain $\Omega$ artificially, then let $\Phi_1$ maps $0$ to this point $P$.
-The work of Mcenteggart \etal \cite{mcenteggart2018uniqueness} is based on Schramm-Loewner evolution(SLE) on random surfaces called Liouville quantum gravity, they proved the equivalence between uniqueness of conformal welding and conformal removable and conculded that if the boundary curve $\eta$ is an $\text{SLE}_k$ for $k \in (0, 4)$ and satisifies some other requirements, the corresponding conformal welding is unique.
-Some may not that care the uniqueness itself, they used equivalent class to guarantee uniqueness in a broader sense or evne just ignored it \cite{katznelson1990conformal,marshall2012conformal,lui2013shape,astala2010random}.
-
-    Another thing is that even the conformal welding is very easy to be changed by simple transformations like rotation, scaling and translation.
-Such a unstable representation is hard to apply in practical applications since these transformations are inevitable in the real world.
-
-    The contribution of this paper is that we propose a brand new presentation for 2D simple connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Beltrami signature.
-Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points.
-Such conformal welding can be extended to the whole unit disk and get a harmonic function $H: \D \rightarrow \D$.
-Under suitable normalization, harmonic extension $H$ can be determined up to a rotation and the Beltrami coefficient of $H$ is then unique and becomes our Beltrami signature.
-
-    The proposed shape representation, Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
-The Beltrami signature is based on computational quasiconformal geometry.
-Computational quasiconformal geometry has been widely used in image processing and image analysis.
-Applications can be found in image segmentation
-    \cite{siu2020image,chan2018topology,zhang2020topology}
-    , image registration
-    \cite{lam2014landmark,lui2014teichmuller,ng2014computing,lui2012optimization,lam2014genus,zhang2012registration,lee2016landmark,lui2010optimized,lui2013texture,lui2010shape,lui2010optimizedc,lui2014geometric,choi2015flash}
-     and image analysis 
-    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shapec,lui2010shape3}
-    .
-What's more worth mentioning is that Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape.
-It means the proposed representation has high practical value and can be applied in computer vision work like classification, segementation and so on.
-
-    The paper is organized as follows: Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem and how Beltrami signature is obtained from given domain; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
-The paper is concluded in Section \ref{conclusion} and we point out future directions.
-
-    \begin{figure}
-        \begin{center}
-        \includegraphics[width=7.6cm]{src/fig1_down.png}
-        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simple connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
-        \end{center}
-        \label{fig1}
-    \end{figure}
-
-\section{Theoretical basis}\label{background}
-    \subsection{Quasi-conformal mapping and Beltrami equation}
-        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
-        \begin{equation*}
-            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
-        \end{equation*}
-
-        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
-        \begin{equation}\label{beltrami eq}
-            \Part{f}{\overline{z}} = \mu(z) \Part{f}{z}
-        \end{equation}
-        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$.
-More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
-        \begin{equation}
-            \mu = \frac{f_{\overline{z}}}{f_{z}}
-        \end{equation}
-        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
-        \begin{equation}
-            f^*(ds^2_E) = \abs{\Part{f}{z}}^2 \abs{dz + \mu(z)d\overline{z}}^2
-        \end{equation}
-        which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$.
-$\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality.
-In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$.
-Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
-        \begin{equation}\label{local f}
-            f(z) = f(p)+f_z(p)(z+\mu(p)\overline{z}).
-        \end{equation}
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig2.jpg}
-            \end{center}
-            \caption{(a) Shows the original hippocampus.
-(b) Shows the parameter domain with circle packing pattern.
-Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
-            \label{fig2}
-        \end{figure}
-
-        If $\mu(z)=0$ everywhere, then $f$ us called \textit{conformal} or \textit{holomorphic}. A conformal map satisfies the following well-known Cauchy-Riemann equation:
-        \begin{equation}\label{cr eq}
-            \Part{f}{\overline{z}} = 0.
-        \end{equation}
-        Inside the local parameter domain, $f$ may be considered as a map composed of a translation to $f(p)$ together with a stretch map $S(z) = z + \mu(p)\overline{z}$, which is postcomposed by multiplication of $f_z(p)$, which is conformal.
-All the conformal distortion of $S(z)$ is caused by $\mu(p)$.
-$S(z)$ is the map that causes $f$ to map a small circle to a small ellipse (see Fig.
-\ref{fig2}).
-Form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well.
-Specially, the angle of maximal magnification is $\arg(\mu(p))/2$ with magnifying factor $1+\abs{\mu(p)}$; the angle of maximal shrinkage is the orthogonal angle $\arg(\mu(p))/2 - \pi/2$ with shrinkage factor $1-\abs{\mu(p)}$.
-The distortion or dilation is given by:
-        \begin{equation}
-            K = \frac{1+\abs{\mu(p)}}{1-\abs{\mu(p)}}.
-        \end{equation}
-        Thus, the Beltrami coefficient $\mu$ gives us important information about the properties of the map (see Fig. \ref{fig3}).
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig3.jpg}
-            \end{center}
-            \caption{Quasi-conformal maps infinitesimal circles to ellipses. The Beltrami coefficient measure the distortion or dilation of the ellipse under the QC map.}
-            \label{fig3}
-        \end{figure}
-
-        Suppose $f, g: \C \rightarrow \C$ are complex-valued function with Beltrami coefficient $\mu_f, \mu_g$ respectively. Then the Beltrami coefficient for the composition $g \circ f$ is given by
-        \begin{equation}\label{mu of composition}
-            \mu_{g \circ f} = \frac{\mu_f+(\mu_g \circ f) \tau}{1+\overline{\mu_f}(\mu_g \circ f) \tau},
-        \end{equation}
-        where $\tau = \frac{\overline{f_z}}{f_z}$. Note that when $g$ is conformal, $\mu_g = 0$ and 
-        \begin{equation}\label{mu of conformal composition}
-            \mu_{g \circ f} = \mu_f.
-        \end{equation}
-
-    \subsection{Conformal welding}
-        Given 2D bounded simple connected shape, we can treat it as a boundary simple connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
-$\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobious transformation}:
-        \begin{equation}
-            M(z) = e^{i \theta} \frac{z - a}{1 - \overline{a}z}.
-        \end{equation}
-        Then we can define \textit{conformal welding} as:
-        \begin{equation}
-            f = \Phi_1^{-1} \circ \Phi_2.
-        \end{equation}
-        Such $f: \partial \D \rightarrow \partial \D$ is a diffeomorphism from $\partial \D$ to itself, which can be also thought as a periodic, real-valued monotone increasing function $f_\R: [0, 2\pi) \rightarrow [0, 2\pi)$ such that $f(e^{i \theta}) = e^{i f_\R(\theta)}$ (see Fig.
-\ref{fig1}).
-
-    \subsection{Harmonic function and Poisson integral}
-        A complex-valued function $f$ defined on $\Omega \subset \C$ is called \textit{harmonic} if it satisfies the \textit{Laplace's equation}:
-        \begin{equation}
-            \Delta f = 4 \frac{\partial^2 f}{\partial z \partial \overline{z}} = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2} = 0,
-        \end{equation}
-        where $z = x + iy$, $x$, $y$ is the real and imaginary value.
-
-        Chen \etal prove following theorem in \cite{chen2010compositions}, which tells us that the composition of harmonic mappings and other mappings can inherit such harmonicity in some condition.
-        \begin{theorem}\label{composition of harmonic}
-            Let $f$ be a harmonic mapping, $f \circ g$ is harmonic if and only if $g(z) = az + b \overline{z} + c$, where $a$, $b$ and $c$ are constaants and $g \circ f$ is harmonic if and only if $g$ is analytic or anti-analytic.
-        \end{theorem}
-
-        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}.
-For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
-            \begin{equation}\label{poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
-            \end{equation}
-        Such $H$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
-$H(e^{i\theta}) = f(e^{i\theta})$ (see Fig.
-\ref{harmonic}).
-Of course, this $H$ is unique.
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig4_down.png}
-            \end{center}
-            \caption{(a) Continious function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$.
-(b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
-Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
-            \label{harmonic}
-        \end{figure}
-
-    \section{Beltrami signature}\label{main}
-        In this chapter, we will propose a new representation, Beltrami signature, to discribe boundary simple connected domain $\Omega$.
-Our proposed signature is based on conformal welding and quasi-conformal theory.
-
-        \subsection{Beltrami signature based on conformal welding}
-            Here we give a brief explaination of how to create our new signature.
-Given the boundary simple connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it.
-Then $f$ can be extended to harmonic function $H$ defined on $\D$ by Poisson integral (\ref{poisson integral}).
-At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
-            \begin{equation}
-                B:= \mu_H = \frac{H_{\overline{z}}}{H_z}.
-            \end{equation}
-            Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $B$ is determined.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig5.png}
-                \end{center}
-                \caption{Illustration of Beltrami signature.
-(a) The input shape, a dolphin.
-(b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b).
-(c) The Beltrami signature of (a).
-Remark that the harmonic funcion and Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
-                \label{illu of BS}
-            \end{figure*}
-
-        \subsection{Analysis of uniqueness of Beltrami signature}
-            According to Riemann mapping theorem, the conformal mapings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
-Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobious transformations.
-Therefore, the corresponding conformal welding is
-            \begin{equation}
-                \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = M_1^{-1} \circ \Phi_1^{-1} \circ \Phi_2 \circ M_2 = M_1^{-1} \circ f \circ M_2.
-            \end{equation}
-
-            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{H}$. The following theorem show the relationship between $H$ and $\tilde{H}$.
-
-            \begin{theorem}
-                Suppose $f$ and $\tilde{f}$ are continious map from $\partial \D$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
-$H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
-            \end{theorem}
-
-            \begin{proof}
-                Since $M_1$ is a Mobious transformations, $M_1^{-1}$ is also a Mobious transformation, so it can be written as $M_1^{-1}(z) = e^{i \theta}\frac{z - p}{1 - \overline{p}z}$, where $\theta \in [0, 2\pi)$ and $p \in \D$.
-
-                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
-$\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
-Therefore, we have
-                \begin{equation*}
-                    e^{i \theta}\frac{z - p}{1 - \overline{p}z} = az + b \overline{z} + c,
-                \end{equation*}
-                which means $p = b = c = 0$, $a = e^{i \theta}$ and so $M_1$ is a rotation.
-
-                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ H \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}.
-It's easy to check that
-                \begin{align*}
-                    M_1^{-1} \circ H \circ M_2 (e^{i \theta})
-                    &= M_1^{-1} \circ f \circ M_2(e^{i \theta})\\
-                    &= \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
-                \end{align*}
-                which means $M_1^{-1} \circ H \circ M_2$ and $\tilde{H}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ H \circ M_2 = \tilde{H}$.
-            \end{proof}
-
-            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{H}$
-            \begin{equation}
-                \tilde{B} = \mu_{\tilde{H}} = \mu_{M_1^{-1} \circ H \circ M_2} = \mu_{H\circ M_2}.
-            \end{equation}
-            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, then we get $M_2$ is identity.
-Therefore, we know that the uniqueness of Beltrami signature is equivalent to following restrictions:
-            \begin{enumerate}
-                \item $M_1$ should be a rotation.
-                \item $M_2$ should be identity.
-            \end{enumerate}
-
-        \subsection{Normalization to $M_1$}\label{norm1}
-            We hope $M_1$ is a rotation.
-It is not that hard, for example, we can achieve it by restricting $\Phi_1(0) = 0$.
-But it need a hypothesis that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold.
-Here we want to show a new approach without any additional assumption.
-
-            In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$.
-Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, where $\Phi_1 : \D \rightarrow \Omega$.
-We claims that $M_1$ can be normalized by restricting the center of $p_i$ to $0$.
-
-            \begin{theorem}\label{unique up to a rotation}
-                Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
-                \begin{align}\label{norm phi1}
-                    \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
-                \end{align}
-                then such $\Phi_1$ is unique up to a rotation $M_1$.
-            \end{theorem}
-
-            Before proving theorem \ref{unique up to a rotation}, we can consider following problem.
-Given boundary points $p_i$ on unit circle, can we find a Mobious transformation $M$ satisfies the following equation (\ref{fz})?
-            \begin{equation}\label{fz}
-                \sum_{k=1}^n M(p_k) = \sum_{k=1}^n e^{i\theta} \frac{p_k - a}{1 - \overline{a}p_k}= 0
-            \end{equation}
-
-            Without lose of generality, we ignore the rotation of $M$ and let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-So $F_a$ is also a Mobius transformation and it's sufficient to find $a \in \D$ such that
-            \begin{equation}\label{eq}
-                f(a) = \sum_{k=1}^n F_a(p_k) = \sum_{k=1}^n \frac{p_k - a}{1 - \overline{a}p_k} = 0
-            \end{equation}
-            to show the equation (\ref{fz}) holds for some $M$. Intuitively, we believe that there is always a unique solution to this equation (\ref{eq}) (see Fig \ref{fasolvable}).
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig6.png}
-                \end{center}
-                \caption{The first row are some randomly generated points in $\partial \D$.
-The second row are the corresponding $\abs{f(a)}$, where $a \in \D$.
-The third row are also $\abs{f(a)}$ but is in top view.
-}
-                \label{fasolvable}
-            \end{figure*}
-
-            \subsubsection{The solvability of equation (\ref{eq})}
-            First thing we want to do is to check whether this equation (\ref{eq}) is always solvable. According to Brouwer fixed point theorem, we have
-
-            \begin{theorem}\label{existence}
-                Given $\{p_1, p_2, \cdots, p_n\} \subset \partial \D$ and $n \ge 3$, let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-The solution of equation (\ref{eq}) always exists.
-            \end{theorem}
-
-            \begin{proof}
-                Note that when $e^{i \theta} \neq p_k$ for any $k$, we have
-                \begin{equation*}
-                    f(e^{i \theta}) = \sum_{k=1}^n \frac{p_k - e^{i \theta}}{1 - e^{-i\theta}p_k} = - n e^{i\theta},
-                \end{equation*}
-                so $\frac{1}{n} f(e^{i\theta}) + e^{i \theta} = 0$. Let 
-                \begin{equation*}
-                    g(a) = \begin{cases}
-                \frac{1}{n} f(a) + a, a \in \D,\\
-                0, a \in \partial \D,
-                \end{cases}
-                \end{equation*}
-                such $g$ is defined on $\overline{\D}$ and is continuous. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.
-
-                Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, then define
-                \begin{equation*}
-                    h(a) = \begin{cases}
-                    g(a), &a \in  \overline{\D} \setminus M,\\
-                    \frac{g(a)}{\norm{g(a)}}, &a \in  M.
-                \end{cases}
-                \end{equation*}
-                $h$ is a continuous map from $\overline{\D}$ to itself, so there exists some $a$ let $h(a) = a$.
-
-                If $a \in \partial \D$, $\norm{a} = 1$, but $\norm{h(a)} = 0 \neq \norm{a}$.
-If $a \in M$, we know $a \notin \partial \D$, so $\norm{a} < 1$, but $\norm{h(a)} = \frac{\norm{g(a)}}{\norm{g(a)}} = 1 \neq \norm{a}$.
-So when $h(a) = a$, $a$ is inside $\D \setminus M$.
-Therefore, such $a$ satisfies $g(a) = a$ and then $f(a) = 0$.
-            \end{proof}
-
-            Therefore, there must be some $a \in \D$ to be the solution of equation (\ref{fz}).
-
-            \subsubsection{The uniqueness of the solution of equation (\ref{eq})}
-            With solvability proved, we naturally want to know if this solution is unique. Let's consider a special case when $\sum_{k=1}^n p_k = 0$, we have
-            \begin{theorem}\label{uniqueness when 0}
-                Suppose $\sum_{k=1}^n p_k = 0$, equation (\ref{eq}) holds if and only if $a = 0$.
-            \end{theorem}
-
-            \begin{proof}
-                If $a = 0$, it's obvious $F_0$ is identity, so $f(0) = \sum_{k=1}^n p_k = 0$.
-
-                If $a \neq 0$, WLOG, we can assume that $0 < a < 1$, then $F_a(1) = 1$ and $F_a(-1) = -1$.
-For any $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$,
-                \begin{align*}
-                    &F_a(p_k) \\
-                    = &F_a(\cos \theta_k + \sin \theta_k i) \\
-                    = &\frac{\cos \theta_k + \sin \theta_k i - a}{1 - a \cos \theta_k - a \sin \theta_k i} \\
-                    = &\frac{(a^2 + 1) \cos \theta_k -2a - (a^2 - 1) \sin \theta_k i}{a^2 + 1 - 2a \cos \theta_k},
-                \end{align*}
-                so
-                \begin{align*}
-                    &\Re(F_a(p_k)) \\
-                    = &\frac{(a^2 + 1) \cos \theta_k -2a}{a^2 + 1 - 2a \cos \theta_k} \\
-                    = &\cos \theta_k - \frac{2a(1-\cos^2 \theta_k)}{(a-1)^2 + 2a(1-\cos \theta_k)} \\
-                    < &\cos \theta_k = \Re(p_k).
-                \end{align*}
-
-                Therefore, if $n \ge 3$, there must be at least one $p_k \neq \pm 1$ and so
-                \begin{align*}
-                    &\Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) \\
-                    < &\sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
-                \end{align*}
-                which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $a=0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
-            \end{proof}
-
-            This theorem confirms the uniqueness for a special situation $\sum_{k=1}^n p_k = 0$ and actually this conclusion is universal no matter how $p_i$ distribute.
-
-            \begin{theorem}\label{uniqueness}
-                The solution of equation (\ref{eq}) is unique.
-            \end{theorem}
-
-            \begin{proof}
-                Assume that $a_0, a_1$ are two different solutions, then we have that
-                \begin{align*}
-                    \sum_{k=1}^n F_{a_0}(p_k) = 0,\sum_{k=1}^n F_{a_1}(p_k) = 0
-                \end{align*}
-
-                Let $p_k' = F_{a_0}(p_k)$, then
-                \begin{align*}
-                    &\sum_{k=1}^n F_{a_1} \circ F_{a_0}^{-1} \circ F_{a_0}(p_k)\\
-                    = &\sum_{k=1}^n (F_{a_1} \circ F_{-a_0})(F_{a_0}(p_k))\\
-                    = &\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}}\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0.
-                \end{align*}
-
-                Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so \\
-                $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$. According to theorem \ref{uniqueness when 0},\\
-                $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, then $a_0 = a_1$, which contradicts to the assumption.
-            \end{proof}
-
-            \subsubsection{Unque $\Phi_1$ up to a rotation}
-
-            Above theorems show that there is alway an unique solution $a \in \D$ for equation (\ref{eq}), so we can come back to theorem \ref{unique up to a rotation}.
-
-            \begin{proof}
-                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobious transformation.
-If $\Phi_1$, $\tilde{\Phi_1} $ satisfy equation (\ref{norm phi1}), let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M_1^{-1} (p_k) = 0$.
-$M_1^{-1}$ is also a Mobious transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
-                \begin{equation*}
-                    e^{i \theta} \sum_{k=1}^n F_a(p_k) = 0.
-                \end{equation*}
-
-                From theorem \ref{uniqueness when 0} we can know $a = 0$, then $M_1^{-1}(z) = e^{i \theta} z$ and $\Phi_1$ is unique up to a rotation $M_1$.
-            \end{proof}
-
-        \subsection{Normalization to $M_2$}\label{norm2}
-            As for $M_2$, we hope it is identity, which is equivalent with the uniqueness of $\Phi_2: \D^c \rightarrow \Omega^c$.
-Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this and derivative to guarantee the uniqueness.
-
-            \begin{theorem}
-                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobious transformation.
-If $\tilde{\Phi_2}, \Phi_2$ satisifies that
-                \begin{align}
-                    &\tilde{\Phi_2}(\infty) = \Phi_2(\infty) = \infty\label{norm phi2 1}\\
-                    &\argmax{z \in \partial \D} \abs{\Phi_2'(z)} = \argmax{z \in \partial \D} \abs{\tilde{\Phi_2'}(z)} = 1,\label{norm phi2 2}
-                \end{align}
-                then such $M_2$ is identity.
-            \end{theorem}
-
-            \begin{proof}
-                Suppose Mobious transformation $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$. Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisify (\ref{norm phi2 1}), then
-                \begin{align*}
-                    &\tilde{\Phi}_2(\infty) = \Phi_2(M_2(\infty)) = \infty, \\
-                    &\Phi_2(\infty) = \infty.
-                \end{align*}
-                Therefore, $M_2(\infty) = e^{i \theta} \frac{\infty - a}{1- \overline{a} \infty} = \infty$, which means that $a = 0$ and $M_2(z) = e^{i \theta} z$.
-
-                Consider the derivative of $\tilde{\Phi}_2$,
-                \begin{equation}
-                    \tilde{\Phi}_2'(z) = \Phi_2' \circ M_2(z) \cdot M_2'(z) = e^{i\theta} \Phi_2' (e^{i \theta}z),
-                \end{equation}
-                then we know that $\abs{\tilde{\Phi}_2'(z)} = \abs{\Phi_2'(e^{i \theta}z)}$.
-Suppose $a = \argmax{z \in \partial \D} |\Phi_2'(z)|$, then we will have that $ae^{-i \theta} = \argmax{z \in \partial \D} |\tilde{\Phi}_2'(z)|$.
-                If condition (\ref{norm phi2 2}) holds for both $\tilde{\Phi}_2$ and $\Phi_2$, it means $a = a e^{-i \theta} = 1$, so $a = 1$, $\theta = 0$ and $M_2$ is identity.
-            \end{proof}
-
-        \subsection{Invariance under simple transformation}
-            With the normalization mentioned above, we can get unique Beltrami signature $B$ corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$.
-Now we want to prove that if we do some simple transformation like rotation, scaling and translation to $\Omega$, the Beltrami signature is invariant.
-
-            \begin{theorem}
-                Given a boundary simple connected domain $\Omega$ and transformation $T$ which is composed by rotation, scaling and transformation.
-Let $B_\Omega$ and $B_{T(\Omega)}$ be the Beltrami signature of $\Omega$ and $T(\Omega)$, then $B_\Omega = B_{T(\Omega)}$
-            \end{theorem}
-
-            \begin{proof}
-                Suppose $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, $\tilde{\Phi}_1: \D \rightarrow T(\Omega)$ and $\tilde{\Phi}_2 : \D^c \rightarrow T(\Omega)$ are conformal.
-Since $T$ is composed by rotation, scaling and translation, $T$ can be written as $T(z) = ke^{i\theta} z + b$.
-Such $T$ is absolutely invertible and conformal.
-
-                Let $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1 : \D \rightarrow \Omega$, $\hat{\Phi}_1$ is conformal.
-Given the boundary points $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$, then $\{T(z_1), T(z_2), \cdots, T(z_n)\} \subset \partial T(\Omega)$.
-Since $\tilde{\Phi}_1$ satisifies condition (\ref{norm phi1}), we have
-                \begin{equation*}
-                    \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0.
-                \end{equation*}
-
-                Therefore
-                \begin{equation*}
-                    \sum_{i=1}^n \hat{\Phi}_1^{-1}(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1} \circ T(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0,
-                \end{equation*}
-                which means $\hat{\Phi}_1$ also satisifies condition (\ref{norm phi1}). Hence $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1= \Phi_1 \circ R$, which equals to
-                \begin{equation}
-                    \tilde{\Phi}_1 = T \circ \Phi_1 \circ R,
-                \end{equation}
-                where $R$ is a rotation.
-
-                Similarly, let $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2: \D^c \rightarrow \Omega^c$, $\hat{\Phi}_2$ is conformal. Since $\tilde{\Phi}_2(\infty) = \infty$, we have
-                \begin{equation*}
-                    \hat{\Phi}_2(\infty) = T \circ \tilde{\Phi}_2(\infty) = \infty,
-                \end{equation*}
-                which means $\hat{\Phi}_2$ satisifies condition (\ref{norm phi2 1}).
-
-                As for condition (\ref{norm phi2 2}), we know that $T'(z) = k e^{i \theta}$, so
-                \begin{equation}
-                    \hat{\Phi}_2'(z) = T' \circ \tilde{\Phi}_2(z) \cdot \tilde{\Phi}_2'(z) = k e^{i \theta} \tilde{\Phi}_2'(z).
-                \end{equation}
-                Hence $\abs{\hat{\Phi}_2'} = \abs{k}\abs{\tilde{\Phi}_2'}$, which means $\hat{\Phi}_2$ also satisifies condition (\ref{norm phi2 2}).
-Therefore, $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2 = \Phi_2$ and then
-                \begin{equation}
-                    \tilde{\Phi}_2 = T \circ \Phi_2.
-                \end{equation}
-
-                We have the conformal welding
-                \begin{equation}
-                    \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = R^{-1} \circ \Phi_1^{-1} \circ T^{-1} \circ T \circ \Phi_2 = R^{-1} \circ f.
-                \end{equation}
-                Then the harmonic extension $\tilde{H} = R^{-1} \circ H$ and 
-                \begin{equation}
-                    B_{T(\Omega)} = \mu_{\tilde{H}} = \mu_{R^{-1} \circ H} = \mu_H = B_\Omega.
-                \end{equation}
-            \end{proof}
-
-    \section{Implementation detail}\label{implementation}
-        \subsection{Zipper algorithm}
-            In oder to find an unique and stable Beltrami signature, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
-As metioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
-
-            Marshall \etal demonstrates the zipper algorithm detailedly with clear diagrams in \cite{marshall2007convergence}.
-For the convenience of readers, we gives a very brief review here.
-Given $N$ clockwise boundary points $z_1, z_2, \cdots, z_N \in \partial \Omega$, this algorithm use a series of linear fractional transformations $g_1, g_2, \cdots, g_N$ to map $z_1, z_2,\cdots, z_N$ to real axis one-by-one, and finally transfrom the upper half plane to unit disk by $g_{N+1}(z) = \frac{z-i}{z+i}$.
-Therefore, $g = g_{N+1} \circ g_N \circ \cdots \circ g_2 \circ g_1$ is a conformal mapping undisputedly and maps all these boundary points to unit circle and the domain $\Omega$ to $\D$.
-Remark that zipper algorithm is sensitive to the order of points.
-If we input the points anti-clockwise, i.e.
-$z_N, z_{N-1}, \cdots, z_1$, the zipper will give us a conformal mapping from $\Omega^c$ to $\D$.
-
-            For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputing points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$.
-For $\Phi_2 : \D^c \rightarrow \Omega^c$, we can input anti-clockwise points and get $g_{\Phi_2} : \Omega^c \rightarrow \D$.
-At the result $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-Because of the invariance of scaling, the number of boundary points $N$ is fixed as $200$ here and they are picked uniformly from the shape contour.
-
-            \begin{algorithm}[H]                           % HERE!!!!!!!!!
-            \caption{Zipper}          % give the algorithm a caption
-            \label{zipper}      % and a label for \ref{} commands later in the document
-            \begin{algorithmic}  % enter the algorithmic environment
-                \STATE \textbf{Inputs:} $z_i \in \partial \Omega$ for $i=1, 2, \cdots, N$, $N=200$. %, $\epsilon = 10^{-10}$(any very small value)
-                \STATE \textbf{Initialize:} Let $r=2$, $g_1(z) = \sqrt{\frac{z-z_2}{z-z_1}}$, $g= g_1$ and compute $p_{i,2}=g(z_i)$.
-                \WHILE{$r < N$}
-                    \STATE Pick $q = p_{r+1, r} = a + b i$, then compute $c = \frac{a}{\abs{q}^2}$, $d = \frac{b}{\abs{q}^2}$.
-                    \STATE Let $g_r(z) = \sqrt{\frac{cz}{1+dzi}}$, then $g = g_r \circ g$ and compute $p_{i, r+1} = g_r(p_{i, k})$.
-                    \STATE Let $r = r+1$.
-                \ENDWHILE
-                \STATE Let $g_{N}(z) = \left(\frac{z}{1-\frac{z}{p_{1,N}}}\right)^2$ and $g_{N+1}(z) = \frac{z-i}{z+i}$, then $g = g_{N+1} \circ g_N \circ g$ and $p_i = g_{N+1} \circ g_N(p_{i,N})$.
-                \RETURN Conformal mapping $g: \Omega \rightarrow \D$ and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-        \subsection{Harmonic extension}\label{detail harmonic}
-            After obtaining the output of zipper algorithm, $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$, the conformal welding can be represented as a series points
-            \begin{equation*}
-                (\varphi_i, \omega_i) = \left(\arg(\hat{\Phi}_2^{-1}(z_i)), \arg(\hat{\Phi}_1^{-1}(z_i))\right),
-            \end{equation*}
-            where $\varphi_i, \omega_i \in [0, 2\pi)$. So in fact we should use discrete form Poisson integral to extend $f$ to a harmonic mapping $H$ on the unit disk
-            \begin{equation}\label{discrete poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi} \sum_{j=1}^k \frac{(1-r^2) e^{i \omega_j} \gamma_j}{1 - 2 r cos (\varphi_j - \theta) + r^2} ,
-            \end{equation}
-            where $\gamma_j = (\varphi_{j} - \varphi_{j-1}) \bmod{ 2\pi}$ and $\varphi_0 = \varphi_k$ and this $\bmod$ can solve some critical value problem, for example, $\varphi_j = 0$ but $\varphi_{j-1} = 6$.
-For the convenience of computation, we only calculate the value of $H$ on a grid
-            \begin{align*}
-                G = \{z=x+iy \mid &\abs{z} \le 1, x=\frac{j}{100}, y=\frac{k}{100},\\
-                &j,k=-100,-99,\cdots,99,100 \}.
-            \end{align*}
-
-        \subsection{Normalization}
-            Because of the arbitrariness of the comformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
-            \begin{equation*}
-                \tilde{H} = M_1 \circ H \circ M_2.
-            \end{equation*}
-            Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then Beltrami signature $B$ can be unique.
-This section will tells how to satisfy equation (\ref{norm phi1}), (\ref{norm phi2 1}) and (\ref{norm phi2 2}) from the output of zipper algorithm.
-
-            To normalization $M_1$, we need to solve equation (\ref{eq}).
-Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concerntrate around a point.
-At that time, $\abs{f(a)} \approx 1$ almost everywhere and the solution of (\ref{eq}) is also very close to the point.
-This means the solution is quite unstable and hard to converge for common algorithms(see Fig \ref{original distribution}).
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig7_down.png}
-                \end{center}
-                \caption{(a) The $p_i \in \partial \D$ gather in a small neiborhood around their arithmetic mean $p_c$, which is labeled in red.
-(b) The corresponding $\abs{f(a)}$ for these $p_i$.
-It's worth to metion that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
-                \label{original distribution}
-            \end{figure}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig8_down.png}
-                \end{center}
-                \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment. (b) The $\abs{f(a)}$.}
-            \end{figure}
-
-            Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobious transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
-For the $r$-th iteration, let
-            \begin{equation*}
-                p_{c,r} = \frac{\sum_{i=1}^k p_{i,r}}{k} \in \D
-            \end{equation*}
-            as the arithmetic center of $p_{i,r} \in \partial \D$.
-Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobious transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
-            \begin{equation*}
-                p_{i,r+1} = F_{p_{c,r}}(p_{i,r}) = \frac{p_{i,r} - p_{c,r}}{1 - \overline{p_{c,r}}p_{i,r}}.
-            \end{equation*}
-            Note that we set $p_{i,0} = p_{i}$ at the beginning.
-Repeat this iteration for $r$ times until the center of boundary points is close to $0$, then the distribution is sufficiently regular and $\Phi_1$ becomes
-            \begin{equation}
-                \tilde{\Phi}_1 = \Phi_1 \circ F_{p_{c,0}}^{-1} \circ F_{p_{c,1}}^{-1} \circ \cdots \circ F_{p_{c,r}}^{-1}.
-            \end{equation}
-            Now equation (\ref{eq}) can be solved without much effort by Newtown's method. Suppose $a \in \D$ is the optimal solution and let 
-            \begin{equation*}
-                F_{\Phi_1} = F_a \circ F_{p_{c,r}} \circ F_{p_{c,r-1}} \circ \cdots \circ F_{p_{c, 0}}
-            \end{equation*}
-            and the final conformal mapping satisfying (\ref{norm phi1}) is
-            \begin{equation}
-                \hat{\Phi}_1 = \tilde{\Phi}_1 \circ F_{a}^{-1} = \Phi_1 \circ F_{\Phi_1}^{-1}
-            \end{equation}
-
-            \begin{algorithm}[H]
-            \caption{Normalize $M_1$}
-            \label{alg norm phi1}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} $\Phi_1$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $\epsilon=0.2$.
-                \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$, $F_{\Phi_1} = id$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$.
-%and $M_{p_{c,0}}(z) = \frac{z-p_{c,0}}{1- \overline{p_{c, 0}}z}$
-                \WHILE{$\abs{p_c,r} > \epsilon$}
-                    \STATE Let $F_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $\Phi_1 = \Phi_1 \circ F_{p_{c,r}}^{-1}$.
-                    \STATE Compute $F_{\Phi_1} = F_{p_{c,r}} \circ F_{\Phi_1}$, $p_{i, r+1} = F_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
-                    \STATE Let $r = r+1$.
-                \ENDWHILE
-                \STATE Solve equation (\ref{eq}) by Newtown's method and get solution $a \in \D$.
-                \STATE Let $F_a(z) = \frac{z-a}{1- \overline{a}z}$, $F_{\Phi_1} = F_a \circ F_{\Phi_1}$ and $\hat{\Phi}_1 = \Phi_1 \circ F^{-1}_{a}$.
-                \STATE Compute $p_i = F_a(p_{i,r})$.
-                \RETURN Mobious transformation $F_{\Phi_1}$, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig9.png}
-                \end{center}
-                \caption{The iteration of distribution adjustment. The boundary points are blue and their arithmetic center is red in each picture. (a)-(d) The 1st, 3rd, 7th, 12th iteration.}
-            \end{figure*}
-
-            As for the normalization of $M_2$, it's much easier.
-For requirement (\ref{norm phi2 1}), we only need to map $\infty$ to $\infty$ by replace $\Phi_2$ with $\tilde{\Phi}_2(z)=\Phi_2 \circ F^{-1}_{b}(\frac{1}{z})$, where $b = \Phi_2^{-1}(\infty)$.
-Another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
-According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
-Here we select $M = 10^5$ points uniformly from $[0, 2\pi)$ as $\theta_j = \frac{2 j \pi}{M}$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}).
-Therefore, the maximal solution $\theta_{\max} = \argmax{j \in [0,10^5)} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ can be used to normalize the rotation and the final mapping is
-            \begin{equation}
-                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
-            \end{equation}
-            where $M_{\Phi_2}(z) = e^{i \theta_{max}} \frac{z-b}{1 - \overline{b}z}$.
-
-            \begin{algorithm}[H]
-            \caption{Normalize $M_2$}
-            \label{alg norm phi2}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} $\Phi_2$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $M=10^5$.
-                \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$.
-                \STATE Let $M_b(z) = \frac{z-b}{1-\overline{b}z}$ and $\tilde{\Phi}_2(z)=\Phi_2 \circ M^{-1}_{b}(\frac{1}{z})$.
-                \STATE Calculate $\abs{\tilde{\Phi}_2'}$ by chain derative rule.
-                \STATE Let $\theta_j = \frac{2\pi}{M}(j-1)$ for $j=1,2, \cdots, M$.
-                \STATE Compute $\abs{\tilde{\Phi}_2'}(e^{i \theta_j})$.
-                \STATE Find maximal value and corresponding $\theta_{max}$.
-                \STATE Let $\hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z)$ and compute $p_i = \frac{e^{-i \theta_{max}}}{M_b(p_i)}$.
-                \RETURN Conformal mapping $\hat{\Phi}_2: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=.76cm]{src/fig10.png}
-                \end{center}
-                \caption{The change of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ for different $\theta_j \in [0, 2\pi)$.
-It shows this function has a significant maximum and $\theta_{max}$ is about $1.25\pi$.}
-                \label{derative}
-            \end{figure}
-
-            After obatining Mobious transformations $F_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
-            \begin{align*}
-                \hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}
-            \end{align*}
-            and it is unique up to a rotation.
-
-        \subsection{Summary of the Algorithm}
-            The totally algorithm is as following.
-            \begin{algorithm}[H]
-            \caption{Calculate Beltrami signature}
-            \label{alg all}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} Bounded simple connected shape $\Omega \subset \C$, $N=200$.
-                \STATE Pick $N$ clockwise points $z_1, z_2, \cdots, z_N$ from $\partial \Omega$ uniformly.
-                \STATE Input $z_1, z_2, \cdots, z_N$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_1}: \D \rightarrow \Omega$ and $p_{i,1} \in \partial\D$.
-                \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$. %and 
-                \STATE Input $z_N, \cdots, z_2, z_1$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_2}: \D \rightarrow \Omega^c$ and $p_{i,2} \in \partial\D$.
-                \STATE Let $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-                \STATE Let $f = \Phi_1^{-1} \circ \Phi_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
-                \STATE Extend $f$ to $H$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
-                \STATE Input $\Phi_1$ and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get $F_{\Phi_1}$.
-                \STATE Input $\Phi_2$ and $p_{i,2}$ to Algorithm \ref{alg norm phi2}, then get $M_{\Phi_2}$.
-                \STATE Calculate normalized harmonic extension $\hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}$.
-                \STATE Calculate Beltrami coefficient $B$ of $\hat{H}$.
-                \RETURN Beltrami signature $B$.
-            \end{algorithmic}
-            \end{algorithm}
-    \section{Experimental result}\label{result}
-        In this section, we will validate key properties of our proposed Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
-Besides that, a good shape representation should keep the similarity with the same kind shape and is significantly different from different kinds of shape.
-
-        Before showing results, what needs illustration is that the distance we used to measure the difference of Beltrami signature is based on $L^2$ norm,
-        \begin{equation}\label{bs dis}
-            d(B_1, B_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{B_1(z_i) - B_2(z_i)}^2},
-        \end{equation}
-        where $B_1, B_2$ are two different Beltrami signature, $z_i \in \D$ is the face center of triangluar mesh $M$ metioned in Section \ref{detail harmonic} and $N=60962$ here.
-        \subsection{Invariance}\label{sec inv}
-            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate Beltrami signature after sacling, translation and rotation and compare them with the original shape's Beltrami signature.
-The result is displayed in Fig \ref{inv}.
-In this figure, the first column are the sets of boundary points and we remark them as $\Omega_a$ to $\Omega_f$.
-The second column are the corresponding Beltrami signatures $B_a$ to $B_f$.
-Note that all the Beltrami signatures are shown in modulus, i.e.
-$\abs{B_n}$ for row $n$, and in top view.
-And the third column(if have) are the histograms of the difference between original shape's Beltrami signature, i.e.
-$\abs{B_n - B_a}$ for row $n$.
-
-            Row b and c are about scaling, the shapes are $\Omega_b = \{z \mid z = 1.5 z_a, z_a \in \Omega_a \}$ and $\Omega_c = \{z \mid z = 0.5 z_a, z_a \in \Omega_a \}$ and the distance are $d(B_a, B_b) = 5.5647 \times 10^{-8}$ and $d(B_a, B_c) = 5.3476 \times 10^{-8}$.
-Row d is about translation, the shape $\Omega_d = \{z \mid z = z_a+100+20i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_d) = 4.7817 \times 10^{-8}$.
-Row e is about rotation, the shape is $\Omega_e = \{z \mid z = e^{0.2\pi i} z_a, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.2144 \times 10^{-8}$.
-Row f is the combination of scaling, tanslation and rotation, the shape is $\Omega_e = \{z \mid z = 3e^{-0.85\pi i} z_a+350+600i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.7635 \times 10^{-8}$.
-These confirm the invariance of Beltrami signature and scaling, translation and rotation.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/inv.png}
-                \end{center}
-                \caption{Beltrami signature under scaling, translation and rotation.}
-                \label{inv}
-            \end{figure*}
-
-        \subsection{Robustness}
-            Similar with Section \ref{sec inv}, here we still treat the dolphin as the original shape and modify some small parts of it and Fig \ref{robust} is the result.
-It shows that the proposed signature is robust and stable and will not have a big mutation cauesd by small disturbance.
-
-            Row g, h and i are result about modification.
-These shapes are generated by removing or adding something, which is in the red circle.
-We can see that Beltrami signatures have slight differences from $B_a$ but are still similar in general.
-And this figure also demonstrates that the bigger the modification part is, the more different the Beltrami signature is.
-For example in row i, losing a half of the tail makes the signature has a marked change.
-Quantitatively, $d(B_a, B_g) = 0.0132$, $d(B_a, B_h) = 0.0316$ and $d(B_a, B_i) = 0.1761$.
-
-            Row j is for distortion. This dolphin is only enlarged in horizontally and becomes fatter, then the $B_j$ moves a little bit and $d(B_a, B_j) = 0.0724$.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/robust.png}
-                \end{center}
-                \caption{Beltrami signature under small modification}
-                \label{robust}
-            \end{figure*}
-
-        \subsection{Classification with Beltrami signature}
-            Above properties ensure the proposed signature having the ablity to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.
-
-            To compare the classification performance, we also use conformal welding directly to classify, and the distance is defined as
-            \begin{equation}\label{welding dis}
-                d_c(f_1, f_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{f_1(z_i) - f_2(z_i)}^2},
-            \end{equation}
-            where $f_1, f_2$ are two different conformal welding, $N=200$ here.
-
-            We prepare 3 kinds of animals, fish, giraffe and elephant.
-There are 3 images for each group so 9 images in total.
-From Fig \ref{classification images}, we can find that each class share similar Beltrami signatures and conformal welding.
-From Fig \ref{dis matrix}, the inter-class distance of Beltrami signature is awlays less than 0.2 while the intra-class distance is greater than 0.2.
-But for conformal welding, the data is messy, for example, fish 3 thinks itself is very different from other fishes but looks most like giraffe 2.
-After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the Beltrami signature shows powerful classification ablity.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/figs.png}
-                \end{center}
-                \caption{These 3 rows are elephant, fish and giraffe. In each subfigure, the top left is the input shape, bottom left is the conformal welding and the right is Beltrami signature.}
-                \label{classification images}
-            \end{figure*}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/distance_down.png}
-                \end{center}
-                \caption{(a) The distance matrix of Beltrami signatures of above 9 shapes by equation (\ref{bs dis}). (b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
-                \label{dis matrix}
-            \end{figure}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/mds_down.png}
-                \end{center}
-                \caption{(a) The MDS result of Beltrami signature. (b) The MDS result of conformal welding.}
-                \label{mds1}
-            \end{figure}
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/mds2.png}
-                \end{center}
-                \caption{(a) The MDS result of Beltrami signature.
-(b) The MDS result of conformal welding.
-(c) The clustering result of Beltrami signature.
-(d) The clustering results of conformal welding.}
-                \label{mds2}
-            \end{figure*}
-
-        \subsection{Classification for more classes}
-            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabit.
-We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes.
-The MDS and clustering results based on Beltrami signature and conformal welding are displayed in Fig \ref{mds2}.
-The classification accuracy based on Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
-
-    \section{Conclusion}\label{conclusion}
-        In this paper, we propose a novel shape representation for 2D bounded simple connected objects called Beltrami signature.
+In this thesis, we propose a novel shape representation for 2D bounded simply-connected objects called Harmonic Beltrami signature.
 The proposed signature is based on conformal welding but overcome a key shortcoming that it can be uniquely determined by the given shape.
 What's more exciting is that the proposed representation is invariance under scaling, translation and rotation.
-For slight deformation and distortion, Beltrami signature keeps roubost and only changes within a reasonable small range.
-Therefore, there are reasons to believe the it does have ablity to represent some invariant geometrical features.
-The experimental results also confirm that the Beltrami signature has excellent performance in multi-classification tasks.
+For slight deformation and distortion, HBS keeps robust and only changes within a reasonable small range.
+Therefore, there are reasons to believe the it does have ability to represent some invariant geometrical features.
+The experimental results also confirm that the HBS has excellent performance in multi-classification tasks.
 
 Although our work has achieved relatively good results, the proposed representation still have some limitations.
-Firstly, the Beltrami signature is only applicable to simple connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world.
-So we are eager for a feasible method to extend our Beltrami signature to multi connected situation.
-Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangluar mesh, which consumes a lot of time.
-Therefore, a fast algorithm to obatin this signature avoiding dense mesh is of high priority in our future work.
-Thirdly, when normalizing the conformal mapping $\Phi_2$ from exterior of unit disk to exterior of the domain, the position where the derivation of $\Phi_2$ reaches the maximum value is used to adjust the rotation.
-We trust this point in the original image has a certain geometric meaning, whereas it is not clear at present.
+Firstly, the HBS is only applicable to simply-connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world.
+So we are eager for a feasible method to extend our HBS to multi connected situation.
+Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangular mesh, which consumes a lot of time.
+Therefore, a fast algorithm to obtain this signature avoiding dense mesh is of high priority in our future work.
 
-        In summary, we will focus on third marjor directions in the future.
-One is that the deeper meaning of Beltrami signature is worth digging and then a multi-connected version of representation based on this work can be proposed.
-Another is that if the Beltrami signature contains some geometrical features of shapes, we can also extract them directly from images and generate the Beltrami signature again.
+In summary, we will focus on three major directions in the future.
+One is that the deeper meaning of HBS is worth digging and then a multi-connected version of representation based on this work can be proposed.
+Another is that if the HBS contains some geometrical features of shapes, we can also extract them directly from images and generate the HBS again.
 Hence the deep learning theory may help us to compute this signature from given images immediately, which is very likely to improve algorithm speed performance greatly.
-A third direction is this representation can be used in more applications like segementation, registration and so on.
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
-% \section*{Conflict of interest}
-%
-% The authors declare that they have no conflict of interest.
-
-% BibTeX users please use one of
-% \bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
-\bibliography{cite}
-% Non-BibTeX users please use
-% \begin{thebibliography}{}
-% %
-% % and use \bibitem to create references. Consult the Instructions
-% % for authors for reference list style.
-% %
-% \bibitem{RefJ}
-% % Format for Journal Reference
-% Author, Article title, Journal, Volume, page numbers (year)
-% % Format for books
-% \bibitem{RefB}
-% Author, Book title, page numbers. Publisher, place (year)
-% % etc
-% \end{thebibliography}
-
-\end{document}
-% end of file template.tex
+A third direction is this representation can be used in more applications like segmentation, registration and so on.

### 2021-06-11 HBS/hbs.tex
final thesis

--- 2021-05-24 paper.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-% \smartqed  % flush right qed marks, e.g. at end of proof
-%
-% \let\equation\relax
-% \let\endequation\relax
-\let\proof\relax
-\let\endproof\relax
-\let\example\relax
-\let\endexample\relax
+\chapter{Harmonic Beltrami signature (HBS)}\label{main}
+In this chapter, we describe our proposed shape signature, called the {\it Harmonic Beltrami signature (HBS)}, to represent a simply-connected domain $\Omega$.
+The space of HBS inherits a natural metric, so that geometric distance between two shapes can be easily measured.
+In the following sections, the definition of HBS and some of its theoretical analysis are addressed.
 
-\usepackage{graphicx}
-\usepackage[margin=1in]{geometry} 
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{hyperref}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\include{snippets}
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
-\begin{document}
-
-\title{Harmonic Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
-% \subtitle{Do you have a subtitle?\\ If so, write it here}
-
-%\titlerunning{Short form of title}        % if too long for running head
-
-\author{Chenran Lin \and Lok Ming Lui}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{Chenran Lin \at
-              Department of Mathematics, The Chinese University of Hong Kong \\
-              \email{crlin@math.cuhk.edu.hk}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           Lok Ming Lui \at
-              Department of Mathematics, The Chinese University of Hong Kong\\
-              \email{lmlui@math.cuhk.edu.hk}           %  \\
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simply-connected domains in this paper, named the Harmonic Beltrami signature.
-The proposed signature is based on the extension of the conformal welding map of a unit circle $S^1$ to a harmonic function of a unit disk $\D$.
-With suitable normalization, the uniqueness of this harmonic function is guaranteed up to a rotation.
-And finally quasi-conformal theory helps get rid of the only uncertainty by computing the Beltrami coefficient of harmonic extension.
-The benifit of the proposed signature is that it keeps to be invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformations and distortions.
-Experiments demonstrate the above properties and also show the excellent classification performance.
-\keywords{
-  Shape representation \and conformal welding \and simply-connected \and invariance}
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
-\end{abstract}
-
-\section{Introduction}
-\label{intro}
-    The outline of a shape contains important information, which can be used in many applications, such as medical image analysis, image segmentation, recognition, registration and so on.
-Nevertheless, it is a big challenge to define a robust descriptor for the space of shapes, even for the simplest situation of 2D simply-connected objects.
-In order to manipulate shapes and utilize their geometric information, there is an urgent demand to find a simple and robust representation to mathematically describe shape contours.
-The shape representation should also inherits a natural metric to measure geometric differences between two shape representations.
-With the geometric dissimilarity metric, two shapes can be quantitatively compared and prior shape information can be incorporated into various imaging models by adding a penalty term to further improve the accuracy.
-Due to its significance, this problem has been widely studied and different models to build the metric shape space have been proposed.
-    % \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.
-
-    Considering 2D simply-connected shapes, conformal welding is a kind of well-known shape signature.
-Given 2D simply-connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$.
-This gives a simple but wonderful representation of $\Omega$ as Fig.
-\ref{fig1} shows.
-However, it has two fatal defects.
-First is that such representation is not unique.
-Because of the arbitrary of Riemann conformal mapping, $\Phi_1$ and $\Phi_2$ can only be determined up to a Mobious transformation, so such conformal welding is not unique.
-Generally speaking, some assumption is required to remove this uncertainty.
-For example, Sharon \etal \cite{sharon20062d} need to select a base point $P$ inside the given domain $\Omega$ artificially, then let $\Phi_1$ maps $0$ to this point $P$.
-The work of Mcenteggart \etal \cite{mcenteggart2018uniqueness} is based on Schramm-Loewner evolution(SLE) on random surfaces called Liouville quantum gravity, they proved the equivalence between uniqueness of conformal welding and conformal removable and conculded that if the boundary curve $\eta$ is an $\text{SLE}_k$ for $k \in (0, 4)$ and satisfies some other requirements, the corresponding conformal welding is unique.
-Some may not that care the uniqueness itself, they used equivalent class to guarantee uniqueness in a broader sense or evne just ignored it \cite{katznelson1990conformal,marshall2012conformal,lui2013shape,astala2010random}.
-
-    Another thing is that even the conformal welding is very easy to be changed by simple transformations like rotation, scaling and translation.
-Such a unstable representation is hard to apply in practical applications since these transformations are inevitable in the real world.
-
-    The contribution of this paper is that we propose a novel presentation for 2D simply-connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Harmonic Beltrami signature.
-Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points.
-Such conformal welding can be extended to the whole unit disk and get a harmonic function $H: \D \rightarrow \D$.
-Under suitable normalization, harmonic extension $H$ can be determined up to a rotation and the Beltrami coefficient of $H$ is then unique and becomes our Harmonic Beltrami signature.
-
-    The proposed shape representation, Harmonic Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
-The Harmonic Beltrami signature is based on computational quasi-conformal geometry.
-Computational quasi-conformal geometry has been widely used in image processing and image analysis.
-Applications can be found in image segmentation
-    \cite{siu2020image,chan2018topology,zhang2020topology}
-    , image registration
-    \cite{lam2014landmark,lui2014teichmuller,ng2014computing,lui2012optimization,lam2014genus,zhang2012registration,lee2016landmark,lui2010optimized,lui2013texture,lui2010shape,lui2010optimizedc,lui2014geometric,choi2015flash}
-     and image analysis 
-    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shape,lui2010shape3}
-    .
-What's more worth mentioning is that Harmonic Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape.
-It means the proposed representation has high practical value and can be applied in computer vision work like classification, segmentation and so on.
-
-    The paper is organized as follows: Section \ref{related work} reviews some related topics about shape representation; Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem and how Harmonic Beltrami signature is obtained from given domain; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
-The paper is concluded in Section \ref{conclusion} and we point out future directions.
-
-    \begin{figure}
-        \begin{center}
-        \includegraphics[width=7.6cm]{src/fig1_down.png}
-        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simply-connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
-        \end{center}
-        \label{fig1}
-    \end{figure}
-
-\section{Contributions}
-The contributions of this paper can be summarized as follows.
-\begin{enumerate}
-    \item Firstly, we propose a new shape signature, called the Harmonic Beltrami signature, to effectively represent 2D simply-connected shapes.
-Every shape has a unique Harmonic Beltrami signature.
-Conversely, given a Harmonic Beltrami signature, its corresponding shape can be determined up to a translation, rotation and scaling.
-    \item Secondly, the proposed Harmonic Beltrami signature solves the issue of conformal ambiguities facing the conformal welding signature.
-    \item Thirdly, we propose a practical procedure to normalize the Harmonic Beltrami signature to handle the non-uniqueness issue, with rigorous theoretical justifications.
-    \item Fourthly, we propose a reconstruction algorithm to construct the corresponding shape from the Harmonic Beltrami signature up to a rotation, translation and scaling.
-This allows us to go back and fro between shapes and Beltrami signatures in the imaging model.
-    \item Finally, the proposed Harmonic Beltrami signature inherits a simple metric, namely, the $L^2$ distance, to measure the geometric dissimilarity between shapes.
-We have applied the shape distance to shape classification and shown satisfactory results.
-\end{enumerate}
-
-\section{Related works}\label{related work}
-    Shape representation and description is an enduring field and there have been extensive and in-depth discussions in the past several decades.
-Demisse \etal \cite{demisse2017deformation} proposed a method to represent an ordered set of points sampled from a curved shape as an element of a finite dimensional matrix Lie group.
-Mokhtarian \etal \cite{mokhtarian1997efficient} use the maxima of curvature zero-crossing contours of Curvature Scale Space image to represent the shapes of object boundary contours.
-Lui \etal \cite{lui2013shape} extracted each component of a 2D multi-connected shape, then the conformal weldings represent all components and conformal modules describe relationships between components.
-
-    A more meticulous survery about shape representations can be found in \cite{zhang2004review}.
-Generally speaking, all of these representation techniques can be divided into two major categories, \textit{contour-based} methods and \textit{region-based} methods, depending on whether shape features are extracted from the contour only or from the whole shape region.
-
-    \subsection{Contour-based methods}
-        As its name suggests, this kind of representations only exploits the information providing by shape boundary.
-A very natural idea is that the boundary can be taken as a whole, from which a multi-dimensional numeric feature vector can be calculated and becomes the demanded representation.
-
-        The simplest features are area, circularity, curvature and so on and their combination can be used as shape representation.
-Peura \etal \cite{peura1997efficiency} proposed such descriptor including convexity, ratio of principle axis, circular variance and elliptic variance.
-Belongie \etal \cite{belongie2002shape} tried in a different way and build a representation based on Hausdorff distance, called shape contexts.
-For any boundary point $p$, they calculated the Hausdorff distance $d_{pq}$ and the orientation $\theta_{pq}$ with any other boundary point $q$, then these $d_{pq}$ and $\theta_{pq}$ are quantized to create a histogram map $H_p$ which is used to represent the point $p$.
-All the histogram $H_p$ is flattened and concatenated to form the context of the shape.
-Asada \etal \cite{asada1986curvature} attempted to smooth the boundary by Gaussian filter and second derivatives of Gaussian filter and the inflection points that remain are expected to be significant object characteristics.
-
-        Some other contour-based representations pay more attention to local boundary information and broke the shape down into many pieces.
-Chain code describes an object by a sequence of unit-size line segments with a given orientation, which was introduced by Freeman \etal \cite{freeman1961encoding}.
-Berretti \etal \cite{berretti2000retrieval} extended the model.
-The curvature zero-crossing points from a Gaussian smoothed boundary are used to obtain smooth curve, called tokens.
-The feature for each token is its maximum curvature and its orientation, and the similarity between two tokens is measured by the weighted Euclidean distance.
-
-    \subsection{Region-based methods}
-        Different from the previous category, region-based representations make the best use of all the pixels within the given shape region.
-Geometric moment is a classical and representative region-based shape description with form
-        \begin{equation*}
-            m_{pq} = \sum_x \sum_y x^p y^q f(x, y),
-        \end{equation*}
-        where $p, q = 0, 1, 2, \cdots$ and $f$ is the given shape.
-Hu published the first significant paper about geometric moment and applied it in pattern recognition \cite{hu1962visual}.
-Taubin \etal \cite{taubin1991object,taubin1991recognition} proposed algebraic moment, which is computed from the first $m$ central moments and is given as the eigenvalues of predefined matrices, $M_{[j; k]}$, whose elements are scaled factors of the central moments.
-Zhang \etal \cite{zhang2002generic} proposed Generic Fourier descriptor which is acquired by applying a 2D Fourier transform on a polar-raster sampled image
-        \begin{equation*}
-            PF_2(\rho, \phi) = \sum_r \sum_k f(r, \theta_k) e^{2 \pi i (\frac{r}{R} \rho + \theta_k \phi)},
-        \end{equation*}
-        where $0 \le r < R$, $0 \le \rho < R$, $0 \le k < T$, $0 \le \phi < T$, $\theta_k = \frac{2\pi k}{T}$ and $R, T$ are the radial frequency resolution and angular frequency resolution respectively
-
-\section{Theoretical basis}\label{background}
-    \subsection{Quasi-conformal mapping and Beltrami equation}
-        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
-        \begin{equation*}
-            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
-        \end{equation*}
-
-        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
-        \begin{equation}\label{beltrami eq}
-            \Part{f}{\overline{z}} = \mu(z) \Part{f}{z}
-        \end{equation}
-        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$.
-More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
-        \begin{equation}
-            \mu = \frac{f_{\overline{z}}}{f_{z}}
-        \end{equation}
-        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
-        \begin{equation}
-            f^*(ds^2_E) = \abs{\Part{f}{z}}^2 \abs{dz + \mu(z)d\overline{z}}^2
-        \end{equation}
-        which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$.
-$\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality.
-In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$.
-Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
-        \begin{equation}\label{local f}
-            f(z) = f(p)+f_z(p)(z+\mu(p)\overline{z}).
-        \end{equation}
-
-        % \begin{figure}
-        %     \begin{center}
-        %         \includegraphics[width=7.6cm]{src/fig2.jpg}
-        %     \end{center}
-        %     \caption{(a) Shows the original hippocampus.
-(b) Shows the parameter domain with circle packing pattern.
-Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
-        %     \label{fig2}
-        % \end{figure}
-
-        If $\mu(z)=0$ everywhere, then $f$ us called \textit{conformal} or \textit{holomorphic}. A conformal map satisfies the following well-known Cauchy-Riemann equation:
-        \begin{equation}\label{cr eq}
-            \Part{f}{\overline{z}} = 0.
-        \end{equation}
-        Inside the local parameter domain, $f$ may be considered as a map composed of a translation to $f(p)$ together with a stretch map $S(z) = z + \mu(p)\overline{z}$, which is postcomposed by multiplication of $f_z(p)$, which is conformal.
-All the conformal distortion of $S(z)$ is caused by $\mu(p)$.
-$S(z)$ is the map that causes $f$ to map a small circle to a small ellipse.
-Form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well.
-Specially, the angle of maximal magnification is $\arg(\mu(p))/2$ with magnifying factor $1+\abs{\mu(p)}$; the angle of maximal shrinkage is the orthogonal angle $\arg(\mu(p))/2 - \pi/2$ with shrinkage factor $1-\abs{\mu(p)}$.
-The distortion or dilation is given by:
-        \begin{equation}
-            K = \frac{1+\abs{\mu(p)}}{1-\abs{\mu(p)}}.
-        \end{equation}
-        Thus, the Beltrami coefficient $\mu$ gives us important information about the properties of the map (see Fig. \ref{fig3}).
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig3.png}
-            \end{center}
-            \caption{Quasi-conformal maps infinitesimal circles to ellipses. The Beltrami coefficient measure the distortion or dilation of the ellipse under the QC map.}
-            \label{fig3}
-        \end{figure}
-
-        Note that there is a one-to-one correspondence between the quasi-conformal mapping f and its Beltrami coefficient $\mu$.
-Given $f$, there exists a Beltrami coefficient $\mu$ satisfying the Beltrami equation.
-Conversely, the following theorem states that given an admissible Beltrami coefficient $\mu$, there always exists an quasi-conformal mapping $f$ associating with this $\mu$.
-
-        \begin{theorem}[Measurable Riemannian Mapping Theorem]\label{Measurable Riemannian Mapping Theorem}
-            Suppose $\mu : \C \rightarrow \C$ is Lebesgue measurable satisfying $\abs{\mu}_\infty <1$; then, there exists a quasi-conformal homeomorphism $f$ from $\C$ onto itself, which is in the Sobolev space $W_{1,2}(\C)$ and satisfies the Beltrami equation in the distribution sense.
-The associated quasi-conformal homeomorphism $f$ is unique up to a Mobious transformation.
-Furthermore, by fixing $0$, $1$ and $\infty$, the $f$ is uniquely determined.
-        \end{theorem}
-
-        Suppose $f, g: \C \rightarrow \C$ are complex-valued function with Beltrami coefficient $\mu_f, \mu_g$ respectively. Then the Beltrami coefficient for the composition $g \circ f$ is given by 
-        \begin{equation}\label{mu of composition}
-            \mu_{g \circ f} = \frac{\mu_f+(\mu_g \circ f) \tau}{1+\overline{\mu_f}(\mu_g \circ f) \tau},
-        \end{equation}
-        where $\tau = \frac{\overline{f_z}}{f_z}$. Note that when $g$ is conformal, $\mu_g = 0$ and 
-        \begin{equation}\label{mu of conformal composition}
-            \mu_{g \circ f} = \mu_f.
-        \end{equation}
-
-    \subsection{Conformal welding}\label{welding}
-        Given 2D bounded simply-connected shape, we can treat it as a boundary simply-connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
-$\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobious transformation}:
-        \begin{equation}
-            M(z) = e^{i \theta} \frac{z - a}{1 - \overline{a}z}.
-        \end{equation}
-        Then we can define \textit{conformal welding} as:
-        \begin{equation}
-            f = \Phi_1^{-1} \circ \Phi_2.
-        \end{equation}
-        Such $f: \partial \D \rightarrow \partial \D$ is a diffeomorphism from $\partial \D$ to itself, which can be also thought as a periodic, real-valued monotone increasing function $f_\R: [0, 2\pi) \rightarrow [0, 2\pi)$ such that $f(e^{i \theta}) = e^{i f_\R(\theta)}$ (see Fig.
-\ref{fig1}).
-
-        However, such welding mappings are not unique because of the arbitrariness of Riemann mappings, as shown in Fig. \ref{unsatble}.
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/unstable welding.png}
-            \end{center}
-            \caption{Different conformal welding mappings (b), (c) and (d) of the same shape (a)}
-            \label{unsatble}
-        \end{figure}
-
-    \subsection{Harmonic function and Poisson integral}
-        A complex-valued function $f$ defined on $\Omega \subset \C$ is called \textit{harmonic} if it satisfies the \textit{Laplace's equation}:
-        \begin{equation}
-            \Delta f = 4 \frac{\partial^2 f}{\partial z \partial \overline{z}} = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2} = 0,
-        \end{equation}
-        where $z = x + iy$, $x$, $y$ is the real and imaginary value.
-
-        Chen \etal prove following theorem in \cite{chen2010compositions}, which tells us that the composition of harmonic mappings and other mappings can inherit such harmonicity in some condition.
-        \begin{theorem}\label{composition of harmonic}
-            Let $f$ be a harmonic mapping, $f \circ g$ is harmonic if and only if $g(z) = az + b \overline{z} + c$, where $a$, $b$ and $c$ are constants and $g \circ f$ is harmonic if and only if $g$ is analytic or anti-analytic.
-        \end{theorem}
-
-        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}.
-For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continuous $f$ on $\partial \D$
-            \begin{equation}\label{poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
-            \end{equation}
-        Such $H$ is harmonic on $\D$ and continuous on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
-$H(e^{i\theta}) = f(e^{i\theta})$ (see Fig.
-\ref{harmonic}).
-Of course, this $H$ is unique.
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig4_down.png}
-            \end{center}
-            \caption{(a) Continuous function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$.
-(b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
-Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
-            \label{harmonic}
-        \end{figure}
-
-    \section{Harmonic Beltrami signature (HBS)}\label{main}
-        In this section, we describe our proposed shape signature, called the {\it Harmonic Beltrami signature (HBS)}, to represent a simply-connected domain $\Omega$.
-The space of HBS inherits a natural metric, so that geometric distance between two shapes can be easily measured.
-In the following subsection, the definition of HBS and some of its theoretical analysis are addressed.
-
-        \subsection{Definition of Harmonic Beltrami Signature}
+\section{Definition of Harmonic Beltrami Signature}
 Consider a bounded simply-connected domain $\Omega\subset \mathbb{C}$.
 Suppose $\Omega$ is a quasicircle, which is the image of the unit disk under a quasiconformal map.
-Let $f = \Phi_1^{-1} \circ \Phi_2$ be the conformal welding of $\Omega$, where  $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are the conformal mappings as described in Section \ref{welding}.
-Denote the harmonic extension of $f$ by $H:\mathbb{D}\to \mathbb{D}$.
+Let $f = \Phi_1^{-1} \circ \Phi_2$ be the conformal welding of $\Omega$, where  $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are the conformal mappings.
+Denote the harmonic extension of $f$ as $H:\mathbb{D}\to \mathbb{D}$ by equation (\ref{poisson integral}).
 
@@
 Note that the HBS is not unique without suitable normalizations of the conformal mappings.
-More precisely, the conformal welding of $\Omega$ is unique up to a pre- and post-composition of Mobi\"us transformations.
-Suppose $f_1$ and $f_2$ are both conformal weldings of $\Omega$.
-Then, $f_2 = M_1\circ f\circ M_2$.
-The harmonic extension and hence the HBS are not unique due to conformal ambiguities.
-This motivates us to give the following definition of equivalence.
+According to Riemann mapping theorem, the conformal mappings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
+Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobi\"us transformations.
+Therefore, the corresponding conformal welding is
+\begin{equation}\label{tilde f}
+    \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = M_1^{-1} \circ \Phi_1^{-1} \circ \Phi_2 \circ M_2 = M_1^{-1} \circ f \circ M_2.
+\end{equation}
+Therefore, the harmonic extension and hence the HBS are not unique due to conformal ambiguities. This motivates us to give the following definition of equivalence.
 
 \begin{definition}
-        Two HBS $B$ and $\tilde{B}$ are said to be {\it equivalent} if $B=\mu_H$ and $\tilde{B} = \mu_{\tilde{H}}$, where $H$ and $\tilde{H}$ are respectively the harmonic extensions of a diffeomorphism $f:\mathbb{S}^1\to \mathbb{S}^1$ and $\tilde{f} = M_1\circ f \circ M_2$ for some Mobi\"us transformations $M_1$ and $M_2$.
+Two HBS $B$ and $\tilde{B}$ are said to be {\it equivalent} if $B=\mu_H$ and $\tilde{B} = \mu_{\tilde{H}}$, where $H$ and $\tilde{H}$ are respectively the harmonic extensions of a diffeomorphism $f:\mathbb{S}^1\to \mathbb{S}^1$ and $\tilde{f} = M_1^{-1} \circ f \circ M_2$ for some Mobi\"us transformations $M_1$ and $M_2$.
 In this case, we denote $B \sim \tilde{B}$.
@@
 
-        In this work, we consider the quotient space of HBS $\mathcal{B} = \{B:\mathbb{D}\to \mathbb{D}:B \text{ is a HBS} \} /\sim$ to study the space of bounded simply-connected shapes.
+In this work, we consider the quotient space of HBS $\mathcal{B} = \{B:\mathbb{D}\to \mathbb{D}:B \text{ is a HBS} \} \,/ \sim$ to study the space of bounded simply-connected shapes.
 The following theorem illustrates that $\mathcal{B}$ is indeed an effective representation for the space of shapes.
 
-        \begin{theorem}
+\begin{theorem}\label{one to one equivalence class}
 There is a one-to-one correspondence between $\mathcal{B}$ and $\mathcal{S}$.
@@
 \begin{proof}
-        Given $\Omega$, there exist a unique $[B]\in \mathcal{B}$ corresponding to $\Omega$ follows from the definition of HBS.
+Given $\Omega$, there exist a unique $[B]\in \mathcal{B}$ corresponding to $\Omega$ follows from the definition of equivalence class of HBS.
 Conversely, let $[B]\in \mathcal{B}$.
@@
 \]
-        According to Quasiconformal Teichm\"uller theory, there exists $G:\mathbb{C}\to \mathbb{C}$ such that $G_{\bar{z}}/G_z = \mu$.
+According to Measurable Riemannian Mapping Theorem \ref{Measurable Riemannian Mapping Theorem}, there exists $G:\mathbb{C}\to \mathbb{C}$ such that $G_{\bar{z}}/G_z = \mu$.
 $G$ is unique up to a Mobi\"us transformation.
@@
 
-\bigskip
+% \bigskip
 
@@
 
-            \begin{figure*}
+    \begin{figure}
         \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig5.png}
+            \includegraphics[width=\textwidth]{fig5.png}
         \end{center}
         \caption{Illustration of Harmonic Beltrami signature.
-(a) The input shape, a dolphin.
-(b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b).
-(c) The Harmonic Beltrami signature of (a).
+(a) The input shape, a dolphin; (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{ill of cw} (b); (c) The Harmonic Beltrami signature of (a).
 Remark that the harmonic function and Harmonic Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
         \label{illu of BS}
-            \end{figure*}
+    \end{figure}
 
-        \subsection{Unique representative of $[B]$}
+\section{Unique representative of $[B]$}
     As discussed, every shape can be represented by its associated HBS, which is an equivalence class.
@@
 
-            According to Riemann mapping theorem, the conformal mappings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
-Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobious transformations.
-Therefore, the corresponding conformal welding is
-            \begin{equation}
-                \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = M_1^{-1} \circ \Phi_1^{-1} \circ \Phi_2 \circ M_2 = M_1^{-1} \circ f \circ M_2.
+    Let $f$ and $\tilde{f}$ be two different conformal welding of the same domain $\Omega$ and they satisfy equation (\ref{tilde f}).
+Their harmonic extension are $H$ and $\tilde{H}$ respectively.
+As we mentioned in last section, the conformal ambiguity of $M_1$ and $M_2$ is the biggest challenge in the way to unique representative, but we still hope $\tilde{H}$ to reserve such relationship, i.e.
+    \begin{equation}\label{tilde H}
+        \tilde{H} = M_1^{-1} \circ H \circ M_2,
     \end{equation}
-
-            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{H}$. The following theorem show the relationship between $H$ and $\tilde{H}$.
+    for the convenience of subsequent discussion. The following theorem tells us it can be achieved when restricting $M_1$:
 
     \begin{theorem}
-                Suppose $f$ and $\tilde{f}$ are continuous map from $\mathbb{S}^1$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
+        Suppose $f$ and $\tilde{f}$ are continuous map from $\mathbb{S}^1$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobi\"us transformations.
 $H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
@@
     \begin{proof}
-                Since $M_1$ is a Mobious transformations, $M_1^{-1}$ is also a Mobious transformation, so it can be written as $M_1^{-1}(z) = e^{i \theta}\frac{z - p}{1 - \overline{p}z}$, where $\theta \in [0, 2\pi)$ and $p \in \D$.
+        Since $M_1$ is a Mobi\"us transformations, $M_1^{-1}$ is also a Mobi\"us transformation, so it can be written as $M_1^{-1}(z) = e^{i \theta}\frac{z - p}{1 - \overline{p}z}$, where $\theta \in [0, 2\pi)$ and $p \in \D$.
 
-                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
+        $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobi\"us transformation $M_2$ is conformal.
 $\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
@@
 It's easy to check that
-                \begin{align*}
-                    M_1^{-1} \circ H \circ M_2 (e^{i \theta})
-                    &= M_1^{-1} \circ f \circ M_2(e^{i \theta})\\
-                    &= \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
-                \end{align*}
+        \begin{equation}
+            M_1^{-1} \circ H \circ M_2 (e^{i \theta}) = M_1^{-1} \circ f \circ M_2(e^{i \theta}) = \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
+        \end{equation}
         which means $M_1^{-1} \circ H \circ M_2$ and $\tilde{H}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ H \circ M_2 = \tilde{H}$.
@@
 
-            Suppose HBS $B$ is the representative of given equivalence class $[B]$ and $H$ is the corresponding Harmonic extension.
-Because of above theorem, we assume $M_1$ is a rotation, then some other $\tilde{B} \in [B]$ of $\tilde{H}$ is
+    Note that if $M_1$ is not only a rotation, $\tilde{f}$ and $\tilde{H}$ also exist but equation (\ref{tilde H}) doesn't hold, as shown in Fig. \ref{harmonic extension not rotation}.
+
+    \begin{figure}
+        \begin{center}
+            \includegraphics[width=15cm]{harmonic_extension_not_rotation.png}
+        \end{center}
+        \caption{Let $f(e^{i \theta}) = \sin(10 \theta) + \cos(10 \theta)+1.5$, $M_1(z) = e^{i \tau}\cfrac{z-p}{1-\overline{p}z}$, where $p=0.6+0.6i$, $\tau = 0.8$.
+The image of $f$ and its harmonic extension $H$ are shown in Fig.
+\ref{harmonic}.
+(a) $\tilde{f} = M_1 \circ f$; (b) harmonic extension $\tilde{H}$ of $\tilde{f}$; (c) $H' = M_1 \circ H$; (d) $H' - \tilde{H}$, and it's clear that $M_1 \circ H \neq \tilde{H}$ except on the boundary.}
+        \label{harmonic extension not rotation}
+    \end{figure}
+
+    Suppose HBS $B$ is the representative of given equivalence class $[B]$ and $H$ is the corresponding harmonic extension.
+Because of above theorem, we assume $M_1$ is a rotation, then for any other $\tilde{B} \in [B]$ of $\tilde{H} = M_1^{-1} \circ H \circ M_2$, we have
     \begin{equation}\label{tildeB}
@@
     \end{equation}
-            If we want to find a unique $B$, it means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, hence some pre- and post-normalizations are required.
+    This equation tells us the uniqueness of $B$ can be achieved by following theorem.
+    \begin{theorem}\label{unique B}
+        Suppose $B = \mu_H$ and $\tilde{B} = \mu_{\tilde{H}}$ are two Harmonic Beltrami signatures in given equivalence class $[B]$ for some domain $\Omega$, where $H$ and $\tilde{H}$ are the corresponding harmonic extensions of conformal welding $f$ and $\tilde{f}$ respectively with $\tilde{f} = M_1^{-1} \circ f \circ M_2$.
+If $M_1$ and $M_2$ are both rotation and
+        \begin{equation}\label{arg integral B is 0}
+            \arg \int_\D B(z) dz = \arg \int_\D \tilde{B}(z)dz = 0,
+        \end{equation}
+        then we have $\tilde{B} = B$.
+    \end{theorem}
 
-        \subsection{Normalization to $M_1$}\label{norm1}
+    \begin{proof}
+        When $M_1$ is rotation, the conformal arbitrary of conformal welding can be delivered to their harmonic extensions and
+        $\tilde{H} = M_1^{-1} \circ H \circ M_2$. Remark $r e^{i \tau} = \int_\D B(z) dz$ and $M_2(z) = e^{i \theta}z$, then the $\tilde{B}$ can be displayed in the form of
+        \begin{equation}
+        \tilde{B}(z) = \mu_{H \circ M_2}(z) = e^{-2i\theta} \mu_H \circ M_2(z) = e^{-2 i \theta} B(e^{i\theta} z).
+        \end{equation}
+        Therefore, we have
+        \begin{eqnarray}
+            \int_B \tilde{B}(z) dz
+            &=& \int_D e^{-2i\theta} B(e^{i\theta} z) dz \nonumber \\
+            &=& e^{-2i\theta} \int_D B(z) dz \nonumber \\
+            &=& r e^{i(\tau-2\theta)}.
+        \end{eqnarray}
+        If equation (\ref{arg integral B is 0}) holds,
+        \begin{equation*}
+            \tau = \tau-2\theta  = 0,
+        \end{equation*}
+        hence $\theta = 0$, $M_2$ is identity and so $\tilde{B} = \mu_H = B$.
+    \end{proof}
+
+    Note that the unique representative $B$ of $[B]$ can be easily generated from any HBS $B_0 = \mu_{H_0} \in [B]$. If $r e^{i\tau_0} =\int_\D B_0(z) dz$ and $\tau_0 \neq 0$, then
+    \begin{equation}\label{normaled B}
+        B(z) = e^{-i\tau_0}B_0(e^{i\frac{\tau_0}{2}}z)
+    \end{equation}
+    is just the desired representative since $B = \mu_{H_0 \circ M_0}$  and
+    \begin{equation}
+        \arg \int_\D B(z) dz = \arg \left( e^{-i\tau_0} \int_\D B_0(e^{i\frac{\tau_0}{2}}z)dz \right) = \arg \left( e^{-i\tau_0} \cdot r e^{i\tau_0} \right) = 0,
+    \end{equation}
+    where $M_0(z) = e^{i \frac{\tau}{2}} z$. Therefore, if we want to find a unique $B$, some pre- and post-normalizations to $M_1$ and $M_2$ are required.
+
+\section{Normalization to $M_1$}\label{norm1}
     We hope $M_1$ is a rotation.
@@
     Before proving theorem \ref{unique up to a rotation}, we can consider following problem.
-Given boundary points $p_i$ on unit circle, can we find a Mobious transformation $M$ satisfies the following equation (\ref{fz})?
+Given boundary points $p_i$ on unit circle, can we find a Mobi\"us transformation $M$ satisfies the following equation (\ref{fz})?
     \begin{equation}\label{fz}
@@
     Without lose of generality, we ignore the rotation of $M$ and let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-So $F_a$ is also a Mobius transformation and it's sufficient to find $a \in \D$ such that
+So $F_a$ is also a Mobi\"us transformation and it's sufficient to find $a \in \D$ such that
     \begin{equation}\label{eq}
@@
 
-            \begin{figure*}
+    \begin{figure}
         \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig6.png}
+            \includegraphics[width=10cm]{fig6.png}
         \end{center}
@@
         \label{fasolvable}
-            \end{figure*}
+    \end{figure}
 
-            \subsubsection{The solvability of equation (\ref{eq})}
+    \subsection{The solvability of equation (\ref{eq})}
     First thing we want to do is to check whether this equation (\ref{eq}) is always solvable. According to Brouwer fixed point theorem, we have
@@
     \begin{theorem}\label{existence}
-                Given $\{p_1, p_2, \cdots, p_n\} \subset \partial \D$ and $n \ge 3$, let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-The solution of equation (\ref{eq}) always exists.
+        Given $\{p_1, p_2, \cdots, p_n\} \subset \partial \D$ and $n \ge 3$, let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$. The solution of equation (\ref{eq}) always exists.
     \end{theorem}
@@
 
-            \subsubsection{The uniqueness of the solution of equation (\ref{eq})}
+    \subsection{The uniqueness of the solution of equation (\ref{eq})}
     With solvability proved, we naturally want to know if this solution is unique. Let's consider a special case when $\sum_{k=1}^n p_k = 0$, we have
@@
 
-            \subsubsection{Unique $\Phi_1$ up to a rotation}
+    \subsection{Unique $\Phi_1$ up to a rotation}
 
@@
     \begin{proof}
-                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobious transformation.
+        Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobi\"us transformation.
 If $\Phi_1$, $\tilde{\Phi_1} $ satisfy equation (\ref{norm phi1}), let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M_1^{-1} (p_k) = 0$.
-$M_1^{-1}$ is also a Mobious transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
+$M_1^{-1}$ is also a Mobi\"us transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
         \begin{equation*}
@@
 
-        \subsection{Normalization to $M_2$}\label{norm2}
+\section{Normalization to $M_2$}\label{norm2}
     As for $M_2$, we also hope it is also a rotation here, which is equivalent with that $\Phi_2$ is uniquely determined up to a rotation.
@@
     \begin{proof}
-                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobious transformation, $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$.
+        Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobi\"us transformation, $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$.
 Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisfy (\ref{norm phi2 1}), then
@@
 
-        \subsection{Post-normalization for $B$}\label{post norm B}
-            After normalizing $M_1$ and $M_2$, where $M_1, M_2$ are both rotation, for $B, \tilde{B} \in [B]$ with harmonic extensions $H, \tilde{H}$, according to equations (\ref{mu of conformal composition}) and (\ref{tildeB}), we have
-            \begin{equation}\label{arg integral B is 0}
-                \tilde{B}(z) = \mu_{H \circ M_2}(z) = e^{-2i\theta} \mu_H \circ M_2(z) = e^{-2 i \theta} B(e^{i\theta} z),
-            \end{equation}
-            where $M_2(z) = e^{i \theta}z$. This equation tells us the uniqueness of $B$ can be achieved by following theorem.
-            \begin{theorem}\label{unique B}
-                Suppose $B$ is HBS in given equivalence class $[B]$ and satisfies requirements (\ref{norm phi1}) and (\ref{norm phi2 1}). If
-                \begin{equation}
-                    \arg \int_\D B(z) dz = 0,
-                \end{equation}
-                then $B$ is unique representative of $[B]$.
-            \end{theorem}
-
-            \begin{proof}
-                Suppose $B, \tilde{B}$ are both HBS in the same equivalence class $[B]$ with harmonic extensions $H$ and $\tilde{H}$ respectively, where $\tilde{H} = M_1^{-1} \circ H \circ M_2$ and $\int_D B(z)dz = r e^{i \tau}$.
-According to requirements (\ref{norm phi1}) and (\ref{norm phi2 1}), $M_1, M_2$ are rotation.
-Let $M_2(z) = e^{i\theta}z$, then we have
-                \begin{eqnarray}
-                    \int_B \tilde{B}(z) dz
-                    &=& \int_D e^{-2i\theta} B(e^{i\theta} z) dz \nonumber \\
-                    &=& e^{-2i\theta} \int_D B(z) dz \nonumber \\
-                    &=& r e^{i(\tau-2\theta)}.
-                \end{eqnarray}
-                If equation (\ref{arg integral B is 0}) holds,
-                \begin{equation*}
-                    \tau = \tau-2\theta  = 0,
-                \end{equation*}
-                hence $\theta = 0$, $M_2$ is identity and so$\tilde{B} = \mu_{H \circ I} = \mu_H = B$.
-            \end{proof}
-
-            Note that the unique representative $B$ of $[B]$ can be easily generated from any HBS $B_0 \in [B]$. If $\tau_0 =\arg \int_\D \tilde{B}(z) dz  \neq 0$, then
-            \begin{equation}\label{normaled B}
-                B(z) = e^{i\tau_0}B_0(e^{-\frac{\tau_0}{2}i}z)
-            \end{equation}
-            is just the desired representative.
-
-        \subsection{Invariance under simple transformation}
+\section{Invariance under simple transformation}
     With the normalization mentioned above, we can get a unique Harmonic Beltrami signature $B$ as the representative corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$.
@@
 \section{Reconstruction}\label{reconstruction}
-
     The above theorems show that our Harmonic Beltrami signature can be uniquely defined by the given shape and is invariant under translation, scaling and rotation.
@@
 
-        If $B_\Omega$ is the HBS of some simply-connected domain $\Omega$, according to the process we mentioned in Section \ref{main}, there exists conformal mappings $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, conformal welding $f: \partial \D \rightarrow \partial \D $ and harmonic extension $H$ of $f$, where $\Phi_1$ satisfies equation (\ref{norm phi1}), $\Phi_2$ satisfies equations (\ref{norm phi2 1}), $f = \Phi_1^{-1} \circ \Phi_2$, $\mu_H = B_\Omega$ and $B_\Omega$ satisfies (\ref{arg integral B is 0}).
+    If $B_\Omega$ is the HBS of some simply-connected domain $\Omega$, according to the process we mentioned at the beginning of Section \ref{main}, there exists conformal mappings $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, conformal welding $f: \partial \D \rightarrow \partial \D $ and harmonic extension $H$ of $f$, where $\Phi_1$ satisfies equation (\ref{norm phi1}), $\Phi_2$ satisfies equations (\ref{norm phi2 1}), $f = \Phi_1^{-1} \circ \Phi_2$, $\mu_H = B_\Omega$ and $B_\Omega$ satisfies (\ref{arg integral B is 0}).
 
@@
     \end{align}
-        where $G$ is uniquely determined up to Mobious transformation $M$.
+    where $G$ is uniquely determined up to Mobi\"us transformation $M$.
 
@@
     \end{equation}
-        By the properties of Mobious transformation, we have $M(z) = az+b$ where $a, b \in \C$.
+    By the properties of Mobi\"us transformation, we have $M(z) = az+b$ where $a, b \in \C$.
 
@@
 
-        That means the relationship between Harmonic Beltrami signatures and shapes is a bijection, up to transformation, scaling and rotation. 
+    That means the map between Harmonic Beltrami signatures and shapes is also a bijection, up to transformation, scaling and rotation.
+In the theorem \ref{one to one equivalence class} tells us that there exists a one-to-one relationship between HBS equivalence classes and shapes and now such bijection can be extended to a special HBS, i.e.
+the unique representative of equivalence class.
     \begin{theorem}
@@
 
-        Hence, following powerful theorem about Beltrami holomorphic flow tells that if two HBS are similar, their corresponding shapes must be very alike.
+\section{Robustness of HBS}
+    Although there exists a one-to-one correspondence between HBS and shapes up to a rotation, translation and scaling, the behavior of HBS under small modification to the original shape is still unknown.
+Of course, we expect the HBS to be slightly deformed within reasonable range so that the proposed signature is robust and useful.
+The following powerful theorem about Beltrami holomorphic flow(BHF) tells that if two HBS are similar, their corresponding shapes must be very alike.
 
@@
     \end{align*}
-        Since $G_1$ is continuous and bounded, the integral $\int_\D \frac{(G_1)_z^2(z)}{G_1(z)(G_1(z)-1)(G_1(z)-G_1(w)}dz$ is bounded for any $w \in \D$.
-Therefore, there exists some $M > 0$ such that
+    Since $G_1$ is continuous and bounded, the integral is bounded and for any $w \in \D$ there exists some $M > 0$ such that
+    \begin{equation}
+    \begin{split}
+        &\norm{\int_\D \frac{(G_1)_z^2(z)}{G_1(z)(G_1(z)-1)(G_1(z)-G_1(w)}dz}_\infty \\
+        \le& \int_\D \norm{\frac{(G_1)_z^2(z)}{G_1(z)(G_1(z)-1)(G_1(z)-G_1(w)}}_\infty dz \\
+        \le& M
+    \end{split}
+    \end{equation}
+
+    then
     \begin{equation}
@@
     This illustrates that if the difference between HBS is small enough, their corresponding domains is almost the same, which means our Harmonic Beltrami signature is a good indicator similarity of shapes.
-
-    \section{Implementation detail}\label{implementation}
-        \subsection{Zipper algorithm}
-            In order to find a unique and stable HBS, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
-As mentioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
-
-            Marshall \etal demonstrates the zipper algorithm detailedly with clear diagrams in \cite{marshall2007convergence}.
-For the convenience of readers, we gives a very brief review here.
-Given $N$ clockwise boundary points $z_1, z_2, \cdots, z_N \in \partial \Omega$, this algorithm use a series of linear fractional transformations $g_1, g_2, \cdots, g_N$ to map $z_1, z_2,\cdots, z_N$ to real axis one-by-one, and finally transform the upper half plane to unit disk by $g_{N+1}(z) = \frac{z-i}{z+i}$.
-Therefore, $g = g_{N+1} \circ g_N \circ \cdots \circ g_2 \circ g_1$ is a conformal mapping indisputably and maps all these boundary points to unit circle and the domain $\Omega$ to $\D$.
-Remark that zipper algorithm is sensitive to the order of points.
-If we input the points anti-clockwise, i.e.
-$z_N, z_{N-1}, \cdots, z_1$, the zipper will give us a conformal mapping from $\Omega^c$ to $\D$.
-
-            For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputting points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$.
-For $\Phi_2 : \D^c \rightarrow \Omega^c$, we can input anti-clockwise points and get $g_{\Phi_2} : \Omega^c \rightarrow \D$.
-At the result $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-Because of the invariance of scaling, the number of boundary points $N$ is fixed as $200$ here and they are picked uniformly from the shape contour.
-
-            \begin{algorithm}[H]                           % HERE!!!!!!!!!
-            \caption{Zipper}          % give the algorithm a caption
-            \label{zipper}      % and a label for \ref{} commands later in the document
-            \begin{algorithmic}  % enter the algorithmic environment
-                \STATE \textbf{Inputs:} $z_i \in \partial \Omega$ for $i=1, 2, \cdots, N$, $N=200$. %, $\epsilon = 10^{-10}$(any very small value)
-                \STATE \textbf{Initialize:} Let $r=2$, $g_1(z) = \sqrt{\frac{z-z_2}{z-z_1}}$, $g= g_1$ and compute $p_{i,2}=g(z_i)$.
-                \WHILE{$r < N$}
-                    \STATE Pick $q = p_{r+1, r} = a + b i$, then compute $c = \frac{a}{\abs{q}^2}$, $d = \frac{b}{\abs{q}^2}$.
-                    \STATE Let $g_r(z) = \sqrt{\frac{cz}{1+dzi}}$, then $g = g_r \circ g$ and compute $p_{i, r+1} = g_r(p_{i, k})$.
-                    \STATE Let $r = r+1$.
-                \ENDWHILE
-                \STATE Let $g_{N}(z) = \left(\frac{z}{1-\frac{z}{p_{1,N}}}\right)^2$ and $g_{N+1}(z) = \frac{z-i}{z+i}$, then $g = g_{N+1} \circ g_N \circ g$ and $p_i = g_{N+1} \circ g_N(p_{i,N})$.
-                \RETURN Conformal mapping $g: \Omega \rightarrow \D$ and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-        \subsection{Harmonic extension}\label{detail harmonic}
-            After obtaining the output of zipper algorithm, $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$, the conformal welding can be represented as a series points
-            \begin{equation*}
-                (\varphi_i, \omega_i) = \left(\arg(\hat{\Phi}_2^{-1}(z_i)), \arg(\hat{\Phi}_1^{-1}(z_i))\right),
-            \end{equation*}
-            where $\varphi_i, \omega_i \in [0, 2\pi)$. So in fact we should use discrete form Poisson integral to extend $f$ to a harmonic mapping $H$ on the unit disk
-            \begin{equation}\label{discrete poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi} \sum_{j=1}^k \frac{(1-r^2) e^{i \omega_j} \gamma_j}{1 - 2 r cos (\varphi_j - \theta) + r^2} ,
-            \end{equation}
-            where $\gamma_j = (\varphi_{j} - \varphi_{j-1}) \bmod{ 2\pi}$ and $\varphi_0 = \varphi_k$ and this $\bmod$ can solve some critical value problem, for example, $\varphi_j = 0$ but $\varphi_{j-1} = 6$.
-For the convenience of computation, we only calculate the value of $H$ on a grid
-            \begin{align*}
-                G = \{z=x+iy \mid &\abs{z} \le 1, x=\frac{j}{100}, y=\frac{k}{100},\\
-                &j,k=-100,-99,\cdots,99,100 \}.
-            \end{align*}
-
-        \subsection{Normalization}
-            Because of the arbitrariness of the conformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
-            \begin{equation*}
-                \tilde{H} = M_1 \circ H \circ M_2.
-            \end{equation*}
-            Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then HBS $B$ can be unique.
-This section will tells how to satisfy equation (\ref{norm phi1}) and (\ref{norm phi2 1}) from the output of zipper algorithm.
-
-            To normalization $M_1$, we need to solve equation (\ref{eq}).
-Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concentrate around a point.
-At that time, $\abs{f(a)} \approx 1$ almost everywhere and the solution of (\ref{eq}) is also very close to the point.
-This means the solution is quite unstable and hard to converge for common algorithms(see Fig \ref{original distribution}).
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig7_down.png}
-                \end{center}
-                \caption{(a) The $p_i \in \partial \D$ gather in a small neighborhood around their arithmetic mean $p_c$, which is labeled in red.
-(b) The corresponding $\abs{f(a)}$ for these $p_i$.
-It's worth to mention that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
-                \label{original distribution}
-            \end{figure}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig8_down.png}
-                \end{center}
-                \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment. (b) The $\abs{f(a)}$.}
-            \end{figure}
-
-            Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobious transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
-For the $r$-th iteration, let
-            \begin{equation*}
-                p_{c,r} = \frac{\sum_{i=1}^k p_{i,r}}{k} \in \D
-            \end{equation*}
-            as the arithmetic center of $p_{i,r} \in \partial \D$.
-Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobious transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
-            \begin{equation*}
-                p_{i,r+1} = F_{p_{c,r}}(p_{i,r}) = \frac{p_{i,r} - p_{c,r}}{1 - \overline{p_{c,r}}p_{i,r}}.
-            \end{equation*}
-            Note that we set $p_{i,0} = p_{i}$ at the beginning.
-Repeat this iteration for $r$ times until the center of boundary points is close to $0$, then the distribution is sufficiently regular and $\Phi_1$ becomes
-            \begin{equation}
-                \tilde{\Phi}_1 = \Phi_1 \circ F_{p_{c,0}}^{-1} \circ F_{p_{c,1}}^{-1} \circ \cdots \circ F_{p_{c,r}}^{-1}.
-            \end{equation}
-            Now equation (\ref{eq}) can be solved without much effort by Newtown's method. Suppose $a \in \D$ is the optimal solution and let 
-            \begin{equation*}
-                M_{\Phi_1} = F_a \circ F_{p_{c,r}} \circ F_{p_{c,r-1}} \circ \cdots \circ F_{p_{c, 0}}
-            \end{equation*}
-            and the final conformal mapping satisfying (\ref{norm phi1}) is
-            \begin{equation}
-                \hat{\Phi}_1 = \tilde{\Phi}_1 \circ F_{a}^{-1} = \Phi_1 \circ M_{\Phi_1}^{-1}
-            \end{equation}
-
-            \begin{algorithm}[H]
-            \caption{Normalize $M_1$}
-            \label{alg norm phi1}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} $\Phi_1$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $\epsilon=0.2$.
-                \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$, $M_{\Phi_1} = id$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$.
-%and $M_{p_{c,0}}(z) = \frac{z-p_{c,0}}{1- \overline{p_{c, 0}}z}$
-                \WHILE{$\abs{p_c,r} > \epsilon$}
-                    \STATE Let $F_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $M_{\Phi_1} = F_{p_{c,r}} \circ M_{\Phi_1}$.%and $\Phi_1 = \Phi_1 \circ F_{p_{c,r}}^{-1}$.
-                    \STATE Compute $p_{i, r+1} = F_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
-                    \STATE Let $r = r+1$.
-                \ENDWHILE
-                \STATE Solve equation (\ref{eq}) by Newtown's method and get solution $a \in \D$.
-                \STATE Let $F_a(z) = \frac{z-a}{1- \overline{a}z}$ and $M_{\Phi_1} = F_a \circ M_{\Phi_1}$.% and $\hat{\Phi}_1 = \Phi_1 \circ F^{-1}_{a}$.
-                %\STATE Compute $p_i = F_a(p_{i,r})$.
-                \RETURN Mobious transformation $M_{\Phi_1}$.%, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig9.png}
-                \end{center}
-                \caption{The iteration of distribution adjustment. The boundary points are blue and their arithmetic center is red in each picture. (a)-(d) The 1st, 3rd, 7th, 12th iteration.}
-            \end{figure*}
-
-            As for the normalization of $M_2$, it's much easier. For requirement (\ref{norm phi2 1}), let $b = \Phi_2^{-1}(\infty)$ and $c = -\frac{1}{\bar{b}}$, from
-            \begin{equation*}
-                F_{c}(\infty) = \lim_{z \rightarrow \infty} \frac{z -c}{1 - \bar{c}z} = -\frac{1}{\overline{c}} = b
-            \end{equation*} we have 
-            \begin{equation*}
-                \tilde{\Phi}_2(\infty) = \Phi_2 \circ F_{c}(\infty) = \Phi_2(b) = \infty.
-            \end{equation*}
-            So we only need replace $\Phi_2$ with $\tilde{\Phi}_2 =\Phi_2 \circ F_{c}$ to map $\infty$ to $\infty$.
-
-            % According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
-And another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
-Here we select $M = 10^5$ points uniformly from $[0, 2\pi)$ as $\theta_j = \frac{2\pi}{M}(j-1)$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}).
-
-            % Therefore, the maximal solution
-            % \begin{equation}
-            %     \theta_{\max} = \argmax{j \in [1,10^5]} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}
-            % \end{equation}
-            % can be used to normalize the rotation and the final mapping is 
-            % \begin{equation}
-            %     \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{\max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
-            % \end{equation}
-            % where $M_{\Phi_2} = e^{i \theta_{\max}} F_{ce^{-i \theta_{\max}}}$.
-
-            \begin{algorithm}[H]
-            \caption{Normalize $M_2$}
-            \label{alg norm phi2}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} $\Phi_2$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $M=10^5$.
-                \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$ and $c = -\frac{1}{\bar{b}}$.
-                \STATE Let $F_c(z) = \frac{z-c}{1-\overline{c}z}$ and $M_{\Phi_2} = F_{c}$.
-                \RETURN Mobious transformation $M_{\Phi_2}$
-                % \RETURN Conformal mapping $\hat{\Phi}_2: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-            After obtaining Mobious transformations $M_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
-            \begin{align*}
-                \hat{H} = M_{\Phi_1} \circ H \circ M_{\Phi_2}
-            \end{align*}
-            and it is unique up to rotation. Finally, the desired HBS can be generated from $\mu_{\hat{H}}$ according to equation (\ref{normaled B}).
-
-        \subsection{Summary of the Algorithm}
-            The totally algorithm is as following.
-            \begin{algorithm}[H]
-            \caption{Calculate HBS}
-            \label{alg all}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} Simply-connected shape $\Omega \subset \C$, $N=200$.
-                \STATE Pick clockwise points $z_1, \cdots, z_N \in \partial \Omega$ uniformly.
-                \STATE Input $z_1, z_2, \cdots, z_N$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_1}: \D \rightarrow \Omega$ and $p_{i,1} \in \partial\D$.
-                \STATE Input $z_N, \cdots, z_2, z_1$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_2}: \D \rightarrow \Omega^c$ and $p_{i,2} \in \partial\D$.
-                \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-                \STATE Let $f = \Phi_1^{-1} \circ \Phi_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
-                \STATE Extend $f$ to $H$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
-                \STATE Input $\Phi_1$ and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get $M_{\Phi_1}$.
-                \STATE Input $\Phi_2$ and $p_{i,2}$ to Algorithm \ref{alg norm phi2}, then get $M_{\Phi_2}$.
-                \STATE Calculate normalized harmonic extension $\hat{H} = M_{\Phi_1} \circ H \circ M_{\Phi_2}$.
-                \STATE Calculate Beltrami coefficient $\mu_{\hat{H}}$.
-                \STATE Calculate $\theta = \arg \int_\D \mu_{\hat{H}}(z) dz$.
-                \STATE Let $B(z) = e^{i \theta} \mu_{\hat{H}}(e^{-\frac{1}{2}i\theta} z)$.
-                \RETURN Harmonic Beltrami signature $B$.
-            \end{algorithmic}
-            \end{algorithm}
-    \section{Experimental result}\label{result}
-        In this section, we will validate key properties of our proposed Harmonic Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
-Besides that, a good shape representation should keep the similarity with the same kind shape and is significantly different from different kinds of shape.
-
-        Before showing results, what needs illustration is that the distance we used to measure the difference of HBS is based on $L^2$ norm,
-        \begin{equation}\label{bs dis}
-            d(B_1, B_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{B_1(z_i) - B_2(z_i)}^2},
-        \end{equation}
-        where $B_1, B_2$ are two different Harmonic Beltrami signatures, $z_i \in \D$ is the face center of triangular mesh $M$ mentioned in Section \ref{detail harmonic} and $N=60962$ here.
-        \subsection{Invariance}\label{sec inv}
-            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate HBS after scaling, translation and rotation and compare them with the original shape's HBS.
-The result is displayed in Fig \ref{inv}.
-In this figure, the first column are the sets of boundary points and we remark them as $\Omega_a$ to $\Omega_f$.
-The second column are the corresponding Harmonic Beltrami signatures $B_a$ to $B_f$.
-Note that all the Harmonic Beltrami signatures are shown in modulus, i.e.
-$\abs{B_n}$ for row $n$, and in top view.
-And the third column(if have) are the histograms of the difference between original shape's Harmonic Beltrami signature, i.e.
-$\abs{B_n - B_a}$ for row $n$.
-
-            Row b and c are about scaling, the shapes are $\Omega_b = \{z \mid z = 1.5 z_a, z_a \in \Omega_a \}$ and $\Omega_c = \{z \mid z = 0.5 z_a, z_a \in \Omega_a \}$ and the distance are $d(B_a, B_b) = 5.5647 \times 10^{-8}$ and $d(B_a, B_c) = 5.3476 \times 10^{-8}$.
-Row d is about translation, the shape $\Omega_d = \{z \mid z = z_a+100+20i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_d) = 4.7817 \times 10^{-8}$.
-Row e is about rotation, the shape is $\Omega_e = \{z \mid z = e^{0.2\pi i} z_a, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.2144 \times 10^{-8}$.
-Row f is the combination of scaling, translation and rotation, the shape is $\Omega_e = \{z \mid z = 3e^{-0.85\pi i} z_a+350+600i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.7635 \times 10^{-8}$.
-These confirm the invariance of HBS and scaling, translation and rotation.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/inv.png}
-                \end{center}
-                \caption{Harmonic Beltrami signature under scaling, translation and rotation.}
-                \label{inv}
-            \end{figure*}
-
-        \subsection{Robustness}
-            Similar with Section \ref{sec inv}, here we still treat the dolphin as the original shape and modify some small parts of it and Fig \ref{robust} is the result.
-It shows that the proposed signature is robust and stable and will not have a big mutation caused by small disturbance.
-
-            Row g, h and i are result about modification.
-These shapes are generated by removing or adding something, which is in the red circle.
-We can see that Harmonic Beltrami signatures have slight differences from $B_a$ but are still similar in general.
-And this figure also demonstrates that the bigger the modification part is, the more different the Harmonic Beltrami signature is.
-For example in row i, losing a half of the tail makes the signature has a marked change.
-Quantitatively, $d(B_a, B_g) = 0.0132$, $d(B_a, B_h) = 0.0316$ and $d(B_a, B_i) = 0.1761$.
-
-            Row j is for distortion. This dolphin is only enlarged in horizontally and becomes fatter, then the $B_j$ moves a little bit and $d(B_a, B_j) = 0.0724$.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/robust.png}
-                \end{center}
-                \caption{Harmonic Beltrami signature under small modification}
-                \label{robust}
-            \end{figure*}
-
-        \subsection{Classification with HBS}
-            Above properties ensure the proposed signature having the ability to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.
-
-            To compare the classification performance, we also use conformal welding directly to classify, and the distance is defined as
-            \begin{equation}\label{welding dis}
-                d_c(f_1, f_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{f_1(z_i) - f_2(z_i)}^2},
-            \end{equation}
-            where $f_1, f_2$ are two different conformal welding, $N=200$ here.
-
-            We prepare 3 kinds of animals, fish, giraffe and elephant.
-There are 3 images for each group so 9 images in total.
-From Fig \ref{classification images}, we can find that each class share similar HBS and conformal welding.
-From Fig \ref{dis matrix}, the intraclass distance of HBS is always less than 0.2 while the interclass distance is greater than 0.2.
-But for conformal welding, the data is messy, for example, fish 3 thinks itself is very different from other fishes but looks most like giraffe 2.
-After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the HBS shows powerful classification ability.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/figs.png}
-                \end{center}
-                \caption{These 3 rows are elephant, fish and giraffe.
-In each subfigure, the top left is the input shape, bottom left is the conformal welding and the right is Harmonic Beltrami signature.}
-                \label{classification images}
-            \end{figure*}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/distance_down.png}
-                \end{center}
-                \caption{(a) The distance matrix of Harmonic Beltrami signatures of above 9 shapes by equation (\ref{bs dis}).
-(b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
-                \label{dis matrix}
-            \end{figure}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/mds_down.png}
-                \end{center}
-                \caption{(a) The MDS result of Harmonic Beltrami signature. (b) The MDS result of conformal welding.}
-                \label{mds1}
-            \end{figure}
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/mds2.png}
-                \end{center}
-                \caption{(a) The MDS result of Harmonic Beltrami signature.
-(b) The MDS result of conformal welding.
-(c) The clustering result of Harmonic Beltrami signature.
-(d) The clustering results of conformal welding.}
-                \label{mds2}
-            \end{figure*}
-
-        \subsection{Classification for more classes}
-            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabbit.
-We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes.
-The MDS and clustering results based on Harmonic Beltrami signature and conformal welding are displayed in Fig \ref{mds2}.
-The classification accuracy based on Harmonic Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
-
-    \section{Conclusion}\label{conclusion}
-        In this paper, we propose a novel shape representation for 2D bounded simply-connected objects called Harmonic Beltrami signature.
-The proposed signature is based on conformal welding but overcome a key shortcoming that it can be uniquely determined by the given shape.
-What's more exciting is that the proposed representation is invariance under scaling, translation and rotation.
-For slight deformation and distortion, HBS keeps robust and only changes within a reasonable small range.
-Therefore, there are reasons to believe the it does have ability to represent some invariant geometrical features.
-The experimental results also confirm that the HBS has excellent performance in multi-classification tasks.
-
-        Although our work has achieved relatively good results, the proposed representation still have some limitations.
-Firstly, the HBS is only applicable to simply-connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world.
-So we are eager for a feasible method to extend our HBS to multi connected situation.
-Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangular mesh, which consumes a lot of time.
-Therefore, a fast algorithm to obtain this signature avoiding dense mesh is of high priority in our future work.
-Thirdly, when normalizing the conformal mapping $\Phi_2$ from exterior of unit disk to exterior of the domain, the position where the derivation of $\Phi_2$ reaches the maximum value is used to adjust the rotation.
-We trust this point in the original image has a certain geometric meaning, whereas it is not clear at present.
-
-        In summary, we will focus on three major directions in the future.
-One is that the deeper meaning of HBS is worth digging and then a multi-connected version of representation based on this work can be proposed.
-Another is that if the HBS contains some geometrical features of shapes, we can also extract them directly from images and generate the HBS again.
-Hence the deep learning theory may help us to compute this signature from given images immediately, which is very likely to improve algorithm speed performance greatly.
-A third direction is this representation can be used in more applications like segmentation, registration and so on.
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
-% \section*{Conflict of interest}
-%
-% The authors declare that they have no conflict of interest.
-
-% BibTeX users please use one of
-% \bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
-\bibliography{cite}
-% Non-BibTeX users please use
-% \begin{thebibliography}{}
-% %
-% % and use \bibitem to create references. Consult the Instructions
-% % for authors for reference list style.
-% %
-% \bibitem{RefJ}
-% % Format for Journal Reference
-% Author, Article title, Journal, Volume, page numbers (year)
-% % Format for books
-% \bibitem{RefB}
-% Author, Book title, page numbers. Publisher, place (year)
-% % etc
-% \end{thebibliography}
-
-\end{document}
-% end of file template.tex

### 2021-06-11 Implementation/Implementation.tex
final thesis

--- 2021-04-08 paper.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-% \smartqed  % flush right qed marks, e.g. at end of proof
-%
-% \let\equation\relax
-% \let\endequation\relax
-\let\proof\relax
-\let\endproof\relax
-\let\example\relax
-\let\endexample\relax
+\chapter{Implementation detail}\label{implementation}
+\section{Zipper algorithm}
+    In order to find a unique and stable HBS, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
+As mentioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
 
-\usepackage{graphicx}
-\usepackage[margin=1in]{geometry} 
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{hyperref}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\include{snippets}
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
-\begin{document}
-
-\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
-% \subtitle{Do you have a subtitle?\\ If so, write it here}
-
-%\titlerunning{Short form of title}        % if too long for running head
-
-\author{Chenran Lin \and Lok Ming Lui}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{Chenran Lin \at
-              Department of Mathematics, The Chinese University of Hong Kong \\
-              \email{crlin@math.cuhk.edu.hk}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           Lok Ming Lui \at
-              Department of Mathematics, The Chinese University of Hong Kong\\
-              \email{lmlui@math.cuhk.edu.hk}           %  \\
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simple connected domain in this paper, named Beltrami signature.
-The proposed signature is based on conformal welding.
-We extended the welding mapping to a harmonic function.
-With suitable normalization, the uniqueness of this harmonic function is guaranteed up to a rotation.
-And finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension.
-The benifits of the proposed signature is it keeps invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformation and distortion.
-Experiments demonstrate the above properties and also show the excellent classification performance.
-\keywords{
-  Shape representation \and conformal welding \and simple connected \and invariance}
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
-\end{abstract}
-
-\section{Introduction}
-\label{intro}
-    The outline of the shape contains very important information and it can be used in many applications, such as segementation, recognition, registration and so on.
-However, even for the simplest situation, 2D simple connected shapes, it is a big challenge to describe clearly what the shape contour looks like.
-Because of the complexity of the image, there is an urgent demand to find a common, simple and robust shape representation for further mining and utilizing of shapes' geometric information.
-Therefore, many different presentations and measures have been widly studied and proposed recently \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.
-
-    Considering 2D simple connected shapes, conformal welding is a kind of well-known shape signature.
-Given 2D simple connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$.
-This gives a simple but wonderful representation of $\Omega$ as Fig.
-\ref{fig1} shows.
-However, it has two fatal defects.
-First is that such representation is not unique.
-Because of the arbitrary of Riemann conformal mapping, $\Phi_1$ and $\Phi_2$ can only be determined up to a Mobious transformation, so such conformal welding is not unique.
-Generally speaking, some assumption is required to remove this uncertainty.
-For example, Sharon \etal \cite{sharon20062d} need to select a base point $P$ inside the given domain $\Omega$ artificially, then let $\Phi_1$ maps $0$ to this point $P$.
-The work of Mcenteggart \etal \cite{mcenteggart2018uniqueness} is based on Schramm-Loewner evolution(SLE) on random surfaces called Liouville quantum gravity, they proved the equivalence between uniqueness of conformal welding and conformal removable and conculded that if the boundary curve $\eta$ is an $\text{SLE}_k$ for $k \in (0, 4)$ and satisifies some other requirements, the corresponding conformal welding is unique.
-Some may not that care the uniqueness itself, they used equivalent class to guarantee uniqueness in a broader sense or evne just ignored it \cite{katznelson1990conformal,marshall2012conformal,lui2013shape,astala2010random}.
-
-    Another thing is that even the conformal welding is very easy to be changed by simple transformations like rotation, scaling and translation.
-Such a unstable representation is hard to apply in practical applications since these transformations are inevitable in the real world.
-
-    The contribution of this paper is that we propose a brand new presentation for 2D simple connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Beltrami signature.
-Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points.
-Such conformal welding can be extended to the whole unit disk and get a harmonic function $H: \D \rightarrow \D$.
-Under suitable normalization, harmonic extension $H$ can be determined up to a rotation and the Beltrami coefficient of $H$ is then unique and becomes our Beltrami signature.
-
-    The proposed shape representation, Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
-The Beltrami signature is based on computational quasiconformal geometry.
-Computational quasiconformal geometry has been widely used in image processing and image analysis.
-Applications can be found in image segmentation
-    \cite{siu2020image,chan2018topology,zhang2020topology}
-    , image registration
-    \cite{lam2014landmark,lui2014teichmuller,ng2014computing,lui2012optimization,lam2014genus,zhang2012registration,lee2016landmark,lui2010optimized,lui2013texture,lui2010shape,lui2010optimizedc,lui2014geometric,choi2015flash}
-     and image analysis 
-    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shapec,lui2010shape3}
-    .
-What's more worth mentioning is that Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape.
-It means the proposed representation has high practical value and can be applied in computer vision work like classification, segementation and so on.
-
-    The paper is organized as follows: Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem and how Beltrami signature is obtained from given domain; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
-The paper is concluded in Section \ref{conclusion} and we point out future directions.
+    Marshall \etal demonstrates the zipper algorithm detailedly with clear diagrams in \cite{marshall2007convergence}.
+For the convenience of readers, we gives a very brief review here.
+Given $N$ clockwise boundary points $z_1, z_2, \cdots, z_N \in \partial \Omega$, this algorithm use a series of linear fractional transformations $g_1, g_2, \cdots, g_N$ to map $z_1, z_2,\cdots, z_N$ to real axis one-by-one, and finally transform the upper half plane to unit disk by $g_{N+1}(z) = \frac{z-i}{z+i}$.
+Therefore, $g = g_{N+1} \circ g_N \circ \cdots \circ g_2 \circ g_1$ is a conformal mapping indisputably and maps all these boundary points to unit circle and the domain $\Omega$ to $\D$.
+Remark that zipper algorithm is sensitive to the order of points.
+If we input the points anti-clockwise, i.e.
+$z_N, z_{N-1}, \cdots, z_1$, the zipper will give us a conformal mapping from $\Omega^c$ to $\D$.
+This progress is shown in Fig.
+\ref{zipper algo}.
 
@@
     \begin{center}
-        \includegraphics[width=7.6cm]{src/fig1_down.png}
-        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simple connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
+        \includegraphics[width=15cm]{zipper_algo.png}
     \end{center}
-        \label{fig1}
+    \caption{Zipper algorithm}
+    \label{zipper algo}
     \end{figure}
 
-\section{Theoretical basis}\label{background}
-    \subsection{Quasi-conformal mapping and Beltrami equation}
-        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
-        \begin{equation*}
-            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
-        \end{equation*}
-
-        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
-        \begin{equation}\label{beltrami eq}
-            \Part{f}{\overline{z}} = \mu(z) \Part{f}{z}
-        \end{equation}
-        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$.
-More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
-        \begin{equation}
-            \mu = \frac{f_{\overline{z}}}{f_{z}}
-        \end{equation}
-        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
-        \begin{equation}
-            f^*(ds^2_E) = \abs{\Part{f}{z}}^2 \abs{dz + \mu(z)d\overline{z}}^2
-        \end{equation}
-        which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$.
-$\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality.
-In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$.
-Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
-        \begin{equation}\label{local f}
-            f(z) = f(p)+f_z(p)(z+\mu(p)\overline{z}).
-        \end{equation}
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig2.jpg}
-            \end{center}
-            \caption{(a) Shows the original hippocampus.
-(b) Shows the parameter domain with circle packing pattern.
-Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
-            \label{fig2}
-        \end{figure}
-
-        If $\mu(z)=0$ everywhere, then $f$ us called \textit{conformal} or \textit{holomorphic}. A conformal map satisfies the following well-known Cauchy-Riemann equation:
-        \begin{equation}\label{cr eq}
-            \Part{f}{\overline{z}} = 0.
-        \end{equation}
-        Inside the local parameter domain, $f$ may be considered as a map composed of a translation to $f(p)$ together with a stretch map $S(z) = z + \mu(p)\overline{z}$, which is postcomposed by multiplication of $f_z(p)$, which is conformal.
-All the conformal distortion of $S(z)$ is caused by $\mu(p)$.
-$S(z)$ is the map that causes $f$ to map a small circle to a small ellipse (see Fig.
-\ref{fig2}).
-Form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well.
-Specially, the angle of maximal magnification is $\arg(\mu(p))/2$ with magnifying factor $1+\abs{\mu(p)}$; the angle of maximal shrinkage is the orthogonal angle $\arg(\mu(p))/2 - \pi/2$ with shrinkage factor $1-\abs{\mu(p)}$.
-The distortion or dilation is given by:
-        \begin{equation}
-            K = \frac{1+\abs{\mu(p)}}{1-\abs{\mu(p)}}.
-        \end{equation}
-        Thus, the Beltrami coefficient $\mu$ gives us important information about the properties of the map (see Fig. \ref{fig3}).
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig3.jpg}
-            \end{center}
-            \caption{Quasi-conformal maps infinitesimal circles to ellipses. The Beltrami coefficient measure the distortion or dilation of the ellipse under the QC map.}
-            \label{fig3}
-        \end{figure}
-
-        Suppose $f, g: \C \rightarrow \C$ are complex-valued function with Beltrami coefficient $\mu_f, \mu_g$ respectively. Then the Beltrami coefficient for the composition $g \circ f$ is given by
-        \begin{equation}\label{mu of composition}
-            \mu_{g \circ f} = \frac{\mu_f+(\mu_g \circ f) \tau}{1+\overline{\mu_f}(\mu_g \circ f) \tau},
-        \end{equation}
-        where $\tau = \frac{\overline{f_z}}{f_z}$. Note that when $g$ is conformal, $\mu_g = 0$ and 
-        \begin{equation}\label{mu of conformal composition}
-            \mu_{g \circ f} = \mu_f.
-        \end{equation}
-
-    \subsection{Conformal welding}
-        Given 2D bounded simple connected shape, we can treat it as a boundary simple connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
-$\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobious transformation}:
-        \begin{equation}
-            M(z) = e^{i \theta} \frac{z - a}{1 - \overline{a}z}.
-        \end{equation}
-        Then we can define \textit{conformal welding} as:
-        \begin{equation}
-            f = \Phi_1^{-1} \circ \Phi_2.
-        \end{equation}
-        Such $f: \partial \D \rightarrow \partial \D$ is a diffeomorphism from $\partial \D$ to itself, which can be also thought as a periodic, real-valued monotone increasing function $f_\R: [0, 2\pi) \rightarrow [0, 2\pi)$ such that $f(e^{i \theta}) = e^{i f_\R(\theta)}$ (see Fig.
-\ref{fig1}).
-
-    \subsection{Harmonic function and Poisson integral}
-        A complex-valued function $f$ defined on $\Omega \subset \C$ is called \textit{harmonic} if it satisfies the \textit{Laplace's equation}:
-        \begin{equation}
-            \Delta f = 4 \frac{\partial^2 f}{\partial z \partial \overline{z}} = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2} = 0,
-        \end{equation}
-        where $z = x + iy$, $x$, $y$ is the real and imaginary value.
-
-        Chen \etal prove following theorem in \cite{chen2010compositions}, which tells us that the composition of harmonic mappings and other mappings can inherit such harmonicity in some condition.
-        \begin{theorem}\label{composition of harmonic}
-            Let $f$ be a harmonic mapping, $f \circ g$ is harmonic if and only if $g(z) = az + b \overline{z} + c$, where $a$, $b$ and $c$ are constaants and $g \circ f$ is harmonic if and only if $g$ is analytic or anti-analytic.
-        \end{theorem}
-
-        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}.
-For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
-            \begin{equation}\label{poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
-            \end{equation}
-        Such $H$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
-$H(e^{i\theta}) = f(e^{i\theta})$ (see Fig.
-\ref{harmonic}).
-Of course, this $H$ is unique.
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig4_down.png}
-            \end{center}
-            \caption{(a) Continious function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$.
-(b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
-Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
-            \label{harmonic}
-        \end{figure}
-
-    \section{Beltrami signature}\label{main}
-        In this chapter, we will propose a new representation, Beltrami signature, to discribe boundary simple connected domain $\Omega$.
-Our proposed signature is based on conformal welding and quasi-conformal theory.
-
-        \subsection{Beltrami signature based on conformal welding}
-            Here we give a brief explaination of how to create our new signature.
-Given the boundary simple connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it.
-Then $f$ can be extended to harmonic function $H$ defined on $\D$ by Poisson integral (\ref{poisson integral}).
-At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
-            \begin{equation}
-                B:= \mu_H = \frac{H_{\overline{z}}}{H_z}.
-            \end{equation}
-            Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $B$ is determined.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig5.png}
-                \end{center}
-                \caption{Illustration of Beltrami signature.
-(a) The input shape, a dolphin.
-(b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b).
-(c) The Beltrami signature of (a).
-Remark that the harmonic funcion and Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
-                \label{illu of BS}
-            \end{figure*}
-
-        \subsection{Analysis of uniqueness of Beltrami signature}
-            According to Riemann mapping theorem, the conformal mapings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
-Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobious transformations.
-Therefore, the corresponding conformal welding is
-            \begin{equation}
-                \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = M_1^{-1} \circ \Phi_1^{-1} \circ \Phi_2 \circ M_2 = M_1^{-1} \circ f \circ M_2.
-            \end{equation}
-
-            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{H}$. The following theorem show the relationship between $H$ and $\tilde{H}$.
-
-            \begin{theorem}
-                Suppose $f$ and $\tilde{f}$ are continious map from $\partial \D$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
-$H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
-            \end{theorem}
-
-            \begin{proof}
-                Since $M_1$ is a Mobious transformations, $M_1^{-1}$ is also a Mobious transformation, so it can be written as $M_1^{-1}(z) = e^{i \theta}\frac{z - p}{1 - \overline{p}z}$, where $\theta \in [0, 2\pi)$ and $p \in \D$.
-
-                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
-$\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
-Therefore, we have
-                \begin{equation*}
-                    e^{i \theta}\frac{z - p}{1 - \overline{p}z} = az + b \overline{z} + c,
-                \end{equation*}
-                which means $p = b = c = 0$, $a = e^{i \theta}$ and so $M_1$ is a rotation.
-
-                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ H \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}.
-It's easy to check that
-                \begin{align*}
-                    M_1^{-1} \circ H \circ M_2 (e^{i \theta})
-                    &= M_1^{-1} \circ f \circ M_2(e^{i \theta})\\
-                    &= \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
-                \end{align*}
-                which means $M_1^{-1} \circ H \circ M_2$ and $\tilde{H}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ H \circ M_2 = \tilde{H}$.
-            \end{proof}
-
-            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{H}$
-            \begin{equation}
-                \tilde{B} = \mu_{\tilde{H}} = \mu_{M_1^{-1} \circ H \circ M_2} = \mu_{H\circ M_2}.
-            \end{equation}
-            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, then we get $M_2$ is identity.
-Therefore, we know that the uniqueness of Beltrami signature is equivalent to following restrictions:
-            \begin{enumerate}
-                \item $M_1$ should be a rotation.
-                \item $M_2$ should be identity.
-            \end{enumerate}
-
-        \subsection{Normalization to $M_1$}\label{norm1}
-            We hope $M_1$ is a rotation.
-It is not that hard, for example, we can achieve it by restricting $\Phi_1(0) = 0$.
-But it need a hypothesis that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold.
-Here we want to show a new approach without any additional assumption.
-
-            In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$.
-Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, where $\Phi_1 : \D \rightarrow \Omega$.
-We claims that $M_1$ can be normalized by restricting the center of $p_i$ to $0$.
-
-            \begin{theorem}\label{unique up to a rotation}
-                Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
-                \begin{align}\label{norm phi1}
-                    \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
-                \end{align}
-                then such $\Phi_1$ is unique up to a rotation $M_1$.
-            \end{theorem}
-
-            Before proving theorem \ref{unique up to a rotation}, we can consider following problem.
-Given boundary points $p_i$ on unit circle, can we find a Mobious transformation $M$ satisfies the following equation (\ref{fz})?
-            \begin{equation}\label{fz}
-                \sum_{k=1}^n M(p_k) = \sum_{k=1}^n e^{i\theta} \frac{p_k - a}{1 - \overline{a}p_k}= 0
-            \end{equation}
-
-            Without lose of generality, we ignore the rotation of $M$ and let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-So $F_a$ is also a Mobius transformation and it's sufficient to find $a \in \D$ such that
-            \begin{equation}\label{eq}
-                f(a) = \sum_{k=1}^n F_a(p_k) = \sum_{k=1}^n \frac{p_k - a}{1 - \overline{a}p_k} = 0
-            \end{equation}
-            to show the equation (\ref{fz}) holds for some $M$. Intuitively, we believe that there is always a unique solution to this equation (\ref{eq}) (see Fig \ref{fasolvable}).
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig6.png}
-                \end{center}
-                \caption{The first row are some randomly generated points in $\partial \D$.
-The second row are the corresponding $\abs{f(a)}$, where $a \in \D$.
-The third row are also $\abs{f(a)}$ but is in top view.
-}
-                \label{fasolvable}
-            \end{figure*}
-
-            \subsubsection{The solvability of equation (\ref{eq})}
-            First thing we want to do is to check whether this equation (\ref{eq}) is always solvable. According to Brouwer fixed point theorem, we have
-
-            \begin{theorem}\label{existence}
-                Given $\{p_1, p_2, \cdots, p_n\} \subset \partial \D$ and $n \ge 3$, let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-The solution of equation (\ref{eq}) always exists.
-            \end{theorem}
-
-            \begin{proof}
-                Note that when $e^{i \theta} \neq p_k$ for any $k$, we have
-                \begin{equation*}
-                    f(e^{i \theta}) = \sum_{k=1}^n \frac{p_k - e^{i \theta}}{1 - e^{-i\theta}p_k} = - n e^{i\theta},
-                \end{equation*}
-                so $\frac{1}{n} f(e^{i\theta}) + e^{i \theta} = 0$. Let 
-                \begin{equation*}
-                    g(a) = \begin{cases}
-                \frac{1}{n} f(a) + a, a \in \D,\\
-                0, a \in \partial \D,
-                \end{cases}
-                \end{equation*}
-                such $g$ is defined on $\overline{\D}$ and is continuous. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.
-
-                Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, then define
-                \begin{equation*}
-                    h(a) = \begin{cases}
-                    g(a), &a \in  \overline{\D} \setminus M,\\
-                    \frac{g(a)}{\norm{g(a)}}, &a \in  M.
-                \end{cases}
-                \end{equation*}
-                $h$ is a continuous map from $\overline{\D}$ to itself, so there exists some $a$ let $h(a) = a$.
-
-                If $a \in \partial \D$, $\norm{a} = 1$, but $\norm{h(a)} = 0 \neq \norm{a}$.
-If $a \in M$, we know $a \notin \partial \D$, so $\norm{a} < 1$, but $\norm{h(a)} = \frac{\norm{g(a)}}{\norm{g(a)}} = 1 \neq \norm{a}$.
-So when $h(a) = a$, $a$ is inside $\D \setminus M$.
-Therefore, such $a$ satisfies $g(a) = a$ and then $f(a) = 0$.
-            \end{proof}
-
-            Therefore, there must be some $a \in \D$ to be the solution of equation (\ref{fz}).
-
-            \subsubsection{The uniqueness of the solution of equation (\ref{eq})}
-            With solvability proved, we naturally want to know if this solution is unique. Let's consider a special case when $\sum_{k=1}^n p_k = 0$, we have
-            \begin{theorem}\label{uniqueness when 0}
-                Suppose $\sum_{k=1}^n p_k = 0$, equation (\ref{eq}) holds if and only if $a = 0$.
-            \end{theorem}
-
-            \begin{proof}
-                If $a = 0$, it's obvious $F_0$ is identity, so $f(0) = \sum_{k=1}^n p_k = 0$.
-
-                If $a \neq 0$, WLOG, we can assume that $0 < a < 1$, then $F_a(1) = 1$ and $F_a(-1) = -1$.
-For any $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$,
-                \begin{align*}
-                    &F_a(p_k) \\
-                    = &F_a(\cos \theta_k + \sin \theta_k i) \\
-                    = &\frac{\cos \theta_k + \sin \theta_k i - a}{1 - a \cos \theta_k - a \sin \theta_k i} \\
-                    = &\frac{(a^2 + 1) \cos \theta_k -2a - (a^2 - 1) \sin \theta_k i}{a^2 + 1 - 2a \cos \theta_k},
-                \end{align*}
-                so
-                \begin{align*}
-                    &\Re(F_a(p_k)) \\
-                    = &\frac{(a^2 + 1) \cos \theta_k -2a}{a^2 + 1 - 2a \cos \theta_k} \\
-                    = &\cos \theta_k - \frac{2a(1-\cos^2 \theta_k)}{(a-1)^2 + 2a(1-\cos \theta_k)} \\
-                    < &\cos \theta_k = \Re(p_k).
-                \end{align*}
-
-                Therefore, if $n \ge 3$, there must be at least one $p_k \neq \pm 1$ and so
-                \begin{align*}
-                    &\Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) \\
-                    < &\sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
-                \end{align*}
-                which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $a=0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
-            \end{proof}
-
-            This theorem confirms the uniqueness for a special situation $\sum_{k=1}^n p_k = 0$ and actually this conclusion is universal no matter how $p_i$ distribute.
-
-            \begin{theorem}\label{uniqueness}
-                The solution of equation (\ref{eq}) is unique.
-            \end{theorem}
-
-            \begin{proof}
-                Assume that $a_0, a_1$ are two different solutions, then we have that
-                \begin{align*}
-                    \sum_{k=1}^n F_{a_0}(p_k) = 0,\sum_{k=1}^n F_{a_1}(p_k) = 0
-                \end{align*}
-
-                Let $p_k' = F_{a_0}(p_k)$, then
-                \begin{align*}
-                    &\sum_{k=1}^n F_{a_1} \circ F_{a_0}^{-1} \circ F_{a_0}(p_k)\\
-                    = &\sum_{k=1}^n (F_{a_1} \circ F_{-a_0})(F_{a_0}(p_k))\\
-                    = &\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}}\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0.
-                \end{align*}
-
-                Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so \\
-                $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$. According to theorem \ref{uniqueness when 0},\\
-                $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, then $a_0 = a_1$, which contradicts to the assumption.
-            \end{proof}
-
-            \subsubsection{Unque $\Phi_1$ up to a rotation}
-
-            Above theorems show that there is alway an unique solution $a \in \D$ for equation (\ref{eq}), so we can come back to theorem \ref{unique up to a rotation}.
-
-            \begin{proof}
-                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobious transformation.
-If $\Phi_1$, $\tilde{\Phi_1} $ satisfy equation (\ref{norm phi1}), let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M_1^{-1} (p_k) = 0$.
-$M_1^{-1}$ is also a Mobious transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
-                \begin{equation*}
-                    e^{i \theta} \sum_{k=1}^n F_a(p_k) = 0.
-                \end{equation*}
-
-                From theorem \ref{uniqueness when 0} we can know $a = 0$, then $M_1^{-1}(z) = e^{i \theta} z$ and $\Phi_1$ is unique up to a rotation $M_1$.
-            \end{proof}
-
-        \subsection{Normalization to $M_2$}\label{norm2}
-            As for $M_2$, we hope it is identity, which is equivalent with the uniqueness of $\Phi_2: \D^c \rightarrow \Omega^c$.
-Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this and derivative to guarantee the uniqueness.
-
-            \begin{theorem}
-                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobious transformation.
-If $\tilde{\Phi_2}, \Phi_2$ satisifies that
-                \begin{align}
-                    &\tilde{\Phi_2}(\infty) = \Phi_2(\infty) = \infty\label{norm phi2 1}\\
-                    &\argmax{z \in \partial \D} \abs{\Phi_2'(z)} = \argmax{z \in \partial \D} \abs{\tilde{\Phi_2'}(z)} = 1,\label{norm phi2 2}
-                \end{align}
-                then such $M_2$ is identity.
-            \end{theorem}
-
-            \begin{proof}
-                Suppose Mobious transformation $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$. Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisify (\ref{norm phi2 1}), then
-                \begin{align*}
-                    &\tilde{\Phi}_2(\infty) = \Phi_2(M_2(\infty)) = \infty, \\
-                    &\Phi_2(\infty) = \infty.
-                \end{align*}
-                Therefore, $M_2(\infty) = e^{i \theta} \frac{\infty - a}{1- \overline{a} \infty} = \infty$, which means that $a = 0$ and $M_2(z) = e^{i \theta} z$.
-
-                Consider the derivative of $\tilde{\Phi}_2$,
-                \begin{equation}
-                    \tilde{\Phi}_2'(z) = \Phi_2' \circ M_2(z) \cdot M_2'(z) = e^{i\theta} \Phi_2' (e^{i \theta}z),
-                \end{equation}
-                then we know that $\abs{\tilde{\Phi}_2'(z)} = \abs{\Phi_2'(e^{i \theta}z)}$.
-Suppose $a = \argmax{z \in \partial \D} |\Phi_2'(z)|$, then we will have that $ae^{-i \theta} = \argmax{z \in \partial \D} |\tilde{\Phi}_2'(z)|$.
-                If condition (\ref{norm phi2 2}) holds for both $\tilde{\Phi}_2$ and $\Phi_2$, it means $a = a e^{-i \theta} = 1$, so $a = 1$, $\theta = 0$ and $M_2$ is identity.
-            \end{proof}
-
-        \subsection{Invariance under simple transformation}
-            With the normalization mentioned above, we can get unique Beltrami signature $B$ corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$.
-Now we want to prove that if we do some simple transformation like rotation, scaling and translation to $\Omega$, the Beltrami signature is invariant.
-
-            \begin{theorem}
-                Given a boundary simple connected domain $\Omega$ and transformation $T$ which is composed by rotation, scaling and transformation.
-Let $B_\Omega$ and $B_{T(\Omega)}$ be the Beltrami signature of $\Omega$ and $T(\Omega)$, then $B_\Omega = B_{T(\Omega)}$
-            \end{theorem}
-
-            \begin{proof}
-                Suppose $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, $\tilde{\Phi}_1: \D \rightarrow T(\Omega)$ and $\tilde{\Phi}_2 : \D^c \rightarrow T(\Omega)$ are conformal.
-Since $T$ is composed by rotation, scaling and translation, $T$ can be written as $T(z) = ke^{i\theta} z + b$.
-Such $T$ is absolutely invertible and conformal.
-
-                Let $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1 : \D \rightarrow \Omega$, $\hat{\Phi}_1$ is conformal.
-Given the boundary points $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$, then $\{T(z_1), T(z_2), \cdots, T(z_n)\} \subset \partial T(\Omega)$.
-Since $\tilde{\Phi}_1$ satisifies condition (\ref{norm phi1}), we have
-                \begin{equation*}
-                    \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0.
-                \end{equation*}
-
-                Therefore
-                \begin{equation*}
-                    \sum_{i=1}^n \hat{\Phi}_1^{-1}(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1} \circ T(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0,
-                \end{equation*}
-                which means $\hat{\Phi}_1$ also satisifies condition (\ref{norm phi1}). Hence $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1= \Phi_1 \circ R$, which equals to
-                \begin{equation}
-                    \tilde{\Phi}_1 = T \circ \Phi_1 \circ R,
-                \end{equation}
-                where $R$ is a rotation.
-
-                Similarly, let $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2: \D^c \rightarrow \Omega^c$, $\hat{\Phi}_2$ is conformal. Since $\tilde{\Phi}_2(\infty) = \infty$, we have
-                \begin{equation*}
-                    \hat{\Phi}_2(\infty) = T \circ \tilde{\Phi}_2(\infty) = \infty,
-                \end{equation*}
-                which means $\hat{\Phi}_2$ satisifies condition (\ref{norm phi2 1}).
-
-                As for condition (\ref{norm phi2 2}), we know that $T'(z) = k e^{i \theta}$, so
-                \begin{equation}
-                    \hat{\Phi}_2'(z) = T' \circ \tilde{\Phi}_2(z) \cdot \tilde{\Phi}_2'(z) = k e^{i \theta} \tilde{\Phi}_2'(z).
-                \end{equation}
-                Hence $\abs{\hat{\Phi}_2'} = \abs{k}\abs{\tilde{\Phi}_2'}$, which means $\hat{\Phi}_2$ also satisifies condition (\ref{norm phi2 2}).
-Therefore, $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2 = \Phi_2$ and then
-                \begin{equation}
-                    \tilde{\Phi}_2 = T \circ \Phi_2.
-                \end{equation}
-
-                We have the conformal welding
-                \begin{equation}
-                    \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = R^{-1} \circ \Phi_1^{-1} \circ T^{-1} \circ T \circ \Phi_2 = R^{-1} \circ f.
-                \end{equation}
-                Then the harmonic extension $\tilde{H} = R^{-1} \circ H$ and 
-                \begin{equation}
-                    B_{T(\Omega)} = \mu_{\tilde{H}} = \mu_{R^{-1} \circ H} = \mu_H = B_\Omega.
-                \end{equation}
-            \end{proof}
-
-    \section{Implementation detail}\label{implementation}
-        \subsection{Zipper algorithm}
-            In oder to find an unique and stable Beltrami signature, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
-As metioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
-
-            Marshall \etal demonstrates the zipper algorithm detailedly with clear diagrams in \cite{marshall2007convergence}.
-For the convenience of readers, we gives a very brief review here.
-Given $N$ clockwise boundary points $z_1, z_2, \cdots, z_N \in \partial \Omega$, this algorithm use a series of linear fractional transformations $g_1, g_2, \cdots, g_N$ to map $z_1, z_2,\cdots, z_N$ to real axis one-by-one, and finally transfrom the upper half plane to unit disk by $g_{N+1}(z) = \frac{z-i}{z+i}$.
-Therefore, $g = g_{N+1} \circ g_N \circ \cdots \circ g_2 \circ g_1$ is a conformal mapping undisputedly and maps all these boundary points to unit circle and the domain $\Omega$ to $\D$.
-Remark that zipper algorithm is sensitive to the order of points.
-If we input the points anti-clockwise, i.e.
-$z_N, z_{N-1}, \cdots, z_1$, the zipper will give us a conformal mapping from $\Omega^c$ to $\D$.
-
-            For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputing points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$.
+    For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputting points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$.
 For $\Phi_2 : \D^c \rightarrow \Omega^c$, we can input anti-clockwise points and get $g_{\Phi_2} : \Omega^c \rightarrow \D$.
@@
 
-        \subsection{Harmonic extension}\label{detail harmonic}
+\section{Harmonic extension}\label{detail harmonic}
     After obtaining the output of zipper algorithm, $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$, the conformal welding can be represented as a series points 
@@
 
-        \subsection{Normalization}
-            Because of the arbitrariness of the comformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
+\section{Normalization}
+    Because of the arbitrariness of the conformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
     \begin{equation*}
@@
     \end{equation*}
-            Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then Beltrami signature $B$ can be unique.
-This section will tells how to satisfy equation (\ref{norm phi1}), (\ref{norm phi2 1}) and (\ref{norm phi2 2}) from the output of zipper algorithm.
+    Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then HBS $B$ can be unique.
+This section will tells how to satisfy equation (\ref{norm phi1}) and (\ref{norm phi2 1}) from the output of zipper algorithm.
 
     To normalization $M_1$, we need to solve equation (\ref{eq}).
-Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concerntrate around a point.
+Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concentrate around a point.
 At that time, $\abs{f(a)} \approx 1$ almost everywhere and the solution of (\ref{eq}) is also very close to the point.
@@
         \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig7_down.png}
+            \includegraphics[width=6cm]{fig7.png}
         \end{center}
-                \caption{(a) The $p_i \in \partial \D$ gather in a small neiborhood around their arithmetic mean $p_c$, which is labeled in red.
-(b) The corresponding $\abs{f(a)}$ for these $p_i$.
-It's worth to metion that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
+        \caption{(a) The $p_i \in \partial \D$ gather in a small neighborhood around their arithmetic mean $p_c$, which is labeled in red; (b) The corresponding $\abs{f(a)}$ for these $p_i$.
+It's worth to mention that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
         \label{original distribution}
@@
         \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig8_down.png}
+            \includegraphics[width=6cm]{fig8.png}
         \end{center}
-                \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment. (b) The $\abs{f(a)}$.}
+        \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment; (b) The $\abs{f(a)}$.}
     \end{figure}
 
-            Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobious transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
+    Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobi\"us transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
 For the $r$-th iteration, let
@@
     as the arithmetic center of $p_{i,r} \in \partial \D$.
-Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobious transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
+Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobi\"us transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
     \begin{equation*}
@@
         %\STATE Compute $p_i = F_a(p_{i,r})$.
-                \RETURN Mobious transformation $M_{\Phi_1}$.%, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
+        \RETURN Mobi\"us transformation $M_{\Phi_1}$.%, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
     \end{algorithmic}
@@
 
-            \begin{figure*}
+    \begin{figure}
         \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig9.png}
+            \includegraphics[width=10cm]{fig9.png}
         \end{center}
         \caption{The iteration of distribution adjustment. The boundary points are blue and their arithmetic center is red in each picture. (a)-(d) The 1st, 3rd, 7th, 12th iteration.}
-            \end{figure*}
+    \end{figure}
 
@@
 
-            According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
+    % According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
 And another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
@@
 
-            Therefore, the maximal solution
-            \begin{equation}
-                \theta_{\max} = \argmax{j \in [1,10^5]} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}
-            \end{equation}
-            can be used to normalize the rotation and the final mapping is 
-            \begin{equation}
-                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{\max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
-            \end{equation}
-            where $M_{\Phi_2} = e^{i \theta_{\max}} F_{ce^{-i \theta_{\max}}}$.
+    % Therefore, the maximal solution
+    % \begin{equation}
+    %     \theta_{\max} = \argmax{j \in [1,10^5]} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}
+    % \end{equation}
+    % can be used to normalize the rotation and the final mapping is 
+    % \begin{equation}
+    %     \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{\max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
+    % \end{equation}
+    % where $M_{\Phi_2} = e^{i \theta_{\max}} F_{ce^{-i \theta_{\max}}}$.
 
@@
         \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$ and $c = -\frac{1}{\bar{b}}$.
-                \STATE Let $F_c(z) = \frac{z-c}{1-\overline{c}z}$ and $\tilde{\Phi}_2(z)=\Phi_2 \circ F_{c}(z)$.
-                \STATE Let $\theta_j = \frac{2\pi}{M}(j-1)$ for $j=1,2, \cdots, M$.
-                \STATE Find maximal value of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ and corresponding $\theta_{\max}$.
-                \STATE Let $M_{\Phi_2} = e^{i \theta_{\max}} F_{ce^{-i \theta_{\max}}}$.
-                \RETURN Mobious transformation $M_{\Phi_2}$
+        \STATE Let $F_c(z) = \frac{z-c}{1-\overline{c}z}$ and $M_{\Phi_2} = F_{c}$.
+        \RETURN Mobi\"us transformation $M_{\Phi_2}$
         % \RETURN Conformal mapping $\hat{\Phi}_2: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
@@
 
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig10.png}
-                \end{center}
-                \caption{The change of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ for different $\theta_j \in [0, 2\pi)$.
-It shows this function has a significant maximum and $\theta_{\max}$ is about $1.25\pi$.}
-                \label{derative}
-            \end{figure}
-
-            After obatining Mobious transformations $M_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
+    After obtaining Mobi\"us transformations $M_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
     \begin{align*}
@@
     \end{align*}
-            and it is unique up to a rotation.
+    and it is unique up to rotation. Finally, the desired HBS can be generated from $\mu_{\hat{H}}$ according to equation (\ref{normaled B}).
 
-        \subsection{Summary of the Algorithm}
+\section{Summary of the Algorithm}
     The totally algorithm is as following.
     \begin{algorithm}[H]
-            \caption{Calculate Beltrami signature}
+    \caption{Calculate HBS}
     \label{alg all}
     \begin{algorithmic}
-                \STATE \textbf{Inputs:} Simple connected shape $\Omega \subset \C$, $N=200$.
+        \STATE \textbf{Inputs:} Simply-connected shape $\Omega \subset \C$, $N=200$.
         \STATE Pick clockwise points $z_1, \cdots, z_N \in \partial \Omega$ uniformly.
@@
         \STATE Calculate normalized harmonic extension $\hat{H} = M_{\Phi_1} \circ H \circ M_{\Phi_2}$.
-                \STATE Calculate Beltrami coefficient $B$ of $\hat{H}$.
-                \RETURN Beltrami signature $B$.
+        \STATE Calculate Beltrami coefficient $\mu_{\hat{H}}$.
+        \STATE Calculate $\theta = \arg \int_\D \mu_{\hat{H}}(z) dz$.
+        \STATE Let $B(z) = e^{i \theta} \mu_{\hat{H}}(e^{-\frac{1}{2}i\theta} z)$.
+        \RETURN Harmonic Beltrami signature $B$.
     \end{algorithmic}
     \end{algorithm}
-    \section{Experimental result}\label{result}
-        In this section, we will validate key properties of our proposed Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
-Besides that, a good shape representation should keep the similarity with the same kind shape and is significantly different from different kinds of shape.
-
-        Before showing results, what needs illustration is that the distance we used to measure the difference of Beltrami signature is based on $L^2$ norm,
-        \begin{equation}\label{bs dis}
-            d(B_1, B_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{B_1(z_i) - B_2(z_i)}^2},
-        \end{equation}
-        where $B_1, B_2$ are two different Beltrami signature, $z_i \in \D$ is the face center of triangluar mesh $M$ metioned in Section \ref{detail harmonic} and $N=60962$ here.
-        \subsection{Invariance}\label{sec inv}
-            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate Beltrami signature after sacling, translation and rotation and compare them with the original shape's Beltrami signature.
-The result is displayed in Fig \ref{inv}.
-In this figure, the first column are the sets of boundary points and we remark them as $\Omega_a$ to $\Omega_f$.
-The second column are the corresponding Beltrami signatures $B_a$ to $B_f$.
-Note that all the Beltrami signatures are shown in modulus, i.e.
-$\abs{B_n}$ for row $n$, and in top view.
-And the third column(if have) are the histograms of the difference between original shape's Beltrami signature, i.e.
-$\abs{B_n - B_a}$ for row $n$.
-
-            Row b and c are about scaling, the shapes are $\Omega_b = \{z \mid z = 1.5 z_a, z_a \in \Omega_a \}$ and $\Omega_c = \{z \mid z = 0.5 z_a, z_a \in \Omega_a \}$ and the distance are $d(B_a, B_b) = 5.5647 \times 10^{-8}$ and $d(B_a, B_c) = 5.3476 \times 10^{-8}$.
-Row d is about translation, the shape $\Omega_d = \{z \mid z = z_a+100+20i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_d) = 4.7817 \times 10^{-8}$.
-Row e is about rotation, the shape is $\Omega_e = \{z \mid z = e^{0.2\pi i} z_a, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.2144 \times 10^{-8}$.
-Row f is the combination of scaling, tanslation and rotation, the shape is $\Omega_e = \{z \mid z = 3e^{-0.85\pi i} z_a+350+600i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.7635 \times 10^{-8}$.
-These confirm the invariance of Beltrami signature and scaling, translation and rotation.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/inv.png}
-                \end{center}
-                \caption{Beltrami signature under scaling, translation and rotation.}
-                \label{inv}
-            \end{figure*}
-
-        \subsection{Robustness}
-            Similar with Section \ref{sec inv}, here we still treat the dolphin as the original shape and modify some small parts of it and Fig \ref{robust} is the result.
-It shows that the proposed signature is robust and stable and will not have a big mutation cauesd by small disturbance.
-
-            Row g, h and i are result about modification.
-These shapes are generated by removing or adding something, which is in the red circle.
-We can see that Beltrami signatures have slight differences from $B_a$ but are still similar in general.
-And this figure also demonstrates that the bigger the modification part is, the more different the Beltrami signature is.
-For example in row i, losing a half of the tail makes the signature has a marked change.
-Quantitatively, $d(B_a, B_g) = 0.0132$, $d(B_a, B_h) = 0.0316$ and $d(B_a, B_i) = 0.1761$.
-
-            Row j is for distortion. This dolphin is only enlarged in horizontally and becomes fatter, then the $B_j$ moves a little bit and $d(B_a, B_j) = 0.0724$.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/robust.png}
-                \end{center}
-                \caption{Beltrami signature under small modification}
-                \label{robust}
-            \end{figure*}
-
-        \subsection{Classification with Beltrami signature}
-            Above properties ensure the proposed signature having the ablity to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.
-
-            To compare the classification performance, we also use conformal welding directly to classify, and the distance is defined as
-            \begin{equation}\label{welding dis}
-                d_c(f_1, f_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{f_1(z_i) - f_2(z_i)}^2},
-            \end{equation}
-            where $f_1, f_2$ are two different conformal welding, $N=200$ here.
-
-            We prepare 3 kinds of animals, fish, giraffe and elephant.
-There are 3 images for each group so 9 images in total.
-From Fig \ref{classification images}, we can find that each class share similar Beltrami signatures and conformal welding.
-From Fig \ref{dis matrix}, the inter-class distance of Beltrami signature is awlays less than 0.2 while the intra-class distance is greater than 0.2.
-But for conformal welding, the data is messy, for example, fish 3 thinks itself is very different from other fishes but looks most like giraffe 2.
-After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the Beltrami signature shows powerful classification ablity.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/figs.png}
-                \end{center}
-                \caption{These 3 rows are elephant, fish and giraffe. In each subfigure, the top left is the input shape, bottom left is the conformal welding and the right is Beltrami signature.}
-                \label{classification images}
-            \end{figure*}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/distance_down.png}
-                \end{center}
-                \caption{(a) The distance matrix of Beltrami signatures of above 9 shapes by equation (\ref{bs dis}). (b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
-                \label{dis matrix}
-            \end{figure}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/mds_down.png}
-                \end{center}
-                \caption{(a) The MDS result of Beltrami signature. (b) The MDS result of conformal welding.}
-                \label{mds1}
-            \end{figure}
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/mds2.png}
-                \end{center}
-                \caption{(a) The MDS result of Beltrami signature.
-(b) The MDS result of conformal welding.
-(c) The clustering result of Beltrami signature.
-(d) The clustering results of conformal welding.}
-                \label{mds2}
-            \end{figure*}
-
-        \subsection{Classification for more classes}
-            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabit.
-We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes.
-The MDS and clustering results based on Beltrami signature and conformal welding are displayed in Fig \ref{mds2}.
-The classification accuracy based on Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
-
-    \section{Conclusion}\label{conclusion}
-        In this paper, we propose a novel shape representation for 2D bounded simple connected objects called Beltrami signature.
-The proposed signature is based on conformal welding but overcome a key shortcoming that it can be uniquely determined by the given shape.
-What's more exciting is that the proposed representation is invariance under scaling, translation and rotation.
-For slight deformation and distortion, Beltrami signature keeps roubost and only changes within a reasonable small range.
-Therefore, there are reasons to believe the it does have ablity to represent some invariant geometrical features.
-The experimental results also confirm that the Beltrami signature has excellent performance in multi-classification tasks.
-
-        Although our work has achieved relatively good results, the proposed representation still have some limitations.
-Firstly, the Beltrami signature is only applicable to simple connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world.
-So we are eager for a feasible method to extend our Beltrami signature to multi connected situation.
-Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangluar mesh, which consumes a lot of time.
-Therefore, a fast algorithm to obatin this signature avoiding dense mesh is of high priority in our future work.
-Thirdly, when normalizing the conformal mapping $\Phi_2$ from exterior of unit disk to exterior of the domain, the position where the derivation of $\Phi_2$ reaches the maximum value is used to adjust the rotation.
-We trust this point in the original image has a certain geometric meaning, whereas it is not clear at present.
-
-        In summary, we will focus on third marjor directions in the future.
-One is that the deeper meaning of Beltrami signature is worth digging and then a multi-connected version of representation based on this work can be proposed.
-Another is that if the Beltrami signature contains some geometrical features of shapes, we can also extract them directly from images and generate the Beltrami signature again.
-Hence the deep learning theory may help us to compute this signature from given images immediately, which is very likely to improve algorithm speed performance greatly.
-A third direction is this representation can be used in more applications like segementation, registration and so on.
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
-% \section*{Conflict of interest}
-%
-% The authors declare that they have no conflict of interest.
-
-% BibTeX users please use one of
-% \bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
-\bibliography{cite}
-% Non-BibTeX users please use
-% \begin{thebibliography}{}
-% %
-% % and use \bibitem to create references. Consult the Instructions
-% % for authors for reference list style.
-% %
-% \bibitem{RefJ}
-% % Format for Journal Reference
-% Author, Article title, Journal, Volume, page numbers (year)
-% % Format for books
-% \bibitem{RefB}
-% Author, Book title, page numbers. Publisher, place (year)
-% % etc
-% \end{thebibliography}
-
-\end{document}
-% end of file template.tex

### 2021-06-11 Relatedworks/relatedworks.tex
final thesis

\chapter{Related works}\label{related work}
Shape representation and description is an enduring field and there have been extensive and in-depth discussions in the past several decades. Demisse \etal \cite{demisse2017deformation} proposed a method to represent an ordered set of points sampled from a curved shape as an element of a finite dimensional matrix Lie group. Mokhtarian \etal \cite{mokhtarian1997efficient} use the maxima of curvature zero-crossing contours of Curvature Scale Space image to represent the shapes of object boundary contours. Lui \etal \cite{lui2013shape} extracted each component of a 2D multi-connected shape, then the conformal weldings represent all components and conformal modules describe relationships between components.

A more meticulous survery about shape representations can be found in \cite{zhang2004review}. Generally speaking, all of these representation techniques can be divided into two major categories, \textit{contour-based} methods and \textit{region-based} methods, depending on whether shape features are extracted from the contour only or from the whole shape region. And the proposed Harmonic Beltrami signature in this thesis is a contour-based method.

\section{Contour-based methods}
As its name suggests, this kind of representations only exploits the information providing by shape boundary. There are generally two types of very different approaches for contour shape modeling: continuous approach (global) and discrete approach (structural).

\subsection{Contunuous approaches}
Continuous approaches do not divide shape into sub-parts and it is A very natural idea is that the boundary can be taken as a whole, from which a multi-dimensional numeric feature vector can be calculated and becomes the demanded representation. Then we will use some metric distance on theses vectors to measure the similarity of shape.

The simplest features are area, circularity, curvature and so on and their combination can be also used as shape representation. Peura \etal \cite{peura1997efficiency} proposed such descriptor including convexity, ratio of principle axis, circular variance and elliptic variance.

Belongie \etal \cite{belongie2002shape} tried in a different way and build a representation based on Hausdorff distance, called \textit{shape contexts}. Shape matching using shape contexts is an improvement to traditional Hausdorff distance based methods. It extracts a global feature, called shape context, for each boundary point. Given point $p$, the Hausdorff distance $r_{pq}$ and the orientation $\theta_{pq}$ with any other boundary point $q$ are calculated, then these $r_{pq}$ and $\theta_{pq}$ are quantized to create a histogram map $H_p$ which is used to represent the point $p$. All the histogram $H_p$ is flattened and concatenated to form the context of the shape. To make the histogram more sensitive to positions of nearby points than to those of points farther away, these vectors are put into log-polar space. This process is shown in Fig. \ref{shape contexts}.

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{shape_contexts.jpg}
\end{center}
\caption{Shape context. (a) a character shape; (b) edge image of (a); (c) some point $p$ on shape (a) and all the vectors started from $p$; (d) the log-polar histogram of the vectors in (c), the histogram is the context of point $p$; (e) the context map of shape (a), each row of the context map is the flattened histogram of each point context, the number of rows is the number of sampled points.}
\label{shape contexts}
\end{figure}

The \textit{scale space} is created by tracking the position of in inflection points in a shape boundary filtered by low-pass Gaussian filters of variable widths. As the width $\sigma$ of Gaussian filter increases, insignificant inflections are eliminated from the boundary and the shape becomes smoother (Fig. \ref{scale space}(a)). The inflection points that remain present in the representation are expectedto be significant object characteristics. The result of this smoothing process is an \textit{interval tree} consisting of inflection points (Fig. \ref{scale space}(b)). Asada \etal \cite{asada1986curvature} improve this method by take use of both Gaussian filter and secondd derivatives of Gaussian filter. The interpretation of the interval tree is based on detecting the peaks of the tree branches from higher scales to lower scales (Fig. \ref{scale space}(c)).

\begin{figure}
\begin{center}
\includegraphics[width=7cm]{scale_space.png}
\end{center}
\caption{(a) The evolution of shape boundary as scale $\sigma$ increases. From left to right: $\sigma=1, 4, 7, 10, 12, 14$. The points marked on the boundary are the inflection points; (b) the interval tree resulted from the smoothing process; (c) the peaks of the interval tree.}
\label{scale space}
\end{figure}

Boundary moments can be used to reduce the dimensions of the boundary representation. Sonka \etal \cite{sonka2014image} assume that the shape boundary has been represented as a shape signature $z(i)$, the $r$-th moment $m_r$ and central moment $\mu_r$ can be estimated as
$$
m_r= \frac{1}{N} \sum_{i=1}^N [z(i)]^r, \mu_r = \frac{1}{N} \sum_{i=1}^N [z(i)-m_1]^r,
$$
where $N$ is the number of boundary points. The normalized moments $\bar{m}_r=m_r /(\mu_2)^{r/2}$ and $\bar{\mu}_r=\mu_r /(\mu_2)^{r/2}$ are invariant to shape translation, rotation andscaling. Less noise-sensitive shape descriptors can be obtained from $F_1 = (\mu_2)^{1/2} / m1$, $F_2 = \mu_3/(\mu_2)^{3/2}$, and $F_3 = \mu_4/(\mu_2)^2$.

\subsection{Discrete approaches}
Another member in the shape analysis family is the \textit{discrete shape representation}. With the this kind of approaches, shapes are broken down into boundary segments called \textit{primitives}. Discrete methods differ in the selection of primitives and the organization of the primitives for shape representation.

The \textit{chain code} describes an object by a sequence of unit-size line segments with a given orientation, which was introduced by Freeman \etal \cite{freeman1961encoding}. In this approach, an arbitrary curve is represented by a sequence of small vectors of unit length and a limited set of possible directions. In the implementation, a digital boundary of an image is superimposed with a grid, the boundary points are approximated to the nearest grid point, then a sampled image is obtained. From a selected starting point, a chain code can be generated by using 4-directional or 8-directional chain code, as shown in Fig. \ref{chain code}. $N$-directional ($N > 8$ and $N = 2^k$) chain code is also possible, it is called \textit{general chain code} \cite{freeman1978generalized}.

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{chain_code.jpg}
\end{center}
\caption{(a) The four-connected chain codes: $(1,0,1,0,0,1,0,1)$; (b) The eight-connected chain codes: $(2,1,0,1,1)$.}
\label{chain code}
\end{figure}

Groskey \etal \cite{grosky1990index}\cite{grosky1992pictorial} proposed \textit{polygon decomposition} as representation. The given shape boundary is broken down into line segments by polygon approximation. The polygon vertices are used as primitives. The feature for each primitive is expressed as a four element string which consists of internal angle, distance from the next vertex, and its x and y coordinates. The similarity between any two shapes can be attained by comparing a fixed number (5 in the paper) of sharpest vertices selected from each shape.

Berretti \etal \cite{berretti2000retrieval} extended Groskey's model. The curvature zero-crossing points from a Gaussian smoothed boundary are used to obtain smooth curve, called \textit{tokens}. The feature for each token is its maximum curvature and its orientation, and the similarity between two tokens is measured by the weighted Euclidean distance.

\begin{figure}\label{Btokens}
\begin{center}
\includegraphics[width=7cm]{Btokens.png}
\caption{A horse shape has been divided into different tokens. The numbers corresponding to each token are the curvature and the orientation of the token.}
\end{center}
\end{figure}

\section{Region-based methods}
Different from the previous category, region-based representations make the best use of all the pixels within the given shape region. These methods can also be divided into global and structural methods, depending on whether they separate shapes into sub parts or not.

\subsection{Global approaches}
\textit{Global methods} treat shape as a whole, the result representation is a numeric feature vector which can be used for shape description. Similarity between shapes is simply measured by the metric distance between their feature vectors.

\textit{Geometric moment} is a classical and representative region-based shape description with form
\begin{equation*}
    m_{pq} = \sum_x \sum_y x^p y^q f(x, y),
\end{equation*}
where $p, q = 0, 1, 2, \cdots$ and $f$ is the given shape. Hu published the first significant paper about geometric moment and applied it in pattern recognition \cite{hu1962visual}. Using nonlinear combinations of the lower order moments, a set of moment invariants, which have the desirable properties of being invariant under translation, scaling and rotation, are derived.

Taubin \etal \cite{taubin1991object,taubin1991recognition} proposed \textit{algebraic moment}, which is computed from the first $m$ central moments and is given as the eigenvalues of predefined matrices, $M_{[j; k]}$, whose elements are scaled factors of the central moments. Different from Hu’s geometric moment invariants, the algebraic moment invariants can be constructed up to arbitrary order and are invariant to affine transformations.

Zhang \etal \cite{zhang2002generic} proposed \textit{generic Fourier descriptor} which is acquired by applying a 2D Fourier transform on a polar-raster sampled image (Fig. \ref{gfd})
\begin{equation*}
    PF_2(\rho, \phi) = \sum_r \sum_k f(r, \theta_k) e^{2 \pi i (\frac{r}{R} \rho + \theta_k \phi)},
\end{equation*}
where $0 \le r < R$, $0 \le \rho < R$, $0 \le k < T$, $0 \le \phi < T$, $\theta_k = \frac{2\pi k}{T}$ and $R, T$ are the radial frequency resolution and angular frequency resolution respectively. The normalized coefficients are the GFD. The similarity between two shapes are measured by the Manhattan distance between their GFDs.

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{gfd.png}
\end{center}
\caption{(a) An original shape in polar space; (b) polar-raster sampled image.}
\label{gfd}
\end{figure}

\subsection{Structural approaches}
Similar to the contour methods, region-based structural methods decompose the shape region into parts which are then used for shape representation and description.

The \textit{convex hull} of a region is the smallest convex region $H$ which satisfies the condition $R \subset H$. The difference $H - R$ is called the \textit{convex deficiency} $D$ of the region $R$. Therefore, in \cite{gonzalez2002digital}, the shape can be described by a tree of convex sets. Here the convex hull of an object is first obtained with its convex deficiencies, then the convex hulls and deficiencies of the convex deficiencies are found and so on until all the derived convex deficiencies are convex. This process is shown in Fig. \ref{convex hull}.

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{convex_hull.png}
\end{center}
\caption{(a) Convex hull andits concavities; (b) Concavity tree representation of convex hull}
\label{convex hull}
\end{figure}

Like the convex hull, a region skeleton can also be employed for shape representation and description, which is represented by Blum’s \textit{medial axis transform} \cite{blum1967transformation}. The medial axis is the locus of centers of maximal disks that fit within the shape. This is illustrated in Fig. \ref{mat}. The boldline in the figure is the skeleton of the shaded rectangular shape. The skeleton can then be decomposed into segments and represented as a graph according to certain criteria.

\begin{figure}
\begin{center}
\includegraphics[width=7cm]{mat.png}
\end{center}
\caption{Construction of the medial axis of a rectangular shape.}
\label{mat}
\end{figure}

### 2021-06-11 abstract.tex
final thesis

--- 2021-04-07 template.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-% \smartqed  % flush right qed marks, e.g. at end of proof
-%
-% \let\equation\relax
-% \let\endequation\relax
-\let\proof\relax
-\let\endproof\relax
-\let\example\relax
-\let\endexample\relax
+\chapter*{Abstract}
 
-\usepackage{graphicx}
-\usepackage[margin=1in]{geometry} 
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{hyperref}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\include{snippets}
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
-\begin{document}
-
-\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
-% \subtitle{Do you have a subtitle?\\ If so, write it here}
-
-%\titlerunning{Short form of title}        % if too long for running head
-
-\author{Chenran Lin \and Lok Ming Lui}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{Chenran Lin \at
-              Department of Mathematics, The Chinese University of Hong Kong \\
-              \email{crlin@math.cuhk.edu.hk}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           Lok Ming Lui \at
-              Department of Mathematics, The Chinese University of Hong Kong\\
-              \email{lmlui@math.cuhk.edu.hk}           %  \\
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simple connected domain in this paper, named Beltrami signature.
-The proposed signature is based on conformal welding.
-We extended the welding mapping to a harmonic function.
-With suitable normalization, the uniqueness of this harmonic function is guaranteed up to a rotation.
-And finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension.
-The benifits of the proposed signature is it keeps invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformation and distortion.
+There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simply-connected domains in this thesis, named the Harmonic Beltrami signature.
+The proposed signature is based on the harmonic extension of the conformal welding map of a unit circle.
+With suitable normalization, the uniqueness of this harmonic function is guaranteed up to rotations.
+And finally quasi-conformal theory helps get rid of the only uncertainty by computing the Beltrami coefficient of harmonic extension.
+There exists one-by-one relationship between shapes and our Harmonic Beltrami signatures and we also give the method to reconstruct the original shapes from our signatures.
+The benifit of the proposed signature is that it keeps to be invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformations and distortions.
 Experiments demonstrate the above properties and also show the excellent classification performance.
-\keywords{
-  Shape representation \and conformal welding \and simple connected \and invariance}
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
-\end{abstract}
-
-\section{Introduction}
-\label{intro}
-    The outline of the shape contains very important information and it can be used in many applications, such as segementation, recognition, registration and so on.
-However, even for the simplest situation, 2D simple connected shapes, it is a big challenge to describe clearly what the shape contour looks like.
-Because of the complexity of the image, there is an urgent demand to find a common, simple and robust shape representation for further mining and utilizing of shapes' geometric information.
-Therefore, many different presentations and measures have been widly studied and proposed recently \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.
-
-    Considering 2D simple connected shapes, conformal welding is a kind of well-known shape signature.
-Given 2D simple connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$.
-This gives a simple but wonderful representation of $\Omega$ as Fig.
-\ref{fig1} shows.
-However, it has two fatal defects.
-First is that such representation is not unique.
-Because of the arbitrary of Riemann conformal mapping, $\Phi_1$ and $\Phi_2$ can only be determined up to a Mobious transformation, so such conformal welding is not unique.
-Generally speaking, some assumption is required to remove this uncertainty.
-For example, Sharon \etal \cite{sharon20062d} need to select a base point $P$ inside the given domain $\Omega$ artificially, then let $\Phi_1$ maps $0$ to this point $P$.
-The work of Mcenteggart \etal \cite{mcenteggart2018uniqueness} is based on Schramm-Loewner evolution(SLE) on random surfaces called Liouville quantum gravity, they proved the equivalence between uniqueness of conformal welding and conformal removable and conculded that if the boundary curve $\eta$ is an $\text{SLE}_k$ for $k \in (0, 4)$ and satisifies some other requirements, the corresponding conformal welding is unique.
-Some may not that care the uniqueness itself, they used equivalent class to guarantee uniqueness in a broader sense or evne just ignored it \cite{katznelson1990conformal,marshall2012conformal,lui2013shape,astala2010random}.
-
-    Another thing is that even the conformal welding is very easy to be changed by simple transformations like rotation, scaling and translation.
-Such a unstable representation is hard to apply in practical applications since these transformations are inevitable in the real world.
-
-    The contribution of this paper is that we propose a brand new presentation for 2D simple connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Beltrami signature.
-Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points.
-Such conformal welding can be extended to the whole unit disk and get a harmonic function $H: \D \rightarrow \D$.
-Under suitable normalization, harmonic extension $H$ can be determined up to a rotation and the Beltrami coefficient of $H$ is then unique and becomes our Beltrami signature.
-
-    The proposed shape representation, Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
-The Beltrami signature is based on computational quasiconformal geometry.
-Computational quasiconformal geometry has been widely used in image processing and image analysis.
-Applications can be found in image segmentation
-    \cite{siu2020image,chan2018topology,zhang2020topology}
-    , image registration
-    \cite{lam2014landmark,lui2014teichmuller,ng2014computing,lui2012optimization,lam2014genus,zhang2012registration,lee2016landmark,lui2010optimized,lui2013texture,lui2010shape,lui2010optimizedc,lui2014geometric,choi2015flash}
-     and image analysis 
-    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shapec,lui2010shape3}
-    .
-What's more worth mentioning is that Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape.
-It means the proposed representation has high practical value and can be applied in computer vision work like classification, segementation and so on.
-
-    The paper is organized as follows: Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem and how Beltrami signature is obtained from given domain; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
-The paper is concluded in Section \ref{conclusion} and we point out future directions.
-
-    \begin{figure}
-        \begin{center}
-        \includegraphics[width=7.6cm]{src/fig1_down.png}
-        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simple connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
-        \end{center}
-        \label{fig1}
-    \end{figure}
-
-\section{Theoretical basis}\label{background}
-    \subsection{Quasi-conformal mapping and Beltrami equation}
-        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
-        \begin{equation*}
-            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
-        \end{equation*}
-
-        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
-        \begin{equation}\label{beltrami eq}
-            \Part{f}{\overline{z}} = \mu(z) \Part{f}{z}
-        \end{equation}
-        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$.
-More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
-        \begin{equation}
-            \mu = \frac{f_{\overline{z}}}{f_{z}}
-        \end{equation}
-        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
-        \begin{equation}
-            f^*(ds^2_E) = \abs{\Part{f}{z}}^2 \abs{dz + \mu(z)d\overline{z}}^2
-        \end{equation}
-        which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$.
-$\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality.
-In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$.
-Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
-        \begin{equation}\label{local f}
-            f(z) = f(p)+f_z(p)(z+\mu(p)\overline{z}).
-        \end{equation}
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig2.jpg}
-            \end{center}
-            \caption{(a) Shows the original hippocampus.
-(b) Shows the parameter domain with circle packing pattern.
-Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
-            \label{fig2}
-        \end{figure}
-
-        If $\mu(z)=0$ everywhere, then $f$ us called \textit{conformal} or \textit{holomorphic}. A conformal map satisfies the following well-known Cauchy-Riemann equation:
-        \begin{equation}\label{cr eq}
-            \Part{f}{\overline{z}} = 0.
-        \end{equation}
-        Inside the local parameter domain, $f$ may be considered as a map composed of a translation to $f(p)$ together with a stretch map $S(z) = z + \mu(p)\overline{z}$, which is postcomposed by multiplication of $f_z(p)$, which is conformal.
-All the conformal distortion of $S(z)$ is caused by $\mu(p)$.
-$S(z)$ is the map that causes $f$ to map a small circle to a small ellipse (see Fig.
-\ref{fig2}).
-Form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well.
-Specially, the angle of maximal magnification is $\arg(\mu(p))/2$ with magnifying factor $1+\abs{\mu(p)}$; the angle of maximal shrinkage is the orthogonal angle $\arg(\mu(p))/2 - \pi/2$ with shrinkage factor $1-\abs{\mu(p)}$.
-The distortion or dilation is given by:
-        \begin{equation}
-            K = \frac{1+\abs{\mu(p)}}{1-\abs{\mu(p)}}.
-        \end{equation}
-        Thus, the Beltrami coefficient $\mu$ gives us important information about the properties of the map (see Fig. \ref{fig3}).
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig3.jpg}
-            \end{center}
-            \caption{Quasi-conformal maps infinitesimal circles to ellipses. The Beltrami coefficient measure the distortion or dilation of the ellipse under the QC map.}
-            \label{fig3}
-        \end{figure}
-
-        Suppose $f, g: \C \rightarrow \C$ are complex-valued function with Beltrami coefficient $\mu_f, \mu_g$ respectively. Then the Beltrami coefficient for the composition $g \circ f$ is given by
-        \begin{equation}\label{mu of composition}
-            \mu_{g \circ f} = \frac{\mu_f+(\mu_g \circ f) \tau}{1+\overline{\mu_f}(\mu_g \circ f) \tau},
-        \end{equation}
-        where $\tau = \frac{\overline{f_z}}{f_z}$. Note that when $g$ is conformal, $\mu_g = 0$ and 
-        \begin{equation}\label{mu of conformal composition}
-            \mu_{g \circ f} = \mu_f.
-        \end{equation}
-
-    \subsection{Conformal welding}
-        Given 2D bounded simple connected shape, we can treat it as a boundary simple connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
-$\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobious transformation}:
-        \begin{equation}
-            M(z) = e^{i \theta} \frac{z - a}{1 - \overline{a}z}.
-        \end{equation}
-        Then we can define \textit{conformal welding} as:
-        \begin{equation}
-            f = \Phi_1^{-1} \circ \Phi_2.
-        \end{equation}
-        Such $f: \partial \D \rightarrow \partial \D$ is a diffeomorphism from $\partial \D$ to itself, which can be also thought as a periodic, real-valued monotone increasing function $f_\R: [0, 2\pi) \rightarrow [0, 2\pi)$ such that $f(e^{i \theta}) = e^{i f_\R(\theta)}$ (see Fig.
-\ref{fig1}).
-
-    \subsection{Harmonic function and Poisson integral}
-        A complex-valued function $f$ defined on $\Omega \subset \C$ is called \textit{harmonic} if it satisfies the \textit{Laplace's equation}:
-        \begin{equation}
-            \Delta f = 4 \frac{\partial^2 f}{\partial z \partial \overline{z}} = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2} = 0,
-        \end{equation}
-        where $z = x + iy$, $x$, $y$ is the real and imaginary value.
-
-        Chen \etal prove following theorem in \cite{chen2010compositions}, which tells us that the composition of harmonic mappings and other mappings can inherit such harmonicity in some condition.
-        \begin{theorem}\label{composition of harmonic}
-            Let $f$ be a harmonic mapping, $f \circ g$ is harmonic if and only if $g(z) = az + b \overline{z} + c$, where $a$, $b$ and $c$ are constaants and $g \circ f$ is harmonic if and only if $g$ is analytic or anti-analytic.
-        \end{theorem}
-
-        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}.
-For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
-            \begin{equation}\label{poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
-            \end{equation}
-        Such $H$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
-$H(e^{i\theta}) = f(e^{i\theta})$ (see Fig.
-\ref{harmonic}).
-Of course, this $H$ is unique.
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig4_down.png}
-            \end{center}
-            \caption{(a) Continious function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$.
-(b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
-Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
-            \label{harmonic}
-        \end{figure}
-
-    \section{Beltrami signature}\label{main}
-        In this chapter, we will propose a new representation, Beltrami signature, to discribe boundary simple connected domain $\Omega$.
-Our proposed signature is based on conformal welding and quasi-conformal theory.
-
-        \subsection{Beltrami signature based on conformal welding}
-            Here we give a brief explaination of how to create our new signature.
-Given the boundary simple connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it.
-Then $f$ can be extended to harmonic function $H$ defined on $\D$ by Poisson integral (\ref{poisson integral}).
-At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
-            \begin{equation}
-                B:= \mu_H = \frac{H_{\overline{z}}}{H_z}.
-            \end{equation}
-            Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $B$ is determined.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig5.png}
-                \end{center}
-                \caption{Illustration of Beltrami signature.
-(a) The input shape, a dolphin.
-(b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b).
-(c) The Beltrami signature of (a).
-Remark that the harmonic funcion and Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
-                \label{illu of BS}
-            \end{figure*}
-
-        \subsection{Analysis of uniqueness of Beltrami signature}
-            According to Riemann mapping theorem, the conformal mapings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
-Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobious transformations.
-Therefore, the corresponding conformal welding is
-            \begin{equation}
-                \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = M_1^{-1} \circ \Phi_1^{-1} \circ \Phi_2 \circ M_2 = M_1^{-1} \circ f \circ M_2.
-            \end{equation}
-
-            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{H}$. The following theorem show the relationship between $H$ and $\tilde{H}$.
-
-            \begin{theorem}
-                Suppose $f$ and $\tilde{f}$ are continious map from $\partial \D$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
-$H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
-            \end{theorem}
-
-            \begin{proof}
-                Since $M_1$ is a Mobious transformations, $M_1^{-1}$ is also a Mobious transformation, so it can be written as $M_1^{-1}(z) = e^{i \theta}\frac{z - p}{1 - \overline{p}z}$, where $\theta \in [0, 2\pi)$ and $p \in \D$.
-
-                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
-$\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
-Therefore, we have
-                \begin{equation*}
-                    e^{i \theta}\frac{z - p}{1 - \overline{p}z} = az + b \overline{z} + c,
-                \end{equation*}
-                which means $p = b = c = 0$, $a = e^{i \theta}$ and so $M_1$ is a rotation.
-
-                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ H \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}.
-It's easy to check that
-                \begin{align*}
-                    M_1^{-1} \circ H \circ M_2 (e^{i \theta})
-                    &= M_1^{-1} \circ f \circ M_2(e^{i \theta})\\
-                    &= \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
-                \end{align*}
-                which means $M_1^{-1} \circ H \circ M_2$ and $\tilde{H}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ H \circ M_2 = \tilde{H}$.
-            \end{proof}
-
-            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{H}$
-            \begin{equation}
-                \tilde{B} = \mu_{\tilde{H}} = \mu_{M_1^{-1} \circ H \circ M_2} = \mu_{H\circ M_2}.
-            \end{equation}
-            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, then we get $M_2$ is identity.
-Therefore, we know that the uniqueness of Beltrami signature is equivalent to following restrictions:
-            \begin{enumerate}
-                \item $M_1$ should be a rotation.
-                \item $M_2$ should be identity.
-            \end{enumerate}
-
-        \subsection{Normalization to $M_1$}\label{norm1}
-            We hope $M_1$ is a rotation.
-It is not that hard, for example, we can achieve it by restricting $\Phi_1(0) = 0$.
-But it need a hypothesis that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold.
-Here we want to show a new approach without any additional assumption.
-
-            In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$.
-Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, where $\Phi_1 : \D \rightarrow \Omega$.
-We claims that $M_1$ can be normalized by restricting the center of $p_i$ to $0$.
-
-            \begin{theorem}\label{unique up to a rotation}
-                Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
-                \begin{align}\label{norm phi1}
-                    \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
-                \end{align}
-                then such $\Phi_1$ is unique up to a rotation $M_1$.
-            \end{theorem}
-
-            Before proving theorem \ref{unique up to a rotation}, we can consider following problem.
-Given boundary points $p_i$ on unit circle, can we find a Mobious transformation $M$ satisfies the following equation (\ref{fz})?
-            \begin{equation}\label{fz}
-                \sum_{k=1}^n M(p_k) = \sum_{k=1}^n e^{i\theta} \frac{p_k - a}{1 - \overline{a}p_k}= 0
-            \end{equation}
-
-            Without lose of generality, we ignore the rotation of $M$ and let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-So $F_a$ is also a Mobius transformation and it's sufficient to find $a \in \D$ such that
-            \begin{equation}\label{eq}
-                f(a) = \sum_{k=1}^n F_a(p_k) = \sum_{k=1}^n \frac{p_k - a}{1 - \overline{a}p_k} = 0
-            \end{equation}
-            to show the equation (\ref{fz}) holds for some $M$. Intuitively, we believe that there is always a unique solution to this equation (\ref{eq}) (see Fig \ref{fasolvable}).
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig6.png}
-                \end{center}
-                \caption{The first row are some randomly generated points in $\partial \D$.
-The second row are the corresponding $\abs{f(a)}$, where $a \in \D$.
-The third row are also $\abs{f(a)}$ but is in top view.
-}
-                \label{fasolvable}
-            \end{figure*}
-
-            \subsubsection{The solvability of equation (\ref{eq})}
-            First thing we want to do is to check whether this equation (\ref{eq}) is always solvable. According to Brouwer fixed point theorem, we have
-
-            \begin{theorem}\label{existence}
-                Given $\{p_1, p_2, \cdots, p_n\} \subset \partial \D$ and $n \ge 3$, let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-The solution of equation (\ref{eq}) always exists.
-            \end{theorem}
-
-            \begin{proof}
-                Note that when $e^{i \theta} \neq p_k$ for any $k$, we have
-                \begin{equation*}
-                    f(e^{i \theta}) = \sum_{k=1}^n \frac{p_k - e^{i \theta}}{1 - e^{-i\theta}p_k} = - n e^{i\theta},
-                \end{equation*}
-                so $\frac{1}{n} f(e^{i\theta}) + e^{i \theta} = 0$. Let 
-                \begin{equation*}
-                    g(a) = \begin{cases}
-                \frac{1}{n} f(a) + a, a \in \D,\\
-                0, a \in \partial \D,
-                \end{cases}
-                \end{equation*}
-                such $g$ is defined on $\overline{\D}$ and is continuous. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.
-
-                Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, then define
-                \begin{equation*}
-                    h(a) = \begin{cases}
-                    g(a), &a \in  \overline{\D} \setminus M,\\
-                    \frac{g(a)}{\norm{g(a)}}, &a \in  M.
-                \end{cases}
-                \end{equation*}
-                $h$ is a continuous map from $\overline{\D}$ to itself, so there exists some $a$ let $h(a) = a$.
-
-                If $a \in \partial \D$, $\norm{a} = 1$, but $\norm{h(a)} = 0 \neq \norm{a}$.
-If $a \in M$, we know $a \notin \partial \D$, so $\norm{a} < 1$, but $\norm{h(a)} = \frac{\norm{g(a)}}{\norm{g(a)}} = 1 \neq \norm{a}$.
-So when $h(a) = a$, $a$ is inside $\D \setminus M$.
-Therefore, such $a$ satisfies $g(a) = a$ and then $f(a) = 0$.
-            \end{proof}
-
-            Therefore, there must be some $a \in \D$ to be the solution of equation (\ref{fz}).
-
-            \subsubsection{The uniqueness of the solution of equation (\ref{eq})}
-            With solvability proved, we naturally want to know if this solution is unique. Let's consider a special case when $\sum_{k=1}^n p_k = 0$, we have
-            \begin{theorem}\label{uniqueness when 0}
-                Suppose $\sum_{k=1}^n p_k = 0$, equation (\ref{eq}) holds if and only if $a = 0$.
-            \end{theorem}
-
-            \begin{proof}
-                If $a = 0$, it's obvious $F_0$ is identity, so $f(0) = \sum_{k=1}^n p_k = 0$.
-
-                If $a \neq 0$, WLOG, we can assume that $0 < a < 1$, then $F_a(1) = 1$ and $F_a(-1) = -1$.
-For any $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$,
-                \begin{align*}
-                    &F_a(p_k) \\
-                    = &F_a(\cos \theta_k + \sin \theta_k i) \\
-                    = &\frac{\cos \theta_k + \sin \theta_k i - a}{1 - a \cos \theta_k - a \sin \theta_k i} \\
-                    = &\frac{(a^2 + 1) \cos \theta_k -2a - (a^2 - 1) \sin \theta_k i}{a^2 + 1 - 2a \cos \theta_k},
-                \end{align*}
-                so
-                \begin{align*}
-                    &\Re(F_a(p_k)) \\
-                    = &\frac{(a^2 + 1) \cos \theta_k -2a}{a^2 + 1 - 2a \cos \theta_k} \\
-                    = &\cos \theta_k - \frac{2a(1-\cos^2 \theta_k)}{(a-1)^2 + 2a(1-\cos \theta_k)} \\
-                    < &\cos \theta_k = \Re(p_k).
-                \end{align*}
-
-                Therefore, if $n \ge 3$, there must be at least one $p_k \neq \pm 1$ and so
-                \begin{align*}
-                    &\Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) \\
-                    < &\sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
-                \end{align*}
-                which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $a=0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
-            \end{proof}
-
-            This theorem confirms the uniqueness for a special situation $\sum_{k=1}^n p_k = 0$ and actually this conclusion is universal no matter how $p_i$ distribute.
-
-            \begin{theorem}\label{uniqueness}
-                The solution of equation (\ref{eq}) is unique.
-            \end{theorem}
-
-            \begin{proof}
-                Assume that $a_0, a_1$ are two different solutions, then we have that
-                \begin{align*}
-                    \sum_{k=1}^n F_{a_0}(p_k) = 0,\sum_{k=1}^n F_{a_1}(p_k) = 0
-                \end{align*}
-
-                Let $p_k' = F_{a_0}(p_k)$, then
-                \begin{align*}
-                    &\sum_{k=1}^n F_{a_1} \circ F_{a_0}^{-1} \circ F_{a_0}(p_k)\\
-                    = &\sum_{k=1}^n (F_{a_1} \circ F_{-a_0})(F_{a_0}(p_k))\\
-                    = &\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}}\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0.
-                \end{align*}
-
-                Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so \\
-                $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$. According to theorem \ref{uniqueness when 0},\\
-                $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, then $a_0 = a_1$, which contradicts to the assumption.
-            \end{proof}
-
-            \subsubsection{Unque $\Phi_1$ up to a rotation}
-
-            Above theorems show that there is alway an unique solution $a \in \D$ for equation (\ref{eq}), so we can come back to theorem \ref{unique up to a rotation}.
-
-            \begin{proof}
-                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobious transformation.
-If $\Phi_1$, $\tilde{\Phi_1} $ satisfy equation (\ref{norm phi1}), let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M_1^{-1} (p_k) = 0$.
-$M_1^{-1}$ is also a Mobious transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
-                \begin{equation*}
-                    e^{i \theta} \sum_{k=1}^n F_a(p_k) = 0.
-                \end{equation*}
-
-                From theorem \ref{uniqueness when 0} we can know $a = 0$, then $M_1^{-1}(z) = e^{i \theta} z$ and $\Phi_1$ is unique up to a rotation $M_1$.
-            \end{proof}
-
-        \subsection{Normalization to $M_2$}\label{norm2}
-            As for $M_2$, we hope it is identity, which is equivalent with the uniqueness of $\Phi_2: \D^c \rightarrow \Omega^c$.
-Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this and derivative to guarantee the uniqueness.
-
-            \begin{theorem}
-                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobious transformation.
-If $\tilde{\Phi_2}, \Phi_2$ satisifies that
-                \begin{align}
-                    &\tilde{\Phi_2}(\infty) = \Phi_2(\infty) = \infty\label{norm phi2 1}\\
-                    &\argmax{z \in \partial \D} \abs{\Phi_2'(z)} = \argmax{z \in \partial \D} \abs{\tilde{\Phi_2'}(z)} = 1,\label{norm phi2 2}
-                \end{align}
-                then such $M_2$ is identity.
-            \end{theorem}
-
-            \begin{proof}
-                Suppose Mobious transformation $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$. Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisify (\ref{norm phi2 1}), then
-                \begin{align*}
-                    &\tilde{\Phi}_2(\infty) = \Phi_2(M_2(\infty)) = \infty, \\
-                    &\Phi_2(\infty) = \infty.
-                \end{align*}
-                Therefore, $M_2(\infty) = e^{i \theta} \frac{\infty - a}{1- \overline{a} \infty} = \infty$, which means that $a = 0$ and $M_2(z) = e^{i \theta} z$.
-
-                Consider the derivative of $\tilde{\Phi}_2$,
-                \begin{equation}
-                    \tilde{\Phi}_2'(z) = \Phi_2' \circ M_2(z) \cdot M_2'(z) = e^{i\theta} \Phi_2' (e^{i \theta}z),
-                \end{equation}
-                then we know that $\abs{\tilde{\Phi}_2'(z)} = \abs{\Phi_2'(e^{i \theta}z)}$.
-Suppose $a = \argmax{z \in \partial \D} |\Phi_2'(z)|$, then we will have that $ae^{-i \theta} = \argmax{z \in \partial \D} |\tilde{\Phi}_2'(z)|$.
-                If condition (\ref{norm phi2 2}) holds for both $\tilde{\Phi}_2$ and $\Phi_2$, it means $a = a e^{-i \theta} = 1$, so $a = 1$, $\theta = 0$ and $M_2$ is identity.
-            \end{proof}
-
-        \subsection{Invariance under simple transformation}
-            With the normalization mentioned above, we can get unique Beltrami signature $B$ corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$.
-Now we want to prove that if we do some simple transformation like rotation, scaling and translation to $\Omega$, the Beltrami signature is invariant.
-
-            \begin{theorem}
-                Given a boundary simple connected domain $\Omega$ and transformation $T$ which is composed by rotation, scaling and transformation.
-Let $B_\Omega$ and $B_{T(\Omega)}$ be the Beltrami signature of $\Omega$ and $T(\Omega)$, then $B_\Omega = B_{T(\Omega)}$
-            \end{theorem}
-
-            \begin{proof}
-                Suppose $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, $\tilde{\Phi}_1: \D \rightarrow T(\Omega)$ and $\tilde{\Phi}_2 : \D^c \rightarrow T(\Omega)$ are conformal.
-Since $T$ is composed by rotation, scaling and translation, $T$ can be written as $T(z) = ke^{i\theta} z + b$.
-Such $T$ is absolutely invertible and conformal.
-
-                Let $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1 : \D \rightarrow \Omega$, $\hat{\Phi}_1$ is conformal.
-Given the boundary points $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$, then $\{T(z_1), T(z_2), \cdots, T(z_n)\} \subset \partial T(\Omega)$.
-Since $\tilde{\Phi}_1$ satisifies condition (\ref{norm phi1}), we have
-                \begin{equation*}
-                    \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0.
-                \end{equation*}
-
-                Therefore
-                \begin{equation*}
-                    \sum_{i=1}^n \hat{\Phi}_1^{-1}(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1} \circ T(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0,
-                \end{equation*}
-                which means $\hat{\Phi}_1$ also satisifies condition (\ref{norm phi1}). Hence $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1= \Phi_1 \circ R$, which equals to
-                \begin{equation}
-                    \tilde{\Phi}_1 = T \circ \Phi_1 \circ R,
-                \end{equation}
-                where $R$ is a rotation.
-
-                Similarly, let $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2: \D^c \rightarrow \Omega^c$, $\hat{\Phi}_2$ is conformal. Since $\tilde{\Phi}_2(\infty) = \infty$, we have
-                \begin{equation*}
-                    \hat{\Phi}_2(\infty) = T \circ \tilde{\Phi}_2(\infty) = \infty,
-                \end{equation*}
-                which means $\hat{\Phi}_2$ satisifies condition (\ref{norm phi2 1}).
-
-                As for condition (\ref{norm phi2 2}), we know that $T'(z) = k e^{i \theta}$, so
-                \begin{equation}
-                    \hat{\Phi}_2'(z) = T' \circ \tilde{\Phi}_2(z) \cdot \tilde{\Phi}_2'(z) = k e^{i \theta} \tilde{\Phi}_2'(z).
-                \end{equation}
-                Hence $\abs{\hat{\Phi}_2'} = \abs{k}\abs{\tilde{\Phi}_2'}$, which means $\hat{\Phi}_2$ also satisifies condition (\ref{norm phi2 2}).
-Therefore, $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2 = \Phi_2$ and then
-                \begin{equation}
-                    \tilde{\Phi}_2 = T \circ \Phi_2.
-                \end{equation}
-
-                We have the conformal welding
-                \begin{equation}
-                    \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = R^{-1} \circ \Phi_1^{-1} \circ T^{-1} \circ T \circ \Phi_2 = R^{-1} \circ f.
-                \end{equation}
-                Then the harmonic extension $\tilde{H} = R^{-1} \circ H$ and 
-                \begin{equation}
-                    B_{T(\Omega)} = \mu_{\tilde{H}} = \mu_{R^{-1} \circ H} = \mu_H = B_\Omega.
-                \end{equation}
-            \end{proof}
-
-    \section{Implementation detail}\label{implementation}
-        \subsection{Zipper algorithm}
-            In oder to find an unique and stable Beltrami signature, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
-As metioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
-
-            Marshall \etal demonstrates the zipper algorithm detailedly with clear diagrams in \cite{marshall2007convergence}.
-For the convenience of readers, we gives a very brief review here.
-Given $N$ clockwise boundary points $z_1, z_2, \cdots, z_N \in \partial \Omega$, this algorithm use a series of linear fractional transformations $g_1, g_2, \cdots, g_N$ to map $z_1, z_2,\cdots, z_N$ to real axis one-by-one, and finally transfrom the upper half plane to unit disk by $g_{N+1}(z) = \frac{z-i}{z+i}$.
-Therefore, $g = g_{N+1} \circ g_N \circ \cdots \circ g_2 \circ g_1$ is a conformal mapping undisputedly and maps all these boundary points to unit circle and the domain $\Omega$ to $\D$.
-Remark that zipper algorithm is sensitive to the order of points.
-If we input the points anti-clockwise, i.e.
-$z_N, z_{N-1}, \cdots, z_1$, the zipper will give us a conformal mapping from $\Omega^c$ to $\D$.
-
-            For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputing points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$.
-For $\Phi_2 : \D^c \rightarrow \Omega^c$, we can input anti-clockwise points and get $g_{\Phi_2} : \Omega^c \rightarrow \D$.
-At the result $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-Because of the invariance of scaling, the number of boundary points $N$ is fixed as $200$ here and they are picked uniformly from the shape contour.
-
-            \begin{algorithm}[H]                           % HERE!!!!!!!!!
-            \caption{Zipper}          % give the algorithm a caption
-            \label{zipper}      % and a label for \ref{} commands later in the document
-            \begin{algorithmic}  % enter the algorithmic environment
-                \STATE \textbf{Inputs:} $z_i \in \partial \Omega$ for $i=1, 2, \cdots, N$, $N=200$. %, $\epsilon = 10^{-10}$(any very small value)
-                \STATE \textbf{Initialize:} Let $r=2$, $g_1(z) = \sqrt{\frac{z-z_2}{z-z_1}}$, $g= g_1$ and compute $p_{i,2}=g(z_i)$.
-                \WHILE{$r < N$}
-                    \STATE Pick $q = p_{r+1, r} = a + b i$, then compute $c = \frac{a}{\abs{q}^2}$, $d = \frac{b}{\abs{q}^2}$.
-                    \STATE Let $g_r(z) = \sqrt{\frac{cz}{1+dzi}}$, then $g = g_r \circ g$ and compute $p_{i, r+1} = g_r(p_{i, k})$.
-                    \STATE Let $r = r+1$.
-                \ENDWHILE
-                \STATE Let $g_{N}(z) = \left(\frac{z}{1-\frac{z}{p_{1,N}}}\right)^2$ and $g_{N+1}(z) = \frac{z-i}{z+i}$, then $g = g_{N+1} \circ g_N \circ g$ and $p_i = g_{N+1} \circ g_N(p_{i,N})$.
-                \RETURN Conformal mapping $g: \Omega \rightarrow \D$ and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-        \subsection{Harmonic extension}\label{detail harmonic}
-            After obtaining the output of zipper algorithm, $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$, the conformal welding can be represented as a series points
-            \begin{equation*}
-                (\varphi_i, \omega_i) = \left(\arg(\hat{\Phi}_2^{-1}(z_i)), \arg(\hat{\Phi}_1^{-1}(z_i))\right),
-            \end{equation*}
-            where $\varphi_i, \omega_i \in [0, 2\pi)$. So in fact we should use discrete form Poisson integral to extend $f$ to a harmonic mapping $H$ on the unit disk
-            \begin{equation}\label{discrete poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi} \sum_{j=1}^k \frac{(1-r^2) e^{i \omega_j} \gamma_j}{1 - 2 r cos (\varphi_j - \theta) + r^2} ,
-            \end{equation}
-            where $\gamma_j = (\varphi_{j} - \varphi_{j-1}) \bmod{ 2\pi}$ and $\varphi_0 = \varphi_k$ and this $\bmod$ can solve some critical value problem, for example, $\varphi_j = 0$ but $\varphi_{j-1} = 6$.
-For the convenience of computation, we only calculate the value of $H$ on a grid
-            \begin{align*}
-                G = \{z=x+iy \mid &\abs{z} \le 1, x=\frac{j}{100}, y=\frac{k}{100},\\
-                &j,k=-100,-99,\cdots,99,100 \}.
-            \end{align*}
-
-        \subsection{Normalization}
-            Because of the arbitrariness of the comformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
-            \begin{equation*}
-                \tilde{H} = M_1 \circ H \circ M_2.
-            \end{equation*}
-            Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then Beltrami signature $B$ can be unique.
-This section will tells how to satisfy equation (\ref{norm phi1}), (\ref{norm phi2 1}) and (\ref{norm phi2 2}) from the output of zipper algorithm.
-
-            To normalization $M_1$, we need to solve equation (\ref{eq}).
-Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concerntrate around a point.
-At that time, $\abs{f(a)} \approx 1$ almost everywhere and the solution of (\ref{eq}) is also very close to the point.
-This means the solution is quite unstable and hard to converge for common algorithms(see Fig \ref{original distribution}).
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig7_down.png}
-                \end{center}
-                \caption{(a) The $p_i \in \partial \D$ gather in a small neiborhood around their arithmetic mean $p_c$, which is labeled in red.
-(b) The corresponding $\abs{f(a)}$ for these $p_i$.
-It's worth to metion that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
-                \label{original distribution}
-            \end{figure}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig8_down.png}
-                \end{center}
-                \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment. (b) The $\abs{f(a)}$.}
-            \end{figure}
-
-            Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobious transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
-For the $r$-th iteration, let
-            \begin{equation*}
-                p_{c,r} = \frac{\sum_{i=1}^k p_{i,r}}{k} \in \D
-            \end{equation*}
-            as the arithmetic center of $p_{i,r} \in \partial \D$.
-Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobious transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
-            \begin{equation*}
-                p_{i,r+1} = F_{p_{c,r}}(p_{i,r}) = \frac{p_{i,r} - p_{c,r}}{1 - \overline{p_{c,r}}p_{i,r}}.
-            \end{equation*}
-            Note that we set $p_{i,0} = p_{i}$ at the beginning.
-Repeat this iteration for $r$ times until the center of boundary points is close to $0$, then the distribution is sufficiently regular and $\Phi_1$ becomes
-            \begin{equation}
-                \tilde{\Phi}_1 = \Phi_1 \circ F_{p_{c,0}}^{-1} \circ F_{p_{c,1}}^{-1} \circ \cdots \circ F_{p_{c,r}}^{-1}.
-            \end{equation}
-            Now equation (\ref{eq}) can be solved without much effort by Newtown's method. Suppose $a \in \D$ is the optimal solution and let 
-            \begin{equation*}
-                F_{\Phi_1} = F_a \circ F_{p_{c,r}} \circ F_{p_{c,r-1}} \circ \cdots \circ F_{p_{c, 0}}
-            \end{equation*}
-            and the final conformal mapping satisfying (\ref{norm phi1}) is
-            \begin{equation}
-                \hat{\Phi}_1 = \tilde{\Phi}_1 \circ F_{a}^{-1} = \Phi_1 \circ F_{\Phi_1}^{-1}
-            \end{equation}
-
-            \begin{algorithm}[H]
-            \caption{Normalize $M_1$}
-            \label{alg norm phi1}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} $\Phi_1$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $\epsilon=0.2$.
-                \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$, $F_{\Phi_1} = id$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$.
-%and $M_{p_{c,0}}(z) = \frac{z-p_{c,0}}{1- \overline{p_{c, 0}}z}$
-                \WHILE{$\abs{p_c,r} > \epsilon$}
-                    \STATE Let $F_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $\Phi_1 = \Phi_1 \circ F_{p_{c,r}}^{-1}$.
-                    \STATE Compute $F_{\Phi_1} = F_{p_{c,r}} \circ F_{\Phi_1}$, $p_{i, r+1} = F_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
-                    \STATE Let $r = r+1$.
-                \ENDWHILE
-                \STATE Solve equation (\ref{eq}) by Newtown's method and get solution $a \in \D$.
-                \STATE Let $F_a(z) = \frac{z-a}{1- \overline{a}z}$, $F_{\Phi_1} = F_a \circ F_{\Phi_1}$ and $\hat{\Phi}_1 = \Phi_1 \circ F^{-1}_{a}$.
-                \STATE Compute $p_i = F_a(p_{i,r})$.
-                \RETURN Mobious transformation $F_{\Phi_1}$, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig9.png}
-                \end{center}
-                \caption{The iteration of distribution adjustment. The boundary points are blue and their arithmetic center is red in each picture. (a)-(d) The 1st, 3rd, 7th, 12th iteration.}
-            \end{figure*}
-
-            As for the normalization of $M_2$, it's much easier.
-For requirement (\ref{norm phi2 1}), we only need to map $\infty$ to $\infty$ by replace $\Phi_2$ with $\tilde{\Phi}_2(z)=\Phi_2 \circ F^{-1}_{b}(\frac{1}{z})$, where $b = \Phi_2^{-1}(\infty)$.
-Another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
-According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
-Here we select $M = 10^5$ points uniformly from $[0, 2\pi)$ as $\theta_j = \frac{2 j \pi}{M}$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}).
-Therefore, the maximal solution $\theta_{\max} = \argmax{j \in [0,10^5)} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ can be used to normalize the rotation and the final mapping is
-            \begin{equation}
-                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
-            \end{equation}
-            where $M_{\Phi_2}(z) = e^{i \theta_{max}} \frac{z-b}{1 - \overline{b}z}$.
-
-            \begin{algorithm}[H]
-            \caption{Normalize $M_2$}
-            \label{alg norm phi2}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} $\Phi_2$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $M=10^5$.
-                \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$.
-                \STATE Let $M_b(z) = \frac{z-b}{1-\overline{b}z}$ and $\tilde{\Phi}_2(z)=\Phi_2 \circ M^{-1}_{b}(\frac{1}{z})$.
-                \STATE Calculate $\abs{\tilde{\Phi}_2'}$ by chain derative rule.
-                \STATE Let $\theta_j = \frac{2\pi}{M}(j-1)$ for $j=1,2, \cdots, M$.
-                \STATE Compute $\abs{\tilde{\Phi}_2'}(e^{i \theta_j})$.
-                \STATE Find maximal value and corresponding $\theta_{max}$.
-                \STATE Let $\hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z)$ and compute $p_i = \frac{e^{-i \theta_{max}}}{M_b(p_i)}$.
-                \RETURN Conformal mapping $\hat{\Phi}_2: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=.76cm]{src/fig10.png}
-                \end{center}
-                \caption{The change of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ for different $\theta_j \in [0, 2\pi)$.
-It shows this function has a significant maximum and $\theta_{max}$ is about $1.25\pi$.}
-                \label{derative}
-            \end{figure}
-
-            After obatining Mobious transformations $F_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
-            \begin{align*}
-                \hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}
-            \end{align*}
-            and it is unique up to a rotation.
-
-        \subsection{Summary of the Algorithm}
-            The totally algorithm is as following.
-            \begin{algorithm}[H]
-            \caption{Calculate Beltrami signature}
-            \label{alg all}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} Bounded simple connected shape $\Omega \subset \C$, $N=200$.
-                \STATE Pick $N$ clockwise points $z_1, z_2, \cdots, z_N$ from $\partial \Omega$ uniformly.
-                \STATE Input $z_1, z_2, \cdots, z_N$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_1}: \D \rightarrow \Omega$ and $p_{i,1} \in \partial\D$.
-                \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$. %and 
-                \STATE Input $z_N, \cdots, z_2, z_1$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_2}: \D \rightarrow \Omega^c$ and $p_{i,2} \in \partial\D$.
-                \STATE Let $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-                \STATE Let $f = \Phi_1^{-1} \circ \Phi_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
-                \STATE Extend $f$ to $H$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
-                \STATE Input $\Phi_1$ and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get $F_{\Phi_1}$.
-                \STATE Input $\Phi_2$ and $p_{i,2}$ to Algorithm \ref{alg norm phi2}, then get $M_{\Phi_2}$.
-                \STATE Calculate normalized harmonic extension $\hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}$.
-                \STATE Calculate Beltrami coefficient $B$ of $\hat{H}$.
-                \RETURN Beltrami signature $B$.
-            \end{algorithmic}
-            \end{algorithm}
-    \section{Experimental result}\label{result}
-        In this section, we will validate key properties of our proposed Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
-Besides that, a good shape representation should keep the similarity with the same kind shape and is significantly different from different kinds of shape.
-
-        Before showing results, what needs illustration is that the distance we used to measure the difference of Beltrami signature is based on $L^2$ norm,
-        \begin{equation}\label{bs dis}
-            d(B_1, B_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{B_1(z_i) - B_2(z_i)}^2},
-        \end{equation}
-        where $B_1, B_2$ are two different Beltrami signature, $z_i \in \D$ is the face center of triangluar mesh $M$ metioned in Section \ref{detail harmonic} and $N=60962$ here.
-        \subsection{Invariance}\label{sec inv}
-            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate Beltrami signature after sacling, translation and rotation and compare them with the original shape's Beltrami signature.
-The result is displayed in Fig \ref{inv}.
-In this figure, the first column are the sets of boundary points and we remark them as $\Omega_a$ to $\Omega_f$.
-The second column are the corresponding Beltrami signatures $B_a$ to $B_f$.
-Note that all the Beltrami signatures are shown in modulus, i.e.
-$\abs{B_n}$ for row $n$, and in top view.
-And the third column(if have) are the histograms of the difference between original shape's Beltrami signature, i.e.
-$\abs{B_n - B_a}$ for row $n$.
-
-            Row b and c are about scaling, the shapes are $\Omega_b = \{z \mid z = 1.5 z_a, z_a \in \Omega_a \}$ and $\Omega_c = \{z \mid z = 0.5 z_a, z_a \in \Omega_a \}$ and the distance are $d(B_a, B_b) = 5.5647 \times 10^{-8}$ and $d(B_a, B_c) = 5.3476 \times 10^{-8}$.
-Row d is about translation, the shape $\Omega_d = \{z \mid z = z_a+100+20i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_d) = 4.7817 \times 10^{-8}$.
-Row e is about rotation, the shape is $\Omega_e = \{z \mid z = e^{0.2\pi i} z_a, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.2144 \times 10^{-8}$.
-Row f is the combination of scaling, tanslation and rotation, the shape is $\Omega_e = \{z \mid z = 3e^{-0.85\pi i} z_a+350+600i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.7635 \times 10^{-8}$.
-These confirm the invariance of Beltrami signature and scaling, translation and rotation.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/inv.png}
-                \end{center}
-                \caption{Beltrami signature under scaling, translation and rotation.}
-                \label{inv}
-            \end{figure*}
-
-        \subsection{Robustness}
-            Similar with Section \ref{sec inv}, here we still treat the dolphin as the original shape and modify some small parts of it and Fig \ref{robust} is the result.
-It shows that the proposed signature is robust and stable and will not have a big mutation cauesd by small disturbance.
-
-            Row g, h and i are result about modification.
-These shapes are generated by removing or adding something, which is in the red circle.
-We can see that Beltrami signatures have slight differences from $B_a$ but are still similar in general.
-And this figure also demonstrates that the bigger the modification part is, the more different the Beltrami signature is.
-For example in row i, losing a half of the tail makes the signature has a marked change.
-Quantitatively, $d(B_a, B_g) = 0.0132$, $d(B_a, B_h) = 0.0316$ and $d(B_a, B_i) = 0.1761$.
-
-            Row j is for distortion. This dolphin is only enlarged in horizontally and becomes fatter, then the $B_j$ moves a little bit and $d(B_a, B_j) = 0.0724$.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/robust.png}
-                \end{center}
-                \caption{Beltrami signature under small modification}
-                \label{robust}
-            \end{figure*}
-
-        \subsection{Classification with Beltrami signature}
-            Above properties ensure the proposed signature having the ablity to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.
-
-            To compare the classification performance, we also use conformal welding directly to classify, and the distance is defined as
-            \begin{equation}\label{welding dis}
-                d_c(f_1, f_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{f_1(z_i) - f_2(z_i)}^2},
-            \end{equation}
-            where $f_1, f_2$ are two different conformal welding, $N=200$ here.
-
-            We prepare 3 kinds of animals, fish, giraffe and elephant.
-There are 3 images for each group so 9 images in total.
-From Fig \ref{classification images}, we can find that each class share similar Beltrami signatures and conformal welding.
-From Fig \ref{dis matrix}, the inter-class distance of Beltrami signature is awlays less than 0.2 while the intra-class distance is greater than 0.2.
-But for conformal welding, the data is messy, for example, fish 3 thinks itself is very different from other fishes but looks most like giraffe 2.
-After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the Beltrami signature shows powerful classification ablity.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/figs.png}
-                \end{center}
-                \caption{These 3 rows are elephant, fish and giraffe. In each subfigure, the top left is the input shape, bottom left is the conformal welding and the right is Beltrami signature.}
-                \label{classification images}
-            \end{figure*}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/distance_down.png}
-                \end{center}
-                \caption{(a) The distance matrix of Beltrami signatures of above 9 shapes by equation (\ref{bs dis}). (b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
-                \label{dis matrix}
-            \end{figure}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/mds_down.png}
-                \end{center}
-                \caption{(a) The MDS result of Beltrami signature. (b) The MDS result of conformal welding.}
-                \label{mds1}
-            \end{figure}
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/mds2.png}
-                \end{center}
-                \caption{(a) The MDS result of Beltrami signature.
-(b) The MDS result of conformal welding.
-(c) The clustering result of Beltrami signature.
-(d) The clustering results of conformal welding.}
-                \label{mds2}
-            \end{figure*}
-
-        \subsection{Classification for more classes}
-            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabit.
-We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes.
-The MDS and clustering results based on Beltrami signature and conformal welding are displayed in Fig \ref{mds2}.
-The classification accuracy based on Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
-
-    \section{Conclusion}\label{conclusion}
-        In this paper, we propose a novel shape representation for 2D bounded simple connected objects called Beltrami signature.
-The proposed signature is based on conformal welding but overcome a key shortcoming that it can be uniquely determined by the given shape.
-What's more exciting is that the proposed representation is invariance under scaling, translation and rotation.
-For slight deformation and distortion, Beltrami signature keeps roubost and only changes within a reasonable small range.
-Therefore, there are reasons to believe the it does have ablity to represent some invariant geometrical features.
-The experimental results also confirm that the Beltrami signature has excellent performance in multi-classification tasks.
-
-        Although our work has achieved relatively good results, the proposed representation still have some limitations.
-Firstly, the Beltrami signature is only applicable to simple connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world.
-So we are eager for a feasible method to extend our Beltrami signature to multi connected situation.
-Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangluar mesh, which consumes a lot of time.
-Therefore, a fast algorithm to obatin this signature avoiding dense mesh is of high priority in our future work.
-Thirdly, when normalizing the conformal mapping $\Phi_2$ from exterior of unit disk to exterior of the domain, the position where the derivation of $\Phi_2$ reaches the maximum value is used to adjust the rotation.
-We trust this point in the original image has a certain geometric meaning, whereas it is not clear at present.
-
-        In summary, we will focus on third marjor directions in the future.
-One is that the deeper meaning of Beltrami signature is worth digging and then a multi-connected version of representation based on this work can be proposed.
-Another is that if the Beltrami signature contains some geometrical features of shapes, we can also extract them directly from images and generate the Beltrami signature again.
-Hence the deep learning theory may help us to compute this signature from given images immediately, which is very likely to improve algorithm speed performance greatly.
-A third direction is this representation can be used in more applications like segementation, registration and so on.
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
-% \section*{Conflict of interest}
-%
-% The authors declare that they have no conflict of interest.
-
-% BibTeX users please use one of
-% \bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
-\bibliography{cite}
-% Non-BibTeX users please use
-% \begin{thebibliography}{}
-% %
-% % and use \bibitem to create references. Consult the Instructions
-% % for authors for reference list style.
-% %
-% \bibitem{RefJ}
-% % Format for Journal Reference
-% Author, Article title, Journal, Volume, page numbers (year)
-% % Format for books
-% \bibitem{RefB}
-% Author, Book title, page numbers. Publisher, place (year)
-% % etc
-% \end{thebibliography}
-
-\end{document}
-% end of file template.tex

### 2021-06-11 abstract1.tex
final thesis

\chapter*{摘要}

近年來，越來越多的人開始關注圖像分析，在這篇論文中，我們將提出一種全新的，基於輪廓的二維有界單連通圖像的表示，我們把它稱為調和Beltrami 特徵函數（Harmonic Beltrami signature, HBS）。我們從給定圖像的共形焊接出發，得到它的調和延拓。在適當的約束條件下，調和延拓可以被唯一確定，最多相差一個旋轉。最後擬共性理論可以通過計算調和延拓的 Beltrami 係數來幫助我們去除這僅剩的不確定性，也就得到了我們需要的特徵函數。可以證明，我們的 HBS 和圖像之間存在一一對應，並且我們在文章中提出了從 HBS 重建原始圖像的方法。 HBS能在對圖像做簡單變換時保持不變，例如旋轉、平移、縮放及這些變換的組合。如果對圖像做合理程度的形變和扭轉，HBS 幾乎不變，同時，HBS 的微小改變也幾乎不影響圖像的還原，這說明了我們的特徵函數具有良好的魯棒性。實驗結果支持了上述結論，同時也展示了 HBS 在分類任務上的優秀表現。

### 2021-06-11 acknowledgement.tex
final thesis

I am deeply grateful to Prof. Ronald Lui not only for his guidance in my two-year M.Phil. study, but also bringing me to the world of applied mathematics and computational differential geometry. The opportunity and support he has given to me is unprecedented, which cultivates me to be an independent researcher at the same time.

Besides, I would also like to thank Dr. ZHANG Daoping for his help and discussions in my projects. His advice really helped me overcome obstacles and brought insights and convenience to me.

I would also like to thank my family for their consistent love, support and understanding to me, without which I can never persist on my way studying and doing mathematics.

Besides, I am also grateful to my friends Mr. LI Zhiwen, Mr. CHEN Qiguang, Mr. LIU Oscar, to name a few, for the happy moments we have in my daily life.

Moreover, I am grateful to CUHK and the math department, for providing support and resources on my way towards the master's degree.

Lastly, thank you my wife Yanyi, for your consistent love and support.

### 2021-06-11 experiments/experiments.tex
final thesis

--- 2021-04-07 template.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-% \smartqed  % flush right qed marks, e.g. at end of proof
-%
-% \let\equation\relax
-% \let\endequation\relax
-\let\proof\relax
-\let\endproof\relax
-\let\example\relax
-\let\endexample\relax
-
-\usepackage{graphicx}
-\usepackage[margin=1in]{geometry} 
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{hyperref}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\include{snippets}
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
-\begin{document}
-
-\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
-% \subtitle{Do you have a subtitle?\\ If so, write it here}
-
-%\titlerunning{Short form of title}        % if too long for running head
-
-\author{Chenran Lin \and Lok Ming Lui}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{Chenran Lin \at
-              Department of Mathematics, The Chinese University of Hong Kong \\
-              \email{crlin@math.cuhk.edu.hk}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           Lok Ming Lui \at
-              Department of Mathematics, The Chinese University of Hong Kong\\
-              \email{lmlui@math.cuhk.edu.hk}           %  \\
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simple connected domain in this paper, named Beltrami signature.
-The proposed signature is based on conformal welding.
-We extended the welding mapping to a harmonic function.
-With suitable normalization, the uniqueness of this harmonic function is guaranteed up to a rotation.
-And finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension.
-The benifits of the proposed signature is it keeps invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformation and distortion.
-Experiments demonstrate the above properties and also show the excellent classification performance.
-\keywords{
-  Shape representation \and conformal welding \and simple connected \and invariance}
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
-\end{abstract}
-
-\section{Introduction}
-\label{intro}
-    The outline of the shape contains very important information and it can be used in many applications, such as segementation, recognition, registration and so on.
-However, even for the simplest situation, 2D simple connected shapes, it is a big challenge to describe clearly what the shape contour looks like.
-Because of the complexity of the image, there is an urgent demand to find a common, simple and robust shape representation for further mining and utilizing of shapes' geometric information.
-Therefore, many different presentations and measures have been widly studied and proposed recently \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.
-
-    Considering 2D simple connected shapes, conformal welding is a kind of well-known shape signature.
-Given 2D simple connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$.
-This gives a simple but wonderful representation of $\Omega$ as Fig.
-\ref{fig1} shows.
-However, it has two fatal defects.
-First is that such representation is not unique.
-Because of the arbitrary of Riemann conformal mapping, $\Phi_1$ and $\Phi_2$ can only be determined up to a Mobious transformation, so such conformal welding is not unique.
-Generally speaking, some assumption is required to remove this uncertainty.
-For example, Sharon \etal \cite{sharon20062d} need to select a base point $P$ inside the given domain $\Omega$ artificially, then let $\Phi_1$ maps $0$ to this point $P$.
-The work of Mcenteggart \etal \cite{mcenteggart2018uniqueness} is based on Schramm-Loewner evolution(SLE) on random surfaces called Liouville quantum gravity, they proved the equivalence between uniqueness of conformal welding and conformal removable and conculded that if the boundary curve $\eta$ is an $\text{SLE}_k$ for $k \in (0, 4)$ and satisifies some other requirements, the corresponding conformal welding is unique.
-Some may not that care the uniqueness itself, they used equivalent class to guarantee uniqueness in a broader sense or evne just ignored it \cite{katznelson1990conformal,marshall2012conformal,lui2013shape,astala2010random}.
-
-    Another thing is that even the conformal welding is very easy to be changed by simple transformations like rotation, scaling and translation.
-Such a unstable representation is hard to apply in practical applications since these transformations are inevitable in the real world.
-
-    The contribution of this paper is that we propose a brand new presentation for 2D simple connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Beltrami signature.
-Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points.
-Such conformal welding can be extended to the whole unit disk and get a harmonic function $H: \D \rightarrow \D$.
-Under suitable normalization, harmonic extension $H$ can be determined up to a rotation and the Beltrami coefficient of $H$ is then unique and becomes our Beltrami signature.
-
-    The proposed shape representation, Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
-The Beltrami signature is based on computational quasiconformal geometry.
-Computational quasiconformal geometry has been widely used in image processing and image analysis.
-Applications can be found in image segmentation
-    \cite{siu2020image,chan2018topology,zhang2020topology}
-    , image registration
-    \cite{lam2014landmark,lui2014teichmuller,ng2014computing,lui2012optimization,lam2014genus,zhang2012registration,lee2016landmark,lui2010optimized,lui2013texture,lui2010shape,lui2010optimizedc,lui2014geometric,choi2015flash}
-     and image analysis 
-    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shapec,lui2010shape3}
-    .
-What's more worth mentioning is that Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape.
-It means the proposed representation has high practical value and can be applied in computer vision work like classification, segementation and so on.
-
-    The paper is organized as follows: Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem and how Beltrami signature is obtained from given domain; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
-The paper is concluded in Section \ref{conclusion} and we point out future directions.
-
-    \begin{figure}
-        \begin{center}
-        \includegraphics[width=7.6cm]{src/fig1_down.png}
-        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simple connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
-        \end{center}
-        \label{fig1}
-    \end{figure}
-
-\section{Theoretical basis}\label{background}
-    \subsection{Quasi-conformal mapping and Beltrami equation}
-        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
-        \begin{equation*}
-            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
-        \end{equation*}
-
-        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
-        \begin{equation}\label{beltrami eq}
-            \Part{f}{\overline{z}} = \mu(z) \Part{f}{z}
-        \end{equation}
-        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$.
-More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
-        \begin{equation}
-            \mu = \frac{f_{\overline{z}}}{f_{z}}
-        \end{equation}
-        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
-        \begin{equation}
-            f^*(ds^2_E) = \abs{\Part{f}{z}}^2 \abs{dz + \mu(z)d\overline{z}}^2
-        \end{equation}
-        which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$.
-$\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality.
-In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$.
-Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
-        \begin{equation}\label{local f}
-            f(z) = f(p)+f_z(p)(z+\mu(p)\overline{z}).
-        \end{equation}
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig2.jpg}
-            \end{center}
-            \caption{(a) Shows the original hippocampus.
-(b) Shows the parameter domain with circle packing pattern.
-Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
-            \label{fig2}
-        \end{figure}
-
-        If $\mu(z)=0$ everywhere, then $f$ us called \textit{conformal} or \textit{holomorphic}. A conformal map satisfies the following well-known Cauchy-Riemann equation:
-        \begin{equation}\label{cr eq}
-            \Part{f}{\overline{z}} = 0.
-        \end{equation}
-        Inside the local parameter domain, $f$ may be considered as a map composed of a translation to $f(p)$ together with a stretch map $S(z) = z + \mu(p)\overline{z}$, which is postcomposed by multiplication of $f_z(p)$, which is conformal.
-All the conformal distortion of $S(z)$ is caused by $\mu(p)$.
-$S(z)$ is the map that causes $f$ to map a small circle to a small ellipse (see Fig.
-\ref{fig2}).
-Form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well.
-Specially, the angle of maximal magnification is $\arg(\mu(p))/2$ with magnifying factor $1+\abs{\mu(p)}$; the angle of maximal shrinkage is the orthogonal angle $\arg(\mu(p))/2 - \pi/2$ with shrinkage factor $1-\abs{\mu(p)}$.
-The distortion or dilation is given by:
-        \begin{equation}
-            K = \frac{1+\abs{\mu(p)}}{1-\abs{\mu(p)}}.
-        \end{equation}
-        Thus, the Beltrami coefficient $\mu$ gives us important information about the properties of the map (see Fig. \ref{fig3}).
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig3.jpg}
-            \end{center}
-            \caption{Quasi-conformal maps infinitesimal circles to ellipses. The Beltrami coefficient measure the distortion or dilation of the ellipse under the QC map.}
-            \label{fig3}
-        \end{figure}
-
-        Suppose $f, g: \C \rightarrow \C$ are complex-valued function with Beltrami coefficient $\mu_f, \mu_g$ respectively. Then the Beltrami coefficient for the composition $g \circ f$ is given by
-        \begin{equation}\label{mu of composition}
-            \mu_{g \circ f} = \frac{\mu_f+(\mu_g \circ f) \tau}{1+\overline{\mu_f}(\mu_g \circ f) \tau},
-        \end{equation}
-        where $\tau = \frac{\overline{f_z}}{f_z}$. Note that when $g$ is conformal, $\mu_g = 0$ and 
-        \begin{equation}\label{mu of conformal composition}
-            \mu_{g \circ f} = \mu_f.
-        \end{equation}
-
-    \subsection{Conformal welding}
-        Given 2D bounded simple connected shape, we can treat it as a boundary simple connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
-$\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobious transformation}:
-        \begin{equation}
-            M(z) = e^{i \theta} \frac{z - a}{1 - \overline{a}z}.
-        \end{equation}
-        Then we can define \textit{conformal welding} as:
-        \begin{equation}
-            f = \Phi_1^{-1} \circ \Phi_2.
-        \end{equation}
-        Such $f: \partial \D \rightarrow \partial \D$ is a diffeomorphism from $\partial \D$ to itself, which can be also thought as a periodic, real-valued monotone increasing function $f_\R: [0, 2\pi) \rightarrow [0, 2\pi)$ such that $f(e^{i \theta}) = e^{i f_\R(\theta)}$ (see Fig.
-\ref{fig1}).
-
-    \subsection{Harmonic function and Poisson integral}
-        A complex-valued function $f$ defined on $\Omega \subset \C$ is called \textit{harmonic} if it satisfies the \textit{Laplace's equation}:
-        \begin{equation}
-            \Delta f = 4 \frac{\partial^2 f}{\partial z \partial \overline{z}} = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2} = 0,
-        \end{equation}
-        where $z = x + iy$, $x$, $y$ is the real and imaginary value.
-
-        Chen \etal prove following theorem in \cite{chen2010compositions}, which tells us that the composition of harmonic mappings and other mappings can inherit such harmonicity in some condition.
-        \begin{theorem}\label{composition of harmonic}
-            Let $f$ be a harmonic mapping, $f \circ g$ is harmonic if and only if $g(z) = az + b \overline{z} + c$, where $a$, $b$ and $c$ are constaants and $g \circ f$ is harmonic if and only if $g$ is analytic or anti-analytic.
-        \end{theorem}
-
-        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}.
-For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
-            \begin{equation}\label{poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
-            \end{equation}
-        Such $H$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
-$H(e^{i\theta}) = f(e^{i\theta})$ (see Fig.
-\ref{harmonic}).
-Of course, this $H$ is unique.
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig4_down.png}
-            \end{center}
-            \caption{(a) Continious function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$.
-(b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
-Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
-            \label{harmonic}
-        \end{figure}
-
-    \section{Beltrami signature}\label{main}
-        In this chapter, we will propose a new representation, Beltrami signature, to discribe boundary simple connected domain $\Omega$.
-Our proposed signature is based on conformal welding and quasi-conformal theory.
-
-        \subsection{Beltrami signature based on conformal welding}
-            Here we give a brief explaination of how to create our new signature.
-Given the boundary simple connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it.
-Then $f$ can be extended to harmonic function $H$ defined on $\D$ by Poisson integral (\ref{poisson integral}).
-At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
-            \begin{equation}
-                B:= \mu_H = \frac{H_{\overline{z}}}{H_z}.
-            \end{equation}
-            Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $B$ is determined.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig5.png}
-                \end{center}
-                \caption{Illustration of Beltrami signature.
-(a) The input shape, a dolphin.
-(b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b).
-(c) The Beltrami signature of (a).
-Remark that the harmonic funcion and Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
-                \label{illu of BS}
-            \end{figure*}
-
-        \subsection{Analysis of uniqueness of Beltrami signature}
-            According to Riemann mapping theorem, the conformal mapings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
-Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobious transformations.
-Therefore, the corresponding conformal welding is
-            \begin{equation}
-                \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = M_1^{-1} \circ \Phi_1^{-1} \circ \Phi_2 \circ M_2 = M_1^{-1} \circ f \circ M_2.
-            \end{equation}
-
-            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{H}$. The following theorem show the relationship between $H$ and $\tilde{H}$.
-
-            \begin{theorem}
-                Suppose $f$ and $\tilde{f}$ are continious map from $\partial \D$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
-$H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
-            \end{theorem}
-
-            \begin{proof}
-                Since $M_1$ is a Mobious transformations, $M_1^{-1}$ is also a Mobious transformation, so it can be written as $M_1^{-1}(z) = e^{i \theta}\frac{z - p}{1 - \overline{p}z}$, where $\theta \in [0, 2\pi)$ and $p \in \D$.
-
-                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
-$\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
-Therefore, we have
-                \begin{equation*}
-                    e^{i \theta}\frac{z - p}{1 - \overline{p}z} = az + b \overline{z} + c,
-                \end{equation*}
-                which means $p = b = c = 0$, $a = e^{i \theta}$ and so $M_1$ is a rotation.
-
-                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ H \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}.
-It's easy to check that
-                \begin{align*}
-                    M_1^{-1} \circ H \circ M_2 (e^{i \theta})
-                    &= M_1^{-1} \circ f \circ M_2(e^{i \theta})\\
-                    &= \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
-                \end{align*}
-                which means $M_1^{-1} \circ H \circ M_2$ and $\tilde{H}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ H \circ M_2 = \tilde{H}$.
-            \end{proof}
-
-            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{H}$
-            \begin{equation}
-                \tilde{B} = \mu_{\tilde{H}} = \mu_{M_1^{-1} \circ H \circ M_2} = \mu_{H\circ M_2}.
-            \end{equation}
-            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, then we get $M_2$ is identity.
-Therefore, we know that the uniqueness of Beltrami signature is equivalent to following restrictions:
-            \begin{enumerate}
-                \item $M_1$ should be a rotation.
-                \item $M_2$ should be identity.
-            \end{enumerate}
-
-        \subsection{Normalization to $M_1$}\label{norm1}
-            We hope $M_1$ is a rotation.
-It is not that hard, for example, we can achieve it by restricting $\Phi_1(0) = 0$.
-But it need a hypothesis that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold.
-Here we want to show a new approach without any additional assumption.
-
-            In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$.
-Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, where $\Phi_1 : \D \rightarrow \Omega$.
-We claims that $M_1$ can be normalized by restricting the center of $p_i$ to $0$.
-
-            \begin{theorem}\label{unique up to a rotation}
-                Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
-                \begin{align}\label{norm phi1}
-                    \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
-                \end{align}
-                then such $\Phi_1$ is unique up to a rotation $M_1$.
-            \end{theorem}
-
-            Before proving theorem \ref{unique up to a rotation}, we can consider following problem.
-Given boundary points $p_i$ on unit circle, can we find a Mobious transformation $M$ satisfies the following equation (\ref{fz})?
-            \begin{equation}\label{fz}
-                \sum_{k=1}^n M(p_k) = \sum_{k=1}^n e^{i\theta} \frac{p_k - a}{1 - \overline{a}p_k}= 0
-            \end{equation}
-
-            Without lose of generality, we ignore the rotation of $M$ and let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-So $F_a$ is also a Mobius transformation and it's sufficient to find $a \in \D$ such that
-            \begin{equation}\label{eq}
-                f(a) = \sum_{k=1}^n F_a(p_k) = \sum_{k=1}^n \frac{p_k - a}{1 - \overline{a}p_k} = 0
-            \end{equation}
-            to show the equation (\ref{fz}) holds for some $M$. Intuitively, we believe that there is always a unique solution to this equation (\ref{eq}) (see Fig \ref{fasolvable}).
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig6.png}
-                \end{center}
-                \caption{The first row are some randomly generated points in $\partial \D$.
-The second row are the corresponding $\abs{f(a)}$, where $a \in \D$.
-The third row are also $\abs{f(a)}$ but is in top view.
-}
-                \label{fasolvable}
-            \end{figure*}
-
-            \subsubsection{The solvability of equation (\ref{eq})}
-            First thing we want to do is to check whether this equation (\ref{eq}) is always solvable. According to Brouwer fixed point theorem, we have
-
-            \begin{theorem}\label{existence}
-                Given $\{p_1, p_2, \cdots, p_n\} \subset \partial \D$ and $n \ge 3$, let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-The solution of equation (\ref{eq}) always exists.
-            \end{theorem}
-
-            \begin{proof}
-                Note that when $e^{i \theta} \neq p_k$ for any $k$, we have
-                \begin{equation*}
-                    f(e^{i \theta}) = \sum_{k=1}^n \frac{p_k - e^{i \theta}}{1 - e^{-i\theta}p_k} = - n e^{i\theta},
-                \end{equation*}
-                so $\frac{1}{n} f(e^{i\theta}) + e^{i \theta} = 0$. Let 
-                \begin{equation*}
-                    g(a) = \begin{cases}
-                \frac{1}{n} f(a) + a, a \in \D,\\
-                0, a \in \partial \D,
-                \end{cases}
-                \end{equation*}
-                such $g$ is defined on $\overline{\D}$ and is continuous. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.
-
-                Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, then define
-                \begin{equation*}
-                    h(a) = \begin{cases}
-                    g(a), &a \in  \overline{\D} \setminus M,\\
-                    \frac{g(a)}{\norm{g(a)}}, &a \in  M.
-                \end{cases}
-                \end{equation*}
-                $h$ is a continuous map from $\overline{\D}$ to itself, so there exists some $a$ let $h(a) = a$.
-
-                If $a \in \partial \D$, $\norm{a} = 1$, but $\norm{h(a)} = 0 \neq \norm{a}$.
-If $a \in M$, we know $a \notin \partial \D$, so $\norm{a} < 1$, but $\norm{h(a)} = \frac{\norm{g(a)}}{\norm{g(a)}} = 1 \neq \norm{a}$.
-So when $h(a) = a$, $a$ is inside $\D \setminus M$.
-Therefore, such $a$ satisfies $g(a) = a$ and then $f(a) = 0$.
-            \end{proof}
-
-            Therefore, there must be some $a \in \D$ to be the solution of equation (\ref{fz}).
-
-            \subsubsection{The uniqueness of the solution of equation (\ref{eq})}
-            With solvability proved, we naturally want to know if this solution is unique. Let's consider a special case when $\sum_{k=1}^n p_k = 0$, we have
-            \begin{theorem}\label{uniqueness when 0}
-                Suppose $\sum_{k=1}^n p_k = 0$, equation (\ref{eq}) holds if and only if $a = 0$.
-            \end{theorem}
-
-            \begin{proof}
-                If $a = 0$, it's obvious $F_0$ is identity, so $f(0) = \sum_{k=1}^n p_k = 0$.
-
-                If $a \neq 0$, WLOG, we can assume that $0 < a < 1$, then $F_a(1) = 1$ and $F_a(-1) = -1$.
-For any $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$,
-                \begin{align*}
-                    &F_a(p_k) \\
-                    = &F_a(\cos \theta_k + \sin \theta_k i) \\
-                    = &\frac{\cos \theta_k + \sin \theta_k i - a}{1 - a \cos \theta_k - a \sin \theta_k i} \\
-                    = &\frac{(a^2 + 1) \cos \theta_k -2a - (a^2 - 1) \sin \theta_k i}{a^2 + 1 - 2a \cos \theta_k},
-                \end{align*}
-                so
-                \begin{align*}
-                    &\Re(F_a(p_k)) \\
-                    = &\frac{(a^2 + 1) \cos \theta_k -2a}{a^2 + 1 - 2a \cos \theta_k} \\
-                    = &\cos \theta_k - \frac{2a(1-\cos^2 \theta_k)}{(a-1)^2 + 2a(1-\cos \theta_k)} \\
-                    < &\cos \theta_k = \Re(p_k).
-                \end{align*}
-
-                Therefore, if $n \ge 3$, there must be at least one $p_k \neq \pm 1$ and so
-                \begin{align*}
-                    &\Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) \\
-                    < &\sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
-                \end{align*}
-                which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $a=0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
-            \end{proof}
-
-            This theorem confirms the uniqueness for a special situation $\sum_{k=1}^n p_k = 0$ and actually this conclusion is universal no matter how $p_i$ distribute.
-
-            \begin{theorem}\label{uniqueness}
-                The solution of equation (\ref{eq}) is unique.
-            \end{theorem}
-
-            \begin{proof}
-                Assume that $a_0, a_1$ are two different solutions, then we have that
-                \begin{align*}
-                    \sum_{k=1}^n F_{a_0}(p_k) = 0,\sum_{k=1}^n F_{a_1}(p_k) = 0
-                \end{align*}
-
-                Let $p_k' = F_{a_0}(p_k)$, then
-                \begin{align*}
-                    &\sum_{k=1}^n F_{a_1} \circ F_{a_0}^{-1} \circ F_{a_0}(p_k)\\
-                    = &\sum_{k=1}^n (F_{a_1} \circ F_{-a_0})(F_{a_0}(p_k))\\
-                    = &\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}}\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0.
-                \end{align*}
-
-                Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so \\
-                $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$. According to theorem \ref{uniqueness when 0},\\
-                $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, then $a_0 = a_1$, which contradicts to the assumption.
-            \end{proof}
-
-            \subsubsection{Unque $\Phi_1$ up to a rotation}
-
-            Above theorems show that there is alway an unique solution $a \in \D$ for equation (\ref{eq}), so we can come back to theorem \ref{unique up to a rotation}.
-
-            \begin{proof}
-                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobious transformation.
-If $\Phi_1$, $\tilde{\Phi_1} $ satisfy equation (\ref{norm phi1}), let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M_1^{-1} (p_k) = 0$.
-$M_1^{-1}$ is also a Mobious transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
-                \begin{equation*}
-                    e^{i \theta} \sum_{k=1}^n F_a(p_k) = 0.
-                \end{equation*}
-
-                From theorem \ref{uniqueness when 0} we can know $a = 0$, then $M_1^{-1}(z) = e^{i \theta} z$ and $\Phi_1$ is unique up to a rotation $M_1$.
-            \end{proof}
-
-        \subsection{Normalization to $M_2$}\label{norm2}
-            As for $M_2$, we hope it is identity, which is equivalent with the uniqueness of $\Phi_2: \D^c \rightarrow \Omega^c$.
-Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this and derivative to guarantee the uniqueness.
-
-            \begin{theorem}
-                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobious transformation.
-If $\tilde{\Phi_2}, \Phi_2$ satisifies that
-                \begin{align}
-                    &\tilde{\Phi_2}(\infty) = \Phi_2(\infty) = \infty\label{norm phi2 1}\\
-                    &\argmax{z \in \partial \D} \abs{\Phi_2'(z)} = \argmax{z \in \partial \D} \abs{\tilde{\Phi_2'}(z)} = 1,\label{norm phi2 2}
-                \end{align}
-                then such $M_2$ is identity.
-            \end{theorem}
-
-            \begin{proof}
-                Suppose Mobious transformation $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$. Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisify (\ref{norm phi2 1}), then
-                \begin{align*}
-                    &\tilde{\Phi}_2(\infty) = \Phi_2(M_2(\infty)) = \infty, \\
-                    &\Phi_2(\infty) = \infty.
-                \end{align*}
-                Therefore, $M_2(\infty) = e^{i \theta} \frac{\infty - a}{1- \overline{a} \infty} = \infty$, which means that $a = 0$ and $M_2(z) = e^{i \theta} z$.
-
-                Consider the derivative of $\tilde{\Phi}_2$,
-                \begin{equation}
-                    \tilde{\Phi}_2'(z) = \Phi_2' \circ M_2(z) \cdot M_2'(z) = e^{i\theta} \Phi_2' (e^{i \theta}z),
-                \end{equation}
-                then we know that $\abs{\tilde{\Phi}_2'(z)} = \abs{\Phi_2'(e^{i \theta}z)}$.
-Suppose $a = \argmax{z \in \partial \D} |\Phi_2'(z)|$, then we will have that $ae^{-i \theta} = \argmax{z \in \partial \D} |\tilde{\Phi}_2'(z)|$.
-                If condition (\ref{norm phi2 2}) holds for both $\tilde{\Phi}_2$ and $\Phi_2$, it means $a = a e^{-i \theta} = 1$, so $a = 1$, $\theta = 0$ and $M_2$ is identity.
-            \end{proof}
-
-        \subsection{Invariance under simple transformation}
-            With the normalization mentioned above, we can get unique Beltrami signature $B$ corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$.
-Now we want to prove that if we do some simple transformation like rotation, scaling and translation to $\Omega$, the Beltrami signature is invariant.
-
-            \begin{theorem}
-                Given a boundary simple connected domain $\Omega$ and transformation $T$ which is composed by rotation, scaling and transformation.
-Let $B_\Omega$ and $B_{T(\Omega)}$ be the Beltrami signature of $\Omega$ and $T(\Omega)$, then $B_\Omega = B_{T(\Omega)}$
-            \end{theorem}
-
-            \begin{proof}
-                Suppose $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, $\tilde{\Phi}_1: \D \rightarrow T(\Omega)$ and $\tilde{\Phi}_2 : \D^c \rightarrow T(\Omega)$ are conformal.
-Since $T$ is composed by rotation, scaling and translation, $T$ can be written as $T(z) = ke^{i\theta} z + b$.
-Such $T$ is absolutely invertible and conformal.
-
-                Let $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1 : \D \rightarrow \Omega$, $\hat{\Phi}_1$ is conformal.
-Given the boundary points $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$, then $\{T(z_1), T(z_2), \cdots, T(z_n)\} \subset \partial T(\Omega)$.
-Since $\tilde{\Phi}_1$ satisifies condition (\ref{norm phi1}), we have
-                \begin{equation*}
-                    \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0.
-                \end{equation*}
-
-                Therefore
-                \begin{equation*}
-                    \sum_{i=1}^n \hat{\Phi}_1^{-1}(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1} \circ T(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0,
-                \end{equation*}
-                which means $\hat{\Phi}_1$ also satisifies condition (\ref{norm phi1}). Hence $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1= \Phi_1 \circ R$, which equals to
-                \begin{equation}
-                    \tilde{\Phi}_1 = T \circ \Phi_1 \circ R,
-                \end{equation}
-                where $R$ is a rotation.
-
-                Similarly, let $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2: \D^c \rightarrow \Omega^c$, $\hat{\Phi}_2$ is conformal. Since $\tilde{\Phi}_2(\infty) = \infty$, we have
-                \begin{equation*}
-                    \hat{\Phi}_2(\infty) = T \circ \tilde{\Phi}_2(\infty) = \infty,
-                \end{equation*}
-                which means $\hat{\Phi}_2$ satisifies condition (\ref{norm phi2 1}).
-
-                As for condition (\ref{norm phi2 2}), we know that $T'(z) = k e^{i \theta}$, so
-                \begin{equation}
-                    \hat{\Phi}_2'(z) = T' \circ \tilde{\Phi}_2(z) \cdot \tilde{\Phi}_2'(z) = k e^{i \theta} \tilde{\Phi}_2'(z).
-                \end{equation}
-                Hence $\abs{\hat{\Phi}_2'} = \abs{k}\abs{\tilde{\Phi}_2'}$, which means $\hat{\Phi}_2$ also satisifies condition (\ref{norm phi2 2}).
-Therefore, $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2 = \Phi_2$ and then
-                \begin{equation}
-                    \tilde{\Phi}_2 = T \circ \Phi_2.
-                \end{equation}
-
-                We have the conformal welding
-                \begin{equation}
-                    \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = R^{-1} \circ \Phi_1^{-1} \circ T^{-1} \circ T \circ \Phi_2 = R^{-1} \circ f.
-                \end{equation}
-                Then the harmonic extension $\tilde{H} = R^{-1} \circ H$ and 
-                \begin{equation}
-                    B_{T(\Omega)} = \mu_{\tilde{H}} = \mu_{R^{-1} \circ H} = \mu_H = B_\Omega.
-                \end{equation}
-            \end{proof}
-
-    \section{Implementation detail}\label{implementation}
-        \subsection{Zipper algorithm}
-            In oder to find an unique and stable Beltrami signature, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
-As metioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
-
-            Marshall \etal demonstrates the zipper algorithm detailedly with clear diagrams in \cite{marshall2007convergence}.
-For the convenience of readers, we gives a very brief review here.
-Given $N$ clockwise boundary points $z_1, z_2, \cdots, z_N \in \partial \Omega$, this algorithm use a series of linear fractional transformations $g_1, g_2, \cdots, g_N$ to map $z_1, z_2,\cdots, z_N$ to real axis one-by-one, and finally transfrom the upper half plane to unit disk by $g_{N+1}(z) = \frac{z-i}{z+i}$.
-Therefore, $g = g_{N+1} \circ g_N \circ \cdots \circ g_2 \circ g_1$ is a conformal mapping undisputedly and maps all these boundary points to unit circle and the domain $\Omega$ to $\D$.
-Remark that zipper algorithm is sensitive to the order of points.
-If we input the points anti-clockwise, i.e.
-$z_N, z_{N-1}, \cdots, z_1$, the zipper will give us a conformal mapping from $\Omega^c$ to $\D$.
-
-            For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputing points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$.
-For $\Phi_2 : \D^c \rightarrow \Omega^c$, we can input anti-clockwise points and get $g_{\Phi_2} : \Omega^c \rightarrow \D$.
-At the result $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-Because of the invariance of scaling, the number of boundary points $N$ is fixed as $200$ here and they are picked uniformly from the shape contour.
-
-            \begin{algorithm}[H]                           % HERE!!!!!!!!!
-            \caption{Zipper}          % give the algorithm a caption
-            \label{zipper}      % and a label for \ref{} commands later in the document
-            \begin{algorithmic}  % enter the algorithmic environment
-                \STATE \textbf{Inputs:} $z_i \in \partial \Omega$ for $i=1, 2, \cdots, N$, $N=200$. %, $\epsilon = 10^{-10}$(any very small value)
-                \STATE \textbf{Initialize:} Let $r=2$, $g_1(z) = \sqrt{\frac{z-z_2}{z-z_1}}$, $g= g_1$ and compute $p_{i,2}=g(z_i)$.
-                \WHILE{$r < N$}
-                    \STATE Pick $q = p_{r+1, r} = a + b i$, then compute $c = \frac{a}{\abs{q}^2}$, $d = \frac{b}{\abs{q}^2}$.
-                    \STATE Let $g_r(z) = \sqrt{\frac{cz}{1+dzi}}$, then $g = g_r \circ g$ and compute $p_{i, r+1} = g_r(p_{i, k})$.
-                    \STATE Let $r = r+1$.
-                \ENDWHILE
-                \STATE Let $g_{N}(z) = \left(\frac{z}{1-\frac{z}{p_{1,N}}}\right)^2$ and $g_{N+1}(z) = \frac{z-i}{z+i}$, then $g = g_{N+1} \circ g_N \circ g$ and $p_i = g_{N+1} \circ g_N(p_{i,N})$.
-                \RETURN Conformal mapping $g: \Omega \rightarrow \D$ and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-        \subsection{Harmonic extension}\label{detail harmonic}
-            After obtaining the output of zipper algorithm, $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$, the conformal welding can be represented as a series points
-            \begin{equation*}
-                (\varphi_i, \omega_i) = \left(\arg(\hat{\Phi}_2^{-1}(z_i)), \arg(\hat{\Phi}_1^{-1}(z_i))\right),
-            \end{equation*}
-            where $\varphi_i, \omega_i \in [0, 2\pi)$. So in fact we should use discrete form Poisson integral to extend $f$ to a harmonic mapping $H$ on the unit disk
-            \begin{equation}\label{discrete poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi} \sum_{j=1}^k \frac{(1-r^2) e^{i \omega_j} \gamma_j}{1 - 2 r cos (\varphi_j - \theta) + r^2} ,
-            \end{equation}
-            where $\gamma_j = (\varphi_{j} - \varphi_{j-1}) \bmod{ 2\pi}$ and $\varphi_0 = \varphi_k$ and this $\bmod$ can solve some critical value problem, for example, $\varphi_j = 0$ but $\varphi_{j-1} = 6$.
-For the convenience of computation, we only calculate the value of $H$ on a grid
-            \begin{align*}
-                G = \{z=x+iy \mid &\abs{z} \le 1, x=\frac{j}{100}, y=\frac{k}{100},\\
-                &j,k=-100,-99,\cdots,99,100 \}.
-            \end{align*}
-
-        \subsection{Normalization}
-            Because of the arbitrariness of the comformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
-            \begin{equation*}
-                \tilde{H} = M_1 \circ H \circ M_2.
-            \end{equation*}
-            Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then Beltrami signature $B$ can be unique.
-This section will tells how to satisfy equation (\ref{norm phi1}), (\ref{norm phi2 1}) and (\ref{norm phi2 2}) from the output of zipper algorithm.
-
-            To normalization $M_1$, we need to solve equation (\ref{eq}).
-Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concerntrate around a point.
-At that time, $\abs{f(a)} \approx 1$ almost everywhere and the solution of (\ref{eq}) is also very close to the point.
-This means the solution is quite unstable and hard to converge for common algorithms(see Fig \ref{original distribution}).
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig7_down.png}
-                \end{center}
-                \caption{(a) The $p_i \in \partial \D$ gather in a small neiborhood around their arithmetic mean $p_c$, which is labeled in red.
-(b) The corresponding $\abs{f(a)}$ for these $p_i$.
-It's worth to metion that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
-                \label{original distribution}
-            \end{figure}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig8_down.png}
-                \end{center}
-                \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment. (b) The $\abs{f(a)}$.}
-            \end{figure}
-
-            Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobious transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
-For the $r$-th iteration, let
-            \begin{equation*}
-                p_{c,r} = \frac{\sum_{i=1}^k p_{i,r}}{k} \in \D
-            \end{equation*}
-            as the arithmetic center of $p_{i,r} \in \partial \D$.
-Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobious transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
-            \begin{equation*}
-                p_{i,r+1} = F_{p_{c,r}}(p_{i,r}) = \frac{p_{i,r} - p_{c,r}}{1 - \overline{p_{c,r}}p_{i,r}}.
-            \end{equation*}
-            Note that we set $p_{i,0} = p_{i}$ at the beginning.
-Repeat this iteration for $r$ times until the center of boundary points is close to $0$, then the distribution is sufficiently regular and $\Phi_1$ becomes
-            \begin{equation}
-                \tilde{\Phi}_1 = \Phi_1 \circ F_{p_{c,0}}^{-1} \circ F_{p_{c,1}}^{-1} \circ \cdots \circ F_{p_{c,r}}^{-1}.
-            \end{equation}
-            Now equation (\ref{eq}) can be solved without much effort by Newtown's method. Suppose $a \in \D$ is the optimal solution and let 
-            \begin{equation*}
-                F_{\Phi_1} = F_a \circ F_{p_{c,r}} \circ F_{p_{c,r-1}} \circ \cdots \circ F_{p_{c, 0}}
-            \end{equation*}
-            and the final conformal mapping satisfying (\ref{norm phi1}) is
-            \begin{equation}
-                \hat{\Phi}_1 = \tilde{\Phi}_1 \circ F_{a}^{-1} = \Phi_1 \circ F_{\Phi_1}^{-1}
-            \end{equation}
-
-            \begin{algorithm}[H]
-            \caption{Normalize $M_1$}
-            \label{alg norm phi1}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} $\Phi_1$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $\epsilon=0.2$.
-                \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$, $F_{\Phi_1} = id$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$.
-%and $M_{p_{c,0}}(z) = \frac{z-p_{c,0}}{1- \overline{p_{c, 0}}z}$
-                \WHILE{$\abs{p_c,r} > \epsilon$}
-                    \STATE Let $F_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $\Phi_1 = \Phi_1 \circ F_{p_{c,r}}^{-1}$.
-                    \STATE Compute $F_{\Phi_1} = F_{p_{c,r}} \circ F_{\Phi_1}$, $p_{i, r+1} = F_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
-                    \STATE Let $r = r+1$.
-                \ENDWHILE
-                \STATE Solve equation (\ref{eq}) by Newtown's method and get solution $a \in \D$.
-                \STATE Let $F_a(z) = \frac{z-a}{1- \overline{a}z}$, $F_{\Phi_1} = F_a \circ F_{\Phi_1}$ and $\hat{\Phi}_1 = \Phi_1 \circ F^{-1}_{a}$.
-                \STATE Compute $p_i = F_a(p_{i,r})$.
-                \RETURN Mobious transformation $F_{\Phi_1}$, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig9.png}
-                \end{center}
-                \caption{The iteration of distribution adjustment. The boundary points are blue and their arithmetic center is red in each picture. (a)-(d) The 1st, 3rd, 7th, 12th iteration.}
-            \end{figure*}
-
-            As for the normalization of $M_2$, it's much easier.
-For requirement (\ref{norm phi2 1}), we only need to map $\infty$ to $\infty$ by replace $\Phi_2$ with $\tilde{\Phi}_2(z)=\Phi_2 \circ F^{-1}_{b}(\frac{1}{z})$, where $b = \Phi_2^{-1}(\infty)$.
-Another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
-According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
-Here we select $M = 10^5$ points uniformly from $[0, 2\pi)$ as $\theta_j = \frac{2 j \pi}{M}$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}).
-Therefore, the maximal solution $\theta_{\max} = \argmax{j \in [0,10^5)} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ can be used to normalize the rotation and the final mapping is
-            \begin{equation}
-                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
-            \end{equation}
-            where $M_{\Phi_2}(z) = e^{i \theta_{max}} \frac{z-b}{1 - \overline{b}z}$.
-
-            \begin{algorithm}[H]
-            \caption{Normalize $M_2$}
-            \label{alg norm phi2}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} $\Phi_2$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $M=10^5$.
-                \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$.
-                \STATE Let $M_b(z) = \frac{z-b}{1-\overline{b}z}$ and $\tilde{\Phi}_2(z)=\Phi_2 \circ M^{-1}_{b}(\frac{1}{z})$.
-                \STATE Calculate $\abs{\tilde{\Phi}_2'}$ by chain derative rule.
-                \STATE Let $\theta_j = \frac{2\pi}{M}(j-1)$ for $j=1,2, \cdots, M$.
-                \STATE Compute $\abs{\tilde{\Phi}_2'}(e^{i \theta_j})$.
-                \STATE Find maximal value and corresponding $\theta_{max}$.
-                \STATE Let $\hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z)$ and compute $p_i = \frac{e^{-i \theta_{max}}}{M_b(p_i)}$.
-                \RETURN Conformal mapping $\hat{\Phi}_2: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=.76cm]{src/fig10.png}
-                \end{center}
-                \caption{The change of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ for different $\theta_j \in [0, 2\pi)$.
-It shows this function has a significant maximum and $\theta_{max}$ is about $1.25\pi$.}
-                \label{derative}
-            \end{figure}
-
-            After obatining Mobious transformations $F_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
-            \begin{align*}
-                \hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}
-            \end{align*}
-            and it is unique up to a rotation.
-
-        \subsection{Summary of the Algorithm}
-            The totally algorithm is as following.
-            \begin{algorithm}[H]
-            \caption{Calculate Beltrami signature}
-            \label{alg all}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} Bounded simple connected shape $\Omega \subset \C$, $N=200$.
-                \STATE Pick $N$ clockwise points $z_1, z_2, \cdots, z_N$ from $\partial \Omega$ uniformly.
-                \STATE Input $z_1, z_2, \cdots, z_N$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_1}: \D \rightarrow \Omega$ and $p_{i,1} \in \partial\D$.
-                \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$. %and 
-                \STATE Input $z_N, \cdots, z_2, z_1$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_2}: \D \rightarrow \Omega^c$ and $p_{i,2} \in \partial\D$.
-                \STATE Let $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-                \STATE Let $f = \Phi_1^{-1} \circ \Phi_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
-                \STATE Extend $f$ to $H$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
-                \STATE Input $\Phi_1$ and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get $F_{\Phi_1}$.
-                \STATE Input $\Phi_2$ and $p_{i,2}$ to Algorithm \ref{alg norm phi2}, then get $M_{\Phi_2}$.
-                \STATE Calculate normalized harmonic extension $\hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}$.
-                \STATE Calculate Beltrami coefficient $B$ of $\hat{H}$.
-                \RETURN Beltrami signature $B$.
-            \end{algorithmic}
-            \end{algorithm}
-    \section{Experimental result}\label{result}
-        In this section, we will validate key properties of our proposed Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
+\chapter{Experimental result}\label{result}
+        In this section, we will validate key properties of our proposed Harmonic Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
 Besides that, a good shape representation should keep the similarity with the same kind shape and is significantly different from different kinds of shape.
 
-        Before showing results, what needs illustration is that the distance we used to measure the difference of Beltrami signature is based on $L^2$ norm,
+        Before showing results, what needs illustration is that the distance we used to measure the difference of HBS is based on $L^2$ norm,
         \begin{equation}\label{bs dis}
@@
         \end{equation}
-        where $B_1, B_2$ are two different Beltrami signature, $z_i \in \D$ is the face center of triangluar mesh $M$ metioned in Section \ref{detail harmonic} and $N=60962$ here.
-        \subsection{Invariance}\label{sec inv}
-            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate Beltrami signature after sacling, translation and rotation and compare them with the original shape's Beltrami signature.
+        where $B_1, B_2$ are two different Harmonic Beltrami signatures, $z_i \in \D$ is the face center of triangular mesh $M$ mentioned in Section \ref{detail harmonic} and $N=60962$ here.
+        \section{Invariance}\label{sec inv}
+            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate HBS after scaling, translation and rotation and compare them with the original shape's HBS.
 The result is displayed in Fig \ref{inv}.
 In this figure, the first column are the sets of boundary points and we remark them as $\Omega_a$ to $\Omega_f$.
-The second column are the corresponding Beltrami signatures $B_a$ to $B_f$.
-Note that all the Beltrami signatures are shown in modulus, i.e.
+The second column are the corresponding Harmonic Beltrami signatures $B_a$ to $B_f$.
+Note that all the Harmonic Beltrami signatures are shown in modulus, i.e.
 $\abs{B_n}$ for row $n$, and in top view.
-And the third column(if have) are the histograms of the difference between original shape's Beltrami signature, i.e.
+And the third column(if have) are the histograms of the difference between original shape's Harmonic Beltrami signature, i.e.
 $\abs{B_n - B_a}$ for row $n$.
@@
 Row e is about rotation, the shape is $\Omega_e = \{z \mid z = e^{0.2\pi i} z_a, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.2144 \times 10^{-8}$.
-Row f is the combination of scaling, tanslation and rotation, the shape is $\Omega_e = \{z \mid z = 3e^{-0.85\pi i} z_a+350+600i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.7635 \times 10^{-8}$.
-These confirm the invariance of Beltrami signature and scaling, translation and rotation.
+Row f is the combination of scaling, translation and rotation, the shape is $\Omega_e = \{z \mid z = 3e^{-0.85\pi i} z_a+350+600i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.7635 \times 10^{-8}$.
+These confirm the invariance of HBS under scaling, translation and rotation.
 
-            \begin{figure*}
+            \begin{figure}
                 \begin{center}
-                    \includegraphics[width=10.5cm]{src/inv.png}
+                    \includegraphics[width=11cm]{inv.png}
                 \end{center}
-                \caption{Beltrami signature under scaling, translation and rotation.}
+                \caption{Harmonic Beltrami signature under scaling, translation and rotation.}
                 \label{inv}
-            \end{figure*}
+            \end{figure}
 
-        \subsection{Robustness}
+        \section{Robustness}
             Similar with Section \ref{sec inv}, here we still treat the dolphin as the original shape and modify some small parts of it and Fig \ref{robust} is the result.
-It shows that the proposed signature is robust and stable and will not have a big mutation cauesd by small disturbance.
+It shows that the proposed signature is robust and stable and will not have a big mutation caused by small disturbance.
 
@@
 
-            Row j is for distortion. This dolphin is only enlarged in horizontally and becomes fatter, then the $B_j$ moves a little bit and $d(B_a, B_j) = 0.0724$.
+            Row j is for distortion. This dolphin is only enlarged horizontally and becomes fatter, then the $B_j$ moves a little bit and $d(B_a, B_j) = 0.0724$.
 
-            \begin{figure*}
+            \begin{figure}
                 \begin{center}
-                    \includegraphics[width=10.5cm]{src/robust.png}
+                    \includegraphics[width=11cm]{robust.png}
                 \end{center}
-                \caption{Beltrami signature under small modification}
+                \caption{Harmonic Beltrami signature under small modification}
                 \label{robust}
-            \end{figure*}
+            \end{figure}
 
-        \subsection{Classification with Beltrami signature}
-            Above properties ensure the proposed signature having the ablity to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.
+        \section{Classification with HBS}
+            Above properties ensure the proposed signature having the ability to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.
 
@@
 There are 3 images for each group so 9 images in total.
-From Fig \ref{classification images}, we can find that each class share similar Beltrami signatures and conformal welding.
-From Fig \ref{dis matrix}, the inter-class distance of Beltrami signature is awlays less than 0.2 while the intra-class distance is greater than 0.2.
+From Fig.
+\ref{classification images}, we can find that each class share similar HBS and conformal welding, where the top left is the input shape,  bottom left is the conformal welding and the right is Harmonic Beltrami signature in each subfigure.
+
+            The distances between each two shapes are as shown in Fig.
+\ref{dis matrix BS} and Fig.
+\ref{dis matrix welding}.
+The intraclass distance of HBS is always less than 0.2 while the interclass distance is greater than 0.2.
 But for conformal welding, the data is messy, for example, fish 3 thinks itself is very different from other fishes but looks most like giraffe 2.
-After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the Beltrami signature shows powerful classification ablity.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/figs.png}
-                \end{center}
-                \caption{These 3 rows are elephant, fish and giraffe. In each subfigure, the top left is the input shape, bottom left is the conformal welding and the right is Beltrami signature.}
-                \label{classification images}
-            \end{figure*}
+After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the HBS shows powerful classification ability.
+For HBS method, points representing shapes of the same kind are closely gathered together while there is no such phenomenon for conformal welding.
 
@@
                 \begin{center}
-                    \includegraphics[width=7.6cm]{src/distance_down.png}
+                    \includegraphics[width=\textwidth]{figs.png}
                 \end{center}
-                \caption{(a) The distance matrix of Beltrami signatures of above 9 shapes by equation (\ref{bs dis}). (b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
-                \label{dis matrix}
+                \caption{These 3 rows are elephant, fish and giraffe.
+In each subfigure, the top left is the input shape, bottom left is the conformal welding and the right is Harmonic Beltrami signature.}
+                \label{classification images}
             \end{figure}
@@
                 \begin{center}
-                    \includegraphics[width=7.6cm]{src/mds_down.png}
+                    \includegraphics[width=14cm]{distance.png}
                 \end{center}
-                \caption{(a) The MDS result of Beltrami signature. (b) The MDS result of conformal welding.}
+                \caption{(a) The distance matrix of Harmonic Beltrami signatures of above 9 shapes by equation (\ref{bs dis}); (b) The distance matrix of conformal weldings of above 9 shapes by equation (\ref{welding dis}).}
+                \label{dis matrix welding}
+            \end{figure}
+
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=12cm]{mds_down.png}
+                \end{center}
+                \caption{(a) The MDS result of Harmonic Beltrami signature; (b) The MDS result of conformal welding.}
                 \label{mds1}
@@
 
-            \begin{figure*}
+        \section{Classification for more classes}\label{classification for more shapes}
+            In the last experiment, the numble of samples is only 9 in total and may be too small to be convincing.
+So here we enlarge the amount of images to 58 with 7 different classes, which are camel, deer, dog, elephant, giraffe, gorilla and rabbit.
+All these shapes are in Fig.
+\ref{all images}.
+
+            We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes.
+The MDS and clustering results based on Harmonic Beltrami signature and conformal welding are displayed in Fig.
+\ref{mds_and_cluster_BS}.
+Not expectedly, our HBS has excellent classification performance: the classification accuracy based on Harmonic Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
+
+            \begin{figure}
                 \begin{center}
-                    \includegraphics[width=\textwidth]{src/mds2.png}
+                    \includegraphics[width=15cm]{all_images.png}
                 \end{center}
-                \caption{(a) The MDS result of Beltrami signature.
-(b) The MDS result of conformal welding.
-(c) The clustering result of Beltrami signature.
-(d) The clustering results of conformal welding.}
-                \label{mds2}
-            \end{figure*}
+                \caption{All 58 shapes within 7 classes used in experiment \ref{classification for more shapes}.}
+                \label{all images}
+            \end{figure}
 
-        \subsection{Classification for more classes}
-            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabit.
-We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes.
-The MDS and clustering results based on Beltrami signature and conformal welding are displayed in Fig \ref{mds2}.
-The classification accuracy based on Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=12cm]{mds_and_cluster_BS.png}
+                \end{center}
+                \caption{(a) The MDS result of Harmonic Beltrami signature; (b) The clustering result of Harmonic Beltrami signature.}
+                \label{mds_and_cluster_BS}
+            \end{figure}
 
-    \section{Conclusion}\label{conclusion}
-        In this paper, we propose a novel shape representation for 2D bounded simple connected objects called Beltrami signature.
-The proposed signature is based on conformal welding but overcome a key shortcoming that it can be uniquely determined by the given shape.
-What's more exciting is that the proposed representation is invariance under scaling, translation and rotation.
-For slight deformation and distortion, Beltrami signature keeps roubost and only changes within a reasonable small range.
-Therefore, there are reasons to believe the it does have ablity to represent some invariant geometrical features.
-The experimental results also confirm that the Beltrami signature has excellent performance in multi-classification tasks.
-
-        Although our work has achieved relatively good results, the proposed representation still have some limitations.
-Firstly, the Beltrami signature is only applicable to simple connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world.
-So we are eager for a feasible method to extend our Beltrami signature to multi connected situation.
-Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangluar mesh, which consumes a lot of time.
-Therefore, a fast algorithm to obatin this signature avoiding dense mesh is of high priority in our future work.
-Thirdly, when normalizing the conformal mapping $\Phi_2$ from exterior of unit disk to exterior of the domain, the position where the derivation of $\Phi_2$ reaches the maximum value is used to adjust the rotation.
-We trust this point in the original image has a certain geometric meaning, whereas it is not clear at present.
-
-        In summary, we will focus on third marjor directions in the future.
-One is that the deeper meaning of Beltrami signature is worth digging and then a multi-connected version of representation based on this work can be proposed.
-Another is that if the Beltrami signature contains some geometrical features of shapes, we can also extract them directly from images and generate the Beltrami signature again.
-Hence the deep learning theory may help us to compute this signature from given images immediately, which is very likely to improve algorithm speed performance greatly.
-A third direction is this representation can be used in more applications like segementation, registration and so on.
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
-% \section*{Conflict of interest}
-%
-% The authors declare that they have no conflict of interest.
-
-% BibTeX users please use one of
-% \bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
-\bibliography{cite}
-% Non-BibTeX users please use
-% \begin{thebibliography}{}
-% %
-% % and use \bibitem to create references. Consult the Instructions
-% % for authors for reference list style.
-% %
-% \bibitem{RefJ}
-% % Format for Journal Reference
-% Author, Article title, Journal, Volume, page numbers (year)
-% % Format for books
-% \bibitem{RefB}
-% Author, Book title, page numbers. Publisher, place (year)
-% % etc
-% \end{thebibliography}
-
-\end{document}
-% end of file template.tex
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=12cm]{mds_and_cluster_welding.png}
+                \end{center}
+                \caption{(a) The MDS result of conformal welding; (b)  The clustering results of conformal welding.}
+                \label{mds_and_cluster_welding}
+            \end{figure}

### 2021-06-11 introduction/introduction.tex
final thesis

--- 2021-04-07 template.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-% \smartqed  % flush right qed marks, e.g. at end of proof
-%
-% \let\equation\relax
-% \let\endequation\relax
-\let\proof\relax
-\let\endproof\relax
-\let\example\relax
-\let\endexample\relax
+% chapter introduction
+\chapter{Introduction}\label{intro}
+    As information objects are digitized, more and more digital images have been generated, hence there is a growing interest in shape  analysis in recent years.
+The outline of a shape contains important information, which can be used in many applications, such as image classification, segmentation, recognition, registration, medical image analysis and so on.
+Nevertheless, it is a big challenge to define a robust descriptor for the space of shapes, even for the simplest situation of 2D simply-connected objects.
+In order to manipulate shapes and utilize their geometric information, there is an urgent demand to find a simple and robust representation to mathematically describe shape contours.
+The shape representation should also inherits a natural metric to measure geometric differences between two shape representations.
+With the geometric dissimilarity metric, two shapes can be quantitatively compared and prior shape information can be incorporated into various imaging models by adding a penalty term to further improve the accuracy.
+Due to its significance, this problem has been widely studied and different models to build the metric shape space have been proposed.
 
-\usepackage{graphicx}
-\usepackage[margin=1in]{geometry} 
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{hyperref}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\include{snippets}
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
-\begin{document}
+    \begin{figure}
+    \begin{center}
+    \includegraphics[width=14cm]{fig1.png}
+    \end{center}
+    \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simply-connected domain $\Omega$; (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
+    \label{ill of cw}
+    \end{figure}
 
-\title{Beltrami Signature: A Novel Invariant 2D Shape Representation for  Object Classification}
-% \subtitle{Do you have a subtitle?\\ If so, write it here}
+    % \begin{figure}\label{ill of cw}
+    %     \begin{center}
+    %     \includegraphics[width=10cm]{fig1_down.png}
+    %     \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simply-connected domain $\Omega$; (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
+    %     \end{center}
+    % \end{figure}
 
-%\titlerunning{Short form of title}        % if too long for running head
+    Considering 2D simply-connected shapes, conformal welding is a kind of well-known shape signature.
+Given 2D simply-connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$.
+This gives a simple but wonderful representation of $\Omega$ as Fig.
+\ref{ill of cw} shows.
+However, it has following two fatal defects.
 
-\author{Chenran Lin \and Lok Ming Lui}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{Chenran Lin \at
-              Department of Mathematics, The Chinese University of Hong Kong \\
-              \email{crlin@math.cuhk.edu.hk}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           Lok Ming Lui \at
-              Department of Mathematics, The Chinese University of Hong Kong\\
-              \email{lmlui@math.cuhk.edu.hk}           %  \\
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simple connected domain in this paper, named Beltrami signature.
-The proposed signature is based on conformal welding.
-We extended the welding mapping to a harmonic function.
-With suitable normalization, the uniqueness of this harmonic function is guaranteed up to a rotation.
-And finally quasi-conformal theory get rid of the only uncertainty by computing Beltrami coefficient of harmonic extension.
-The benifits of the proposed signature is it keeps invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformation and distortion.
-Experiments demonstrate the above properties and also show the excellent classification performance.
-\keywords{
-  Shape representation \and conformal welding \and simple connected \and invariance}
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
-\end{abstract}
-
-\section{Introduction}
-\label{intro}
-    The outline of the shape contains very important information and it can be used in many applications, such as segementation, recognition, registration and so on.
-However, even for the simplest situation, 2D simple connected shapes, it is a big challenge to describe clearly what the shape contour looks like.
-Because of the complexity of the image, there is an urgent demand to find a common, simple and robust shape representation for further mining and utilizing of shapes' geometric information.
-Therefore, many different presentations and measures have been widly studied and proposed recently \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.
-
-    Considering 2D simple connected shapes, conformal welding is a kind of well-known shape signature.
-Given 2D simple connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$.
-This gives a simple but wonderful representation of $\Omega$ as Fig.
-\ref{fig1} shows.
-However, it has two fatal defects.
     First is that such representation is not unique.
-Because of the arbitrary of Riemann conformal mapping, $\Phi_1$ and $\Phi_2$ can only be determined up to a Mobious transformation, so such conformal welding is not unique.
+Because of the arbitrary of Riemann conformal mapping, $\Phi_1$ and $\Phi_2$ can only be determined up to a Mobi\"us transformation, so such conformal welding is not unique.
 Generally speaking, some assumption is required to remove this uncertainty.
 For example, Sharon \etal \cite{sharon20062d} need to select a base point $P$ inside the given domain $\Omega$ artificially, then let $\Phi_1$ maps $0$ to this point $P$.
-The work of Mcenteggart \etal \cite{mcenteggart2018uniqueness} is based on Schramm-Loewner evolution(SLE) on random surfaces called Liouville quantum gravity, they proved the equivalence between uniqueness of conformal welding and conformal removable and conculded that if the boundary curve $\eta$ is an $\text{SLE}_k$ for $k \in (0, 4)$ and satisifies some other requirements, the corresponding conformal welding is unique.
+The work of Mcenteggart \etal \cite{mcenteggart2018uniqueness} is based on Schramm-Loewner evolution(SLE) on random surfaces called Liouville quantum gravity, they proved the equivalence between uniqueness of conformal welding and conformal removable and conculded that if the boundary curve $\eta$ is an $\text{SLE}_k$ for $k \in (0, 4)$ and satisfies some other requirements, the corresponding conformal welding is unique.
 Some may not that care the uniqueness itself, they used equivalent class to guarantee uniqueness in a broader sense or evne just ignored it \cite{katznelson1990conformal,marshall2012conformal,lui2013shape,astala2010random}.
 
-    Another thing is that even the conformal welding is very easy to be changed by simple transformations like rotation, scaling and translation.
+    Another thing is that even the conformal welding is very easy to be changed under transformations, like rotation, scaling and translation.
+This means that it becomes quite difficult to determin the differences between two shapes under simple metric like $L^2$ norm.
 Such a unstable representation is hard to apply in practical applications since these transformations are inevitable in the real world.
 
-    The contribution of this paper is that we propose a brand new presentation for 2D simple connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Beltrami signature.
+    Under such a situation, we propose a novel presentation for 2D simply-connected shape with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Harmonic Beltrami signature.
 Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points.
-Such conformal welding can be extended to the whole unit disk and get a harmonic function $H: \D \rightarrow \D$.
-Under suitable normalization, harmonic extension $H$ can be determined up to a rotation and the Beltrami coefficient of $H$ is then unique and becomes our Beltrami signature.
+Then we have conformal welding $f = \Phi^{-1}_1 \circ \Phi_2$.
+Such conformal welding $f$ can be extended to the whole unit disk and get a harmonic function $H: \D \rightarrow \D$.
+Under suitable normalization, harmonic extension $H$ can be determined up to rotations and the Beltrami coefficient $B = \mu_H$ is then unique and becomes our Harmonic Beltrami signature.
 
-    The proposed shape representation, Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
-The Beltrami signature is based on computational quasiconformal geometry.
-Computational quasiconformal geometry has been widely used in image processing and image analysis.
+    The proposed shape representation, Harmonic Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
+The Harmonic Beltrami signature is based on computational quasi-conformal geometry.
+Computational quasi-conformal geometry has been widely used in image processing and image analysis.
 Applications can be found in image segmentation
@@
      and image analysis 
-    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shapec,lui2010shape3}
+    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shape,lui2010shape3}
     .
-What's more worth mentioning is that Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape.
-It means the proposed representation has high practical value and can be applied in computer vision work like classification, segementation and so on.
 
-    The paper is organized as follows: Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem and how Beltrami signature is obtained from given domain; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
-The paper is concluded in Section \ref{conclusion} and we point out future directions.
+    What's more worth mentioning is that Harmonic Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape.
+Conversely, The original shape can also be reconstructed from the given Harmonic Beltrami signature.
+Hence, it can be proved there exists a bijective between the shapes and our signatures up to rotation, translation and rotation, which means the proposed representation has high practical value and can be applied in computer vision work like classification, segmentation and so on.
 
-    \begin{figure}
-        \begin{center}
-        \includegraphics[width=7.6cm]{src/fig1_down.png}
-        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simple connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
-        \end{center}
-        \label{fig1}
-    \end{figure}
-
-\section{Theoretical basis}\label{background}
-    \subsection{Quasi-conformal mapping and Beltrami equation}
-        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
-        \begin{equation*}
-            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
-        \end{equation*}
-
-        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
-        \begin{equation}\label{beltrami eq}
-            \Part{f}{\overline{z}} = \mu(z) \Part{f}{z}
-        \end{equation}
-        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$.
-More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
-        \begin{equation}
-            \mu = \frac{f_{\overline{z}}}{f_{z}}
-        \end{equation}
-        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
-        \begin{equation}
-            f^*(ds^2_E) = \abs{\Part{f}{z}}^2 \abs{dz + \mu(z)d\overline{z}}^2
-        \end{equation}
-        which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$.
-$\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality.
-In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$.
-Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
-        \begin{equation}\label{local f}
-            f(z) = f(p)+f_z(p)(z+\mu(p)\overline{z}).
-        \end{equation}
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig2.jpg}
-            \end{center}
-            \caption{(a) Shows the original hippocampus.
-(b) Shows the parameter domain with circle packing pattern.
-Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
-            \label{fig2}
-        \end{figure}
-
-        If $\mu(z)=0$ everywhere, then $f$ us called \textit{conformal} or \textit{holomorphic}. A conformal map satisfies the following well-known Cauchy-Riemann equation:
-        \begin{equation}\label{cr eq}
-            \Part{f}{\overline{z}} = 0.
-        \end{equation}
-        Inside the local parameter domain, $f$ may be considered as a map composed of a translation to $f(p)$ together with a stretch map $S(z) = z + \mu(p)\overline{z}$, which is postcomposed by multiplication of $f_z(p)$, which is conformal.
-All the conformal distortion of $S(z)$ is caused by $\mu(p)$.
-$S(z)$ is the map that causes $f$ to map a small circle to a small ellipse (see Fig.
-\ref{fig2}).
-Form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well.
-Specially, the angle of maximal magnification is $\arg(\mu(p))/2$ with magnifying factor $1+\abs{\mu(p)}$; the angle of maximal shrinkage is the orthogonal angle $\arg(\mu(p))/2 - \pi/2$ with shrinkage factor $1-\abs{\mu(p)}$.
-The distortion or dilation is given by:
-        \begin{equation}
-            K = \frac{1+\abs{\mu(p)}}{1-\abs{\mu(p)}}.
-        \end{equation}
-        Thus, the Beltrami coefficient $\mu$ gives us important information about the properties of the map (see Fig. \ref{fig3}).
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig3.jpg}
-            \end{center}
-            \caption{Quasi-conformal maps infinitesimal circles to ellipses. The Beltrami coefficient measure the distortion or dilation of the ellipse under the QC map.}
-            \label{fig3}
-        \end{figure}
-
-        Suppose $f, g: \C \rightarrow \C$ are complex-valued function with Beltrami coefficient $\mu_f, \mu_g$ respectively. Then the Beltrami coefficient for the composition $g \circ f$ is given by
-        \begin{equation}\label{mu of composition}
-            \mu_{g \circ f} = \frac{\mu_f+(\mu_g \circ f) \tau}{1+\overline{\mu_f}(\mu_g \circ f) \tau},
-        \end{equation}
-        where $\tau = \frac{\overline{f_z}}{f_z}$. Note that when $g$ is conformal, $\mu_g = 0$ and 
-        \begin{equation}\label{mu of conformal composition}
-            \mu_{g \circ f} = \mu_f.
-        \end{equation}
-
-    \subsection{Conformal welding}
-        Given 2D bounded simple connected shape, we can treat it as a boundary simple connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
-$\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobious transformation}:
-        \begin{equation}
-            M(z) = e^{i \theta} \frac{z - a}{1 - \overline{a}z}.
-        \end{equation}
-        Then we can define \textit{conformal welding} as:
-        \begin{equation}
-            f = \Phi_1^{-1} \circ \Phi_2.
-        \end{equation}
-        Such $f: \partial \D \rightarrow \partial \D$ is a diffeomorphism from $\partial \D$ to itself, which can be also thought as a periodic, real-valued monotone increasing function $f_\R: [0, 2\pi) \rightarrow [0, 2\pi)$ such that $f(e^{i \theta}) = e^{i f_\R(\theta)}$ (see Fig.
-\ref{fig1}).
-
-    \subsection{Harmonic function and Poisson integral}
-        A complex-valued function $f$ defined on $\Omega \subset \C$ is called \textit{harmonic} if it satisfies the \textit{Laplace's equation}:
-        \begin{equation}
-            \Delta f = 4 \frac{\partial^2 f}{\partial z \partial \overline{z}} = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2} = 0,
-        \end{equation}
-        where $z = x + iy$, $x$, $y$ is the real and imaginary value.
-
-        Chen \etal prove following theorem in \cite{chen2010compositions}, which tells us that the composition of harmonic mappings and other mappings can inherit such harmonicity in some condition.
-        \begin{theorem}\label{composition of harmonic}
-            Let $f$ be a harmonic mapping, $f \circ g$ is harmonic if and only if $g(z) = az + b \overline{z} + c$, where $a$, $b$ and $c$ are constaants and $g \circ f$ is harmonic if and only if $g$ is analytic or anti-analytic.
-        \end{theorem}
-
-        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}.
-For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continious $f$ on $\partial \D$
-            \begin{equation}\label{poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi}\int_0^{2\pi} \frac{(1-r^2)f(e^{i \varphi})}{1 - 2 r cos (\varphi - \theta) + r^2} d\varphi.
-            \end{equation}
-        Such $H$ is harmonic on $\D$ and continious on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
-$H(e^{i\theta}) = f(e^{i\theta})$ (see Fig.
-\ref{harmonic}).
-Of course, this $H$ is unique.
-
-        \begin{figure}
-            \begin{center}
-                \includegraphics[width=7.6cm]{src/fig4_down.png}
-            \end{center}
-            \caption{(a) Continious function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$.
-(b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
-Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
-            \label{harmonic}
-        \end{figure}
-
-    \section{Beltrami signature}\label{main}
-        In this chapter, we will propose a new representation, Beltrami signature, to discribe boundary simple connected domain $\Omega$.
-Our proposed signature is based on conformal welding and quasi-conformal theory.
-
-        \subsection{Beltrami signature based on conformal welding}
-            Here we give a brief explaination of how to create our new signature.
-Given the boundary simple connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it.
-Then $f$ can be extended to harmonic function $H$ defined on $\D$ by Poisson integral (\ref{poisson integral}).
-At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
-            \begin{equation}
-                B:= \mu_H = \frac{H_{\overline{z}}}{H_z}.
-            \end{equation}
-            Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $B$ is determined.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig5.png}
-                \end{center}
-                \caption{Illustration of Beltrami signature.
-(a) The input shape, a dolphin.
-(b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b).
-(c) The Beltrami signature of (a).
-Remark that the harmonic funcion and Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
-                \label{illu of BS}
-            \end{figure*}
-
-        \subsection{Analysis of uniqueness of Beltrami signature}
-            According to Riemann mapping theorem, the conformal mapings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
-Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobious transformations.
-Therefore, the corresponding conformal welding is
-            \begin{equation}
-                \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = M_1^{-1} \circ \Phi_1^{-1} \circ \Phi_2 \circ M_2 = M_1^{-1} \circ f \circ M_2.
-            \end{equation}
-
-            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{H}$. The following theorem show the relationship between $H$ and $\tilde{H}$.
-
-            \begin{theorem}
-                Suppose $f$ and $\tilde{f}$ are continious map from $\partial \D$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
-$H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
-            \end{theorem}
-
-            \begin{proof}
-                Since $M_1$ is a Mobious transformations, $M_1^{-1}$ is also a Mobious transformation, so it can be written as $M_1^{-1}(z) = e^{i \theta}\frac{z - p}{1 - \overline{p}z}$, where $\theta \in [0, 2\pi)$ and $p \in \D$.
-
-                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
-$\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
-Therefore, we have
-                \begin{equation*}
-                    e^{i \theta}\frac{z - p}{1 - \overline{p}z} = az + b \overline{z} + c,
-                \end{equation*}
-                which means $p = b = c = 0$, $a = e^{i \theta}$ and so $M_1$ is a rotation.
-
-                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ H \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}.
-It's easy to check that
-                \begin{align*}
-                    M_1^{-1} \circ H \circ M_2 (e^{i \theta})
-                    &= M_1^{-1} \circ f \circ M_2(e^{i \theta})\\
-                    &= \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
-                \end{align*}
-                which means $M_1^{-1} \circ H \circ M_2$ and $\tilde{H}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ H \circ M_2 = \tilde{H}$.
-            \end{proof}
-
-            Because of above theorem, suppose that $M_1$ is a rotation, then we consider the Beltrami signature of $\tilde{H}$
-            \begin{equation}
-                \tilde{B} = \mu_{\tilde{H}} = \mu_{M_1^{-1} \circ H \circ M_2} = \mu_{H\circ M_2}.
-            \end{equation}
-            If we want such Beltrami signature is unique, which means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, then we get $M_2$ is identity.
-Therefore, we know that the uniqueness of Beltrami signature is equivalent to following restrictions:
+    The contributions of this thesis can be summarized as follows.
 \begin{enumerate}
-                \item $M_1$ should be a rotation.
-                \item $M_2$ should be identity.
+    \item Firstly, we propose a new shape signature, called the Harmonic Beltrami signature, to effectively represent 2D simply-connected shapes.
+Every shape has a unique Harmonic Beltrami signature.
+Conversely, given a Harmonic Beltrami signature, its corresponding shape can be determined up to a translation, rotation and scaling.
+    \item Secondly, the proposed Harmonic Beltrami signature solves the issue of conformal ambiguities facing the conformal welding signature.
+    \item Thirdly, we propose a practical procedure to normalize the Harmonic Beltrami signature to handle the non-uniqueness issue, with rigorous theoretical justifications.
+    \item Fourthly, we propose a reconstruction algorithm to construct the corresponding shape from the Harmonic Beltrami signature up to a rotation, translation and scaling.
+This allows us to go back and fro between shapes and Beltrami signatures in the imaging model.
+    \item Finally, the proposed Harmonic Beltrami signature inherits a simple metric, namely, the $L^2$ distance, to measure the geometric dissimilarity between shapes.
+We have applied the shape distance to shape classification and shown satisfactory results.
 \end{enumerate}
 
-        \subsection{Normalization to $M_1$}\label{norm1}
-            We hope $M_1$ is a rotation.
-It is not that hard, for example, we can achieve it by restricting $\Phi_1(0) = 0$.
-But it need a hypothesis that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold.
-Here we want to show a new approach without any additional assumption.
-
-            In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$.
-Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, where $\Phi_1 : \D \rightarrow \Omega$.
-We claims that $M_1$ can be normalized by restricting the center of $p_i$ to $0$.
-
-            \begin{theorem}\label{unique up to a rotation}
-                Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
-                \begin{align}\label{norm phi1}
-                    \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
-                \end{align}
-                then such $\Phi_1$ is unique up to a rotation $M_1$.
-            \end{theorem}
-
-            Before proving theorem \ref{unique up to a rotation}, we can consider following problem.
-Given boundary points $p_i$ on unit circle, can we find a Mobious transformation $M$ satisfies the following equation (\ref{fz})?
-            \begin{equation}\label{fz}
-                \sum_{k=1}^n M(p_k) = \sum_{k=1}^n e^{i\theta} \frac{p_k - a}{1 - \overline{a}p_k}= 0
-            \end{equation}
-
-            Without lose of generality, we ignore the rotation of $M$ and let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-So $F_a$ is also a Mobius transformation and it's sufficient to find $a \in \D$ such that
-            \begin{equation}\label{eq}
-                f(a) = \sum_{k=1}^n F_a(p_k) = \sum_{k=1}^n \frac{p_k - a}{1 - \overline{a}p_k} = 0
-            \end{equation}
-            to show the equation (\ref{fz}) holds for some $M$. Intuitively, we believe that there is always a unique solution to this equation (\ref{eq}) (see Fig \ref{fasolvable}).
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig6.png}
-                \end{center}
-                \caption{The first row are some randomly generated points in $\partial \D$.
-The second row are the corresponding $\abs{f(a)}$, where $a \in \D$.
-The third row are also $\abs{f(a)}$ but is in top view.
-}
-                \label{fasolvable}
-            \end{figure*}
-
-            \subsubsection{The solvability of equation (\ref{eq})}
-            First thing we want to do is to check whether this equation (\ref{eq}) is always solvable. According to Brouwer fixed point theorem, we have
-
-            \begin{theorem}\label{existence}
-                Given $\{p_1, p_2, \cdots, p_n\} \subset \partial \D$ and $n \ge 3$, let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-The solution of equation (\ref{eq}) always exists.
-            \end{theorem}
-
-            \begin{proof}
-                Note that when $e^{i \theta} \neq p_k$ for any $k$, we have
-                \begin{equation*}
-                    f(e^{i \theta}) = \sum_{k=1}^n \frac{p_k - e^{i \theta}}{1 - e^{-i\theta}p_k} = - n e^{i\theta},
-                \end{equation*}
-                so $\frac{1}{n} f(e^{i\theta}) + e^{i \theta} = 0$. Let 
-                \begin{equation*}
-                    g(a) = \begin{cases}
-                \frac{1}{n} f(a) + a, a \in \D,\\
-                0, a \in \partial \D,
-                \end{cases}
-                \end{equation*}
-                such $g$ is defined on $\overline{\D}$ and is continuous. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.
-
-                Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, then define
-                \begin{equation*}
-                    h(a) = \begin{cases}
-                    g(a), &a \in  \overline{\D} \setminus M,\\
-                    \frac{g(a)}{\norm{g(a)}}, &a \in  M.
-                \end{cases}
-                \end{equation*}
-                $h$ is a continuous map from $\overline{\D}$ to itself, so there exists some $a$ let $h(a) = a$.
-
-                If $a \in \partial \D$, $\norm{a} = 1$, but $\norm{h(a)} = 0 \neq \norm{a}$.
-If $a \in M$, we know $a \notin \partial \D$, so $\norm{a} < 1$, but $\norm{h(a)} = \frac{\norm{g(a)}}{\norm{g(a)}} = 1 \neq \norm{a}$.
-So when $h(a) = a$, $a$ is inside $\D \setminus M$.
-Therefore, such $a$ satisfies $g(a) = a$ and then $f(a) = 0$.
-            \end{proof}
-
-            Therefore, there must be some $a \in \D$ to be the solution of equation (\ref{fz}).
-
-            \subsubsection{The uniqueness of the solution of equation (\ref{eq})}
-            With solvability proved, we naturally want to know if this solution is unique. Let's consider a special case when $\sum_{k=1}^n p_k = 0$, we have
-            \begin{theorem}\label{uniqueness when 0}
-                Suppose $\sum_{k=1}^n p_k = 0$, equation (\ref{eq}) holds if and only if $a = 0$.
-            \end{theorem}
-
-            \begin{proof}
-                If $a = 0$, it's obvious $F_0$ is identity, so $f(0) = \sum_{k=1}^n p_k = 0$.
-
-                If $a \neq 0$, WLOG, we can assume that $0 < a < 1$, then $F_a(1) = 1$ and $F_a(-1) = -1$.
-For any $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$,
-                \begin{align*}
-                    &F_a(p_k) \\
-                    = &F_a(\cos \theta_k + \sin \theta_k i) \\
-                    = &\frac{\cos \theta_k + \sin \theta_k i - a}{1 - a \cos \theta_k - a \sin \theta_k i} \\
-                    = &\frac{(a^2 + 1) \cos \theta_k -2a - (a^2 - 1) \sin \theta_k i}{a^2 + 1 - 2a \cos \theta_k},
-                \end{align*}
-                so
-                \begin{align*}
-                    &\Re(F_a(p_k)) \\
-                    = &\frac{(a^2 + 1) \cos \theta_k -2a}{a^2 + 1 - 2a \cos \theta_k} \\
-                    = &\cos \theta_k - \frac{2a(1-\cos^2 \theta_k)}{(a-1)^2 + 2a(1-\cos \theta_k)} \\
-                    < &\cos \theta_k = \Re(p_k).
-                \end{align*}
-
-                Therefore, if $n \ge 3$, there must be at least one $p_k \neq \pm 1$ and so
-                \begin{align*}
-                    &\Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) \\
-                    < &\sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
-                \end{align*}
-                which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $a=0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
-            \end{proof}
-
-            This theorem confirms the uniqueness for a special situation $\sum_{k=1}^n p_k = 0$ and actually this conclusion is universal no matter how $p_i$ distribute.
-
-            \begin{theorem}\label{uniqueness}
-                The solution of equation (\ref{eq}) is unique.
-            \end{theorem}
-
-            \begin{proof}
-                Assume that $a_0, a_1$ are two different solutions, then we have that
-                \begin{align*}
-                    \sum_{k=1}^n F_{a_0}(p_k) = 0,\sum_{k=1}^n F_{a_1}(p_k) = 0
-                \end{align*}
-
-                Let $p_k' = F_{a_0}(p_k)$, then
-                \begin{align*}
-                    &\sum_{k=1}^n F_{a_1} \circ F_{a_0}^{-1} \circ F_{a_0}(p_k)\\
-                    = &\sum_{k=1}^n (F_{a_1} \circ F_{-a_0})(F_{a_0}(p_k))\\
-                    = &\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}}\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0.
-                \end{align*}
-
-                Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so \\
-                $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$. According to theorem \ref{uniqueness when 0},\\
-                $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, then $a_0 = a_1$, which contradicts to the assumption.
-            \end{proof}
-
-            \subsubsection{Unque $\Phi_1$ up to a rotation}
-
-            Above theorems show that there is alway an unique solution $a \in \D$ for equation (\ref{eq}), so we can come back to theorem \ref{unique up to a rotation}.
-
-            \begin{proof}
-                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobious transformation.
-If $\Phi_1$, $\tilde{\Phi_1} $ satisfy equation (\ref{norm phi1}), let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M_1^{-1} (p_k) = 0$.
-$M_1^{-1}$ is also a Mobious transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
-                \begin{equation*}
-                    e^{i \theta} \sum_{k=1}^n F_a(p_k) = 0.
-                \end{equation*}
-
-                From theorem \ref{uniqueness when 0} we can know $a = 0$, then $M_1^{-1}(z) = e^{i \theta} z$ and $\Phi_1$ is unique up to a rotation $M_1$.
-            \end{proof}
-
-        \subsection{Normalization to $M_2$}\label{norm2}
-            As for $M_2$, we hope it is identity, which is equivalent with the uniqueness of $\Phi_2: \D^c \rightarrow \Omega^c$.
-Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this and derivative to guarantee the uniqueness.
-
-            \begin{theorem}
-                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobious transformation.
-If $\tilde{\Phi_2}, \Phi_2$ satisifies that
-                \begin{align}
-                    &\tilde{\Phi_2}(\infty) = \Phi_2(\infty) = \infty\label{norm phi2 1}\\
-                    &\argmax{z \in \partial \D} \abs{\Phi_2'(z)} = \argmax{z \in \partial \D} \abs{\tilde{\Phi_2'}(z)} = 1,\label{norm phi2 2}
-                \end{align}
-                then such $M_2$ is identity.
-            \end{theorem}
-
-            \begin{proof}
-                Suppose Mobious transformation $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$. Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisify (\ref{norm phi2 1}), then
-                \begin{align*}
-                    &\tilde{\Phi}_2(\infty) = \Phi_2(M_2(\infty)) = \infty, \\
-                    &\Phi_2(\infty) = \infty.
-                \end{align*}
-                Therefore, $M_2(\infty) = e^{i \theta} \frac{\infty - a}{1- \overline{a} \infty} = \infty$, which means that $a = 0$ and $M_2(z) = e^{i \theta} z$.
-
-                Consider the derivative of $\tilde{\Phi}_2$,
-                \begin{equation}
-                    \tilde{\Phi}_2'(z) = \Phi_2' \circ M_2(z) \cdot M_2'(z) = e^{i\theta} \Phi_2' (e^{i \theta}z),
-                \end{equation}
-                then we know that $\abs{\tilde{\Phi}_2'(z)} = \abs{\Phi_2'(e^{i \theta}z)}$.
-Suppose $a = \argmax{z \in \partial \D} |\Phi_2'(z)|$, then we will have that $ae^{-i \theta} = \argmax{z \in \partial \D} |\tilde{\Phi}_2'(z)|$.
-                If condition (\ref{norm phi2 2}) holds for both $\tilde{\Phi}_2$ and $\Phi_2$, it means $a = a e^{-i \theta} = 1$, so $a = 1$, $\theta = 0$ and $M_2$ is identity.
-            \end{proof}
-
-        \subsection{Invariance under simple transformation}
-            With the normalization mentioned above, we can get unique Beltrami signature $B$ corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$.
-Now we want to prove that if we do some simple transformation like rotation, scaling and translation to $\Omega$, the Beltrami signature is invariant.
-
-            \begin{theorem}
-                Given a boundary simple connected domain $\Omega$ and transformation $T$ which is composed by rotation, scaling and transformation.
-Let $B_\Omega$ and $B_{T(\Omega)}$ be the Beltrami signature of $\Omega$ and $T(\Omega)$, then $B_\Omega = B_{T(\Omega)}$
-            \end{theorem}
-
-            \begin{proof}
-                Suppose $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, $\tilde{\Phi}_1: \D \rightarrow T(\Omega)$ and $\tilde{\Phi}_2 : \D^c \rightarrow T(\Omega)$ are conformal.
-Since $T$ is composed by rotation, scaling and translation, $T$ can be written as $T(z) = ke^{i\theta} z + b$.
-Such $T$ is absolutely invertible and conformal.
-
-                Let $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1 : \D \rightarrow \Omega$, $\hat{\Phi}_1$ is conformal.
-Given the boundary points $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$, then $\{T(z_1), T(z_2), \cdots, T(z_n)\} \subset \partial T(\Omega)$.
-Since $\tilde{\Phi}_1$ satisifies condition (\ref{norm phi1}), we have
-                \begin{equation*}
-                    \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0.
-                \end{equation*}
-
-                Therefore
-                \begin{equation*}
-                    \sum_{i=1}^n \hat{\Phi}_1^{-1}(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1} \circ T(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0,
-                \end{equation*}
-                which means $\hat{\Phi}_1$ also satisifies condition (\ref{norm phi1}). Hence $\hat{\Phi}_1 =  T^{-1} \circ \tilde{\Phi}_1= \Phi_1 \circ R$, which equals to
-                \begin{equation}
-                    \tilde{\Phi}_1 = T \circ \Phi_1 \circ R,
-                \end{equation}
-                where $R$ is a rotation.
-
-                Similarly, let $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2: \D^c \rightarrow \Omega^c$, $\hat{\Phi}_2$ is conformal. Since $\tilde{\Phi}_2(\infty) = \infty$, we have
-                \begin{equation*}
-                    \hat{\Phi}_2(\infty) = T \circ \tilde{\Phi}_2(\infty) = \infty,
-                \end{equation*}
-                which means $\hat{\Phi}_2$ satisifies condition (\ref{norm phi2 1}).
-
-                As for condition (\ref{norm phi2 2}), we know that $T'(z) = k e^{i \theta}$, so
-                \begin{equation}
-                    \hat{\Phi}_2'(z) = T' \circ \tilde{\Phi}_2(z) \cdot \tilde{\Phi}_2'(z) = k e^{i \theta} \tilde{\Phi}_2'(z).
-                \end{equation}
-                Hence $\abs{\hat{\Phi}_2'} = \abs{k}\abs{\tilde{\Phi}_2'}$, which means $\hat{\Phi}_2$ also satisifies condition (\ref{norm phi2 2}).
-Therefore, $\hat{\Phi}_2 = T^{-1} \circ \tilde{\Phi}_2 = \Phi_2$ and then
-                \begin{equation}
-                    \tilde{\Phi}_2 = T \circ \Phi_2.
-                \end{equation}
-
-                We have the conformal welding
-                \begin{equation}
-                    \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = R^{-1} \circ \Phi_1^{-1} \circ T^{-1} \circ T \circ \Phi_2 = R^{-1} \circ f.
-                \end{equation}
-                Then the harmonic extension $\tilde{H} = R^{-1} \circ H$ and 
-                \begin{equation}
-                    B_{T(\Omega)} = \mu_{\tilde{H}} = \mu_{R^{-1} \circ H} = \mu_H = B_\Omega.
-                \end{equation}
-            \end{proof}
-
-    \section{Implementation detail}\label{implementation}
-        \subsection{Zipper algorithm}
-            In oder to find an unique and stable Beltrami signature, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
-As metioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
-
-            Marshall \etal demonstrates the zipper algorithm detailedly with clear diagrams in \cite{marshall2007convergence}.
-For the convenience of readers, we gives a very brief review here.
-Given $N$ clockwise boundary points $z_1, z_2, \cdots, z_N \in \partial \Omega$, this algorithm use a series of linear fractional transformations $g_1, g_2, \cdots, g_N$ to map $z_1, z_2,\cdots, z_N$ to real axis one-by-one, and finally transfrom the upper half plane to unit disk by $g_{N+1}(z) = \frac{z-i}{z+i}$.
-Therefore, $g = g_{N+1} \circ g_N \circ \cdots \circ g_2 \circ g_1$ is a conformal mapping undisputedly and maps all these boundary points to unit circle and the domain $\Omega$ to $\D$.
-Remark that zipper algorithm is sensitive to the order of points.
-If we input the points anti-clockwise, i.e.
-$z_N, z_{N-1}, \cdots, z_1$, the zipper will give us a conformal mapping from $\Omega^c$ to $\D$.
-
-            For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputing points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$.
-For $\Phi_2 : \D^c \rightarrow \Omega^c$, we can input anti-clockwise points and get $g_{\Phi_2} : \Omega^c \rightarrow \D$.
-At the result $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-Because of the invariance of scaling, the number of boundary points $N$ is fixed as $200$ here and they are picked uniformly from the shape contour.
-
-            \begin{algorithm}[H]                           % HERE!!!!!!!!!
-            \caption{Zipper}          % give the algorithm a caption
-            \label{zipper}      % and a label for \ref{} commands later in the document
-            \begin{algorithmic}  % enter the algorithmic environment
-                \STATE \textbf{Inputs:} $z_i \in \partial \Omega$ for $i=1, 2, \cdots, N$, $N=200$. %, $\epsilon = 10^{-10}$(any very small value)
-                \STATE \textbf{Initialize:} Let $r=2$, $g_1(z) = \sqrt{\frac{z-z_2}{z-z_1}}$, $g= g_1$ and compute $p_{i,2}=g(z_i)$.
-                \WHILE{$r < N$}
-                    \STATE Pick $q = p_{r+1, r} = a + b i$, then compute $c = \frac{a}{\abs{q}^2}$, $d = \frac{b}{\abs{q}^2}$.
-                    \STATE Let $g_r(z) = \sqrt{\frac{cz}{1+dzi}}$, then $g = g_r \circ g$ and compute $p_{i, r+1} = g_r(p_{i, k})$.
-                    \STATE Let $r = r+1$.
-                \ENDWHILE
-                \STATE Let $g_{N}(z) = \left(\frac{z}{1-\frac{z}{p_{1,N}}}\right)^2$ and $g_{N+1}(z) = \frac{z-i}{z+i}$, then $g = g_{N+1} \circ g_N \circ g$ and $p_i = g_{N+1} \circ g_N(p_{i,N})$.
-                \RETURN Conformal mapping $g: \Omega \rightarrow \D$ and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-        \subsection{Harmonic extension}\label{detail harmonic}
-            After obtaining the output of zipper algorithm, $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$, the conformal welding can be represented as a series points
-            \begin{equation*}
-                (\varphi_i, \omega_i) = \left(\arg(\hat{\Phi}_2^{-1}(z_i)), \arg(\hat{\Phi}_1^{-1}(z_i))\right),
-            \end{equation*}
-            where $\varphi_i, \omega_i \in [0, 2\pi)$. So in fact we should use discrete form Poisson integral to extend $f$ to a harmonic mapping $H$ on the unit disk
-            \begin{equation}\label{discrete poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi} \sum_{j=1}^k \frac{(1-r^2) e^{i \omega_j} \gamma_j}{1 - 2 r cos (\varphi_j - \theta) + r^2} ,
-            \end{equation}
-            where $\gamma_j = (\varphi_{j} - \varphi_{j-1}) \bmod{ 2\pi}$ and $\varphi_0 = \varphi_k$ and this $\bmod$ can solve some critical value problem, for example, $\varphi_j = 0$ but $\varphi_{j-1} = 6$.
-For the convenience of computation, we only calculate the value of $H$ on a grid
-            \begin{align*}
-                G = \{z=x+iy \mid &\abs{z} \le 1, x=\frac{j}{100}, y=\frac{k}{100},\\
-                &j,k=-100,-99,\cdots,99,100 \}.
-            \end{align*}
-
-        \subsection{Normalization}
-            Because of the arbitrariness of the comformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
-            \begin{equation*}
-                \tilde{H} = M_1 \circ H \circ M_2.
-            \end{equation*}
-            Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then Beltrami signature $B$ can be unique.
-This section will tells how to satisfy equation (\ref{norm phi1}), (\ref{norm phi2 1}) and (\ref{norm phi2 2}) from the output of zipper algorithm.
-
-            To normalization $M_1$, we need to solve equation (\ref{eq}).
-Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concerntrate around a point.
-At that time, $\abs{f(a)} \approx 1$ almost everywhere and the solution of (\ref{eq}) is also very close to the point.
-This means the solution is quite unstable and hard to converge for common algorithms(see Fig \ref{original distribution}).
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig7_down.png}
-                \end{center}
-                \caption{(a) The $p_i \in \partial \D$ gather in a small neiborhood around their arithmetic mean $p_c$, which is labeled in red.
-(b) The corresponding $\abs{f(a)}$ for these $p_i$.
-It's worth to metion that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
-                \label{original distribution}
-            \end{figure}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig8_down.png}
-                \end{center}
-                \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment. (b) The $\abs{f(a)}$.}
-            \end{figure}
-
-            Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobious transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
-For the $r$-th iteration, let
-            \begin{equation*}
-                p_{c,r} = \frac{\sum_{i=1}^k p_{i,r}}{k} \in \D
-            \end{equation*}
-            as the arithmetic center of $p_{i,r} \in \partial \D$.
-Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobious transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
-            \begin{equation*}
-                p_{i,r+1} = F_{p_{c,r}}(p_{i,r}) = \frac{p_{i,r} - p_{c,r}}{1 - \overline{p_{c,r}}p_{i,r}}.
-            \end{equation*}
-            Note that we set $p_{i,0} = p_{i}$ at the beginning.
-Repeat this iteration for $r$ times until the center of boundary points is close to $0$, then the distribution is sufficiently regular and $\Phi_1$ becomes
-            \begin{equation}
-                \tilde{\Phi}_1 = \Phi_1 \circ F_{p_{c,0}}^{-1} \circ F_{p_{c,1}}^{-1} \circ \cdots \circ F_{p_{c,r}}^{-1}.
-            \end{equation}
-            Now equation (\ref{eq}) can be solved without much effort by Newtown's method. Suppose $a \in \D$ is the optimal solution and let 
-            \begin{equation*}
-                F_{\Phi_1} = F_a \circ F_{p_{c,r}} \circ F_{p_{c,r-1}} \circ \cdots \circ F_{p_{c, 0}}
-            \end{equation*}
-            and the final conformal mapping satisfying (\ref{norm phi1}) is
-            \begin{equation}
-                \hat{\Phi}_1 = \tilde{\Phi}_1 \circ F_{a}^{-1} = \Phi_1 \circ F_{\Phi_1}^{-1}
-            \end{equation}
-
-            \begin{algorithm}[H]
-            \caption{Normalize $M_1$}
-            \label{alg norm phi1}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} $\Phi_1$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $\epsilon=0.2$.
-                \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$, $F_{\Phi_1} = id$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$.
-%and $M_{p_{c,0}}(z) = \frac{z-p_{c,0}}{1- \overline{p_{c, 0}}z}$
-                \WHILE{$\abs{p_c,r} > \epsilon$}
-                    \STATE Let $F_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $\Phi_1 = \Phi_1 \circ F_{p_{c,r}}^{-1}$.
-                    \STATE Compute $F_{\Phi_1} = F_{p_{c,r}} \circ F_{\Phi_1}$, $p_{i, r+1} = F_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
-                    \STATE Let $r = r+1$.
-                \ENDWHILE
-                \STATE Solve equation (\ref{eq}) by Newtown's method and get solution $a \in \D$.
-                \STATE Let $F_a(z) = \frac{z-a}{1- \overline{a}z}$, $F_{\Phi_1} = F_a \circ F_{\Phi_1}$ and $\hat{\Phi}_1 = \Phi_1 \circ F^{-1}_{a}$.
-                \STATE Compute $p_i = F_a(p_{i,r})$.
-                \RETURN Mobious transformation $F_{\Phi_1}$, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig9.png}
-                \end{center}
-                \caption{The iteration of distribution adjustment. The boundary points are blue and their arithmetic center is red in each picture. (a)-(d) The 1st, 3rd, 7th, 12th iteration.}
-            \end{figure*}
-
-            As for the normalization of $M_2$, it's much easier.
-For requirement (\ref{norm phi2 1}), we only need to map $\infty$ to $\infty$ by replace $\Phi_2$ with $\tilde{\Phi}_2(z)=\Phi_2 \circ F^{-1}_{b}(\frac{1}{z})$, where $b = \Phi_2^{-1}(\infty)$.
-Another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
-According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
-Here we select $M = 10^5$ points uniformly from $[0, 2\pi)$ as $\theta_j = \frac{2 j \pi}{M}$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}).
-Therefore, the maximal solution $\theta_{\max} = \argmax{j \in [0,10^5)} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ can be used to normalize the rotation and the final mapping is
-            \begin{equation}
-                \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
-            \end{equation}
-            where $M_{\Phi_2}(z) = e^{i \theta_{max}} \frac{z-b}{1 - \overline{b}z}$.
-
-            \begin{algorithm}[H]
-            \caption{Normalize $M_2$}
-            \label{alg norm phi2}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} $\Phi_2$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $M=10^5$.
-                \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$.
-                \STATE Let $M_b(z) = \frac{z-b}{1-\overline{b}z}$ and $\tilde{\Phi}_2(z)=\Phi_2 \circ M^{-1}_{b}(\frac{1}{z})$.
-                \STATE Calculate $\abs{\tilde{\Phi}_2'}$ by chain derative rule.
-                \STATE Let $\theta_j = \frac{2\pi}{M}(j-1)$ for $j=1,2, \cdots, M$.
-                \STATE Compute $\abs{\tilde{\Phi}_2'}(e^{i \theta_j})$.
-                \STATE Find maximal value and corresponding $\theta_{max}$.
-                \STATE Let $\hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{max}}z)$ and compute $p_i = \frac{e^{-i \theta_{max}}}{M_b(p_i)}$.
-                \RETURN Conformal mapping $\hat{\Phi}_2: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
-            \end{algorithmic}
-            \end{algorithm}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=.76cm]{src/fig10.png}
-                \end{center}
-                \caption{The change of $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ for different $\theta_j \in [0, 2\pi)$.
-It shows this function has a significant maximum and $\theta_{max}$ is about $1.25\pi$.}
-                \label{derative}
-            \end{figure}
-
-            After obatining Mobious transformations $F_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
-            \begin{align*}
-                \hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}
-            \end{align*}
-            and it is unique up to a rotation.
-
-        \subsection{Summary of the Algorithm}
-            The totally algorithm is as following.
-            \begin{algorithm}[H]
-            \caption{Calculate Beltrami signature}
-            \label{alg all}
-            \begin{algorithmic}
-                \STATE \textbf{Inputs:} Bounded simple connected shape $\Omega \subset \C$, $N=200$.
-                \STATE Pick $N$ clockwise points $z_1, z_2, \cdots, z_N$ from $\partial \Omega$ uniformly.
-                \STATE Input $z_1, z_2, \cdots, z_N$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_1}: \D \rightarrow \Omega$ and $p_{i,1} \in \partial\D$.
-                \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$. %and 
-                \STATE Input $z_N, \cdots, z_2, z_1$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_2}: \D \rightarrow \Omega^c$ and $p_{i,2} \in \partial\D$.
-                \STATE Let $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-                \STATE Let $f = \Phi_1^{-1} \circ \Phi_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
-                \STATE Extend $f$ to $H$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
-                \STATE Input $\Phi_1$ and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get $F_{\Phi_1}$.
-                \STATE Input $\Phi_2$ and $p_{i,2}$ to Algorithm \ref{alg norm phi2}, then get $M_{\Phi_2}$.
-                \STATE Calculate normalized harmonic extension $\hat{H} = F_{\Phi_1} \circ H \circ M_{\Phi_2}$.
-                \STATE Calculate Beltrami coefficient $B$ of $\hat{H}$.
-                \RETURN Beltrami signature $B$.
-            \end{algorithmic}
-            \end{algorithm}
-    \section{Experimental result}\label{result}
-        In this section, we will validate key properties of our proposed Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
-Besides that, a good shape representation should keep the similarity with the same kind shape and is significantly different from different kinds of shape.
-
-        Before showing results, what needs illustration is that the distance we used to measure the difference of Beltrami signature is based on $L^2$ norm,
-        \begin{equation}\label{bs dis}
-            d(B_1, B_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{B_1(z_i) - B_2(z_i)}^2},
-        \end{equation}
-        where $B_1, B_2$ are two different Beltrami signature, $z_i \in \D$ is the face center of triangluar mesh $M$ metioned in Section \ref{detail harmonic} and $N=60962$ here.
-        \subsection{Invariance}\label{sec inv}
-            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate Beltrami signature after sacling, translation and rotation and compare them with the original shape's Beltrami signature.
-The result is displayed in Fig \ref{inv}.
-In this figure, the first column are the sets of boundary points and we remark them as $\Omega_a$ to $\Omega_f$.
-The second column are the corresponding Beltrami signatures $B_a$ to $B_f$.
-Note that all the Beltrami signatures are shown in modulus, i.e.
-$\abs{B_n}$ for row $n$, and in top view.
-And the third column(if have) are the histograms of the difference between original shape's Beltrami signature, i.e.
-$\abs{B_n - B_a}$ for row $n$.
-
-            Row b and c are about scaling, the shapes are $\Omega_b = \{z \mid z = 1.5 z_a, z_a \in \Omega_a \}$ and $\Omega_c = \{z \mid z = 0.5 z_a, z_a \in \Omega_a \}$ and the distance are $d(B_a, B_b) = 5.5647 \times 10^{-8}$ and $d(B_a, B_c) = 5.3476 \times 10^{-8}$.
-Row d is about translation, the shape $\Omega_d = \{z \mid z = z_a+100+20i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_d) = 4.7817 \times 10^{-8}$.
-Row e is about rotation, the shape is $\Omega_e = \{z \mid z = e^{0.2\pi i} z_a, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.2144 \times 10^{-8}$.
-Row f is the combination of scaling, tanslation and rotation, the shape is $\Omega_e = \{z \mid z = 3e^{-0.85\pi i} z_a+350+600i, z_a \in \Omega_a \}$ and the distance is $d(B_a, B_e) = 5.7635 \times 10^{-8}$.
-These confirm the invariance of Beltrami signature and scaling, translation and rotation.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/inv.png}
-                \end{center}
-                \caption{Beltrami signature under scaling, translation and rotation.}
-                \label{inv}
-            \end{figure*}
-
-        \subsection{Robustness}
-            Similar with Section \ref{sec inv}, here we still treat the dolphin as the original shape and modify some small parts of it and Fig \ref{robust} is the result.
-It shows that the proposed signature is robust and stable and will not have a big mutation cauesd by small disturbance.
-
-            Row g, h and i are result about modification.
-These shapes are generated by removing or adding something, which is in the red circle.
-We can see that Beltrami signatures have slight differences from $B_a$ but are still similar in general.
-And this figure also demonstrates that the bigger the modification part is, the more different the Beltrami signature is.
-For example in row i, losing a half of the tail makes the signature has a marked change.
-Quantitatively, $d(B_a, B_g) = 0.0132$, $d(B_a, B_h) = 0.0316$ and $d(B_a, B_i) = 0.1761$.
-
-            Row j is for distortion. This dolphin is only enlarged in horizontally and becomes fatter, then the $B_j$ moves a little bit and $d(B_a, B_j) = 0.0724$.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/robust.png}
-                \end{center}
-                \caption{Beltrami signature under small modification}
-                \label{robust}
-            \end{figure*}
-
-        \subsection{Classification with Beltrami signature}
-            Above properties ensure the proposed signature having the ablity to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.
-
-            To compare the classification performance, we also use conformal welding directly to classify, and the distance is defined as
-            \begin{equation}\label{welding dis}
-                d_c(f_1, f_2) = \sqrt{\frac{1}{N} \sum_{i=1}^N \abs{f_1(z_i) - f_2(z_i)}^2},
-            \end{equation}
-            where $f_1, f_2$ are two different conformal welding, $N=200$ here.
-
-            We prepare 3 kinds of animals, fish, giraffe and elephant.
-There are 3 images for each group so 9 images in total.
-From Fig \ref{classification images}, we can find that each class share similar Beltrami signatures and conformal welding.
-From Fig \ref{dis matrix}, the inter-class distance of Beltrami signature is awlays less than 0.2 while the intra-class distance is greater than 0.2.
-But for conformal welding, the data is messy, for example, fish 3 thinks itself is very different from other fishes but looks most like giraffe 2.
-After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the Beltrami signature shows powerful classification ablity.
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/figs.png}
-                \end{center}
-                \caption{These 3 rows are elephant, fish and giraffe. In each subfigure, the top left is the input shape, bottom left is the conformal welding and the right is Beltrami signature.}
-                \label{classification images}
-            \end{figure*}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/distance_down.png}
-                \end{center}
-                \caption{(a) The distance matrix of Beltrami signatures of above 9 shapes by equation (\ref{bs dis}). (b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
-                \label{dis matrix}
-            \end{figure}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/mds_down.png}
-                \end{center}
-                \caption{(a) The MDS result of Beltrami signature. (b) The MDS result of conformal welding.}
-                \label{mds1}
-            \end{figure}
-
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/mds2.png}
-                \end{center}
-                \caption{(a) The MDS result of Beltrami signature.
-(b) The MDS result of conformal welding.
-(c) The clustering result of Beltrami signature.
-(d) The clustering results of conformal welding.}
-                \label{mds2}
-            \end{figure*}
-
-        \subsection{Classification for more classes}
-            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabit.
-We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes.
-The MDS and clustering results based on Beltrami signature and conformal welding are displayed in Fig \ref{mds2}.
-The classification accuracy based on Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
-
-    \section{Conclusion}\label{conclusion}
-        In this paper, we propose a novel shape representation for 2D bounded simple connected objects called Beltrami signature.
-The proposed signature is based on conformal welding but overcome a key shortcoming that it can be uniquely determined by the given shape.
-What's more exciting is that the proposed representation is invariance under scaling, translation and rotation.
-For slight deformation and distortion, Beltrami signature keeps roubost and only changes within a reasonable small range.
-Therefore, there are reasons to believe the it does have ablity to represent some invariant geometrical features.
-The experimental results also confirm that the Beltrami signature has excellent performance in multi-classification tasks.
-
-        Although our work has achieved relatively good results, the proposed representation still have some limitations.
-Firstly, the Beltrami signature is only applicable to simple connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world.
-So we are eager for a feasible method to extend our Beltrami signature to multi connected situation.
-Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangluar mesh, which consumes a lot of time.
-Therefore, a fast algorithm to obatin this signature avoiding dense mesh is of high priority in our future work.
-Thirdly, when normalizing the conformal mapping $\Phi_2$ from exterior of unit disk to exterior of the domain, the position where the derivation of $\Phi_2$ reaches the maximum value is used to adjust the rotation.
-We trust this point in the original image has a certain geometric meaning, whereas it is not clear at present.
-
-        In summary, we will focus on third marjor directions in the future.
-One is that the deeper meaning of Beltrami signature is worth digging and then a multi-connected version of representation based on this work can be proposed.
-Another is that if the Beltrami signature contains some geometrical features of shapes, we can also extract them directly from images and generate the Beltrami signature again.
-Hence the deep learning theory may help us to compute this signature from given images immediately, which is very likely to improve algorithm speed performance greatly.
-A third direction is this representation can be used in more applications like segementation, registration and so on.
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
-% \section*{Conflict of interest}
-%
-% The authors declare that they have no conflict of interest.
-
-% BibTeX users please use one of
-% \bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
-\bibliography{cite}
-% Non-BibTeX users please use
-% \begin{thebibliography}{}
-% %
-% % and use \bibitem to create references. Consult the Instructions
-% % for authors for reference list style.
-% %
-% \bibitem{RefJ}
-% % Format for Journal Reference
-% Author, Article title, Journal, Volume, page numbers (year)
-% % Format for books
-% \bibitem{RefB}
-% Author, Book title, page numbers. Publisher, place (year)
-% % etc
-% \end{thebibliography}
-
-\end{document}
-% end of file template.tex
+    The thesis is organized as follows: Chapter \ref{related work} reviews some related topics about shape representation; Chapter \ref{background} introduces some theoretic background; Chapter \ref{main} shows the main theorem about how the unique Harmonic Beltrami signature is obtained from given domain and shows the method to reconstruct the original shape from given HBS; Chapter \ref{implementation} gives the details about the implementation; Chapter \ref{result} reports our experimental results.
+The thesis is concluded in Chapter \ref{conclusion} and we point out future directions.

### 2021-06-11 paper.tex
final thesis

@@
   There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simply-connected domains in this paper, named the Harmonic Beltrami signature.
-The proposed signature is based on the extension of the conformal welding map of a unit circle $S^1$ to a harmonic function of a unit disk $\D$.
-With suitable normalization, the uniqueness of this harmonic function is guaranteed up to a rotation.
+The proposed signature is based on the harmonic extension of the conformal welding map of a unit circle.
+With suitable normalization, the uniqueness of this harmonic function is guaranteed up to rotations.
 And finally quasi-conformal theory helps get rid of the only uncertainty by computing the Beltrami coefficient of harmonic extension.
+There exists one-by-one relationship between shapes and our Harmonic Beltrami signatures and we also give the method to reconstruct the original shapes from our signatures.
 The benifit of the proposed signature is that it keeps to be invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformations and distortions.
@@
 First is that such representation is not unique.
-Because of the arbitrary of Riemann conformal mapping, $\Phi_1$ and $\Phi_2$ can only be determined up to a Mobious transformation, so such conformal welding is not unique.
+Because of the arbitrary of Riemann conformal mapping, $\Phi_1$ and $\Phi_2$ can only be determined up to a Mobi\"us transformation, so such conformal welding is not unique.
 Generally speaking, some assumption is required to remove this uncertainty.
@@
         \begin{center}
-        \includegraphics[width=7.6cm]{src/fig1_down.png}
-        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simply-connected domain $\Omega$. (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
+        \includegraphics[width=7.6cm]{fig1_down.png}
+        \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simply-connected domain $\Omega$; (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
         \end{center}
@@
         %     \begin{center}
-        %         \includegraphics[width=7.6cm]{src/fig2.jpg}
+        %         \includegraphics[width=7.6cm]{fig2.jpg}
         %     \end{center}
-        %     \caption{(a) Shows the original hippocampus.
-(b) Shows the parameter domain with circle packing pattern.
+        %     \caption{(a) Shows the original hippocampus; (b) Shows the parameter domain with circle packing pattern.
 Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
@@
             \begin{center}
-                \includegraphics[width=7.6cm]{src/fig3.png}
+                \includegraphics[width=7.6cm]{fig3.png}
             \end{center}
@@
             Suppose $\mu : \C \rightarrow \C$ is Lebesgue measurable satisfying $\abs{\mu}_\infty <1$; then, there exists a quasi-conformal homeomorphism $f$ from $\C$ onto itself, which is in the Sobolev space $W_{1,2}(\C)$ and satisfies the Beltrami equation in the distribution sense.
-The associated quasi-conformal homeomorphism $f$ is unique up to a Mobious transformation.
+The associated quasi-conformal homeomorphism $f$ is unique up to a Mobi\"us transformation.
 Furthermore, by fixing $0$, $1$ and $\infty$, the $f$ is uniquely determined.
@@
         Given 2D bounded simply-connected shape, we can treat it as a boundary simply-connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
-$\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobious transformation}:
+$\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobi\"us transformation}:
         \begin{equation}
@@
             \begin{center}
-                \includegraphics[width=7.6cm]{src/unstable welding.png}
+                \includegraphics[width=7.6cm]{unstable_welding.png}
             \end{center}
@@
             \begin{center}
-                \includegraphics[width=7.6cm]{src/fig4_down.png}
-            \end{center}
-            \caption{(a) Continuous function $f(e^{i \theta}) = \sin(100 \theta) + \cos(100 \theta)$ defined on $\partial \D$.
-(b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
+                \includegraphics[width=7.6cm]{fig4_down.png}
+            \end{center}
+            \caption{(a) Continuous function $f(e^{i \theta}) = \sin(10 \theta) + \cos(10 \theta)$ defined on $\partial \D$; (b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
 Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
@@
 
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig5.png}
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=\textwidth]{fig5.png}
                 \end{center}
                 \caption{Illustration of Harmonic Beltrami signature.
-(a) The input shape, a dolphin.
-(b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b).
-(c) The Harmonic Beltrami signature of (a).
+(a) The input shape, a dolphin; (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b); (c) The Harmonic Beltrami signature of (a).
 Remark that the harmonic function and Harmonic Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
                 \label{illu of BS}
-            \end{figure*}
+            \end{figure}
 
@@
             According to Riemann mapping theorem, the conformal mappings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
-Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobious transformations.
+Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobi\"us transformations.
 Therefore, the corresponding conformal welding is
@@
             \begin{theorem}
-                Suppose $f$ and $\tilde{f}$ are continuous map from $\mathbb{S}^1$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
+                Suppose $f$ and $\tilde{f}$ are continuous map from $\mathbb{S}^1$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobi\"us transformations.
 $H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
@@
             \begin{proof}
-                Since $M_1$ is a Mobious transformations, $M_1^{-1}$ is also a Mobious transformation, so it can be written as $M_1^{-1}(z) = e^{i \theta}\frac{z - p}{1 - \overline{p}z}$, where $\theta \in [0, 2\pi)$ and $p \in \D$.
-
-                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
+                Since $M_1$ is a Mobi\"us transformations, $M_1^{-1}$ is also a Mobi\"us transformation, so it can be written as $M_1^{-1}(z) = e^{i \theta}\frac{z - p}{1 - \overline{p}z}$, where $\theta \in [0, 2\pi)$ and $p \in \D$.
+
+                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobi\"us transformation $M_2$ is conformal.
 $\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
@@
             Before proving theorem \ref{unique up to a rotation}, we can consider following problem.
-Given boundary points $p_i$ on unit circle, can we find a Mobious transformation $M$ satisfies the following equation (\ref{fz})?
+Given boundary points $p_i$ on unit circle, can we find a Mobi\"us transformation $M$ satisfies the following equation (\ref{fz})?
             \begin{equation}\label{fz}
@@
             Without lose of generality, we ignore the rotation of $M$ and let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-So $F_a$ is also a Mobius transformation and it's sufficient to find $a \in \D$ such that
+So $F_a$ is also a Mobi\"us transformation and it's sufficient to find $a \in \D$ such that
             \begin{equation}\label{eq}
@@
 
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig6.png}
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=\textwidth]{fig6.png}
                 \end{center}
@@
                 \label{fasolvable}
-            \end{figure*}
+            \end{figure}
 
@@
             \begin{proof}
-                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobious transformation.
+                Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobi\"us transformation.
 If $\Phi_1$, $\tilde{\Phi_1} $ satisfy equation (\ref{norm phi1}), let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M_1^{-1} (p_k) = 0$.
-$M_1^{-1}$ is also a Mobious transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
+$M_1^{-1}$ is also a Mobi\"us transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
                 \begin{equation*}
@@
             \begin{proof}
-                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobious transformation, $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$.
+                Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobi\"us transformation, $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$.
 Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisfy (\ref{norm phi2 1}), then
@@
         \end{align}
-        where $G$ is uniquely determined up to Mobious transformation $M$.
+        where $G$ is uniquely determined up to Mobi\"us transformation $M$.
 
@@
         \end{equation}
-        By the properties of Mobious transformation, we have $M(z) = az+b$ where $a, b \in \C$.
+        By the properties of Mobi\"us transformation, we have $M(z) = az+b$ where $a, b \in \C$.
 
@@
                 \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig7_down.png}
-                \end{center}
-                \caption{(a) The $p_i \in \partial \D$ gather in a small neighborhood around their arithmetic mean $p_c$, which is labeled in red.
-(b) The corresponding $\abs{f(a)}$ for these $p_i$.
+                    \includegraphics[width=7.6cm]{fig7_down.png}
+                \end{center}
+                \caption{(a) The $p_i \in \partial \D$ gather in a small neighborhood around their arithmetic mean $p_c$, which is labeled in red; (b) The corresponding $\abs{f(a)}$ for these $p_i$.
 It's worth to mention that the minimal of $\abs{f(a)}$ can reach actually, but it isn't shown in the picture since the grid is not small enough.}
@@
                 \begin{center}
-                    \includegraphics[width=7.6cm]{src/fig8_down.png}
-                \end{center}
-                \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment. (b) The $\abs{f(a)}$.}
-            \end{figure}
-
-            Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobious transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
+                    \includegraphics[width=7.6cm]{fig8_down.png}
+                \end{center}
+                \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment; (b) The $\abs{f(a)}$.}
+            \end{figure}
+
+            Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobi\"us transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
 For the $r$-th iteration, let
@@
             as the arithmetic center of $p_{i,r} \in \partial \D$.
-Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobious transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
+Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobi\"us transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
             \begin{equation*}
@@
                 %\STATE Compute $p_i = F_a(p_{i,r})$.
-                \RETURN Mobious transformation $M_{\Phi_1}$.%, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
+                \RETURN Mobi\"us transformation $M_{\Phi_1}$.%, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
             \end{algorithmic}
@@
 
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/fig9.png}
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=\textwidth]{fig9.png}
                 \end{center}
                 \caption{The iteration of distribution adjustment. The boundary points are blue and their arithmetic center is red in each picture. (a)-(d) The 1st, 3rd, 7th, 12th iteration.}
-            \end{figure*}
+            \end{figure}
 
@@
                 \STATE Let $F_c(z) = \frac{z-c}{1-\overline{c}z}$ and $M_{\Phi_2} = F_{c}$.
-                \RETURN Mobious transformation $M_{\Phi_2}$
+                \RETURN Mobi\"us transformation $M_{\Phi_2}$
                 % \RETURN Conformal mapping $\hat{\Phi}_2: \D^c \rightarrow \Omega^c$ satisfied (\ref{norm phi2 1}), (\ref{norm phi2 2}) and boundary points $p_i \in \partial \D$.
@@
 
-            After obtaining Mobious transformations $M_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
+            After obtaining Mobi\"us transformations $M_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
             \begin{align*}
@@
 
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/inv.png}
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=10.5cm]{inv.png}
                 \end{center}
@@
                 \label{inv}
-            \end{figure*}
+            \end{figure}
 
@@
 
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=10.5cm]{src/robust.png}
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=10.5cm]{robust.png}
                 \end{center}
@@
                 \label{robust}
-            \end{figure*}
+            \end{figure}
 
@@
 
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/figs.png}
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=\textwidth]{figs.png}
                 \end{center}
@@
                 \label{classification images}
-            \end{figure*}
-
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=7.6cm]{src/distance_down.png}
-                \end{center}
-                \caption{(a) The distance matrix of Harmonic Beltrami signatures of above 9 shapes by equation (\ref{bs dis}).
-(b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
+            \end{figure}
+
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=7.6cm]{distance_down.png}
+                \end{center}
+                \caption{(a) The distance matrix of Harmonic Beltrami signatures of above 9 shapes by equation (\ref{bs dis}); (b) The distance matrix of conformal weldings by equation (\ref{welding dis}).}
                 \label{dis matrix}
@@
                 \begin{center}
-                    \includegraphics[width=7.6cm]{src/mds_down.png}
-                \end{center}
-                \caption{(a) The MDS result of Harmonic Beltrami signature. (b) The MDS result of conformal welding.}
+                    \includegraphics[width=7.6cm]{mds_down.png}
+                \end{center}
+                \caption{(a) The MDS result of Harmonic Beltrami signature; (b) The MDS result of conformal welding.}
                 \label{mds1}
@@
 
-            \begin{figure*}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{src/mds2.png}
-                \end{center}
-                \caption{(a) The MDS result of Harmonic Beltrami signature.
-(b) The MDS result of conformal welding.
-(c) The clustering result of Harmonic Beltrami signature.
-(d) The clustering results of conformal welding.}
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=\textwidth]{mds2.png}
+                \end{center}
+                \caption{(a) The MDS result of Harmonic Beltrami signature; (b) The MDS result of conformal welding; (c) The clustering result of Harmonic Beltrami signature; (d) The clustering results of conformal welding.}
                 \label{mds2}
-            \end{figure*}
+            \end{figure}
 

### 2021-06-15 paper.tex
thesis

@@
 \date{Received: date / Accepted: date}
+\graphicspath{ {./src/} }
+
 % The correct dates will be entered by the editor
@@
 
-    The paper is organized as follows: Section \ref{related work} reviews some related topics about shape representation; Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem and how Harmonic Beltrami signature is obtained from given domain; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
+    The paper is organized as follows: Section \ref{related work} reviews some related topics about shape representation; Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem about how the unique Harmonic Beltrami signature is obtained from given domain and shows the method to reconstruct the original shape from given HBS; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
 The paper is concluded in Section \ref{conclusion} and we point out future directions.
@@
 \section{Harmonic Beltrami signature (HBS)}\label{main}
-        In this section, we describe our proposed shape signature, called the {\it Harmonic Beltrami signature (HBS)}, to represent a simply-connected domain $\Omega$.
+In this chapter, we describe our proposed shape signature, called the {\it Harmonic Beltrami signature (HBS)}, to represent a simply-connected domain $\Omega$.
 The space of HBS inherits a natural metric, so that geometric distance between two shapes can be easily measured.
-In the following subsection, the definition of HBS and some of its theoretical analysis are addressed.
+In the following sections, the definition of HBS and some of its theoretical analysis are addressed.
 
@@
 Suppose $\Omega$ is a quasicircle, which is the image of the unit disk under a quasiconformal map.
-Let $f = \Phi_1^{-1} \circ \Phi_2$ be the conformal welding of $\Omega$, where  $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are the conformal mappings as described in Section \ref{welding}.
-Denote the harmonic extension of $f$ by $H:\mathbb{D}\to \mathbb{D}$.
+Let $f = \Phi_1^{-1} \circ \Phi_2$ be the conformal welding of $\Omega$, where  $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are the conformal mappings.
+Denote the harmonic extension of $f$ as $H:\mathbb{D}\to \mathbb{D}$ by equation (\ref{poisson integral}).
 
@@
         \caption{Illustration of Harmonic Beltrami signature.
-(a) The input shape, a dolphin; (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b); (c) The Harmonic Beltrami signature of (a).
+(a) The input shape, a dolphin; (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{ill of cw} (b); (c) The Harmonic Beltrami signature of (a).
 Remark that the harmonic function and Harmonic Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
@@
 
-            According to Riemann mapping theorem, the conformal mappings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
-Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobi\"us transformations.
-Therefore, the corresponding conformal welding is
-            \begin{equation}
-                \tilde{f} = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 = M_1^{-1} \circ \Phi_1^{-1} \circ \Phi_2 \circ M_2 = M_1^{-1} \circ f \circ M_2.
-            \end{equation}
-
-            With equation (\ref{poisson integral}), it can be also extended to harmonic function $\tilde{H}$. The following theorem show the relationship between $H$ and $\tilde{H}$.
+    Let $f$ and $\tilde{f}$ be two different conformal welding of the same domain $\Omega$ and they satisfy equation (\ref{tilde f}).
+Their harmonic extension are $H$ and $\tilde{H}$ respectively.
+As we mentioned in last section, the conformal ambiguity of $M_1$ and $M_2$ is the biggest challenge in the way to unique representative, but we still hope $\tilde{H}$ to reserve such relationship, i.e.
+    \begin{equation}\label{tilde H}
+        \tilde{H} = M_1^{-1} \circ H \circ M_2,
+    \end{equation}
+    for the convenience of subsequent discussion. The following theorem tells us it can be achieved when restricting $M_1$:
 
@@
     \end{equation}
-            If we want to find a unique $B$, it means $\tilde{B} = \mu_{H \circ M_2} = \mu_{H} = B$, hence some pre- and post-normalizations are required.
+    This equation tells us the uniqueness of $B$ can be achieved by following theorem.
+    \begin{theorem}\label{unique B}
+        Suppose $B = \mu_H$ and $\tilde{B} = \mu_{\tilde{H}}$ are two Harmonic Beltrami signatures in given equivalence class $[B]$ for some domain $\Omega$, where $H$ and $\tilde{H}$ are the corresponding harmonic extensions of conformal welding $f$ and $\tilde{f}$ respectively with $\tilde{f} = M_1^{-1} \circ f \circ M_2$.
+If $M_1$ and $M_2$ are both rotation and
+        \begin{equation}\label{arg integral B is 0}
+            \arg \int_\D B(z) dz = \arg \int_\D \tilde{B}(z)dz = 0,
+        \end{equation}
+        then we have $\tilde{B} = B$.
+    \end{theorem}
+
+    \begin{proof}
+        When $M_1$ is rotation, the conformal arbitrary of conformal welding can be delivered to their harmonic extensions and
+        $\tilde{H} = M_1^{-1} \circ H \circ M_2$. Remark $r e^{i \tau} = \int_\D B(z) dz$ and $M_2(z) = e^{i \theta}z$, then the $\tilde{B}$ can be displayed in the form of
+        \begin{equation}
+        \tilde{B}(z) = \mu_{H \circ M_2}(z) = e^{-2i\theta} \mu_H \circ M_2(z) = e^{-2 i \theta} B(e^{i\theta} z).
+        \end{equation}
+        Therefore, we have
+        \begin{eqnarray}
+            \int_B \tilde{B}(z) dz
+            &=& \int_D e^{-2i\theta} B(e^{i\theta} z) dz \nonumber \\
+            &=& e^{-2i\theta} \int_D B(z) dz \nonumber \\
+            &=& r e^{i(\tau-2\theta)}.
+        \end{eqnarray}
+        If equation (\ref{arg integral B is 0}) holds,
+        \begin{equation*}
+            \tau = \tau-2\theta  = 0,
+        \end{equation*}
+        hence $\theta = 0$, $M_2$ is identity and so $\tilde{B} = \mu_H = B$.
+    \end{proof}
+
+    Note that the unique representative $B$ of $[B]$ can be easily generated from any HBS $B_0 = \mu_{H_0} \in [B]$. If $r e^{i\tau_0} =\int_\D B_0(z) dz$ and $\tau_0 \neq 0$, then
+    \begin{equation}\label{normaled B}
+        B(z) = e^{-i\tau_0}B_0(e^{i\frac{\tau_0}{2}}z)
+    \end{equation}
+    is just the desired representative since $B = \mu_{H_0 \circ M_0}$  and
+    \begin{equation}
+        \arg \int_\D B(z) dz = \arg \left( e^{-i\tau_0} \int_\D B_0(e^{i\frac{\tau_0}{2}}z)dz \right) = \arg \left( e^{-i\tau_0} \cdot r e^{i\tau_0} \right) = 0,
+    \end{equation}
+    where $M_0(z) = e^{i \frac{\tau}{2}} z$. Therefore, if we want to find a unique $B$, some pre- and post-normalizations to $M_1$ and $M_2$ are required.
 
@@
         \begin{center}
-                    \includegraphics[width=\textwidth]{fig6.png}
+            \includegraphics[width=10cm]{fig6.png}
         \end{center}
@@
 
-        \subsection{Post-normalization for $B$}\label{post norm B}
-            After normalizing $M_1$ and $M_2$, where $M_1, M_2$ are both rotation, for $B, \tilde{B} \in [B]$ with harmonic extensions $H, \tilde{H}$, according to equations (\ref{mu of conformal composition}) and (\ref{tildeB}), we have
-            \begin{equation}\label{arg integral B is 0}
-                \tilde{B}(z) = \mu_{H \circ M_2}(z) = e^{-2i\theta} \mu_H \circ M_2(z) = e^{-2 i \theta} B(e^{i\theta} z),
-            \end{equation}
-            where $M_2(z) = e^{i \theta}z$. This equation tells us the uniqueness of $B$ can be achieved by following theorem.
-            \begin{theorem}\label{unique B}
-                Suppose $B$ is HBS in given equivalence class $[B]$ and satisfies requirements (\ref{norm phi1}) and (\ref{norm phi2 1}). If
-                \begin{equation}
-                    \arg \int_\D B(z) dz = 0,
-                \end{equation}
-                then $B$ is unique representative of $[B]$.
-            \end{theorem}
-
-            \begin{proof}
-                Suppose $B, \tilde{B}$ are both HBS in the same equivalence class $[B]$ with harmonic extensions $H$ and $\tilde{H}$ respectively, where $\tilde{H} = M_1^{-1} \circ H \circ M_2$ and $\int_D B(z)dz = r e^{i \tau}$.
-According to requirements (\ref{norm phi1}) and (\ref{norm phi2 1}), $M_1, M_2$ are rotation.
-Let $M_2(z) = e^{i\theta}z$, then we have
-                \begin{eqnarray}
-                    \int_B \tilde{B}(z) dz
-                    &=& \int_D e^{-2i\theta} B(e^{i\theta} z) dz \nonumber \\
-                    &=& e^{-2i\theta} \int_D B(z) dz \nonumber \\
-                    &=& r e^{i(\tau-2\theta)}.
-                \end{eqnarray}
-                If equation (\ref{arg integral B is 0}) holds,
-                \begin{equation*}
-                    \tau = \tau-2\theta  = 0,
-                \end{equation*}
-                hence $\theta = 0$, $M_2$ is identity and so$\tilde{B} = \mu_{H \circ I} = \mu_H = B$.
-            \end{proof}
-
-            Note that the unique representative $B$ of $[B]$ can be easily generated from any HBS $B_0 \in [B]$. If $\tau_0 =\arg \int_\D \tilde{B}(z) dz  \neq 0$, then
-            \begin{equation}\label{normaled B}
-                B(z) = e^{i\tau_0}B_0(e^{-\frac{\tau_0}{2}i}z)
-            \end{equation}
-            is just the desired representative.
-
 \subsection{Invariance under simple transformation}
@@
 
-    \section{Reconstruction}\label{reconstruction}
-
+\subsection{Reconstruction}\label{reconstruction}
     The above theorems show that our Harmonic Beltrami signature can be uniquely defined by the given shape and is invariant under translation, scaling and rotation.
@@
 
-        Hence, following powerful theorem about Beltrami holomorphic flow tells that if two HBS are similar, their corresponding shapes must be very alike.
+\subsection{Robustness of HBS}
+    Although there exists a one-to-one correspondence between HBS and shapes up to a rotation, translation and scaling, the behavior of HBS under small modification to the original shape is still unknown.
+Of course, we expect the HBS to be slightly deformed within reasonable range so that the proposed signature is robust and useful.
+The following powerful theorem about Beltrami holomorphic flow(BHF) tells that if two HBS are similar, their corresponding shapes must be very alike.
 
@@
 $z_N, z_{N-1}, \cdots, z_1$, the zipper will give us a conformal mapping from $\Omega^c$ to $\D$.
+This progress is shown in Fig.
+\ref{zipper algo}.
+
+    \begin{figure}
+    \begin{center}
+        \includegraphics[width=15cm]{zipper_algo.png}
+    \end{center}
+    \caption{Zipper algorithm}
+    \label{zipper algo}
+    \end{figure}
 
@@
         \begin{center}
-                    \includegraphics[width=7.6cm]{fig7_down.png}
+            \includegraphics[width=6cm]{fig7.png}
         \end{center}
@@
         \begin{center}
-                    \includegraphics[width=7.6cm]{fig8_down.png}
+            \includegraphics[width=6cm]{fig8.png}
         \end{center}
@@
         \begin{center}
-                    \includegraphics[width=\textwidth]{fig9.png}
+            \includegraphics[width=10cm]{fig9.png}
         \end{center}
@@
     \end{algorithm}
+
     \section{Experimental result}\label{result}

### 2021-06-15 elsarticle-template.tex
pattern recongnition

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Pattern Recognition}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

%% Group authors per affiliation:
\author{Elsevier\fnref{myfootnote}}
\address{Radarweg 29, Amsterdam}
\fntext[myfootnote]{Since 1880.}

%% or include affiliations in footnotes:
\author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
\ead[url]{www.elsevier.com}

\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{support@elsevier.com}

\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
\address[mysecondaryaddress]{360 Park Avenue South, New York}

\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.
\end{abstract}

\begin{keyword}
\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
\MSC[2010] 00-01\sep  99-00
\end{keyword}

\end{frontmatter}

\linenumbers

\section{The Elsevier article class}

\paragraph{Installation} If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.

\paragraph{Usage} Once the package is properly installed, you can use the document class \emph{elsarticle} to create a manuscript. Please make sure that your manuscript follows the guidelines in the Guide for Authors of the relevant journal. It is not necessary to typeset your manuscript in exactly the same way as an article, unless you are submitting to a camera-ready copy (CRC) journal.

\paragraph{Functionality} The Elsevier article class is based on the standard article class and supports almost all of the functionality of that class. In addition, it features commands and options to format the
\begin{itemize}
\item document style
\item baselineskip
\item front matter
\item keywords and MSC codes
\item theorems, definitions and proofs
\item lables of enumerations
\item citation style and labeling.
\end{itemize}

\section{Front matter}

The author names and affiliations could be formatted in two ways:
\begin{enumerate}[(1)]
\item Group the authors per affiliation.
\item Use footnotes to indicate the affiliations.
\end{enumerate}
See the front matter of this document for examples. You are recommended to conform your choice to the journal you are submitting to.

\section{Bibliography styles}

There are various bibliography styles available. You can select the style of your choice in the preamble of this document. These styles are Elsevier styles based on standard styles like Harvard and Vancouver. Please use Bib\TeX\ to generate your bibliography and include DOIs whenever available.

Here are two sample references: \cite{Feynman1963118,Dirac1953888}.

\section*{References}

\bibliography{mybibfile}

\end{document}

### 2021-06-15 paper.tex
pattern recongnition

@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-% \smartqed  % flush right qed marks, e.g. at end of proof
-%
-% \let\equation\relax
-% \let\endequation\relax
-\let\proof\relax
-\let\endproof\relax
-\let\example\relax
-\let\endexample\relax
+\documentclass[review]{elsarticle}
 
 \usepackage{graphicx}
-\usepackage[margin=1in]{geometry} 
+% \usepackage{geometry}
 \usepackage{amsmath}
 \usepackage{amsthm}
+\usepackage{lineno}
 \usepackage{amssymb}
-\usepackage{hyperref}
+% \usepackage{hyperref}
 \usepackage{algorithm}
@@
 %
+\modulolinenumbers[5]
+
+\journal{Pattern Recognition}
 % \usepackage{mathptmx}      % use Times fonts if available on your TeX system
@@
 %
+\newtheorem{theorem}{Theorem}
+% \newtheorem{lem}[thm]{Lemma}
+% \newdefinition{rmk}{Remark}
+% \newproof{proof}{Proof}
+\newdefinition{definition}{Definition}
+\graphicspath{ {./src/} }
+% \linespread{2.0}
 \begin{document}
-
+\begin{frontmatter}
 \title{Harmonic Beltrami Signature: A Novel Invariant 2D Shape Representation for Object Classification}
-% \subtitle{Do you have a subtitle?\\ If so, write it here}
-
-%\titlerunning{Short form of title}        % if too long for running head
-
-\author{Chenran Lin \and Lok Ming Lui}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{Chenran Lin \at
-              Department of Mathematics, The Chinese University of Hong Kong \\
-              \email{crlin@math.cuhk.edu.hk}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           Lok Ming Lui \at
-              Department of Mathematics, The Chinese University of Hong Kong\\
-              \email{lmlui@math.cuhk.edu.hk}           %  \\
-}
-
-\date{Received: date / Accepted: date}
-\graphicspath{ {./src/} }
-
-% The correct dates will be entered by the editor
-
-\maketitle
+\author[1]{Chenran Lin\corref{cor1}}
+\ead{crlin@math.cuhk.edu.hk}
+\address[1]{Department of Mathematics, The Chinese University of Hong Kong, Shatin, Hong Kong}
+\cortext[cor1]{Corresponding author}
+
+\author[1]{Lok Ming Lui}
+\ead{lmlui@math.cuhk.edu.hk}
+% \address[2]{Department of Mathematics, The Chinese University of Hong Kong}
 
@@
 Experiments demonstrate the above properties and also show the excellent classification performance.
-\keywords{
-  Shape representation \and conformal welding \and simply-connected \and invariance}
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
 \end{abstract}
+
+\begin{keyword}
+  Shape representation \sep conformal welding \sep simply-connected \sep invariance
+\end{keyword}
+\end{frontmatter}
+
+\linenumbers
 
@@
         \begin{center}
-        \includegraphics[width=7.6cm]{fig1_down.png}
+        \includegraphics[width=11cm]{fig1.png}
         \caption{(a) The Illustration of how conformal welding $f$ is defined from given 2D simply-connected domain $\Omega$; (b) The image of conformal welding $f: [0, 2\pi) \rightarrow [0, 2\pi)$}
@@
 
-        % \begin{figure}
-        %     \begin{center}
-        %         \includegraphics[width=7.6cm]{fig2.jpg}
-        %     \end{center}
-        %     \caption{(a) Shows the original hippocampus; (b) Shows the parameter domain with circle packing pattern.
-Under the quasiconformal parameterization, the infinitesimal circles on the parameter domain are mapped to infinitesimal ellipses on the hippocampus, as shown in (c).}
-        %     \label{fig2}
-        % \end{figure}
-
         If $\mu(z)=0$ everywhere, then $f$ us called \textit{conformal} or \textit{holomorphic}. A conformal map satisfies the following well-known Cauchy-Riemann equation:
@@
             \begin{center}
-                \includegraphics[width=7.6cm]{unstable_welding.png}
+                \includegraphics[width=8cm]{unstable_welding.png}
             \end{center}
@@
             \begin{center}
-                \includegraphics[width=7.6cm]{fig4_down.png}
+                \includegraphics[width=12cm]{fig4.png}
             \end{center}
@@
         \begin{center}
-            \includegraphics[width=\textwidth]{fig5.png}
+            \includegraphics[width=13cm]{fig5.png}
         \end{center}
         \caption{Illustration of Harmonic Beltrami signature.
-(a) The input shape, a dolphin; (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{ill of cw} (b); (c) The Harmonic Beltrami signature of (a).
+(a) The input shape, a dolphin; (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b); (c) The Harmonic Beltrami signature of (a).
 Remark that the harmonic function and Harmonic Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
@@
         \begin{center}
-            \includegraphics[width=15cm]{harmonic_extension_not_rotation.png}
+            \includegraphics[width=11cm]{harmonic_extension_not_rotation.png}
         \end{center}
@@
     \begin{center}
-        \includegraphics[width=15cm]{zipper_algo.png}
+        \includegraphics[width=9cm]{zipper_algo.png}
     \end{center}
@@
         \begin{center}
-            \includegraphics[width=6cm]{fig7.png}
+            \includegraphics[width=9cm]{fig7.png}
         \end{center}
@@
         \begin{center}
-            \includegraphics[width=6cm]{fig8.png}
+            \includegraphics[width=9cm]{fig8.png}
         \end{center}
@@
         \begin{center}
-            \includegraphics[width=10cm]{fig9.png}
+            \includegraphics[width=8cm]{fig9.png}
         \end{center}
@@
                 \begin{center}
-                    \includegraphics[width=\textwidth]{figs.png}
+                    \includegraphics[width=12cm]{figs.png}
                 \end{center}
@@
                 \begin{center}
-                    \includegraphics[width=7.6cm]{distance_down.png}
+                    \includegraphics[width=13cm]{distance2.png}
                 \end{center}
@@
                 \begin{center}
-                    \includegraphics[width=7.6cm]{mds_down.png}
+                    \includegraphics[width=13cm]{mds.png}
                 \end{center}
@@
 
-            \begin{figure}
-                \begin{center}
-                    \includegraphics[width=\textwidth]{mds2.png}
-                \end{center}
-                \caption{(a) The MDS result of Harmonic Beltrami signature; (b) The MDS result of conformal welding; (c) The clustering result of Harmonic Beltrami signature; (d) The clustering results of conformal welding.}
-                \label{mds2}
-            \end{figure}
-
-        \subsection{Classification for more classes}
-            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabbit.
+        \subsection{Classification for more classes}\label{more class}
+            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabbit. All these shapes are in Fig \ref{more class all}
+
             We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes.
@@
 The classification accuracy based on Harmonic Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
+            \begin{figure}
+                \begin{center}
+                    \includegraphics[width=10cm]{all_images.png}
+                \end{center}
+                \caption{All 58 shapes within 7 classes used in experiment \ref{more class}}
+                \label{more class all}
+            \end{figure}
+
+            \begin{figure*}
+                \begin{center}
+                    \includegraphics[width=\textwidth]{mds2.png}
+                \end{center}
+                \caption{(a) The MDS result of Harmonic Beltrami signature; (b) The MDS result of conformal welding; (c) The clustering result of Harmonic Beltrami signature; (d) The clustering results of conformal welding.}
+                \label{mds2}
+            \end{figure*}
 
@@
 
+\biboptions{sort&compress}
 % BibTeX users please use one of
 % \bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
+% \bibliographystyle{spmpsci}      % mathematics and physical sciences
+\bibliographystyle{elsarticle-num}       % APS-like style for physics
 \bibliography{cite}

### 2021-06-15 paper.tex
siims

@@
-\documentclass[review]{elsarticle}
+\documentclass[review,onefignum,onetabnum]{siamonline190516}
 
 \usepackage{graphicx}
-% \usepackage{geometry}
-\usepackage{amsmath}
-\usepackage{amsthm}
 \usepackage{lineno}
-\usepackage{amssymb}
-% \usepackage{hyperref}
+\usepackage{amsfonts}
 \usepackage{algorithm}
 \usepackage{algorithmic}
+\usepackage{lipsum}
+\usepackage{epstopdf}
+\ifpdf
+  \DeclareGraphicsExtensions{.eps,.pdf,.png,.jpg}
+\else
+  \DeclareGraphicsExtensions{.eps}
+\fi
+
+\usepackage{enumitem}
+\setlist[enumerate]{leftmargin=.5in}
+\setlist[itemize]{leftmargin=.5in}
 \include{snippets}
-%
-\modulolinenumbers[5]
-
-\journal{Pattern Recognition}
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
-\newtheorem{theorem}{Theorem}
-% \newtheorem{lem}[thm]{Lemma}
-% \newdefinition{rmk}{Remark}
-% \newproof{proof}{Proof}
-\newdefinition{definition}{Definition}
+
 \graphicspath{ {./src/} }
@@
 \begin{document}
-\begin{frontmatter}
+
+% \begin{frontmatter}
 \title{Harmonic Beltrami Signature: A Novel Invariant 2D Shape Representation for Object Classification}
-\author[1]{Chenran Lin\corref{cor1}}
-\ead{crlin@math.cuhk.edu.hk}
-\address[1]{Department of Mathematics, The Chinese University of Hong Kong, Shatin, Hong Kong}
-\cortext[cor1]{Corresponding author}
-
-\author[1]{Lok Ming Lui}
-\ead{lmlui@math.cuhk.edu.hk}
-% \address[2]{Department of Mathematics, The Chinese University of Hong Kong}
+
+\author{
+    Chenran Lin\thanks{Department of Mathematics, The Chinese University of Hong Kong, Hong Kong (\email{crlin@math.cuhk.edu.hk})}
+\and
+    Lok Ming Lui\thanks{Department of Mathematics, The Chinese University of Hong Kong, Hong Kong (\email{lmlui@math.cuhk.edu.hk})}
+}
+\headers{Harmonic Beltrami Signature: A Novel Invariant 2D Shape Representation for Object Classification}{Chenran Lin, and Lok Ming Lui}
+
+\maketitle
 
@@
 
-\begin{keyword}
-  Shape representation \sep conformal welding \sep simply-connected \sep invariance
-\end{keyword}
-\end{frontmatter}
-
-\linenumbers
+\begin{keywords}
+  Shape representation, conformal welding, simply-connected, invariance
+\end{keywords}
 
@@
 Due to its significance, this problem has been widely studied and different models to build the metric shape space have been proposed.
-    % \cite{belongie2002shape,demisse2017deformation,hagedoorn2000pattern,lades1993distortion,latecki2000shape,mokhtarian1997efficient,zahn1972fourier}.
 
@@
 
-% \bigskip
-
 The above theorem demonstrates that the HBS is indeed an effective geometric representation or ``fingerprint" of a shape. It determines a shape up to a scaling, rotation and translation.
-
-    %Here we give a brief explanation of how to create our new signature.
-Given the boundary simply-connected domain $\Omega \subset \C$, we can get conformal welding $f = \Phi_1^{-1} \circ \Phi_2$ of it.
-Then $f$ can be extended to harmonic function $H$ defined on $\D$ by Poisson integral (\ref{poisson integral}).
-At the end, the Beltrami coefficient of $F$ becomes a signature of domain $\Omega$, we call it as \textit{Beltrami signature}:
-   % \begin{equation}
-  %      B:= \mu_H = %\frac{H_{\overline{z}}}{H_z}.
-%     \end{equation}
-%    Note that with some suitable normalization methods, which will be revealed in detail in Section \ref{norm1} and \ref{norm2}, $B$ is determined.
 
@@
 
-\biboptions{sort&compress}
+% \biboptions{sort&compress}
 % BibTeX users please use one of
@@
 % \bibliographystyle{spmpsci}      % mathematics and physical sciences
-\bibliographystyle{elsarticle-num}       % APS-like style for physics
+\bibliographystyle{siamplain}       % APS-like style for physics
 \bibliography{cite}

### 2021-08-11 paper.tex
update
b1,b2 \in [B} then O1=O2

@@
 }
-\headers{Harmonic Beltrami Signature: A Novel Invariant 2D Shape Representation for Object Classification}{Chenran Lin, and Lok Ming Lui}
+\headers{Harmonic Beltrami Signature}{Chenran Lin, and Lok Ming Lui}
 
@@
 Define $\mu:\mathbb{C}\to \mathbb{C}$ as
-\[
+\begin{equation}\label{reconstructionmu}
 \mu := \begin{cases}
@@
 \end{cases}
-\]
+\end{equation}
+
 According to Measurable Riemannian Mapping Theorem \ref{Measurable Riemannian Mapping Theorem}, there exists $G:\mathbb{C}\to \mathbb{C}$ such that $G_{\bar{z}}/G_z = \mu$.
@@
 
-Now, $\Omega$ is uniquely determined up to a Mobi\"us transformation $M=\frac{az+b}{cz+d}$.
+Now, $\Omega$ is determined up to a Mobi\"us transformation $M=\frac{az+b}{cz+d}$.
 If $G(\infty) = \infty$, then $M$ is of the form: $M = az+b= re^{i\theta}z +b$, $r\in \mathbb{R}^+$, $\theta \in [0,2\pi)$ and $b\in \mathbb{C}$.
 Hence, $\Omega$ is uniquely determined up to a scaling, rotation and translation, which are reflected by $r, \theta$ and $b$ respectively.
+
+Suppose $B_1, B_2 \in [B]$ are two different HBS, we want to demonstrate that their reconstructed domain $\Omega_1$ and $\Omega_2$ are the same up to scaling, rotation and translation.
+By definition, their corresponding conformal welding $f_1, f_2$ satisfy $f_2 = M_1^{-1} \circ f_1 \circ M_2$.
+Let $f_1 = \Phi_1^{-1} \circ \Phi_2$, then $f_2 = (\Phi_1 \circ M_1)^{-1} \circ (\Phi_2 \circ M_2)$ and $H_1, H_2$ are the harmonic extension of $f_1$ and $f_2$ respectively.
+It's easy to check that the Beltrami coefficient of
+\begin{equation}
+    G_1 := \begin{cases}
+    \Phi_1 \circ H_1 \text{ on } \mathbb{\D}\\
+    \Phi_2 \text{ on } \mathbb{D}^c
+    \end{cases}
+\end{equation}
+is just $\mu$ in equation (\ref{reconstructionmu}), so $\Omega_1 = T_1 \circ G_1(\D) = T_1 \circ \Phi_1 \circ H_1 (\D)$, where $T_1$ is any composition of scaling, rotation and translation.
+Note that $H_1$ maps unit disk to unit disk, we have $\Omega_1 = T_1 \circ \Phi_1 (\D)$.
+Similarly, let
+\begin{equation}
+    G_2 := \begin{cases}
+    \Phi_1 \circ M_1 \circ H_2 \text{ on } \mathbb{\D}\\
+    \Phi_2 \circ M_2 \text{ on } \mathbb{D}^c,
+    \end{cases}
+\end{equation}
+the reconstructed domain of $B_2$ is $\Omega_2 = T_2 \circ G_2(\D) = T_2 \circ \Phi_1 \circ M_1 \circ H_2(\D)$, where $T_2$ is also a composition of scaling, rotation and translation.
+Since $M_1(\D) = H_2(\D) = \D$, $\Omega_2$ can be represented as $\Omega_2 = T_2 \circ \Phi_1(\D)$.
+Therefore, $\Omega_1 = T_1 \circ T_2^{-1} (\Omega_2)$, which shows that the reconstructed shape is invariant (up to a scaling, rotation and translation) regardless of the selection of HBS.
 \end{proof}
@@
 The above theorem demonstrates that the HBS is indeed an effective geometric representation or ``fingerprint" of a shape. It determines a shape up to a scaling, rotation and translation.
+
+\bigskip
+
+\noindent {\it Remark:}
+{\it The proof of the above theorem also provides us with a method to reconstruct the shape associated to a given HBS $B$.
+More precisely, given $B$, we can define a Beltrami coefficient $\mu$ according to equation (\ref{reconstructionmu}).
+By solving the Beltrami's equation with Beltrami coefficient $\mu$, we obtain the quasiconformal map $G$.
+If we fix $G$ at $\infty$, the associated shape $\Omega = G(\mathbb{D})$ is uniquely determined up to a rotation, translation and scaling.
+The associated quasiconformal map can be solved by some computational methods developed earlier \cite{lui2013texture,lui2012optimization}}
 
@@
 
-    Let $f$ and $\tilde{f}$ be two different conformal welding of the same domain $\Omega$ and they satisfy equation (\ref{tilde f}).
-Their harmonic extension are $H$ and $\tilde{H}$ respectively.
-As we mentioned in last section, the conformal ambiguity of $M_1$ and $M_2$ is the biggest challenge in the way to unique representative, but we still hope $\tilde{H}$ to reserve such relationship, i.e.
-    \begin{equation}\label{tilde H}
-        \tilde{H} = M_1^{-1} \circ H \circ M_2,
-    \end{equation}
-    for the convenience of subsequent discussion. The following theorem tells us it can be achieved when restricting $M_1$:
+            Let $B_1$ and $B_2$ be two harmonic Beltrami signatures in the same equivalence class $[B]$ in $\mathcal{B}$.
+Suppose $B_1$ is computed by conformal parameterizations $\Phi_1^1:\mathbb{D}\to \Omega$ and $\Phi_2^1:\mathbb{D}^c\to \Omega^c$.
+Similarly, suppose $B_2$ is computed by conformal parameterizations $\Phi_1^2:\mathbb{D}\to \Omega$ and $\Phi_2^2:\mathbb{D}^c\to \Omega^c$.
+
+            We proceed to investigate the relationship between $B_1$ and $B_2$. In order to proceed, the following theorem is needed.
 
             \begin{theorem}
-        Suppose $f$ and $\tilde{f}$ are continuous map from $\mathbb{S}^1$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobi\"us transformations.
+                Suppose $f$ and $\tilde{f}$ are continuous map from $\mathbb{S}^1$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
 $H$ and $\tilde{H}$ are harmonic extension of $f$ and $\tilde{f}$, then $\tilde{H} = M_1^{-1} \circ H \circ M_2$ iff $M_1$ is a rotation.
@@
 
-        $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobi\"us transformation $M_2$ is conformal.
+                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
 $\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
@@
 It's easy to check that
-        \begin{equation}
-            M_1^{-1} \circ H \circ M_2 (e^{i \theta}) = M_1^{-1} \circ f \circ M_2(e^{i \theta}) = \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
-        \end{equation}
+                \begin{align*}
+                    M_1^{-1} \circ H \circ M_2 (e^{i \theta})
+                    &= M_1^{-1} \circ f \circ M_2(e^{i \theta})\\
+                    &= \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
+                \end{align*}
                 which means $M_1^{-1} \circ H \circ M_2$ and $\tilde{H}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ H \circ M_2 = \tilde{H}$.
@@
 
-    Note that if $M_1$ is not only a rotation, $\tilde{f}$ and $\tilde{H}$ also exist but equation (\ref{tilde H}) doesn't hold, as shown in Fig. \ref{harmonic extension not rotation}.
+    Note that if $M_1$ is not only a rotation, $\tilde{f}$ and $\tilde{H}$ also exist but $\tilde{H} = M_1^{-1} \circ H \circ M_2$ doesn't hold, as shown in Fig. \ref{harmonic extension not rotation}.
 
@@
 
-    Suppose HBS $B$ is the representative of given equivalence class $[B]$ and $H$ is the corresponding harmonic extension.
-Because of above theorem, we assume $M_1$ is a rotation, then for any other $\tilde{B} \in [B]$ of $\tilde{H} = M_1^{-1} \circ H \circ M_2$, we have
-    \begin{equation}\label{tildeB}
-        \tilde{B} = \mu_{\tilde{H}} = \mu_{M_1^{-1} \circ H \circ M_2} = \mu_{H\circ M_2}.
-    \end{equation}
-    This equation tells us the uniqueness of $B$ can be achieved by following theorem.
+ Now, we have the following theorem about the relationship between $B_1$ and $B_2$.
+
+            \begin{theorem}
+                Suppose $\Phi_j^1$ and $\Phi_j^2$ are the same up to a rotation for $j=1,2$.
+That is, $\Phi_1^2 = \Phi_1^1\circ M_1$ and $\Phi_2^2 = \Phi_2^1\circ M_2$, where $M_1(z) = e^{i\theta_1}z$ and $M_2(z) = e^{i\theta_2}z$.
+Then:
+                \[
+                B_2(z) = e^{-2i\theta_2} B_1(e^{i\theta_2}z)
+                \]
+            \end{theorem}
+            \begin{proof}
+                Under the assumptions, we have: 
+                \[
+                f_2 = M_1^{-1}\circ f_1 \circ M_2,
+                \]
+                \noindent where $f_1 = {\Phi_1^1}^{-1}\circ \Phi_2^1$ and $f_2 = {\Phi_1^2}^{-1}\circ \Phi_2^2$.
+Let $H_1$ and $H_2$ be the harmonic extensions of $B_1$ and $B_2$ respectively.
+According to Theorem 4, we have:
+                \[
+                H_2 = M_1^{-1}\circ H_1 \circ M_2,
+                \]
+                Since $M_1$ is a Mobi\"us transformation and thus conformal, we have $B_2 = \mu_{H_2} = \mu_{H_1\circ M_2}$. Using Equation \ref{mu of conformal composition}, we obtain:
+                \begin{equation*}
+                    \begin{split}
+                B_2(z) = \mu_{H_1\circ M_2}(z) &= \frac{\bar{M_2}}{M_2} \mu_{H_1}\circ M_2(z) \\
+                &= e^{i\theta_2} B_1( e^{i\theta_2} z).
+                \end{split}
+                \end{equation*}
+
+            \end{proof}
+
+            The above theorem tells us the relationship between $B_1$ and $B_2$ if $\Phi_j^1$ and $\Phi_j^2$ are unique up to a rotation for $j=1, 2$.
+In this work, we will assume $\Phi_j^1$ and $\Phi_j^2$ are unique up to a rotation.
+
+            With further normalization on the Harmonic Beltrami signature, we can obtain a unique representation in $[B]$.
+
 \begin{theorem}\label{unique B}
@@
 
-\subsection{Normalization to $M_1$}\label{norm1}
-    We hope $M_1$ is a rotation.
-It is not that hard, for example, we can achieve it by restricting $\Phi_1(0) = 0$.
-But it need a hypothesis that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold.
-Here we want to show a new approach without any additional assumption.
-
-    In actual application, we usually only know finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$.
+\subsection{Normalization to $M_1$}\label{norm_to_m1}
+To obtain a unique representative in $[B]$, we assume both $M_1$ and $M_2$ is a rotation. In this subsection, we discuss how to normalize $M_1$.
+
+Suppose $\Phi_1:\mathbb{D}\to \Omega$ be the conformal parameterization of $\Omega$.
+We proceed to normalize $\Phi_1$ so that $M_1$ is a rotation.
+One possible way is to achieve restrict $\Phi_1(0) = 0$.
+But it requires the assumption that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold.
+In this work, we introduce a new approach without any additional assumption.
+
+In actual scenario, we usually only have finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$ representing the boundary of $\Omega$.
 Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, where $\Phi_1 : \D \rightarrow \Omega$.
-We claims that $M_1$ can be normalized by restricting the center of $p_i$ to $0$.
-
-    \begin{theorem}\label{unique up to a rotation}
-        Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
-        \begin{align}\label{norm phi1}
-            \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
-        \end{align}
-        then such $\Phi_1$ is unique up to a rotation $M_1$.
-    \end{theorem}
-
-    Before proving theorem \ref{unique up to a rotation}, we can consider following problem.
+We claims that $M_1$ can be normalized by restricting the centroid of $p_i$'s to be $0$.
+That is equation \ref{norm phi1}.
+
+A natural question is the existence of a conformal parameterization that satisfies equation \ref{norm phi1}.
+To study this, we consider following problem.
 Given boundary points $p_i$ on unit circle, can we find a Mobi\"us transformation $M$ satisfies the following equation (\ref{fz})?
+
     \begin{equation}\label{fz}
@@
 
-    Without lose of generality, we ignore the rotation of $M$ and let $F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
-So $F_a$ is also a Mobi\"us transformation and it's sufficient to find $a \in \D$ such that
+    Without lose of generality, we ignore the rotational component of $M$ and let $ M = F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$. We proceed to find $a \in \D$ such that
     \begin{equation}\label{eq}
-        f(a) = \sum_{k=1}^n F_a(p_k) = \sum_{k=1}^n \frac{p_k - a}{1 - \overline{a}p_k} = 0
-    \end{equation}
-    to show the equation (\ref{fz}) holds for some $M$. Intuitively, we believe that there is always a unique solution to this equation (\ref{eq}) (see Fig \ref{fasolvable}).
+        f(a) = \sum_{k=1}^n F_a(p_k) = \sum_{k=1}^n \frac{p_k - a}{1 - \overline{a}p_k} = 0.
+    \end{equation}
+    Figure \ref{fasolvable}) shows some graphs of $|f(a)|$ corresponding to various boundary points, illustrating the uniqueness of the solution to equation (\ref{eq}).
 
@@
 
-    \subsubsection{The solvability of equation (\ref{eq})}
-    First thing we want to do is to check whether this equation (\ref{eq}) is always solvable. According to Brouwer fixed point theorem, we have
+    According to Brouwer fixed point theorem, the existence of the solution to equation (\ref{eq}) can be shown.
 
@@
 
-    \subsubsection{The uniqueness of the solution of equation (\ref{eq})}
-    With solvability proved, we naturally want to know if this solution is unique. Let's consider a special case when $\sum_{k=1}^n p_k = 0$, we have
+    The uniqueness of the solution to equation (\ref{eq}) can also be studied. Firstly, we consider a special case when $\sum_{k=1}^n p_k = 0$, we have
+
     \begin{theorem}\label{uniqueness when 0}
@@
         Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so \\
-        $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$. According to theorem \ref{uniqueness when 0},\\
-        $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, then $a_0 = a_1$, which contradicts to the assumption.
+        $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$.
+According to theorem \ref{uniqueness when 0}, $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, then $a_0 = a_1$, which contradicts to the assumption.
     \end{proof}
 
-    \subsubsection{Unique $\Phi_1$ up to a rotation}
-
-    Above theorems show that there is always a unique solution $a \in \D$ for equation (\ref{eq}), so we can come back to theorem \ref{unique up to a rotation}.
+    With the above observations, we have the following theorem.
+
+    \begin{theorem}\label{unique up to a rotation}
+        Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
+        \begin{align}\label{norm phi1}
+            \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
+        \end{align}
+        then such $\Phi_1$ is unique up to a rotation $M_1$.
+    \end{theorem}
 
@@
     \end{proof}
+
+    Theorem \ref{unique up to a rotation} gives a condition that leads to the uniqueness of $\Phi_1$ up to a rotation.
 
@@
 
-\subsection{Reconstruction}\label{reconstruction}
-    The above theorems show that our Harmonic Beltrami signature can be uniquely defined by the given shape and is invariant under translation, scaling and rotation.
-Conversely, we will further demonstrate the method to reconstruct the original shape when given a Beltrami signature in this section.
-
-    If $B_\Omega$ is the HBS of some simply-connected domain $\Omega$, according to the process we mentioned at the beginning of Section \ref{main}, there exists conformal mappings $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, conformal welding $f: \partial \D \rightarrow \partial \D $ and harmonic extension $H$ of $f$, where $\Phi_1$ satisfies equation (\ref{norm phi1}), $\Phi_2$ satisfies equations (\ref{norm phi2 1}), $f = \Phi_1^{-1} \circ \Phi_2$, $\mu_H = B_\Omega$ and $B_\Omega$ satisfies (\ref{arg integral B is 0}).
-
-    Given a Harmonic Beltrami signature $B_\Omega$, define
-    \begin{equation}
-        g(z) = \begin{cases}
-            B_\Omega(z), z \in \D \\
-            0, z \in \D^c
-        \end{cases}
-    \end{equation}
-    According to Theorem \ref{Measurable Riemannian Mapping Theorem}, we can find mapping $G: \overline{\C} \rightarrow \overline{\C}$ such that
-    \begin{align}
-        &\mu_G = \frac{G_{\overline{z}}}{G_z} = g \nonumber\\
-        &G(\infty) = \infty\label{Ginfty}
-    \end{align}
-    where $G$ is uniquely determined up to Mobi\"us transformation $M$.
-
-    Claim that $\Omega' = G(\D)$ is the reconstructed domain satisfying $\Omega' = T(\Omega)$, where $T$ is composed by rotation, scaling and translation. Note that
-    \begin{equation}
-        G_0(z) = \begin{cases}
-            \Phi_1 \circ H(z), z \in \D\\
-            \Phi_2(z), z \in \D^c
-        \end{cases}
-    \end{equation}
-    is one solution of (\ref{Ginfty}) since $\mu_{\Phi_1 \circ H} = \mu_H = B_\Omega$ inside $\D$, $\mu_{\Phi_2} = 0$ outside $\D$ and $\Phi_2(\infty) = \infty$. Therefore, we have 
-    \begin{equation}
-        G = M \circ G_0 \text{ and } M(\infty) = \infty.
-    \end{equation}
-    By the properties of Mobi\"us transformation, we have $M(z) = az+b$ where $a, b \in \C$.
-
-    On the other side, $H$ is a harmonic mapping from $\D$ onto itself, so $G_0(\D) = \Phi_1 \circ H(\D) = \Omega$, then $\Omega' = G(\D) = M(\Omega) = a \Omega + b$, which show the claim is correct.
-
-    That means the map between Harmonic Beltrami signatures and shapes is also a bijection, up to transformation, scaling and rotation.
-In the theorem \ref{one to one equivalence class} tells us that there exists a one-to-one relationship between HBS equivalence classes and shapes and now such bijection can be extended to a special HBS, i.e.
-the unique representative of equivalence class.
-    \begin{theorem}
-        Let $\Omega_1, \Omega_2$ be two different simply-connected domains and $B_{\Omega_1}, B_{\Omega_2}$ are the corresponding HBS, then $B_{\Omega_1} = B_{\Omega_2}$ if and only is $\Omega_1 = T(\Omega_2)$, where $T$ is composed by rotation, scaling and translation.
-    \end{theorem}
-
-    \begin{proof}
-        The direction from signatures to shapes is proved in this section, and another direction is derived from theorem \ref{invariance theorem}.
-    \end{proof}
-
-\subsection{Robustness of HBS}
-    Although there exists a one-to-one correspondence between HBS and shapes up to a rotation, translation and scaling, the behavior of HBS under small modification to the original shape is still unknown.
-Of course, we expect the HBS to be slightly deformed within reasonable range so that the proposed signature is robust and useful.
-The following powerful theorem about Beltrami holomorphic flow(BHF) tells that if two HBS are similar, their corresponding shapes must be very alike.
-
-    \begin{theorem}[Beltrami holomorphic flow on $\mathbb{S}^2$]\label{BHF}
-        There is a one-to-one correspondence between the set of quasiconformal diffeomorphisms of $\mathbb{S}^2$ that fix the points 0, 1, and $\infty$ and the set of smooth complex-valued functions $\mu$ on $\mathbb{S}^2$ with $\norm{\mu}_\infty = k < 1$.
-Here, we have identified $\mathbb{S}^2$ with the extended complex plane $\overline{\C}$.
+\subsection{Geometric implication of HBS}
+    Although there exists a one-to-one correspondence between HBS and shapes up to a rotation, translation and scaling, the geometric implication of HBS is still unknown.
+More precisely, if two shapes are compared based on the HBS, it is necessary to know whether two shapes are close when their corresponding HBS are close.
+To study this, we first define the distance between two shapes $\Omega_1\subset \mathbb{R}^2$ and $\Omega_2\subset \mathbb{R}^2$ as follows:
+    \begin{equation}
+        d(\Omega_1,\Omega_2) = \frac{1}{2}\left(\max_{q\in\partial \Omega_2} \min_{p\in\partial \Omega_1} ||p-q|| + \max_{p\in\partial \Omega_1} \min_{q\in\partial \Omega_2} ||p-q||\right),
+    \end{equation}
+    \noindent where $||\cdot||$ refers to the Euclidean norm. We shall show that $d(\Omega_1,\Omega_2)$ is small if their Harmonic Beltrami Signatures are alike.
+
+The following theorem is useful, which describe the perturbation of the quasiconformal map under the perturbation of the associated Beltrami coefficient.
+
+    \begin{theorem}[Beltrami holomorphic flow on $\overline{\C}$]\label{BHF}
+        There is a one-to-one correspondence between the set of quasiconformal diffeomorphisms of $\overline{\C}$ that fix the points 0, 1, and $\infty$ and the set of smooth complex-valued functions $\mu$ on $\overline{\C}$ with $\norm{\mu}_\infty = k < 1$.
+Here, we have identified $\overline{\C}$ with the extended complex plane $\overline{\C}$.
 Furthermore, the solution $f^\mu$ to the Beltrami equation depends holomorphically on $\mu$.
@@
         \begin{equation}
-            \mu(t)(z) = \mu(z) + tv(z) + t \epsilon(t)(z)
-        \end{equation}
-        for $z \in \C$, with suitable $\mu$ in the unit ball of $C^\infty(\C)$, $v, \epsilon(t) \in L^\infty(\C)$ such that $\lim_{t \rightarrow 0} \norm{\epsilon(t)}_\infty = 0$.
-Then for all $w \in \C$,
+            \mu(t)(z) = \mu(z) + tv(z) + t \epsilon(t)(z) \text{ for }z \in \C,
+        \end{equation}
+        \noindent with suitable $\mu$ in the unit ball of $C^\infty(\C)$, $v, \epsilon(t) \in L^\infty(\C)$ such that $\lim_{t \rightarrow 0} \norm{\epsilon(t)}_\infty = 0$. Then for all $w \in \C$,
         \begin{equation}
@@
 
-    Given HBS $B_1, B_2$, we can solve PDE (\ref{Ginfty}) and get solutions $G_1, G_2$, then the corresponding original simply-connected domains $\Omega_1 = G_1(\D), \Omega_2 = G_2(\D)$. Let
+    Recall that given a HBS, its associated shape is uniquely determined up to a translation, scaling and rotation.
+Therefore, in order to analyze the geometric implication of HBS, we shall normalize the shape associated to a given HBS.
+According to Theorem \ref{one to one equivalence class}, given $[B] \in \mathcal{B}$, its corresponding shape can be determined by computing a quasiconformal map $G$ associated to $\mu$ given by Equation \ref{reconstructionmu}.
+The shape $\Omega = G(\mathbb{D})$ can be reconstructed, which is unique up to a rotation, translation and scaling.
+In particular, $\Omega$ can be normalized by constraining $G$ to fix $0, 1$ and $\infty$.
+In this subsection, we assume the shape $\Omega$ corresponding to a HBS is normalized as described above.
+
+    Now, the geometric implication of HBS can be explained by the following theorem.
+
+    \begin{theorem}
+    Let $[B_1]$ and $[B_2]$ be two harmonic Beltrami signatures.
+Suppose $B_1$ and $B_2$ are the unique representatives.
+Let $\Omega_1$ and $\Omega_2$ be the normalized shapes associated to $B_1$ and $B_2$ respectively.
+If
+    $||B_1 - B_2||_{\infty} < \epsilon$, then $d(\Omega_1,\Omega_2)<\frac{2M}{\pi}\epsilon$ for some $M>0$.
+    \end{theorem}
+    \begin{proof}
+    According to Theorem \ref{one to one equivalence class}, $\Omega_1$ and $\Omega_2$ can be reconstructed by solving for the quasiconformal maps $G_1$ and $G_2$.
+Then, $\Omega_1 = G_1(\D)$ and $\Omega_2 = G_2(\D)$.
+
+    Let
     \begin{equation}
@@
     \end{equation}
-    where $v(z) = B_2(z) - B_1(z)$ if $z \in \D$ and $v(z) = 0$ if $z \notin \D$, so $G(t)(z) = G_1(z) + tV(G_1, v)(z)$. When $t=1$, we have $G(1)(z) = G_2(z)$ and
+    where $v(z) = \frac{B_2(z) - B_1(z)}{||B_1 - B_2||_{\infty}}$ if $z \in \D$ and $v(z) = 0$ if $z \notin \D$.
+Then, $G_1$ and $G_2$ are quasiconformal maps associated to the Beltrami coefficients $g(0)$ and $g(||B_1 - B_2||_{\infty})$ respectively.
+According to Theorem \ref{BHF},
     \begin{align*}
-        &\norm{G_2 - G_1}_\infty = \norm{V(G_1, v)}_\infty \\
-        &\le \frac{1}{\pi}\norm{G_1}_\infty \norm{G_1 - 1}_\infty \norm{W(G_1, v)}\\
-        &\le \frac{2}{\pi} \norm{W(G_1, v)}_\infty.
+        &\norm{G_2 - G_1}_\infty = \norm{V(G_1, v) + o(||B_1 - B_2||_{\infty})}_\infty \\
+        &\le \frac{1}{\pi}\norm{G_1}_\infty \norm{G_1 - 1}_\infty \norm{W(G_1, v)} + o(||B_1 - B_2||_{\infty})\\
+        &\le \frac{2}{\pi} \norm{W(G_1, v)}_\infty + o(||B_1 - B_2||_{\infty}).
     \end{align*}
@@
 
-    then
-    \begin{equation}
-        \norm{G_2 - G_1}_\infty \le \frac{2M}{\pi} \norm{B_2-B_1}_\infty.
-    \end{equation}
-
-    This illustrates that if the difference between HBS is small enough, their corresponding domains is almost the same, which means our Harmonic Beltrami signature is a good indicator similarity of shapes.
+    Then,
+    \begin{equation}
+        \norm{G_2 - G_1}_\infty \le \frac{2M}{\pi} \norm{B_2-B_1}_\infty\le \frac{2M}{\pi} \epsilon.
+    \end{equation}
+
+    Now, for any $q = G_2(z) \in \Omega_2$ ($z\in \D$), we have $\min_{p\in \Omega_1} ||p-q|| \leq ||G_1(z) - G_2(z)||\leq \frac{2M}{\pi}\epsilon$.
+Thus, $\max_{q\in \Omega_2}\min_{p\in \Omega_1} ||p-q|| \leq \frac{2M}{\pi}\epsilon$.
+
+    Similarly, $\max_{p\in \Omega_1}\min_{q\in \Omega_2} ||p-q|| \leq \frac{2M}{\pi}\epsilon$. As a result, we have 
+    \[
+    d(\Omega_1,\Omega_2)<\frac{2M}{\pi}\epsilon
+    \]
+    \end{proof}
+
+    This above theorem illustrates that if the difference between HBS is small enough, their corresponding domains is almost the same, which means our Harmonic Beltrami signature is a good indicator similarity of shapes.
 
@@
     In order to find a unique and stable HBS, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
-As mentioned in Section \ref{norm1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
+As mentioned in Section \ref{norm_to_m1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
 
@@
     \begin{center}
-        \includegraphics[width=9cm]{zipper_algo.png}
+        \includegraphics[width=12cm]{zipper_algo.png}
     \end{center}
@@
     \end{equation*}
-    Section \ref{norm1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then HBS $B$ can be unique.
+    Section \ref{norm_to_m1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then HBS $B$ can be unique.
 This section will tells how to satisfy equation (\ref{norm phi1}) and (\ref{norm phi2 1}) from the output of zipper algorithm.
@@
                 \begin{center}
-                    \includegraphics[width=10.5cm]{inv.png}
+                    \includegraphics[width=10cm]{inv.png}
                 \end{center}
@@
 % end of file template.tex
+
+\subsection{Reconstruction}\label{reconstruction}
+    The above theorems show that our Harmonic Beltrami signature can be uniquely defined by the given shape and is invariant under translation, scaling and rotation.
+Conversely, we will further demonstrate the method to reconstruct the original shape when given a Beltrami signature in this section.
+
+    If $B_\Omega$ is the HBS of some simply-connected domain $\Omega$, according to the process we mentioned at the beginning of Section \ref{main}, there exists conformal mappings $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, conformal welding $f: \partial \D \rightarrow \partial \D $ and harmonic extension $H$ of $f$, where $\Phi_1$ satisfies equation (\ref{norm phi1}), $\Phi_2$ satisfies equations (\ref{norm phi2 1}), $f = \Phi_1^{-1} \circ \Phi_2$, $\mu_H = B_\Omega$ and $B_\Omega$ satisfies (\ref{arg integral B is 0}).
+
+    Given a Harmonic Beltrami signature $B_\Omega$, define
+    \begin{equation}
+        g(z) = \begin{cases}
+            B_\Omega(z), z \in \D \\
+            0, z \in \D^c
+        \end{cases}
+    \end{equation}
+    According to Theorem \ref{Measurable Riemannian Mapping Theorem}, we can find mapping $G: \overline{\C} \rightarrow \overline{\C}$ such that
+    \begin{align}
+        &\mu_G = \frac{G_{\overline{z}}}{G_z} = g \nonumber\\
+        &G(\infty) = \infty\label{Ginfty}
+    \end{align}
+    where $G$ is uniquely determined up to Mobi\"us transformation $M$.
+
+    Claim that $\Omega' = G(\D)$ is the reconstructed domain satisfying $\Omega' = T(\Omega)$, where $T$ is composed by rotation, scaling and translation. Note that
+    \begin{equation}
+        G_0(z) = \begin{cases}
+            \Phi_1 \circ H(z), z \in \D\\
+            \Phi_2(z), z \in \D^c
+        \end{cases}
+    \end{equation}
+    is one solution of (\ref{Ginfty}) since $\mu_{\Phi_1 \circ H} = \mu_H = B_\Omega$ inside $\D$, $\mu_{\Phi_2} = 0$ outside $\D$ and $\Phi_2(\infty) = \infty$. Therefore, we have 
+    \begin{equation}
+        G = M \circ G_0 \text{ and } M(\infty) = \infty.
+    \end{equation}
+    By the properties of Mobi\"us transformation, we have $M(z) = az+b$ where $a, b \in \C$.
+
+    On the other side, $H$ is a harmonic mapping from $\D$ onto itself, so $G_0(\D) = \Phi_1 \circ H(\D) = \Omega$, then $\Omega' = G(\D) = M(\Omega) = a \Omega + b$, which show the claim is correct.
+
+    That means the map between Harmonic Beltrami signatures and shapes is also a bijection, up to transformation, scaling and rotation.
+In the theorem \ref{one to one equivalence class} tells us that there exists a one-to-one relationship between HBS equivalence classes and shapes and now such bijection can be extended to a special HBS, i.e.
+the unique representative of equivalence class.
+    \begin{theorem}
+        Let $\Omega_1, \Omega_2$ be two different simply-connected domains and $B_{\Omega_1}, B_{\Omega_2}$ are the corresponding HBS, then $B_{\Omega_1} = B_{\Omega_2}$ if and only is $\Omega_1 = T(\Omega_2)$, where $T$ is composed by rotation, scaling and translation.
+    \end{theorem}
+
+    \begin{proof}
+        The direction from signatures to shapes is proved in this section, and another direction is derived from theorem \ref{invariance theorem}.
+    \end{proof}

### 2021-10-08 paper.tex
save

@@
 % \begin{frontmatter}
-\title{Harmonic Beltrami Signature: A Novel Invariant 2D Shape Representation for Object Classification}
+\title{Harmonic Beltrami Signature: A Novel 2D Shape Representation for Object Classification}
 
@@
 \begin{abstract}
-  There is a growing interest in shape analysis in recent years and we present a novel contour-based shape representation for 2D bounded simply-connected domains in this paper, named the Harmonic Beltrami signature.
-The proposed signature is based on the harmonic extension of the conformal welding map of a unit circle.
-With suitable normalization, the uniqueness of this harmonic function is guaranteed up to rotations.
-And finally quasi-conformal theory helps get rid of the only uncertainty by computing the Beltrami coefficient of harmonic extension.
-There exists one-by-one relationship between shapes and our Harmonic Beltrami signatures and we also give the method to reconstruct the original shapes from our signatures.
-The benifit of the proposed signature is that it keeps to be invariant under simple transformations like sacling, transformation and rotation and is roubost under slight deformations and distortions.
-Experiments demonstrate the above properties and also show the excellent classification performance.
+  There is a growing interest in shape analysis in recent years.
+We present a novel shape signature for 2D bounded simply-connected domains, named the Harmonic Beltrami signature (HBS).
+The proposed signature is based on the harmonic extension of the conformal welding map of a unit circle and its Beltrami coefficient.
+We show that there is a one-to-one correspondence between the quotient space of HBS and the space of 2D simply-connected shapes up to a translation, rotation and scaling.
+With a suitable normalization, each equivalence class in the quotient space of HBS is associated to a unique representative.
+It gets rid of the conformal ambiguity.
+As such, each shape is associated to a unique HBS.
+Conversely, the associated shape of a HBS can be reconstructed based on quasiconformal Teichm\"uller theories, which is uniquely determined up to a translation, rotation and scaling.
+The HBS is thus an effective fingerprint to represent a 2D shape.
+The robustness of HBS is studied both theoretically and experimentally.
+With the HBS, simple metric, such as $L^2$, can be used to measure geometric dissimilarity between shapes.
+Experiments have been carried out to classify shapes in different classes using HBS.
+Results show good classification performance, which demonstrate the efficacy of our proposed shape signature.
 \end{abstract}
@@
 \label{intro}
+
+% Working on the introduction
+
     The outline of a shape contains important information, which can be used in many applications, such as medical image analysis, image segmentation, recognition, registration and so on.
-Nevertheless, it is a big challenge to define a robust descriptor for the space of shapes, even for the simplest situation of 2D simply-connected objects.
+In order to utilize the shape information, an effective descriptor to represent a shape is a necessary and fundamental tool for many applications in pattern recognition and computer visions.
+Nevertheless, defining a robust shape signature to describe the space of shapes is still a mathematically challenging problem.
+A good shape signature should be easy to compute and retain essential geometric features of a shape.
+Meanwhile, a practical shape signature should be invariant under rigid motion (rotation, translation and scaling) and robust to noise.
+More desirably, the space of shape signatures should inherits a natural and simple metric.
+With the natural metric, two shapes can be quantitatively compared and prior shape information can be incorporated into various imaging models by adding a penalty term to further improve the accuracy.
+Of course, the shape signature must be simple to manipulate such that the modified imaging model is numerically manageable.
+
+    Because of its significance, this problem has been widely studied and different models to build the metric shape space have been proposed.
+In general, existing approaches for constructing shape descriptors can be divided into two main categories, namely, the region-based methods and the contour-based methods.
+Region-based methods use all information of pixels within a shape.
+While more information is considered, these methods are often more computationally demanding.
+In contrast, the contour-based methods only use the boundary information of the shape.
+Various descriptors capturing the essential geometric features of the shape contour have been recently proposed.
+It is worth mentioning that many of these shape descriptors in either categories cannot completely capture the geometric information of the shape.
+In other words, the shape associated to a given shape descriptor cannot be uniquely determined up to rigid motions.
+Motivated by this, we propose in this paper a shape signature for 2D bounded simply-connected shapes, called the Harmonic Beltrami signature, based on the quasiconformal Teichm\"uller theories.
+Each shape signature is associated to a unique shape up to rigid motions.
+Thus, the proposed signature can capture the geometric information of a shape completely.
+
+    %Nevertheless, it is a big challenge to define a robust descriptor for the space of shapes, even for the simplest situation of 2D simply-connected objects.
 In order to manipulate shapes and utilize their geometric information, there is an urgent demand to find a simple and robust representation to mathematically describe shape contours.
@@
 
-    Considering 2D simply-connected shapes, conformal welding is a kind of well-known shape signature.
+    More specifically, given a simply-connected bounded domain, the conformal disk parameterizations of the inner and outer regions are computed.
+It gives rise to the conformal welding of the boundary contour of the domain.
+The harmonic extension of the welding map can be computed, whose Beltrami coefficient then defines the shape signature, called the {\it Harmonic Beltrami signature (HBS)}.
+Theoretically, it can be shown that there is a one-to-one correspondene between the quotient space of HBS and the space of 2D simply-connected shapes up to rigid motions.
+With a suitable normalization, each equivalence class in the quotient space of HBS has a unique representative, which helps to get rid of the conformal ambiguity.
+In particular, each shape is associated to a unique HBS.
+Also, given a HBS, the associated shape can be uniquely reconstructed up to a translation, rotation and scaling.
+As such, the HBS can be regarded as an effective fingerprint to represent a 2D shape.
+Note that conformal map of a region is robust to noises on the boundary contour of the domain.
+The proposed HBS, which is based on the conformal maps and the harmonic extension, is robust to noises.
+The proposed signature also allows us to study the space of shapes by analyzing the space of HBS, which is easy to manipulate.
+In fact, with the HBS, simple metric can be used to measure geometric dissimilarity between shapes.
+This can be applied to various pattern recognition and image analysis tasks.
+
+   % Considering 2D simply-connected shapes, conformal welding is a kind of well-known shape signature.
 Given 2D simply-connected domain $\Omega \subset \C$ with Jordan curve boundary $\eta = \partial \D$, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$, then conformal welding can be defined as $f = \Phi_1^{-1} \circ \Phi_2$.
-This gives a simple but wonderful representation of $\Omega$ as Fig.
-\ref{fig1} shows.
+This gives a simple but wonderful representation of $\Omega$ as figure \ref{fig1} shows.
 However, it has two fatal defects.
@@
 
-    Another thing is that even the conformal welding is very easy to be changed by simple transformations like rotation, scaling and translation.
+   % Another thing is that even the conformal welding is very easy to be changed by simple transformations like rotation, scaling and translation.
 Such a unstable representation is hard to apply in practical applications since these transformations are inevitable in the real world.
 
-    The contribution of this paper is that we propose a novel presentation for 2D simply-connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Harmonic Beltrami signature.
+  %  The contribution of this paper is that we propose a novel presentation for 2D simply-connected shape based on conformal welding with help of quasi-conformal theorem, which is invariant under simple transformation, and we name it Harmonic Beltrami signature.
 Given a shape $\Omega$, $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ can be calculated by zipper algorithm, which is a mature and efficient algorithm to find the conformal mapping from the given domain to unit disk by finite boundary points.
@@
 
-    The proposed shape representation, Harmonic Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
+  %  The proposed shape representation, Harmonic Beltrami signature, is uniquely determined by the given domain without any assumption and artificial restriction to domain.
 The Harmonic Beltrami signature is based on computational quasi-conformal geometry.
@@
 Applications can be found in image segmentation
-    \cite{siu2020image,chan2018topology,zhang2020topology}
-    , image registration
-    \cite{lam2014landmark,lui2014teichmuller,ng2014computing,lui2012optimization,lam2014genus,zhang2012registration,lee2016landmark,lui2010optimized,lui2013texture,lui2010shape,lui2010optimizedc,lui2014geometric,choi2015flash}
-     and image analysis 
-    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shape,lui2010shape3}
-    .
+  %  \cite{siu2020image,chan2018topology,zhang2020topology}
+ %   , image registration
+ %   \cite{lam2014landmark,lui2014teichmuller,ng2014computing,lui2012optimization,lam2014genus,zhang2012registration,lee2016landmark,lui2010optimized,lui2013texture,lui2010shape,lui2010optimizedc,lui2014geometric,choi2015flash}
+ %    and image analysis 
+%    \cite{wang2007brain,lui2007landmark,choi2020shape,chan2016quasi,zeng2008shape,lui2013shape,lui2010shape3}
+  %  .
 What's more worth mentioning is that Harmonic Beltrami signature is invariant under rotation, translation and scaling and is robust to small deformation and distortion of the original shape.
@@
 
-    The paper is organized as follows: Section \ref{related work} reviews some related topics about shape representation; Section \ref{background} introduces some theoretic background; Section \ref{main} shows the main theorem about how the unique Harmonic Beltrami signature is obtained from given domain and shows the method to reconstruct the original shape from given HBS; Section \ref{implementation} gives the details about the implementation; Section \ref{result} reports our experimental results.
-The paper is concluded in Section \ref{conclusion} and we point out future directions.
+    The paper is organized as follows: Section \ref{related work} reviews some related topics about shape descriptors; Section \ref{background} introduces some theoretic background; Section \ref{main} explains our proposed Harmonic Beltrami signature in details; Section \ref{implementation} gives the implementation details; Section \ref{result} reports our experimental results.
+The paper is concluded in Section \ref{conclusion} and we point out several future directions.
 
@@
 Demisse \etal \cite{demisse2017deformation} proposed a method to represent an ordered set of points sampled from a curved shape as an element of a finite dimensional matrix Lie group.
-Mokhtarian \etal \cite{mokhtarian1997efficient} use the maxima of curvature zero-crossing contours of Curvature Scale Space image to represent the shapes of object boundary contours.
+Mokhtarian \etal \cite{mokhtarian1997efficient} used the maxima of curvature zero-crossing contours of Curvature Scale Space image to represent the shapes of object boundary contours.
 Lui \etal \cite{lui2013shape} extracted each component of a 2D multi-connected shape, then the conformal weldings represent all components and conformal modules describe relationships between components.
 
-    A more meticulous survery about shape representations can be found in \cite{zhang2004review}.
+    A more meticulous survey about shape representations can be found in \cite{zhang2004review}.
 Generally speaking, all of these representation techniques can be divided into two major categories, \textit{contour-based} methods and \textit{region-based} methods, depending on whether shape features are extracted from the contour only or from the whole shape region.
@@
         The simplest features are area, circularity, curvature and so on and their combination can be used as shape representation.
-Peura \etal \cite{peura1997efficiency} proposed such descriptor including convexity, ratio of principle axis, circular variance and elliptic variance.
-Belongie \etal \cite{belongie2002shape} tried in a different way and build a representation based on Hausdorff distance, called shape contexts.
-For any boundary point $p$, they calculated the Hausdorff distance $d_{pq}$ and the orientation $\theta_{pq}$ with any other boundary point $q$, then these $d_{pq}$ and $\theta_{pq}$ are quantized to create a histogram map $H_p$ which is used to represent the point $p$.
-All the histogram $H_p$ is flattened and concatenated to form the context of the shape.
-Asada \etal \cite{asada1986curvature} attempted to smooth the boundary by Gaussian filter and second derivatives of Gaussian filter and the inflection points that remain are expected to be significant object characteristics.
-
-        Some other contour-based representations pay more attention to local boundary information and broke the shape down into many pieces.
+Peura \etal \cite{peura1997efficiency} proposed such a descriptor including convexity, ratio of principle axis, circular variance and elliptic variance.
+Belongie \etal \cite{belongie2002shape} tried in a different way and built a representation based on Hausdorff distance, called shape context.
+For any boundary point $p$, they calculated the Hausdorff distance $d_{pq}$ and the orientation $\theta_{pq}$ with any other boundary point $q$, then these $d_{pq}$ and $\theta_{pq}$ are quantized to create a histogram map $H_p$, which is used to represent the point $p$.
+All the histograms $H_p$ are flattened and concatenated to form the context of the shape.
+Asada \etal \cite{asada1986curvature} attempted to smooth the boundary by Gaussian filter as well as the second derivatives of Gaussian filter, then the remained inflection points are expected to be significant object characteristics.
+
+        Some other contour-based representations pay more attention to local boundary information and break the shape down into many pieces.
 Chain code describes an object by a sequence of unit-size line segments with a given orientation, which was introduced by Freeman \etal \cite{freeman1961encoding}.
-Berretti \etal \cite{berretti2000retrieval} extended the model.
+Groskey \etal \cite{grosky1990index} proposed polygon decomposition as representation.
+The given shape boundary is broken down into line segments by polygon approximation.
+The feature for each segment is expressed as four elements, internal angle, distance from the next vertex, and its $x$ and $y$ coordinates.
+Berretti \etal \cite{berretti2000retrieval} extended Groskeyet's model.
 The curvature zero-crossing points from a Gaussian smoothed boundary are used to obtain smooth curve, called tokens.
-The feature for each token is its maximum curvature and its orientation, and the similarity between two tokens is measured by the weighted Euclidean distance.
+The features for each token are its maximum curvature and orientation, and the similarity between two tokens is measured by the weighted Euclidean distance.
 
@@
 Hu published the first significant paper about geometric moment and applied it in pattern recognition \cite{hu1962visual}.
-Taubin \etal \cite{taubin1991object,taubin1991recognition} proposed algebraic moment, which is computed from the first $m$ central moments and is given as the eigenvalues of predefined matrices, $M_{[j; k]}$, whose elements are scaled factors of the central moments.
+Taubin \etal \cite{taubin1991object,taubin1991recognition} proposed algebraic moment, which is computed from the first $m$ central moments and is given as the eigenvalues of predefined matrices $M_{j, k}$, whose elements are scaled factors of the central moments.
 Zhang \etal \cite{zhang2002generic} proposed Generic Fourier descriptor which is acquired by applying a 2D Fourier transform on a polar-raster sampled image
@@
     \subsection{Quasi-conformal mapping and Beltrami equation}
-        Let $f: \Omega \subset \C \rightarrow \C$ be a complex function. The following differential operators are more convenient for discussion
-        \begin{equation*}
-            \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
-        \end{equation*}
-
-        $f$ is said to be \textit{quasi-conformal} associated to $\mu$ if it oriention-preserving and satisfies the following \textit{Beltrami equation}:
+        % Let $f: \Omega \subset \C \rightarrow \C$ be .
+        % The following differential operators are more convenient for discussion
+        % \begin{equation*}
+        %     \frac{\partial}{\partial z} := \frac{1}{2}(\Part{}{x} - i \Part{}{y}), \Part{}{\overline{z}}:= \frac{1}{2}(\Part{}{x}+i \Part{}{y})
+        % \end{equation*}
+        A complex function $f: \Omega \subset \C \rightarrow \C$ is said to be \textit{quasi-conformal} associated to $\mu$ if $f$ is orientation-preserving and satisfies the following \textit{Beltrami equation}:
         \begin{equation}\label{beltrami eq}
@@
         \end{equation}
-        where $\mu(z)$ is some complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$.
+        where $\mu(z)$ is a complex-valued Lebesgue measurable function satisfying $\norm{\mu}_\infty < 1$.
 More specifically, this $\mu: \Omega \rightarrow \D$ is called the \textit{Beltrami coefficient} of $f$
-        \begin{equation}
+        \begin{equation}\label{mu def}
             \mu = \frac{f_{\overline{z}}}{f_{z}}
         \end{equation}
-        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$; the resulting metric is given by:
+
+        In terms of the metric tensor, consider the effect of the pullback under $f$ of the Euclidean metric $ds^2_E$, the resulting metric is given by:
         \begin{equation}
@@
         which, relative to the background Euclidean metric $dz$ and $d\overline{z}$, has eigenvalue $(1+\abs{\mu})^2 \abs{\Part{f}{z}}^2$ and $(1-\abs{\mu})^2 \abs{\Part{f}{z}}^2$.
-$\mu$ is call the \textit{Beltrami coefficient}, which is a measure of nonconformality.
-In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$.
-Infinitesimally, around a point $p$, $f$ may be expressed with respect to its local parameters as follows:
+
+        Therefore, inside the local parameter domain around some point $p$, $f$ can be considered as a map composed of a translation to $f(p)$ together with the multiplication of a stretch map $S(z) = z + \mu(p)\overline{z}$ and conformal function $f_z(p)$, which may be expressed as follows:
         \begin{equation}\label{local f}
-            f(z) = f(p)+f_z(p)(z+\mu(p)\overline{z}).
-        \end{equation}
-
-        If $\mu(z)=0$ everywhere, then $f$ us called \textit{conformal} or \textit{holomorphic}. A conformal map satisfies the following well-known Cauchy-Riemann equation:
-        \begin{equation}\label{cr eq}
-            \Part{f}{\overline{z}} = 0.
-        \end{equation}
-        Inside the local parameter domain, $f$ may be considered as a map composed of a translation to $f(p)$ together with a stretch map $S(z) = z + \mu(p)\overline{z}$, which is postcomposed by multiplication of $f_z(p)$, which is conformal.
-All the conformal distortion of $S(z)$ is caused by $\mu(p)$.
-$S(z)$ is the map that causes $f$ to map a small circle to a small ellipse.
-Form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well.
+            f(z) =  f(p)+S(z)f_z(p) = f(p)+(z+\mu(p)\overline{z})f_z(p).
+        \end{equation}
+        $S(z)$ makes $f$ map a small circle to a small ellipse and all the conformal distortion of $f$ is caused by $\mu$.
+To form $\mu(p)$, we can determine the angles of the directions of maximal magnification and shrinkage and the amount of them as well.
 Specially, the angle of maximal magnification is $\arg(\mu(p))/2$ with magnifying factor $1+\abs{\mu(p)}$; the angle of maximal shrinkage is the orthogonal angle $\arg(\mu(p))/2 - \pi/2$ with shrinkage factor $1-\abs{\mu(p)}$.
@@
         \end{equation}
-        Thus, the Beltrami coefficient $\mu$ gives us important information about the properties of the map (see Fig. \ref{fig3}).
+        Thus, the Beltrami coefficient $\mu$ gives us important information about the properties of the map (see figure \ref{fig3}) and $\mu$ is a measure of non-conformality.
+In particular, the map $f$ is conformal around a small neighborhood of $p$ when $\mu(p)=0$ and if $\mu(z)=0$ everywhere on $\Omega$, $f$ us called \textit{conformal} or \textit{holomorphic} on $\Omega$.
 
@@
 
-        Note that there is a one-to-one correspondence between the quasi-conformal mapping f and its Beltrami coefficient $\mu$.
-Given $f$, there exists a Beltrami coefficient $\mu$ satisfying the Beltrami equation.
+        Note that there is a one-to-one correspondence between the quasi-conformal mapping $f$ and its Beltrami coefficient $\mu$.
+Given $f$, there exists a Beltrami coefficient $\mu$ satisfying the Beltrami equation by equation (\ref{mu def}).
 Conversely, the following theorem states that given an admissible Beltrami coefficient $\mu$, there always exists an quasi-conformal mapping $f$ associating with this $\mu$.
@@
         \begin{theorem}[Measurable Riemannian Mapping Theorem]\label{Measurable Riemannian Mapping Theorem}
-            Suppose $\mu : \C \rightarrow \C$ is Lebesgue measurable satisfying $\abs{\mu}_\infty <1$; then, there exists a quasi-conformal homeomorphism $f$ from $\C$ onto itself, which is in the Sobolev space $W_{1,2}(\C)$ and satisfies the Beltrami equation in the distribution sense.
+            Suppose $\mu : \C \rightarrow \C$ is Lebesgue measurable satisfying $\norm{\mu}_\infty <1$; then, there exists a quasi-conformal homeomorphism $f$ from $\C$ onto itself, which is in the Sobolev space $W_{1,2}(\C)$ and satisfies the Beltrami equation in the distribution sense.
 The associated quasi-conformal homeomorphism $f$ is unique up to a Mobi\"us transformation.
@@
     \subsection{Conformal welding}\label{welding}
-        Given 2D bounded simply-connected shape, we can treat it as a boundary simply-connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal function $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
+        Given a 2D bounded simply-connected shape, we can treat it as a 2D bounded simply-connected domain $\Omega \subset \C$, by Riemann mapping theorem, there exist conformal functions $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$.
 $\Phi_1$ and $\Phi_2$ are unique up to a \textit{Mobi\"us transformation}:
@@
         \end{equation}
-        Such $f: \partial \D \rightarrow \partial \D$ is a diffeomorphism from $\partial \D$ to itself, which can be also thought as a periodic, real-valued monotone increasing function $f_\R: [0, 2\pi) \rightarrow [0, 2\pi)$ such that $f(e^{i \theta}) = e^{i f_\R(\theta)}$ (see Fig.
-\ref{fig1}).
-
-        However, such welding mappings are not unique because of the arbitrariness of Riemann mappings, as shown in Fig. \ref{unsatble}.
+        Such $f: \partial \D \rightarrow \partial \D$ is a diffeomorphism from $\partial \D$ to itself, which can be also thought as a periodic real-valued monotone increasing function $f_\R: [0, 2\pi) \rightarrow [0, 2\pi)$ such that $f(e^{i \theta}) = e^{i f_\R(\theta)}$ (see figure \ref{fig1}).
+
+        However, such welding mappings are not unique because of the arbitrariness of Riemann mappings, as shown in figure \ref{unsatble}.
 
@@
         \end{equation}
-        where $z = x + iy$, $x$, $y$ is the real and imaginary value.
-
-        Chen \etal prove following theorem in \cite{chen2010compositions}, which tells us that the composition of harmonic mappings and other mappings can inherit such harmonicity in some condition.
+        where $z = x + iy$, $\bar{z} = x -iy$.
+
+        Chen \etal \cite{chen2010compositions} proved following theorem, which tells us in what condition the composition of harmonic mappings and other mappings can inherit the harmonicity.
         \begin{theorem}\label{composition of harmonic}
@@
 
-        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress of find a harmonic function from the given domain and continuous boundary value is call \textit{Dirichlet problem}.
-For a special case, where the domain is unit disk on complex plane, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continuous $f$ on $\partial \D$
+        The harmonic function on a compact set is determined by its restriction to the boundary, which follows from the maximum principle, and the progress to find a harmonic function from the given domain and the value in domain's boundary is call \textit{Dirichlet problem}.
+For a special case, where the domain is unit disk, \textit{Poisson integral} shows a method to obtain the solution $H : \overline{\D} \rightarrow \C$ of Dirichlet problem from a continuous $f$ on $\partial \D$
             \begin{equation}\label{poisson integral}
@@
             \end{equation}
-        Such $H$ is harmonic on $\D$ and continuous on $\overline{\D}$ and have the same value with $f$ on the $\partial \D$, i.e.
-$H(e^{i\theta}) = f(e^{i\theta})$ (see Fig.
-\ref{harmonic}).
-Of course, this $H$ is unique.
+        Such $H$ is harmonic on $\D$ and continuous on $\overline{\D}$ and has the same value with $f$ on the $\partial \D$, i.e.
+$H(e^{i\theta}) = f(e^{i\theta})$ (see figure \ref{harmonic}).
+Of course, it is uniquely determined by $f$.
 
@@
             \caption{(a) Continuous function $f(e^{i \theta}) = \sin(10 \theta) + \cos(10 \theta)$ defined on $\partial \D$; (b) The corresponding harmonic function $H$ generated from $f$ by the equation (\ref{poisson integral}).
-Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience of demonstration.}
+Note that we used real-valued function to illustrate the progress of harmonic extension for the convenience, but it is also feasible for complex-valued function.}
             \label{harmonic}
@@
 \section{Harmonic Beltrami signature (HBS)}\label{main}
-In this chapter, we describe our proposed shape signature, called the {\it Harmonic Beltrami signature (HBS)}, to represent a simply-connected domain $\Omega$.
+In this chapter, we describe our proposed shape signature, called the {\it Harmonic Beltrami signature (HBS)}, to represent a 2D bounded simply-connected domain $\Omega$.
 The space of HBS inherits a natural metric, so that geometric distance between two shapes can be easily measured.
@@
 
-Note that the HBS is not unique without suitable normalizations of the conformal mappings.
+Note that the HBS is not unique without suitable normalization.
 According to Riemann mapping theorem, the conformal mappings $\Phi_1: \D \rightarrow \Omega$ and $\Phi_2: \D^c \rightarrow \Omega^c$ are not unique.
-Suppose $\tilde{\Phi}_1: \D \rightarrow \Omega$, $\tilde{\Phi}_2: \D^c \rightarrow \Omega^c$ are also conformal and $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobi\"us transformations.
-Therefore, the corresponding conformal welding is
+Suppose $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_1, M_2$ are Mobi\"us transformations, the corresponding conformal welding is
 \begin{equation}\label{tilde f}
@@
 
-In this work, we consider the quotient space of HBS $\mathcal{B} = \{B:\mathbb{D}\to \mathbb{D}:B \text{ is a HBS} \} \,/ \sim$ to study the space of bounded simply-connected shapes.
-The following theorem illustrates that $\mathcal{B}$ is indeed an effective representation for the space of shapes.
+In this work, we consider the quotient space of HBS $\mathcal{B} = \{B:\mathbb{D}\to \mathbb{D}:B \text{ is a HBS} \} \,/ \sim$ to study the quotient space of shapes $\mathcal{S} = \{\Omega \subset \C : \Omega \text{ is bounded simply-connected}\} \, / \approx$, where $\Omega \approx \bar{\Omega}$ iff $\bar{\Omega} = F(\Omega)$ and $F$ is composed of translation, rotation and scaling.
+The following theorem illustrates that HBS is indeed an effective representation.
 
@@
 \begin{proof}
-Given $\Omega$, there exist a unique $[B]\in \mathcal{B}$ corresponding to $\Omega$ follows from the definition of equivalence class of HBS.
-Conversely, let $[B]\in \mathcal{B}$.
+Given $\Omega$, there exists a unique $[B]\in \mathcal{B}$ corresponding to $\Omega$ by the definition of equivalence class of HBS.
+Conversely, let $[B]\in \mathcal{B}$ and $B$ is a HBS in $[B]$.
 Define $\mu:\mathbb{C}\to \mathbb{C}$ as
@@
 In other words, if $G_1$ and $G_2$ are two quasiconformal maps satisfying the above requirement, then $G_2=M\circ G_1$, where $M$ is a Mobi\"us transformation.
-In particular, $G$ is uniquely determined if we fix $0, 1$ and $\infty$.
-Let $\Omega = G(\mathbb{D})$.
-We claim that the HBS of $\Omega$ is $B$.
+Let $\Omega = G(\mathbb{D})$, we claim that the HBS of $\Omega$ is $B$.
 To see this, let $\Phi_1: \mathbb{D}\to \Omega$ be the conformal parameterization of $\Omega$.
@@
 Now, $\Omega$ is determined up to a Mobi\"us transformation $M=\frac{az+b}{cz+d}$.
-If $G(\infty) = \infty$, then $M$ is of the form: $M = az+b= re^{i\theta}z +b$, $r\in \mathbb{R}^+$, $\theta \in [0,2\pi)$ and $b\in \mathbb{C}$.
+If $G(\infty) = \infty$, $M$ is in the form: $M = az+b= re^{i\theta}z +b$, $r\in \mathbb{R}^+$, $\theta \in [0,2\pi)$ and $b\in \mathbb{C}$.
 Hence, $\Omega$ is uniquely determined up to a scaling, rotation and translation, which are reflected by $r, \theta$ and $b$ respectively.
 
-Suppose $B_1, B_2 \in [B]$ are two different HBS, we want to demonstrate that their reconstructed domain $\Omega_1$ and $\Omega_2$ are the same up to scaling, rotation and translation.
+Suppose $B_1, B_2 \in [B]$ are two different HBS, we want to demonstrate that their reconstructed domains $\Omega_1$ and $\Omega_2$ are the same up to scaling, rotation and translation.
 By definition, their corresponding conformal welding $f_1, f_2$ satisfy $f_2 = M_1^{-1} \circ f_1 \circ M_2$.
@@
 \end{equation}
-is just $\mu$ in equation (\ref{reconstructionmu}), so $\Omega_1 = T_1 \circ G_1(\D) = T_1 \circ \Phi_1 \circ H_1 (\D)$, where $T_1$ is any composition of scaling, rotation and translation.
+is just $\mu$ in equation (\ref{reconstructionmu}), so $\Omega_1 = T_1 \circ G_1(\D) = T_1 \circ \Phi_1 \circ H_1 (\D)$, where $T_1$ is a composition of scaling, rotation and translation.
 Note that $H_1$ maps unit disk to unit disk, we have $\Omega_1 = T_1 \circ \Phi_1 (\D)$.
@@
 \end{equation}
-the reconstructed domain of $B_2$ is $\Omega_2 = T_2 \circ G_2(\D) = T_2 \circ \Phi_1 \circ M_1 \circ H_2(\D)$, where $T_2$ is also a composition of scaling, rotation and translation.
+the reconstructed domain of $B_2$ is $\Omega_2 = T_2 \circ G_2(\D) = T_2 \circ \Phi_1 \circ M_1 \circ H_2(\D)$, where $T_2$ is also composed of scaling, rotation and translation.
 Since $M_1(\D) = H_2(\D) = \D$, $\Omega_2$ can be represented as $\Omega_2 = T_2 \circ \Phi_1(\D)$.
-Therefore, $\Omega_1 = T_1 \circ T_2^{-1} (\Omega_2)$, which shows that the reconstructed shape is invariant (up to a scaling, rotation and translation) regardless of the selection of HBS.
+Therefore, $\Omega_1= T_1 \circ T_2^{-1} (\Omega_2)$, which shows that the reconstructed shape is invariant (up to a scaling, rotation and translation) regardless of the selection of HBS in given $[B]$.
 \end{proof}
@@
 If we fix $G$ at $\infty$, the associated shape $\Omega = G(\mathbb{D})$ is uniquely determined up to a rotation, translation and scaling.
-The associated quasiconformal map can be solved by some computational methods developed earlier \cite{lui2013texture,lui2012optimization}}
+The associated quasiconformal map can be solved by some computational methods developed earlier \cite{lui2013texture,lui2012optimization,choi2020shape}}
 
@@
         \caption{Illustration of Harmonic Beltrami signature.
-(a) The input shape, a dolphin; (b) The corresponding harmonic extension, where the conformal welding is shown in Fig \ref{fig1} (b); (c) The Harmonic Beltrami signature of (a).
+(a) The input shape, a dolphin; (b) The corresponding harmonic extension, where the conformal welding is shown in figure \ref{fig1} (b); (c) The Harmonic Beltrami signature of (a).
 Remark that the harmonic function and Harmonic Beltrami signature should be complex-valued function and we only show modulus of them in z-axis in (b) and (c).}
@@
 \subsection{Unique representative of $[B]$}
-               As discussed, every shape can be represented by its associated HBS, which is an equivalence class.
+    As discussed, every shape can be represented by its associated equivalence class of HBS.
 In order to measure the geometric difference between shapes based on HBS, it is necessary to find a unique representative in the equivalence class $[B]$.
@@
 
-            Let $B_1$ and $B_2$ be two harmonic Beltrami signatures in the same equivalence class $[B]$ in $\mathcal{B}$.
-Suppose $B_1$ is computed by conformal parameterizations $\Phi_1^1:\mathbb{D}\to \Omega$ and $\Phi_2^1:\mathbb{D}^c\to \Omega^c$.
-Similarly, suppose $B_2$ is computed by conformal parameterizations $\Phi_1^2:\mathbb{D}\to \Omega$ and $\Phi_2^2:\mathbb{D}^c\to \Omega^c$.
-
-            We proceed to investigate the relationship between $B_1$ and $B_2$. In order to proceed, the following theorem is needed.
-
-            \begin{theorem}
+    In order to proceed to investigate the relationship between $B_1$ and $B_2$, the following theorem is needed.
+
+    \begin{theorem}\label{rotation keep f}
         Suppose $f$ and $\tilde{f}$ are continuous map from $\mathbb{S}^1$ to itself and $\tilde{f} = M_1^{-1} \circ f \circ M_2$, where $M_1, M_2$ are both Mobious transformations.
@@
 
-                $\Rightarrow :$ When $\tilde{H} = M_1^{-1} \circ H \circ M_2$, from Theorem \ref{composition of harmonic} we can know that $H \circ M_2$ is harmonic since there is no doubt that Mobious transformation $M_2$ is conformal.
-$\tilde{H}$ and $H \circ M_2$ are both harmonic, so $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
+        $\Rightarrow :$ From theorem \ref{composition of harmonic}, we know that $H \circ M_2$ is harmonic since there is no doubt that $M_2$ is conformal.
+Since $\tilde{H} = M_1^{-1} \circ H \circ M_2$ and $H \circ M_2$ are both harmonic, $M_1^{-1}$ can be represented as $M_1^{-1}(z) = az + b \overline{z} + c$, where $a, b, c \in \C$.
 Therefore, we have
@@
 
-                $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ H \circ M_2$ is a harmonic function according to Theorem \ref{composition of harmonic}.
+        $\Leftarrow :$ When $M_1$ is a rotation, $M_1^{-1}$ is also a rotation, so $M_1^{-1} \circ H \circ M_2$ is a harmonic function according to theorem \ref{composition of harmonic}.
 It's easy to check that
-                \begin{align*}
+        \begin{equation*}
             M_1^{-1} \circ H \circ M_2 (e^{i \theta})
-                    &= M_1^{-1} \circ f \circ M_2(e^{i \theta})\\
-                    &= \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
-                \end{align*}
+            = M_1^{-1} \circ f \circ M_2(e^{i \theta})
+            = \tilde{f}(e^{i \theta}) = \tilde{H} (e^{i \theta}),
+        \end{equation*}
         which means $M_1^{-1} \circ H \circ M_2$ and $\tilde{H}$ have the same boundary value. From the uniqueness of harmonic mapping, $M_1^{-1} \circ H \circ M_2 = \tilde{H}$.
@@
 
-    Note that if $M_1$ is not only a rotation, $\tilde{f}$ and $\tilde{H}$ also exist but $\tilde{H} = M_1^{-1} \circ H \circ M_2$ doesn't hold, as shown in Fig. \ref{harmonic extension not rotation}.
+    Note that if $M_1$ is not only a rotation, $\tilde{f}$ and $\tilde{H}$ also exist but $\tilde{H} \neq M_1^{-1} \circ H \circ M_2$, as shown in figure \ref{harmonic extension not rotation}.
 
@@
         \caption{Let $f(e^{i \theta}) = \sin(10 \theta) + \cos(10 \theta)+1.5$, $M_1(z) = e^{i \tau}\cfrac{z-p}{1-\overline{p}z}$, where $p=0.6+0.6i$, $\tau = 0.8$.
-The image of $f$ and its harmonic extension $H$ are shown in Fig.
-\ref{harmonic}.
+The image of $f$ and its harmonic extension $H$ are shown in figure \ref{harmonic}.
 (a) $\tilde{f} = M_1 \circ f$; (b) harmonic extension $\tilde{H}$ of $\tilde{f}$; (c) $H' = M_1 \circ H$; (d) $H' - \tilde{H}$, and it's clear that $M_1 \circ H \neq \tilde{H}$ except on the boundary.}
@@
 
+    Let $B_1$ and $B_2$ be two harmonic Beltrami signatures in the same equivalence class $[B]$ and $B_k$ is computed by conformal parameterizations $\Phi_1^k:\mathbb{D}\to \Omega$ and $\Phi_2^k:\mathbb{D}^c\to \Omega^c$, where $k=1,2$.
 Now, we have the following theorem about the relationship between $B_1$ and $B_2$.
 
-            \begin{theorem}
-                Suppose $\Phi_j^1$ and $\Phi_j^2$ are the same up to a rotation for $j=1,2$.
-That is, $\Phi_1^2 = \Phi_1^1\circ M_1$ and $\Phi_2^2 = \Phi_2^1\circ M_2$, where $M_1(z) = e^{i\theta_1}z$ and $M_2(z) = e^{i\theta_2}z$.
-Then:
-                \[
+    \begin{theorem}\label{b1 b2 relationship}
+        Suppose $B_k$ and $\Phi_j^k$ are defined as above for $j = 1, 2$ and $k=1,2$. If $\Phi_j^2 = \Phi_j^1\circ M_j$ where $M_j(z) = e^{i\theta_j}z$, then:
+        \begin{equation}
           B_2(z) = e^{-2i\theta_2} B_1(e^{i\theta_2}z)  
-                \]
+        \end{equation}
     \end{theorem}
+
     \begin{proof}
@@
         \noindent where $f_1 = {\Phi_1^1}^{-1}\circ \Phi_2^1$ and $f_2 = {\Phi_1^2}^{-1}\circ \Phi_2^2$.
-Let $H_1$ and $H_2$ be the harmonic extensions of $B_1$ and $B_2$ respectively.
-According to Theorem 4, we have:
+Let $H_1$ and $H_2$ be the harmonic extensions of $f_1$ and $f_2$ respectively.
+According to theorem \ref{rotation keep f}, we have:
         \[
-                H_2 = M_1^{-1}\circ H_1 \circ M_2,
+        H_2 = M_1^{-1}\circ H_1 \circ M_2.
         \]
-                Since $M_1$ is a Mobi\"us transformation and thus conformal, we have $B_2 = \mu_{H_2} = \mu_{H_1\circ M_2}$. Using Equation \ref{mu of conformal composition}, we obtain:
-                \begin{equation*}
-                    \begin{split}
-                B_2(z) = \mu_{H_1\circ M_2}(z) &= \frac{\bar{M_2}}{M_2} \mu_{H_1}\circ M_2(z) \\
-                &= e^{i\theta_2} B_1( e^{i\theta_2} z).
-                \end{split}
-                \end{equation*}
-
+        Since $M_1$ is a Mobi\"us transformation and thus conformal, we have $B_2 = \mu_{H_2} = \mu_{H_1\circ M_2}$. Using equation (\ref{mu of composition}), we obtain:
+        \begin{equation*}
+        B_2(z) = \mu_{H_1\circ M_2}(z) = \frac{\bar{M_2}}{M_2} \mu_{H_1}\circ M_2(z) = e^{-2i\theta_2} B_1( e^{i\theta_2} z).
+        \end{equation*}
     \end{proof}
 
-            The above theorem tells us the relationship between $B_1$ and $B_2$ if $\Phi_j^1$ and $\Phi_j^2$ are unique up to a rotation for $j=1, 2$.
-In this work, we will assume $\Phi_j^1$ and $\Phi_j^2$ are unique up to a rotation.
-
-            With further normalization on the Harmonic Beltrami signature, we can obtain a unique representation in $[B]$.
+    When $\Phi_j^1$ and $\Phi_j^2$ are unique up to a rotation for $j=1, 2$, the relationship between $B_1$ and $B_2$ is shown in the above theorem.
+And with further normalization on the HBS, we can obtain a unique representative of $[B]$.
 
@@
 If $M_1$ and $M_2$ are both rotation and
-        \begin{equation}\label{arg integral B is 0}
-            \arg \int_\D B(z) dz = \arg \int_\D \tilde{B}(z)dz = 0,
-        \end{equation}
+        \begin{gather}
+                \arg \int_\D B(z) dz = \arg \int_\D \tilde{B}(z)dz = 0,\label{arg integral B is 0}\\
+                \arg \int_\D \frac{B(z)}{z} dz = \arg \int_\D \frac{\tilde{B}(z)}{z}dz \in [0, \pi),\label{arg in 0 and pi}
+        \end{gather}
         then we have $\tilde{B} = B$.
@@
     \begin{proof}
-        When $M_1$ is rotation, the conformal arbitrary of conformal welding can be delivered to their harmonic extensions and
-        $\tilde{H} = M_1^{-1} \circ H \circ M_2$. Remark $r e^{i \tau} = \int_\D B(z) dz$ and $M_2(z) = e^{i \theta}z$, then the $\tilde{B}$ can be displayed in the form of
-        \begin{equation}
-        \tilde{B}(z) = \mu_{H \circ M_2}(z) = e^{-2i\theta} \mu_H \circ M_2(z) = e^{-2 i \theta} B(e^{i\theta} z).
-        \end{equation}
-        Therefore, we have
-        \begin{eqnarray}
-            \int_B \tilde{B}(z) dz
-            &=& \int_D e^{-2i\theta} B(e^{i\theta} z) dz \nonumber \\
-            &=& e^{-2i\theta} \int_D B(z) dz \nonumber \\
-            &=& r e^{i(\tau-2\theta)}.
-        \end{eqnarray}
-        If equation (\ref{arg integral B is 0}) holds,
-        \begin{equation*}
-            \tau = \tau-2\theta  = 0,
-        \end{equation*}
-        hence $\theta = 0$, $M_2$ is identity and so $\tilde{B} = \mu_H = B$.
+        According to theorem \ref{b1 b2 relationship}, the $\tilde{B}$ can be displayed in the form of
+        \begin{equation*}
+        \tilde{B}(z) = e^{-2 i \theta} B(e^{i\theta} z),
+        \end{equation*}
+        when $M_1, M_2$ are rotations and $M_2(z) = e^{i \theta} z$. Suppose $\int_\D B(z) dz = r e^{i \tau}$, the integral of $\tilde{B}$ on $\D$ can be written as
+        \begin{equation}
+            \int_\D \tilde{B}(z) dz
+            = \int_\D e^{-2i\theta} B(e^{i\theta} z) dz
+            = e^{-2i\theta} \int_\D B(z) dz
+            = r e^{i(\tau-2\theta)}.
+        \end{equation}
+        If equation (\ref{arg integral B is 0}) holds, we have
+        \begin{equation*}
+            \tau = \tau-2\theta  = 2k\pi ,k \in \Z,
+        \end{equation*}
+        hence $\theta = k \pi$ and so $\tilde{B}(z) = B(z)$ or $\tilde{B}(z) = B(-z)$. Suppose $\tilde{B}(z) = B(-z)$, then
+        \begin{equation*}
+            \arg  \int_\D \frac{\tilde{B}(z)}{z} dz 
+            = \arg \left(- \int_\D \frac{B(z)}{z} dz \right)
+            = \arg \int_\D \frac{B(z)}{z} dz + \pi,
+        \end{equation*}
+        which can not satisfy (\ref{arg in 0 and pi}), so we must have $\tilde{B} = B$.
     \end{proof}
 
-    Note that the unique representative $B$ of $[B]$ can be easily generated from any HBS $B_0 = \mu_{H_0} \in [B]$. If $r e^{i\tau_0} =\int_\D B_0(z) dz$ and $\tau_0 \neq 0$, then
+    \bigskip
+
+    \noindent {\it Remark:}
+    {\it Note that the unique representative of $[B]$ can be easily generated from any HBS $B_0 = \mu_{H_0} \in [B]$ when $M_1$ and $M_2$ are rotations.
+Suppose $\arg \int_\D B_0(z) dz = \tau_0$, $\tau_0 \neq 0$ and $\arg \int_\D B_0(z)/z dz = \tau_1$, then
     \begin{equation}\label{normaled B}
-        B(z) = e^{-i\tau_0}B_0(e^{i\frac{\tau_0}{2}}z)
-    \end{equation}
-    is just the desired representative since $B = \mu_{H_0 \circ M_0}$  and
-    \begin{equation}
-        \arg \int_\D B(z) dz = \arg \left( e^{-i\tau_0} \int_\D B_0(e^{i\frac{\tau_0}{2}}z)dz \right) = \arg \left( e^{-i\tau_0} \cdot r e^{i\tau_0} \right) = 0,
-    \end{equation}
-    where $M_0(z) = e^{i \frac{\tau}{2}} z$. Therefore, if we want to find a unique $B$, some pre- and post-normalizations to $M_1$ and $M_2$ are required.
+        B(z) = \begin{cases}
+            e^{-i\tau_0}B_0(e^{i\frac{\tau_0}{2}}z), \text{ if } \tau_1 - \frac{\tau_0}{2} \in [0, \pi),\\
+            e^{-i\tau_0}B_0(-e^{i\frac{\tau_0}{2}}z), \text{ if } \tau_1 - \frac{\tau_0}{2} \in [\pi, 2\pi),
+            \end{cases}
+    \end{equation}
+    is just the desired representative since
+    \begin{gather*}
+        \arg \int_\D B(z) dz = \arg \left( e^{-i\tau_0} \int_\D B_0(\pm e^{i\frac{\tau_0}{2}}z)dz \right) = \tau_0-\tau_0 = 0,
+        % \arg \int_\D \frac{B(z)}{z} dz = 
+        % \begin{cases}
+        % \arg \left( e^{-i\frac{\tau_0}{2}} \int_\D \frac{B_0(e^{i\frac{\tau_0}{2}}z)}{e^{i\frac{\tau_0}{2}}z}dz \right) = \tau_1 - \frac{\tau_0}{2} \in [0, \pi), \text{ if } \tau_1 - \frac{\tau_0}{2} \in [0, \pi),\\
+        % \arg \left(-e^{-i\frac{\tau_0}{2}} \int_\D \frac{B_0(-e^{i\frac{\tau_0}{2}}z)}{-e^{i\frac{\tau_0}{2}}z}dz \right) = \tau_1 - \frac{\tau_0}{2}  - \pi \in [0, \pi), \text{ if } \tau_1 - \frac{\tau_0}{2} \in [\pi, 2\pi).
+        % \end{cases}
+    \end{gather*}
+    for $\tau_1 - \frac{\tau_0}{2} \in [0, \pi)$
+    \begin{gather*}
+        \arg \int_\D \frac{B(z)}{z} dz = \arg \left( e^{-i\frac{\tau_0}{2}} \int_\D \frac{B_0(e^{i\frac{\tau_0}{2}}z)}{e^{i\frac{\tau_0}{2}}z}dz \right) = \tau_1 - \frac{\tau_0}{2} \in [0, \pi),
+    \end{gather*}
+    and for $\tau_1 - \frac{\tau_0}{2} \in [\pi, 2\pi)$
+    \begin{gather*}
+        \arg \int_\D \frac{B(z)}{z} dz = \arg \left(-e^{-i\frac{\tau_0}{2}} \int_\D \frac{B_0(-e^{i\frac{\tau_0}{2}}z)}{-e^{i\frac{\tau_0}{2}}z}dz \right) = \tau_1 - \frac{\tau_0}{2}  - \pi \in [0, \pi).
+    \end{gather*}
+    Therefore, the only difficulty on the way to the unique representative $B$ of $[B]$ is how to normalize $M_1$ and $M_2$ to be rotations.
+    }
 
     \subsection{Normalization to $M_1$}\label{norm_to_m1}
-To obtain a unique representative in $[B]$, we assume both $M_1$ and $M_2$ is a rotation. In this subsection, we discuss how to normalize $M_1$.
-
     Suppose $\Phi_1:\mathbb{D}\to \Omega$ be the conformal parameterization of $\Omega$.
 We proceed to normalize $\Phi_1$ so that $M_1$ is a rotation.
-One possible way is to achieve restrict $\Phi_1(0) = 0$.
-But it requires the assumption that $0$ is in $\Omega$, which is equivalent to limiting the position of shape and cannot always hold.
+One possible way is to fix $\Phi_1$ on some special points, like $\Phi_1(0) = 0$.
+But it requires the assumption that these points are inside $\Omega$, which is equivalent to limiting the position of shape.
 In this work, we introduce a new approach without any additional assumption.
 
-In actual scenario, we usually only have finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$ representing the boundary of $\Omega$.
-Denote $p_i = \Phi_1^{-1}(z_i) \in \partial \D$, where $\Phi_1 : \D \rightarrow \Omega$.
-We claims that $M_1$ can be normalized by restricting the centroid of $p_i$'s to be $0$.
-That is equation \ref{norm phi1}.
-
-A natural question is the existence of a conformal parameterization that satisfies equation \ref{norm phi1}.
-To study this, we consider following problem.
-Given boundary points $p_i$ on unit circle, can we find a Mobi\"us transformation $M$ satisfies the following equation (\ref{fz})?
-
-    \begin{equation}\label{fz}
-        \sum_{k=1}^n M(p_k) = \sum_{k=1}^n e^{i\theta} \frac{p_k - a}{1 - \overline{a}p_k}= 0
-    \end{equation}
-
-    Without lose of generality, we ignore the rotational component of $M$ and let $ M = F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$. We proceed to find $a \in \D$ such that
+    In practical application, we usually use finite boundary points $z_1, z_2, \cdots, z_n \in \partial \Omega$ to represent $\Omega$.
+Denote $p_k = \Phi_1^{-1}(z_k) \in \partial \D$ for $k=1,\cdots,n$, we claims that $M_1$ can be normalized by restricting the arithmetic mean of $p_k$ to be $0$, that is
+    \begin{equation}\label{norm phi1}
+        \sum^n_{k=1} \Phi_1^{-1}(z_k) = \sum_{k=1}^n p_k = 0.
+    \end{equation}
+
+    A natural question is whether there exists a conformal parameterization $\Phi_1$ satisfying equation (\ref{norm phi1}).
+Actually, the existence is equivalent to that given boundary points $p_k$ on unit circle, there is a Mobi\"us transformation $M$ such that $\sum_{k=1}^n M(p_k) = 0$.
+Without lose of generality, we ignore the rotational component of $M$ and let $M = F_a(z) = \frac{z - a}{1 - \overline{a}z}$, where $a \in \D$.
+We proceed to solve
     \begin{equation}\label{eq}
@@
     \end{equation}
-    Figure \ref{fasolvable}) shows some graphs of $|f(a)|$ corresponding to various boundary points, illustrating the uniqueness of the solution to equation (\ref{eq}).
 
@@
 
-    According to Brouwer fixed point theorem, the existence of the solution to equation (\ref{eq}) can be shown.
+    Figure \ref{fasolvable} shows some graphs of $|f(a)|$ corresponding to various boundary points and illustrates equation (\ref{eq}) may be solvable.
+And with the help of Brouwer fixed point theorem, the existence of the solution to equation (\ref{eq}) can be achieved.
 
@@
         \end{equation*}
-        such $g$ is defined on $\overline{\D}$ and is continuous. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.
-
-        Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, then define
+        such $g$ is continuous on $\overline{\D}$. It's clear that $\norm{g(a)} \le \frac{1}{n} \norm{f(a)} + \norm{a} \le 2$.
+
+        Let $M = \{a \in \D ~|~ \norm{g(a)} \ge 1 \}$, we define
         \begin{equation*}
@@
         \end{equation*}
-        $h$ is a continuous map from $\overline{\D}$ to itself, so there exists some $a$ let $h(a) = a$.
-
-        If $a \in \partial \D$, $\norm{a} = 1$, but $\norm{h(a)} = 0 \neq \norm{a}$.
+        Since $h$ is a continuous map from $\overline{\D}$ to itself, there exists some $a \in \overline{\D}$ such that $h(a) = a$.
+
+        If $a \in \partial \D$, $\norm{a} = 1$ but $\norm{h(a)} = 0 \neq \norm{a}$.
 If $a \in M$, we know $a \notin \partial \D$, so $\norm{a} < 1$, but $\norm{h(a)} = \frac{\norm{g(a)}}{\norm{g(a)}} = 1 \neq \norm{a}$.
-So when $h(a) = a$, $a$ is inside $\D \setminus M$.
-Therefore, such $a$ satisfies $g(a) = a$ and then $f(a) = 0$.
+So there exists $a \in \D \setminus M$ such that
+        \begin{equation*}
+            h(a) = g(a) = \frac{1}{n}f(a) + a = a,
+        \end{equation*}
+        which means $f(a) = 0$.
     \end{proof}
 
-    Therefore, there must be some $a \in \D$ to be the solution of equation (\ref{fz}).
-
-    The uniqueness of the solution to equation (\ref{eq}) can also be studied. Firstly, we consider a special case when $\sum_{k=1}^n p_k = 0$, we have
+    The uniqueness of the solution of equation (\ref{eq}) is another thing we concern. Firstly, we consider a special case.
 
@@
 
-        If $a \neq 0$, WLOG, we can assume that $0 < a < 1$, then $F_a(1) = 1$ and $F_a(-1) = -1$.
-For any $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$,
+        If $a \neq 0$, WLOG, we can assume that $\arg(a) = 0$ and $0 < a < 1$.
+We have $F_a(1) = 1$ and $F_a(-1) = -1$.
+As for $p_k \neq \pm 1$, there is some $\theta_k \in (0, \pi) \cup (\pi, 2\pi)$ such that $p_k = \cos \theta_k + \sin \theta_k i$ and
         \begin{align*}
@@
         Therefore, if $n \ge 3$, there must be at least one $p_k \neq \pm 1$ and so
-        \begin{align*}
-            &\Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) \\
-            < &\sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
-        \end{align*}
-        which means $\sum_{k=1}^n F_a(p_k) \neq 0$. So $a=0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
+        \begin{equation*}
+            \Re(\sum_{k=1}^n F_a(p_k)) = \sum_{k=1}^n \Re(F_a(p_k)) < \sum_{k=1}^n \Re(p_k) = \Re(\sum_{k=1}^n p_k)  = 0,
+        \end{equation*}
+        which means $\sum_{k=1}^n F_a(p_k) \neq 0$.
+Note that we can rotate all $p_k$ to get the same conclusion when $\arg(a) \neq 0$.
+So $a=0$ is the only solution of equation (\ref{eq}) when $\sum_{k=1}^n p_k = 0$.
     \end{proof}
 
-    This theorem confirms the uniqueness for a special situation $\sum_{k=1}^n p_k = 0$ and actually this conclusion is universal no matter how $p_i$ distribute.
+    This above theorem confirms the uniqueness for a special situation but actually this conclusion is universal no matter how $p_i$ distribute.
 
@@
     \begin{proof}
-        Assume that $a_0, a_1$ are two different solutions, then we have that
+        Assume that $a_0, a_1$ are two solutions, then we have that
         \begin{align*}
@@
         Let $p_k' = F_{a_0}(p_k)$, then
-        \begin{align*}
-            &\sum_{k=1}^n F_{a_1} \circ F_{a_0}^{-1} \circ F_{a_0}(p_k)\\
-            = &\sum_{k=1}^n (F_{a_1} \circ F_{-a_0})(F_{a_0}(p_k))\\
-            = &\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}}\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0.
-        \end{align*}
-
-        Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so \\
-        $\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}} p_k' = 0$.
-According to theorem \ref{uniqueness when 0}, $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, then $a_0 = a_1$, which contradicts to the assumption.
+        \begin{equation*}
+            \sum_{k=1}^n F_{a_1} (p_k)
+            = \sum_{k=1}^n (F_{a_1} \circ F_{a_0}^{-1})(F_{a_0}(p_k))
+            = \frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}}\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}}(p_k') = 0.
+        \end{equation*}
+        Since $a_0, a_1 \in \D$, then $\frac{1- a_1 \overline{a_0}}{1- a_0 \overline{a_1}} \neq 0$ and so
+        $$\sum_{k=1}^n F_{\frac{a_1-a_0}{1-a_1\overline{a_0}}}(p_k') = 0.$$
+        According to theorem \ref{uniqueness when 0}, $\frac{a_1-a_0}{1-a_1\overline{a_0}} = 0$, then $a_0 = a_1$.
     \end{proof}
 
-    With the above observations, we have the following theorem.
+    With the above observations, we can come back to the original problem about normalization $M_1$ and have the following theorem.
 
     \begin{theorem}\label{unique up to a rotation}
-        Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies
-        \begin{align}\label{norm phi1}
-            \sum_{k=1}^n \Phi_1^{-1}(z_k) = 0,
-        \end{align}
-        then such $\Phi_1$ is unique up to a rotation $M_1$.
+        Given $\{z_1, z_2, \cdots, z_n\} \subset \partial \Omega$ and $n \ge 3$, if conformal mapping $\Phi_1: \D \rightarrow \Omega$ satisfies equation (\ref{norm phi1}), then such $\Phi_1$ is unique up to a rotation $M_1$.
     \end{theorem}
@@
         Suppose $\Phi_1$ and $\tilde{\Phi}_1$ are two arbitrary conformal map from $\D$ to $\Omega$  then $\tilde{\Phi}_1 = \Phi_1 \circ M_1$, where $M_1$ is a Mobi\"us transformation.
-If $\Phi_1$, $\tilde{\Phi_1} $ satisfy equation (\ref{norm phi1}), let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M_1^{-1} (p_k) = 0$.
+If $\Phi_1$, $\tilde{\Phi}_1 $ satisfy equation (\ref{norm phi1}), let $p_k = \Phi_1^{-1}(z_k)$, then we have $\sum_{k=1}^n p_k = 0$ and $\sum_{k=1}^n M_1^{-1} (p_k) = 0$.
 $M_1^{-1}$ is also a Mobi\"us transformation so let $M_1^{-1}(z) = e^{i \theta}\frac{z - a}{1 - \overline{a} z} = e^{i \theta} F_a(z)$, then we have
@@
 
-        From theorem \ref{uniqueness when 0} we can know $a = 0$, then $M_1^{-1}(z) = e^{i \theta} z$ and $\Phi_1$ is unique up to a rotation $M_1$.
+        From theorem \ref{uniqueness when 0} we can know $a = 0$, then $M_1^{-1}(z) = e^{i \theta} z$ and $\Phi_1$ and $\tilde{\Phi}_1$ are the same up to a rotation $M_1$.
     \end{proof}
 
-    Theorem \ref{unique up to a rotation} gives a condition that leads to the uniqueness of $\Phi_1$ up to a rotation.
-
     \subsection{Normalization to $M_2$}\label{norm2}
-    As for $M_2$, we also hope it is also a rotation here, which is equivalent with that $\Phi_2$ is uniquely determined up to a rotation.
-Luckily, we always have that $\infty \in \D^c$ and $\infty \in \Omega^c$, then we can use this guarantee this uniqueness.
+    As for $M_2$, we also hope it is a rotation, which is equivalent to that $\Phi_2$ is uniquely determined up to a rotation.
+Luckily, $\infty$ is always inside $\D^c$ and $\Omega^c$, and we can use this to ensure $M_2$ to be a rotation.
 
     \begin{theorem}
-        Let $\Phi_2$ be a conformal map from $\D^c$ to $\Omega^c$ satisfying that
-        \begin{equation}
-            \Phi_2(\infty) = \infty\label{norm phi2 1}
-        \end{equation}
-        then such $\Phi_2$ is uniquely determined a rotation.
+        Let $\Phi_2$ be a conformal map from $\D^c$ to $\Omega^c$ satisfying
+        \begin{equation}
+            \Phi_2(\infty) = \infty, \label{norm phi2 1}
+        \end{equation}
+        then such $\Phi_2$ is uniquely determined up to a rotation.
     \end{theorem}
@@
     \begin{proof}
-        Let $\Phi_2$ and $\tilde{\Phi_2}$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, $\tilde{\Phi_2} = \Phi_2 \circ M_2$, where $M_2$ is Mobi\"us transformation, $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$.
-Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisfy (\ref{norm phi2 1}), then
-        \begin{align*}
-            &\tilde{\Phi}_2(\infty) = \Phi_2(M_2(\infty)) = \infty, \\
-            &\Phi_2(\infty) = \infty.
-        \end{align*}
-        Therefore, $M_2(\infty) = e^{i \theta} \frac{\infty - a}{1- \overline{a} \infty} = \infty$, which means that $a = 0$ and $M_2(z) = e^{i \theta} z$.
+        Let $\Phi_2$ and $\tilde{\Phi}_2$ be two arbitrary conformal map from $\D^c$ to $\Omega^c$, then $\tilde{\Phi}_2 = \Phi_2 \circ M_2$, where $M_2$ is Mobi\"us transformation and $M_2(z) = e^{i \theta} \frac{z - a}{1- \overline{a}z}$.
+Since $\Phi_2$ and $\tilde{\Phi}_2$ both satisfy equation (\ref{norm phi2 1}), then
+        \begin{equation*}
+            \tilde{\Phi}_2(\infty) = \Phi_2(M_2(\infty)) = \infty, \Phi_2(\infty) = \infty.
+        \end{equation*}
+        Therefore, $M_2$ maps $\infty$ to $\infty$, which means that $a = 0$ and $M_2(z) = e^{i \theta} z$.
     \end{proof}
@@
 \subsection{Invariance under simple transformation}
-    With the normalization mentioned above, we can get a unique Harmonic Beltrami signature $B$ as the representative corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$.
+    With the normalization mentioned above, we can get a unique HBS $B$ as the representative corresponding to domain $\Omega$, so we can remark $B$ as $B_\Omega$.
 Now we want to prove that if we do some simple transformation like rotation, scaling and translation to $\Omega$, the HBS is invariant.
@@
     \begin{theorem}\label{invariance theorem}
-        Given a boundary simply-connected domain $\Omega$ and transformation $T$ which is composed by rotation, scaling and transformation.
-Let $B_\Omega$ and $B_{T(\Omega)}$ be the HBS of $\Omega$ and $T(\Omega)$, then $B_\Omega = B_{T(\Omega)}$
+        Given a boundary simply-connected domain $\Omega$ and transformation $T$ composed of rotation, scaling and transformation.
+Let $B_\Omega$ and $B_{T(\Omega)}$ be the HBS of $\Omega$ and $T(\Omega)$, then $B_\Omega = B_{T(\Omega)}$.
     \end{theorem}
@@
         Suppose $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, $\tilde{\Phi}_1: \D \rightarrow T(\Omega)$ and $\tilde{\Phi}_2 : \D^c \rightarrow T(\Omega)$ are conformal.
-Since $T$ is composed by rotation, scaling and translation, $T$ can be written as $T(z) = ke^{i\theta} z + b$.
-Such $T$ is absolutely invertible and conformal.
+Since $T$ is composed of rotation, scaling and translation, $T$ can be written as $T(z) = ke^{i\theta} z + b$ and such $T$ is absolutely invertible and conformal.
 
@@
         \begin{equation*}
-            \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0.
-        \end{equation*}
-
-        Therefore
-        \begin{equation*}
             \sum_{i=1}^n \hat{\Phi}_1^{-1}(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1} \circ T(z_i) = \sum_{i=1}^n \tilde{\Phi}_1^{-1}(T(z_i)) = 0,
@@
 
-        We have the conformal welding
-        \begin{eqnarray}
+        The corresponding conformal welding of $T(\Omega)$ is
+        \begin{equation*}
             \tilde{f}
-            &=& \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 \\
-            &=& M_1^{-1} \circ \Phi_1^{-1} \circ T^{-1} \circ T \circ \Phi_2 \circ M_2 \\
-            &=& M_1^{-1} \circ f \circ M_2.
-        \end{eqnarray}
-        Then the harmonic extension $\tilde{H} = M_1^{-1} \circ H \circ M_2$ and so $B_\Omega = \mu_H$ and $B_{T(\Omega)} = \mu_{\tilde{H}}$ are both the representative of the same equivalence class.
-Therefore, $B_\Omega = B_{T(\Omega)}$ because of theorem \ref{unique B}.
+            = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2 
+            = M_1^{-1} \circ \Phi_1^{-1} \circ T^{-1} \circ T \circ \Phi_2 \circ M_2 
+            = M_1^{-1} \circ f \circ M_2,
+        \end{equation*}
+        which means $B_\Omega$ and $B_{T(\Omega)}$ are both the representative of the same equivalence class. Therefore, $B_\Omega = B_{T(\Omega)}$ because of theorem \ref{unique B}.
     \end{proof}
 
-\subsection{Geometric implication of HBS}
+\subsection{Geometric implication of HBS}\label{geometric implication}
     Although there exists a one-to-one correspondence between HBS and shapes up to a rotation, translation and scaling, the geometric implication of HBS is still unknown.
 More precisely, if two shapes are compared based on the HBS, it is necessary to know whether two shapes are close when their corresponding HBS are close.
-To study this, we first define the distance between two shapes $\Omega_1\subset \mathbb{R}^2$ and $\Omega_2\subset \mathbb{R}^2$ as follows:
-    \begin{equation}
-        d(\Omega_1,\Omega_2) = \frac{1}{2}\left(\max_{q\in\partial \Omega_2} \min_{p\in\partial \Omega_1} ||p-q|| + \max_{p\in\partial \Omega_1} \min_{q\in\partial \Omega_2} ||p-q||\right),
-    \end{equation}
-    \noindent where $||\cdot||$ refers to the Euclidean norm. We shall show that $d(\Omega_1,\Omega_2)$ is small if their Harmonic Beltrami Signatures are alike.
+To study this, we first define the distance between two shapes $\Omega_1\subset \C$ and $\Omega_2\subset \C$ as follows:
+    \begin{equation}\label{shape distance}
+        d_\Omega(\Omega_1,\Omega_2) = \frac{1}{2}\left(\max_{q\in\partial \Omega_2} \min_{p\in\partial \Omega_1} ||p-q|| + \max_{p\in\partial \Omega_1} \min_{q\in\partial \Omega_2} ||p-q||\right),
+    \end{equation}
+    \noindent where $||\cdot||$ refers to the Euclidean norm. We shall show that $d_\Omega(\Omega_1,\Omega_2)$ is small if their Harmonic Beltrami Signatures are alike.
 
@@
         \begin{equation}
-            \mu(t)(z) = \mu(z) + tv(z) + t \epsilon(t)(z) \text{ for }z \in \C,
+            \mu(t)(z) = \mu(z) + tv(z) + t \epsilon(t)(z),
         \end{equation}
@@
 Therefore, in order to analyze the geometric implication of HBS, we shall normalize the shape associated to a given HBS.
-According to Theorem \ref{one to one equivalence class}, given $[B] \in \mathcal{B}$, its corresponding shape can be determined by computing a quasiconformal map $G$ associated to $\mu$ given by Equation \ref{reconstructionmu}.
-The shape $\Omega = G(\mathbb{D})$ can be reconstructed, which is unique up to a rotation, translation and scaling.
+According to theorem \ref{one to one equivalence class}, given $[B] \in \mathcal{B}$, its corresponding shape can be determined by computing a quasiconformal map $G$ associated to $\mu$ given by equation (\ref{reconstructionmu}) and the shape $\Omega = G(\mathbb{D})$ can be reconstructed.
 In particular, $\Omega$ can be normalized by constraining $G$ to fix $0, 1$ and $\infty$.
@@
 
-    \begin{theorem}
-    Let $[B_1]$ and $[B_2]$ be two harmonic Beltrami signatures.
-Suppose $B_1$ and $B_2$ are the unique representatives.
+    \begin{theorem}\label{reconstruction robust theorem}
+    Let $[B_1]$, $[B_2]$ be two equivalence class of HBS and $B_1$, $B_2$ be the unique representatives.
 Let $\Omega_1$ and $\Omega_2$ be the normalized shapes associated to $B_1$ and $B_2$ respectively.
 If
-    $||B_1 - B_2||_{\infty} < \epsilon$, then $d(\Omega_1,\Omega_2)<\frac{2M}{\pi}\epsilon$ for some $M>0$.
+    $||B_1 - B_2||_{\infty} < \epsilon$, then $d_\Omega(\Omega_1,\Omega_2)<\frac{2M}{\pi}\epsilon$ for some $M>0$.
     \end{theorem}
     \begin{proof}
-    According to Theorem \ref{one to one equivalence class}, $\Omega_1$ and $\Omega_2$ can be reconstructed by solving for the quasiconformal maps $G_1$ and $G_2$.
+    According to theorem \ref{one to one equivalence class}, $\Omega_1$ and $\Omega_2$ can be reconstructed by solving for the quasiconformal maps $G_1$ and $G_2$.
 Then, $\Omega_1 = G_1(\D)$ and $\Omega_2 = G_2(\D)$.
@@
     where $v(z) = \frac{B_2(z) - B_1(z)}{||B_1 - B_2||_{\infty}}$ if $z \in \D$ and $v(z) = 0$ if $z \notin \D$.
-Then, $G_1$ and $G_2$ are quasiconformal maps associated to the Beltrami coefficients $g(0)$ and $g(||B_1 - B_2||_{\infty})$ respectively.
-According to Theorem \ref{BHF},
+Then, $G_1$ and $G_2$ are quasiconformal maps associated to the Beltrami coefficients $g(0)$ and $g(t)$ respectively, where $t = ||B_1 - B_2||_{\infty} \in (0, \epsilon)$.
+According to theorem \ref{BHF},
     \begin{align*}
-        &\norm{G_2 - G_1}_\infty = \norm{V(G_1, v) + o(||B_1 - B_2||_{\infty})}_\infty \\
-        &\le \frac{1}{\pi}\norm{G_1}_\infty \norm{G_1 - 1}_\infty \norm{W(G_1, v)} + o(||B_1 - B_2||_{\infty})\\
-        &\le \frac{2}{\pi} \norm{W(G_1, v)}_\infty + o(||B_1 - B_2||_{\infty}).
+        &\norm{G_2 - G_1}_\infty = \norm{t V(G_1, v) + o(t)}_\infty \\
+        \le& \frac{t}{\pi}\norm{G_1}_\infty \norm{G_1 - 1}_\infty \norm{W(G_1, v)}_\infty + o(t)\\
+        \le& \frac{2t}{\pi} \norm{W(G_1, v)}_\infty + o(t).
     \end{align*}
-    Since $G_1$ is continuous and bounded, the integral is bounded and for any $w \in \D$ there exists some $M > 0$ such that
+    Since $G_1$ is continuous and bounded, the following integral is bounded and for any $w \in \D$ there exists some $M > 0$ such that
     \begin{equation}
     \begin{split}
-        &\norm{\int_\D \frac{(G_1)_z^2(z)}{G_1(z)(G_1(z)-1)(G_1(z)-G_1(w)}dz}_\infty \\
-        \le& \int_\D \norm{\frac{(G_1)_z^2(z)}{G_1(z)(G_1(z)-1)(G_1(z)-G_1(w)}}_\infty dz \\
-        \le& M
+        &\norm{\int_\D \frac{(G_1)_z^2(z)}{G_1(z)(G_1(z)-1)(G_1(z)-G_1(w)}dz} \\
+        \le& \int_\D \norm{\frac{(G_1)_z^2(z)}{G_1(z)(G_1(z)-1)(G_1(z)-G_1(w)}} dz \\
+        \le& M.
     \end{split}
     \end{equation}
-
-    Then,
-    \begin{equation}
-        \norm{G_2 - G_1}_\infty \le \frac{2M}{\pi} \norm{B_2-B_1}_\infty\le \frac{2M}{\pi} \epsilon.
+    Therefore, we have $\norm{W(G_1, v)}_\infty \le M \norm{v}_\infty \le M$ and
+    \begin{equation}
+        \norm{G_2 - G_1}_\infty \le \frac{2t}{\pi} \norm{W(G_1, v)}_\infty \le \frac{2Mt}{\pi} \le \frac{2M}{\pi} \epsilon.
     \end{equation}
@@
 Thus, $\max_{q\in \Omega_2}\min_{p\in \Omega_1} ||p-q|| \leq \frac{2M}{\pi}\epsilon$.
-
-    Similarly, $\max_{p\in \Omega_1}\min_{q\in \Omega_2} ||p-q|| \leq \frac{2M}{\pi}\epsilon$. As a result, we have 
+Similarly, $\max_{p\in \Omega_1}\min_{q\in \Omega_2} ||p-q|| \leq \frac{2M}{\pi}\epsilon$.
+As a result, we have
     \[
-    d(\Omega_1,\Omega_2)<\frac{2M}{\pi}\epsilon
+    d_\Omega(\Omega_1,\Omega_2)<\frac{2M}{\pi}\epsilon
     \]
@@
 
-    This above theorem illustrates that if the difference between HBS is small enough, their corresponding domains is almost the same, which means our Harmonic Beltrami signature is a good indicator similarity of shapes.
+    This above theorem illustrates that if the difference between HBS is small enough, their corresponding domains is almost the same, which means our Harmonic Beltrami signature is a good similarity indicator of shapes.
 
@@
 \subsection{Zipper algorithm}
-    In order to find a unique and stable HBS, the first thing is to do find a way to calculate a conformal mapping from the given domain to unit disk.
+    In order to find a unique and stable HBS, the first thing is to find a way to calculate a conformal mapping from the given domain to unit disk.
 As mentioned in Section \ref{norm_to_m1}, we only have finite boundary points of the shape and zipper algorithm invented in the 1980s is a suitable and accurate method to deal with this situation numerically.
@@
 $z_N, z_{N-1}, \cdots, z_1$, the zipper will give us a conformal mapping from $\Omega^c$ to $\D$.
-This progress is shown in Fig.
-\ref{zipper algo}.
+This progress is shown in figure \ref{zipper algo}.
 
@@
     For $\Phi_1 : \D \rightarrow \Omega$, we can find a conformal mapping $g_{\Phi_1}: \Omega \rightarrow \D$ by inputting points clockwise, and $\Phi_1 = g_{\Phi_1}^{-1}$.
-For $\Phi_2 : \D^c \rightarrow \Omega^c$, we can input anti-clockwise points and get $g_{\Phi_2} : \Omega^c \rightarrow \D$.
-At the result $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-Because of the invariance of scaling, the number of boundary points $N$ is fixed as $200$ here and they are picked uniformly from the shape contour.
+For $\Phi_2 : \D^c \rightarrow \Omega^c$, we can input anti-clockwise points and get $g_{\Phi_2} : \Omega^c \rightarrow \D$, then $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
+Because of the invariance of HBS under scaling, the number of boundary points $N$ can be fixed as $200$ here and these points are picked uniformly from the shape contour.
 
@@
             \STATE \textbf{Inputs:} $z_i \in \partial \Omega$ for $i=1, 2, \cdots, N$, $N=200$. %, $\epsilon = 10^{-10}$(any very small value)
-                \STATE \textbf{Initialize:} Let $r=2$, $g_1(z) = \sqrt{\frac{z-z_2}{z-z_1}}$, $g= g_1$ and compute $p_{i,2}=g(z_i)$.
-                \WHILE{$r < N$}
-                    \STATE Pick $q = p_{r+1, r} = a + b i$, then compute $c = \frac{a}{\abs{q}^2}$, $d = \frac{b}{\abs{q}^2}$.
-                    \STATE Let $g_r(z) = \sqrt{\frac{cz}{1+dzi}}$, then $g = g_r \circ g$ and compute $p_{i, r+1} = g_r(p_{i, k})$.
-                    \STATE Let $r = r+1$.
+            \STATE \textbf{Initialize:} Let $k=2$, $g_1(z) = \sqrt{\frac{z-z_2}{z-z_1}}$, $g= g_1$ and compute $p_{i,2}=g(z_i)$.
+            \WHILE{$k < N$}
+                \STATE Pick $q = p_{k+1, k} = a + b i$, then compute $c = \frac{a}{\abs{q}^2}$, $d = \frac{b}{\abs{q}^2}$.
+                \STATE Let $g_k(z) = \sqrt{\frac{cz}{1+dzi}}$, then $g = g_k \circ g$ and compute $p_{i, k+1} = g_k(p_{i, k})$.
+                \STATE Let $k = k+1$.
             \ENDWHILE
@@
 
-        \subsection{Harmonic extension}\label{detail harmonic}
-            After obtaining the output of zipper algorithm, $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$, the conformal welding can be represented as a series points
-            \begin{equation*}
-                (\varphi_i, \omega_i) = \left(\arg(\hat{\Phi}_2^{-1}(z_i)), \arg(\hat{\Phi}_1^{-1}(z_i))\right),
-            \end{equation*}
-            where $\varphi_i, \omega_i \in [0, 2\pi)$. So in fact we should use discrete form Poisson integral to extend $f$ to a harmonic mapping $H$ on the unit disk
-            \begin{equation}\label{discrete poisson integral}
-                H(re^{i\theta}) = \frac{1}{2\pi} \sum_{j=1}^k \frac{(1-r^2) e^{i \omega_j} \gamma_j}{1 - 2 r cos (\varphi_j - \theta) + r^2} ,
-            \end{equation}
-            where $\gamma_j = (\varphi_{j} - \varphi_{j-1}) \bmod{ 2\pi}$ and $\varphi_0 = \varphi_k$ and this $\bmod$ can solve some critical value problem, for example, $\varphi_j = 0$ but $\varphi_{j-1} = 6$.
-For the convenience of computation, we only calculate the value of $H$ on a grid
-            \begin{align*}
-                G = \{z=x+iy \mid &\abs{z} \le 1, x=\frac{j}{100}, y=\frac{k}{100},\\
-                &j,k=-100,-99,\cdots,99,100 \}.
-            \end{align*}
-
     \subsection{Normalization}
-    Because of the arbitrariness of the conformal mapping, two different harmonic extension $H$ and $\tilde{H}$ of the given domain $\Omega$ have relationship
-    \begin{equation*}
-        \tilde{H} = M_1 \circ H \circ M_2.
-    \end{equation*}
     Section \ref{norm_to_m1} and \ref{norm2} show that we can normalize $M_1$ and $M_2$ by some restrictions and then HBS $B$ can be unique.
@@
     To normalization $M_1$, we need to solve equation (\ref{eq}).
-Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \D, i = 1, 2, \cdots, N$, will concentrate around a point.
-At that time, $\abs{f(a)} \approx 1$ almost everywhere and the solution of (\ref{eq}) is also very close to the point.
-This means the solution is quite unstable and hard to converge for common algorithms(see Fig \ref{original distribution}).
+Generally speaking, the output of zipper, $p_i = g_{\Phi_1}(z_i) \in \partial \D$ for $i = 1, 2, \cdots, N$, gather around some point.
+At that time, $\abs{f(a)} \approx 1$ almost everywhere and the solution of (\ref{eq}) is also very close to that point.
+This means the solution is quite unstable and hard to converge for common algorithms(see figure \ref{original distribution}).
 
@@
         \end{center}
-        \caption{Similar with Fig \ref{original distribution}. (a) The boundary points after adjustment; (b) The $\abs{f(a)}$.}
-    \end{figure}
-
-    Instead of proposing a complicated method to solve equation directly, the solution we adopted to solve this problem is to use some Mobi\"us transformations to adjust the distribution of $p_{i}$ until it becomes almost uniform.
-For the $r$-th iteration, let
-    \begin{equation*}
-        p_{c,r} = \frac{\sum_{i=1}^k p_{i,r}}{k} \in \D
-    \end{equation*}
-    as the arithmetic center of $p_{i,r} \in \partial \D$.
-Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobi\"us transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points on unit disk as
-    \begin{equation*}
-        p_{i,r+1} = F_{p_{c,r}}(p_{i,r}) = \frac{p_{i,r} - p_{c,r}}{1 - \overline{p_{c,r}}p_{i,r}}.
-    \end{equation*}
-    Note that we set $p_{i,0} = p_{i}$ at the beginning.
-Repeat this iteration for $r$ times until the center of boundary points is close to $0$, then the distribution is sufficiently regular and $\Phi_1$ becomes
-    \begin{equation}
-        \tilde{\Phi}_1 = \Phi_1 \circ F_{p_{c,0}}^{-1} \circ F_{p_{c,1}}^{-1} \circ \cdots \circ F_{p_{c,r}}^{-1}.
-    \end{equation}
-    Now equation (\ref{eq}) can be solved without much effort by Newtown's method. Suppose $a \in \D$ is the optimal solution and let 
-    \begin{equation*}
-        M_{\Phi_1} = F_a \circ F_{p_{c,r}} \circ F_{p_{c,r-1}} \circ \cdots \circ F_{p_{c, 0}}
+        \caption{Similar with figure \ref{original distribution}. (a) The boundary points after adjustment; (b) The $\abs{f(a)}$.}
+    \end{figure}
+
+    Instead of proposing a complicated method to solve equation directly, the way we adopted to solve this problem is to use some Mobi\"us transformations to adjust the distribution of $p_{i}$ until their arithmetic center is very close to 0.
+We set $p_{i,0} = p_{i}$ at the beginning and for the $k$-th iteration, let $p_{i,k} \in \partial \D$ be the boundary points and
+    \begin{equation*}
+        p_{c,k} = \frac{\sum_{i=1}^N p_{i,k}}{N} \in \D
+    \end{equation*}
+    as the arithmetic center of $p_{i,k}$. Remark that $F_a(z) = \frac{z-a}{1-\overline{a}z}$ is a Mobi\"us transformation ignoring rotation, then the $F_{p_{c,r}}$ gives new boundary points as 
+    \begin{equation*}
+        p_{i,k+1} = F_{p_{c,k}}(p_{i,k}) = \frac{p_{i,k} - p_{c,k}}{1 - \overline{p_{c,k}}p_{i,k}}.
+    \end{equation*}
+    Repeat this iteration for $k$ times until $\abs{p_{c,k+1}}$ is close to $0$, then the distribution of $p_{i, k+1}$ is sufficiently regular and almost uniform. At that time, suppose 
+    \begin{equation*}
+        M_{\Phi_1} = F_{p_{c,k}} \circ F_{p_{c,k-1}} \circ \cdots \circ F_{p_{c, 0}}
     \end{equation*}
@@
     \begin{equation}
-        \hat{\Phi}_1 = \tilde{\Phi}_1 \circ F_{a}^{-1} = \Phi_1 \circ M_{\Phi_1}^{-1}
+        \tilde{\Phi}_1 = \Phi_1 \circ M_{\Phi_1}^{-1}
     \end{equation}
@@
     \begin{algorithmic}
-        \STATE \textbf{Inputs:} $\Phi_1$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $\epsilon=0.2$.
-        \STATE \textbf{Initialize:} Let $r=0$, $p_{i,0} = p_i$, $M_{\Phi_1} = id$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$.
+        \STATE \textbf{Inputs:} $\Phi_1$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $\epsilon=10^{-5}$.
+        \STATE \textbf{Initialize:} Let $k=0$, $p_{i,0} = p_i$, $M_{\Phi_1} = id$ and compute $p_{c,0}= \frac{1}{N} \sum_{i=1}^N p_{i}$.
 %and $M_{p_{c,0}}(z) = \frac{z-p_{c,0}}{1- \overline{p_{c, 0}}z}$
-        \WHILE{$\abs{p_c,r} > \epsilon$}
-            \STATE Let $F_{p_{c,r}}(z) = \frac{z-p_{c,r}}{1- \overline{p_{c, r}}z}$ and $M_{\Phi_1} = F_{p_{c,r}} \circ M_{\Phi_1}$.%and $\Phi_1 = \Phi_1 \circ F_{p_{c,r}}^{-1}$.
-            \STATE Compute $p_{i, r+1} = F_{p_{c,r}}(p_{i, r})$ and $p_{c,r+1} = \frac{1}{N} \sum_{i=1}^N p_{i, r+1}$.
-            \STATE Let $r = r+1$.
+        \WHILE{$\abs{p_{c,k}} > \epsilon$}
+            \STATE Let $F_{p_{c,k}}(z) = \frac{z-p_{c,k}}{1- \overline{p_{c, k}}z}$ and $M_{\Phi_1} = F_{p_{c,k}} \circ M_{\Phi_1}$.%and $\Phi_1 = \Phi_1 \circ F_{p_{c,k}}^{-1}$.
+            \STATE Compute $p_{i, k+1} = F_{p_{c,k}}(p_{i, k})$ and $p_{c,k+1} = \frac{1}{N} \sum_{i=1}^N p_{i, k+1}$.
+            \STATE Let $k = k+1$.
         \ENDWHILE
-        \STATE Solve equation (\ref{eq}) by Newtown's method and get solution $a \in \D$.
-        \STATE Let $F_a(z) = \frac{z-a}{1- \overline{a}z}$ and $M_{\Phi_1} = F_a \circ M_{\Phi_1}$.% and $\hat{\Phi}_1 = \Phi_1 \circ F^{-1}_{a}$.
-        %\STATE Compute $p_i = F_a(p_{i,r})$.
-        \RETURN Mobi\"us transformation $M_{\Phi_1}$.%, conformal mapping $\hat{\Phi}_1: \D \rightarrow \Omega$ satisfying (\ref{norm phi1}) and boundary points $p_i \in \partial \D$.
+        % \STATE Solve equation (\ref{eq}) by Newtown's method and get solution $a \in \D$.
+        % \STATE Let $F_a(z) = \frac{z-a}{1- \overline{a}z}$ and $M_{\Phi_1} = F_a \circ M_{\Phi_1}$.% and $\hat{\Phi}_1 = \Phi_1 \circ F^{-1}_{a}$.
+        \RETURN Mobi\"us transformation $M_{\Phi_1}$.
     \end{algorithmic}
@@
     \begin{equation*}
-        F_{c}(\infty) = \lim_{z \rightarrow \infty} \frac{z -c}{1 - \bar{c}z} = -\frac{1}{\overline{c}} = b
-    \end{equation*} we have 
-    \begin{equation*}
-        \tilde{\Phi}_2(\infty) = \Phi_2 \circ F_{c}(\infty) = \Phi_2(b) = \infty.
-    \end{equation*}
-    So we only need replace $\Phi_2$ with $\tilde{\Phi}_2 =\Phi_2 \circ F_{c}$ to map $\infty$ to $\infty$.
-
-    % According to zipper algorithm, we know each linear fractional transformation composing $\Phi_2$, and the derivative of $\tilde{\Phi}_2$ can be found by the chain derivative rule.
-And another requirement (\ref{norm phi2 2}) can be satisfied by finding $a=\argmax{z \in \partial\D} \abs{\tilde{\Phi}_2'(z)}$.
-Here we select $M = 10^5$ points uniformly from $[0, 2\pi)$ as $\theta_j = \frac{2\pi}{M}(j-1)$ and calculate the $\abs{\tilde{\Phi}_2'(e^{i \theta_j})}$ (see Fig \ref{derative}).
-
-    % Therefore, the maximal solution
-    % \begin{equation}
-    %     \theta_{\max} = \argmax{j \in [1,10^5]} \abs{\tilde{\Phi}_2'(e^{i \theta_j})}
-    % \end{equation}
-    % can be used to normalize the rotation and the final mapping is 
-    % \begin{equation}
-    %     \hat{\Phi}_2(z) = \tilde{\Phi}_2(e^{i \theta_{\max}}z) = \Phi_2 \circ M_{\Phi_2}(z),
-    % \end{equation}
-    % where $M_{\Phi_2} = e^{i \theta_{\max}} F_{ce^{-i \theta_{\max}}}$.
+        M_{\Phi_2}(\infty) = F_{c}(\infty) = \lim_{z \rightarrow \infty} \frac{z -c}{1 - \bar{c}z} = -\frac{1}{\overline{c}} = b
+    \end{equation*}
+    we have 
+    \begin{equation*}
+        \tilde{\Phi}_2(\infty) = \Phi_2 \circ M_{\Phi_2}(\infty) = \Phi_2(b) = \infty.
+    \end{equation*}
 
@@
     \begin{algorithmic}
-        \STATE \textbf{Inputs:} $\Phi_2$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$, $M=10^5$.
-        \STATE Compute $b = \overline{\Phi_2^{-1}(\infty)}$ and $c = -\frac{1}{\bar{b}}$.
+        \STATE \textbf{Inputs:} $\Phi_2$ and $p_i \in \partial \D$ for $i=1, 2, \cdots, N$, $N=200$.
+        \STATE Compute $b = \Phi_2^{-1}(\infty)$ and $c = -\frac{1}{\overline{b}}$.
         \STATE Let $F_c(z) = \frac{z-c}{1-\overline{c}z}$ and $M_{\Phi_2} = F_{c}$.
@@
 
-    After obtaining Mobi\"us transformations $M_{\Phi_1}$ and $M_{\Phi_2}$, the normalized harmonic extension is
-    \begin{align*}
-        \hat{H} = M_{\Phi_1} \circ H \circ M_{\Phi_2}
-    \end{align*}
-    and it is unique up to rotation. Finally, the desired HBS can be generated from $\mu_{\hat{H}}$ according to equation (\ref{normaled B}).
+    \subsection{Harmonic extension}\label{detail harmonic}
+        After obtaining the normalized $\tilde{\Phi}_1(z) = g_{\Phi_1}^{-1} \circ M_{\Phi_1}^{-1}(z)$ and $\tilde{\Phi}_2(z) = g_{\Phi_2}^{-1} \circ M_{\Phi_2} (\frac{1}{z})$, the conformal welding can be represented as a series points
+        \begin{equation*}
+            (\varphi_i, \omega_i) = \left(\arg(\tilde{\Phi}_2^{-1}(z_i)), \arg(\tilde{\Phi}_1^{-1}(z_i))\right),
+        \end{equation*}
+        where $\varphi_i, \omega_i \in [0, 2\pi)$. So in fact we should use discrete form Poisson integral to extend $f$ to a harmonic mapping $H$ on the unit disk
+        \begin{equation}\label{discrete poisson integral}
+            H(re^{i\theta}) = \frac{1}{2\pi} \sum_{j=1}^N \frac{(1-r^2) e^{i \omega_j} \gamma_j}{1 - 2 r cos (\varphi_j - \theta) + r^2} ,
+        \end{equation}
+        where $\gamma_j = (\varphi_{j} - \varphi_{j-1}) \bmod{ 2\pi}$ and $\varphi_0 = \varphi_N$ and this $\bmod$ can solve some critical value problem, for example, $\varphi_j = 0$ but $\varphi_{j-1} = 6$.
+For the convenience of computation, we only calculate the value of $H$ on a grid inside unit disk
+        \begin{equation}\label{grid G}
+            G := \{z=x+i y \, \mid \abs{z} \le 1, x=\frac{j}{M}, y=\frac{k}{M}, j,k=-M,\cdots,M \},
+        \end{equation}
+        where $M$ is a fixed number and we choose $M=100$ here. Finally, the desired HBS can be generated from $\mu_H$ according to equation (\ref{normaled B}).
 
 \subsection{Summary of the Algorithm}
-    The totally algorithm is as following.
+    The totally algorithm to get HBS is as following.
     \begin{algorithm}[H]
@@
         \STATE Pick clockwise points $z_1, \cdots, z_N \in \partial \Omega$ uniformly.
-        \STATE Input $z_1, z_2, \cdots, z_N$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_1}: \D \rightarrow \Omega$ and $p_{i,1} \in \partial\D$.
-        \STATE Input $z_N, \cdots, z_2, z_1$ to Algorithm \ref{zipper} and get conformal mapping $g_{\Phi_2}: \D \rightarrow \Omega^c$ and $p_{i,2} \in \partial\D$.
+        \STATE Input $z_1, \cdots, z_N$ to Algorithm \ref{zipper} then get $g_{\Phi_1}: \Omega \rightarrow \D$ and $p_{i,1} \in \partial\D$.
+        \STATE Input $z_N, \cdots, z_1$ to Algorithm \ref{zipper} then get $g_{\Phi_2}: \Omega^c \rightarrow \D$ and $p_{i,2} \in \partial\D$.
         \STATE Let $\Phi_1(z) = g_{\Phi_1}^{-1}(z)$ and $\Phi_2(z) = g_{\Phi_2}^{-1}(\frac{1}{z})$.
-        \STATE Let $f = \Phi_1^{-1} \circ \Phi_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
-        \STATE Extend $f$ to $H$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
         \STATE Input $\Phi_1$ and $p_{i,1}$ to Algorithm \ref{alg norm phi1}, then get $M_{\Phi_1}$.
         \STATE Input $\Phi_2$ and $p_{i,2}$ to Algorithm \ref{alg norm phi2}, then get $M_{\Phi_2}$.
-        \STATE Calculate normalized harmonic extension $\hat{H} = M_{\Phi_1} \circ H \circ M_{\Phi_2}$.
-        \STATE Calculate Beltrami coefficient $\mu_{\hat{H}}$.
-        \STATE Calculate $\theta = \arg \int_\D \mu_{\hat{H}}(z) dz$.
-        \STATE Let $B(z) = e^{i \theta} \mu_{\hat{H}}(e^{-\frac{1}{2}i\theta} z)$.
+        \STATE Let $\tilde{\Phi}_1 = \Phi_1 \circ M_{\Phi_1}^{-1}$ and $\tilde{\Phi}_2 = \Phi_2 \circ M_{\Phi_2}$.
+        \STATE Let $f = \tilde{\Phi}_1^{-1} \circ \tilde{\Phi}_2$ and represent it by $(\varphi_i, \omega_i) = (\arg(p_{i,2}), \arg(p_{i,1}))$.
+        \STATE Extend $f$ to $H$ on $\D$ by equation (\ref{discrete poisson integral}) on grid $G$.
+        \STATE Calculate Beltrami coefficient $\mu_{H}$.
+        \STATE Calculate $\theta = \arg \int_\D \mu_H(z) dz$, $\theta' = \arg \int_\D \mu_H(z) / z dz$.
+        \IF{$0 \le \theta - \theta'/2 < \pi$}
+        \STATE Let $B(z) = e^{i \theta} \mu_{H}(e^{-\frac{1}{2}i\theta} z)$.
+        \ELSE
+        \STATE Let $B(z) = e^{i \theta} \mu_{H}(-e^{-\frac{1}{2}i\theta} z)$.
+        \ENDIF
         \RETURN Harmonic Beltrami signature $B$.
@@
 
+    \subsection{Reconstruction from HBS}
+    The proposed HBS is an effective fingerprint of 2D shape and we can also construct the corresponding shape $\Omega$ from given HBS $B$ easily.
+Different from the theory metioned in theorem \ref{one to one equivalence class}, there is no computational algorithm to find the quasiconformal map $G$ on $\hat{\C}$ directly from its Beltrami coefficient $\mu$ in equation (\ref{reconstructionmu}), so we adopt the following method.
+
+    Since $\mu=0$ on $\D^c$, we just focus on the part inside $\D$ and get $F: \D \rightarrow \Omega_0$ by the free boundary quasiconformal deformation method in \cite{choi2020shape}.
+Since $B$ is the Beltrami coefficient of some harmonic extension $H$ and $\mu_F = B$, such $F$ is also harmonic.
+Then we pick $z_1, \cdots, z_k$ from $\partial \D$ uniformly and $F(z_1), \cdots, F(z_k) \in \partial \Omega_1$ respectively.
+After that, the geodesic algorithm \cite{marshall2009lens} welds all $z_i$ and $F(z_i)$, generating conformal maps $g_1 : \Omega_0 \rightarrow \Omega$ and $g_2: \D^c \rightarrow \Omega^c$, where $\Omega = g_1 \circ F (\D)$ and $g_1 \circ F(z_i) = g_2(z_i)$.
+
+    Claims that $\Omega$ is the shape we want to reconstruct, up to a rotation, scaling and transformation.
+There must be some comformal function $C$ maps $\Omega_0$ to $\D$, then $g_1 \circ C^{-1}$ maps $\D$ to $\Omega$ and $C \circ g_1^{-1} \circ g_2$ is conformal welding of $\Omega$.
+For each $z_i \in \partial \D$, we have
+    $$C \circ F(z_i) = C \circ g_1^{-1} \circ g_2(z_i)$$
+    and $C \circ F$ is harmonic, so $C \circ F$ is the harmonic extension of conformal welding. Therefore the HBS of $\Omega$ is $\mu_{C \circ F} = B$ and $\Omega$ is the desired shape.
+
+    As metioned in section \ref{geometric implication}, we fix
+    \begin{equation*}
+        G = \begin{cases}
+            g_1 \circ F \text{ on } \D,\\
+            g2 \text{ on } \D^c
+        \end{cases}
+    \end{equation*}
+    at $0, 1, \infty$ in order to eliminate the arbitrariness and compare the distance between different reconstructed shapes directly. For above method, it's equivalent with
+    \begin{gather*}
+        F(0) = 0, F(1) = 1,\\
+        g_1(0) = 0, g_1(1) = 1,\\
+        g_2(\infty) = \infty.
+    \end{gather*}
+    These requirements can be achieved naturally in free boundary quasiconformal deformation and geodesic welding algorithm. So the reconstruction algorithm can be described as following.
+
+    \begin{algorithm}[H]
+    \caption{reconstruction from HBS}
+    \label{reconstruction algo}
+    \begin{algorithmic}
+        \STATE \textbf{Inputs:} HBS $B: \D \rightarrow \D$, $N=1000$.
+        \STATE Let $z_k=e^{2\pi\frac{k}{N}i}\in \partial \D, k=1,\cdots, N$.
+        \STATE Reconstruct $F: \D \rightarrow \Omega_1$ from $B$ by free boundary quasiconformal deformation with $F(0)=0$ and $F(1)=1$.
+        \STATE Compute $g_1: \Omega_1 \rightarrow \Omega$ and $g_2: \D^c \rightarrow \Omega^c$ by geodesic welding algorithm with $g_1(0) = 0, g_1(1) = 1, g_2(\infty) = \infty$ and $g_2(z_k) = g_1(F(z_k))$.
+        \RETURN Reconstructed shape $\Omega = g_1 \circ F(\D)$.
+    \end{algorithmic}
+    \end{algorithm}
+
     \section{Experimental result}\label{result}
-        In this section, we will validate key properties of our proposed Harmonic Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
-Besides that, a good shape representation should keep the similarity with the same kind shape and is significantly different from different kinds of shape.
-
-        Before showing results, what needs illustration is that the distance we used to measure the difference of HBS is based on $L^2$ norm,
+        In this section, we validate key properties of our proposed Harmonic Beltrami signature, the invariance of under simple transformations and the robustness under small distortion and modification.
+Then we try to reconstruct shapes from HBS and verify the robustness of reconstruction algorithm.
+Besides we test the classification performance of HBS.
+
+        Before showing results, what needs to illustrate is that the distance we used to measure the difference of HBS is based on $L^2$ norm as
         \begin{equation}\label{bs dis}
@@
         \end{equation}
-        where $B_1, B_2$ are two different Harmonic Beltrami signatures, $z_i \in \D$ is the face center of triangular mesh $M$ mentioned in Section \ref{detail harmonic} and $N=60962$ here.
+        where $B_1, B_2$ are two different Harmonic Beltrami signatures, $z_i \in \D$ is the face center of triangular mesh $M$ on grid $G$ mentioned in (\ref{grid G}) and $N=62504$ here.
+All following experiments are implemented in MATLAB R2014a running on 4-way Intel(R) Xeon(R) Gold 6230 processers with 80 cores at 2.10GHz base frequency and 1024 GB RAM with Ubuntu 18.04LTS 64-bit operating system.
+
     \subsection{Invariance}\label{sec inv}
-            We use the dolphin shown in Fig \ref{illu of BS} (a) as the original shape, then calculate HBS after scaling, translation and rotation and compare them with the original shape's HBS.
-The result is displayed in Fig \ref{inv}.
+        We use the dolphin shown in figure \ref{illu of BS} (a) as the original shape, then calculate HBS after scaling, translation and rotation and compare them with the original shape's HBS.
+The result is displayed in figure \ref{inv}.
 In this figure, the first column are the sets of boundary points and we remark them as $\Omega_a$ to $\Omega_f$.
@@
     \subsection{Robustness}
-            Similar with Section \ref{sec inv}, here we still treat the dolphin as the original shape and modify some small parts of it and Fig \ref{robust} is the result.
+        Similar with Section \ref{sec inv}, here we still treat the dolphin as the original shape and modify some small parts of it and figure \ref{robust} is the result.
 It shows that the proposed signature is robust and stable and will not have a big mutation caused by small disturbance.
@@
 For example in row i, losing a half of the tail makes the signature has a marked change.
-Quantitatively, $d(B_a, B_g) = 0.0132$, $d(B_a, B_h) = 0.0316$ and $d(B_a, B_i) = 0.1761$.
-
-            Row j is for distortion. This dolphin is only enlarged in horizontally and becomes fatter, then the $B_j$ moves a little bit and $d(B_a, B_j) = 0.0724$.
-
-            \begin{figure*}
+Quantitatively, $d(B_a, B_g) = 0.0154$, $d(B_a, B_h) = 0.0461$ and $d(B_a, B_i) = 0.2518$.
+
+        Row j is for distortion. This dolphin is only enlarged in horizontally and becomes fatter, then the $B_j$ moves a little bit and $d(B_a, B_j) = 0.0825$.
+
+        \begin{figure}
             \begin{center}
@@
             \label{robust}
-            \end{figure*}
+        \end{figure}
+
+    \subsection{Reconstruction from HBS}
+        In this experiment, we show our reconstruction results and compare them with their corresponding original shapes.
+For each row in figure \ref{reconstruction experiment 1}, the left one is original shape, the middle one is HBS and the right one is reconstructed shape.
+We can find that each reconstructed shape is almost the same with the original one up to a transformation, rotation and scaling, which is owing to no any normalization to original shapes.
+
+        Some reconstructed shapes may lose many points where the border is recessed because these points are concentrated in a very small range in HBS.
+If we use a bigger $N$ in algorithm \ref{reconstruction algo}, The missing part in reconstructed shape will get smaller, as shown in figure \ref{reconstruction experiment 2}.
+
+        \begin{figure}
+            \begin{center}
+                \includegraphics[width=10cm]{reconstruct.png}
+            \end{center}
+            \caption{Reconstruction from HBS}
+            \label{reconstruction experiment 1}
+        \end{figure}
+
+        \begin{figure}
+            \begin{center}
+                \includegraphics[width=10cm]{reconstruct_num.png}
+            \end{center}
+            \caption{(a) is the HBS and (b)-(f) are reconstructed shapes with different $N$, which are 500, 1000, 1500, 2000 and 2500 respectively.}
+            \label{reconstruction experiment 2}
+        \end{figure}
+
+    \subsection{Robustness of reconstruction}
+        Here we modify HBS directly by some function and then reconstruct.  The basic HBS $B_0$ is from figure \ref{reconstruction experiment 1} (b2) and
+        \[
+            B_k(z) = \abs{B_0(z)}^k B_0(z).
+        \]
+        $\Omega_k$ is reconstructed from $B_k$ as algorithm \ref{reconstruction algo}.
+In figure \ref{modify HBS}, the reconstructed whales become fatter and fatter when $k$ increases, but they still retain some important features.
+
+        In order to describe this similarity more accurately, the distance of HBS from basic HBS is calculated by $L_\infty$ norm
+        $$d_{HBS}(B, B_0) = \norm{B_0 - B}_\infty,$$
+        and distance between reconstructed shape and original shape is computed as equation (\ref{shape distance})
+        $$d_{\Omega}(\Omega, \Omega_0) =  \frac{1}{2}\left(\max_{q\in\partial \Omega_0} \min_{p\in\partial \Omega} ||p-q|| + \max_{p\in\partial \Omega} \min_{q\in\partial \Omega_0} ||p-q||\right).$$
+        Except the $B_k$ metioned above, we also try many different $k$ and some other methods to edit the basic HBS $B_0$, like %$\tilde{B}_k(z) = e^{ik} B_0(z)$, 
+        $\tilde{B}_k(z) = e^{i(1-\abs{B_0(z)})k}B_0(z)$ and so on.
+All these $d_{HBS}$ and $d_\Omega$ are shown in figure \ref{d_hbs and d_omega}, which indicates they are linearly related and support our theorem \ref{reconstruction robust theorem} strongly.
+
+        \begin{figure}
+            \begin{center}
+                \includegraphics[height=22cm]{modify_HBS.png}
+            \end{center}
+            \caption{Different $B_k$ and their reconstructed shapes, where the $k$ is -0.1, 0.2, 0.5, 1 and 1.5 for (a)-(e)}
+            \label{modify HBS}
+        \end{figure}
+
+        \begin{figure}
+            \begin{center}
+                \includegraphics[width=8cm]{d_hbs_and_d_omega.png}
+            \end{center}
+            \caption{$d_{HBS}$ and $d_\Omega$, each small blue point here means a pair of HBS and its reconstructed shape.}
+            \label{d_hbs and d_omega}
+        \end{figure}
 
@@
         Above properties ensure the proposed signature having the ability to reflect some stable features of given shape, but another much more important thing people concerned is that whether it can distinguish a shape from many different kinds of shapes and classify it correctly.
-
-            To compare the classification performance, we also use conformal welding directly to classify, and the distance is defined as
+A good signature should keep the similarity in the same kind of shapes and be significantly different for different kinds of shapes.
+
+        To compare the classification performance, we also calculate the conformal welding of all the shapes directly to classify, and the distance is defined as
         \begin{equation}\label{welding dis}
@@
         \end{equation}
-            where $f_1, f_2$ are two different conformal welding, $N=200$ here.
-
-            We prepare 3 kinds of animals, fish, giraffe and elephant.
-There are 3 images for each group so 9 images in total.
-From Fig \ref{classification images}, we can find that each class share similar HBS and conformal welding.
-From Fig \ref{dis matrix}, the intraclass distance of HBS is always less than 0.2 while the interclass distance is greater than 0.2.
-But for conformal welding, the data is messy, for example, fish 3 thinks itself is very different from other fishes but looks most like giraffe 2.
-After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as Fig \ref{mds1}, where the HBS shows powerful classification ability.
+        where $f_1, f_2$ are two different conformal welding, $z_i \in \partial \D$ and $N=1000$ here. Note that the conformal welding is not unique, but we can normalize it by
+        \begin{equation}
+        \begin{split}\label{norm to cw}
+            \sum_{i=1}^N \Phi_1^{-1}(z_i) = 0,\\
+            \Phi_2(\infty) = \infty,\\
+            \Phi_2'(\infty) >= 0,\\
+            f(1) = 1.
+        \end{split}
+        \end{equation}
+
+        The first requirement is what we proposed in section \ref{norm_to_m1} and the other three are from \cite{sharon20062d}.
+After above normalizations, we can fix a unique conformal welding from the given shape.
+
+        We prepare 3 images for 3 kinds of animals, fish, giraffe and elephant, so 9 images in total.
+From figure \ref{classification images}, we can find that each class share similar HBS but their conformal weldings look different.
+
+        Figure \ref{dis matrix} shows the intraclass distance of HBS is always smaller than interclass distance.
+But for conformal welding, the data is messy, for example, elephant 2 thinks itself is very different from other two elements but looks most like fish 3.
+After multidimensional scaling(MDS), we can maps all these 9 shapes to points on 2D plane as figure \ref{mds1}, where the HBS shows powerful classification ability.
+
+        Actually, a closer look on figure \ref{classification images} shows the biggest difference between conformal weldings of the same class is just a translation.
+For example, if the conformal welding of giraffe 3 moves a little right up (mod by 2$\pi$), it will become very similar with other two giraffes.
+Further research tells us this difference is the result of the third requirement of (\ref{norm to cw}), which essentially looks for a starting point on shape boundary to be mapped to $(0, 0)$ in conformal welding.
+However, the starting point determined in this way is sensitive, so the corresponding conformal welding is unstable.
 
@@
             \begin{center}
-                    \includegraphics[width=13cm]{distance2.png}
+                \includegraphics[width=13cm]{distance.png}
             \end{center}
@@
 
-        \subsection{Classification for more classes}\label{more class}
-            In this experiment, we enlarge the amount of images to 58 in 7 different classes, camel, deer, dog, elephant, giraffe, gorilla and rabbit. All these shapes are in Fig \ref{more class all}
-
-            We calculate the distance matrix by equation (\ref{bs dis}) and (\ref{welding dis}) and use MDS to remap these shapes to 2D plane accordingly, then $k$-medoids method is used to cluster these points to 7 classes.
-The MDS and clustering results based on Harmonic Beltrami signature and conformal welding are displayed in Fig \ref{mds2}.
-The classification accuracy based on Harmonic Beltrami signature is 94.83\%, while the accuracy based on conformal welding is only 37.93\%.
+    \subsection{Multi-class classification}\label{more class}
+        In this experiment, we enlarge the amount of images to 58 in 7 different classes, which are camel, deer, dog, elephant, giraffe, gorilla and rabbit.
+All these shapes are in figure \ref{more class all}.
+
+        We compare the classification performance of our HBS with conformal welding, shape context \cite{belongie2002shape} and boundary moments \cite{gupta1987267}.
+The distance of HBS and conformal welding are equation (\ref{bs dis}) and (\ref{welding dis}) respectively.
+Then the shape context distance defined in \cite{belongie2006matching} can measure the difference between shape contexts.
+And $L_2$ norm is a suitable distance for boundary moments.
+
+        For each algorithm, the distances of any two shapes are calculated and form a distance matrix as last experiment, then MDS remaps these shapes to 2D plane accordingly and $k$-medoids method is used to cluster these points to 7 classes.
+The MDS and clustering results are displayed in figure \ref{mds2} and the classification accuracy can be found in table \ref{acc table}.
+
+        These results demonstrate the multi-class classification performance of our proposed HBS is much better than boundary moments and conformal welding.
+As for shape context, Although its classification accuracy of is is very close to our HBS, we can find from $(a1)$ and $(b1)$ of figure \ref{mds2} that our HBS can separate different types more apart and keep relatively clear boundaries while shape context concentrates dogs, gorillas, camel and elephants in a very small range.
+By the way, the shape context distance is much more complicated and it takes more 5 hours(18377.49 seconds) to calculate distances between each 2 of these 58 shapes but our HBS only need 0.23 seconds.
+
         \begin{figure}
@@
             \begin{center}
-                    \includegraphics[width=\textwidth]{mds2.png}
-                \end{center}
-                \caption{(a) The MDS result of Harmonic Beltrami signature; (b) The MDS result of conformal welding; (c) The clustering result of Harmonic Beltrami signature; (d) The clustering results of conformal welding.}
+                \includegraphics[width=\textwidth]{mds_km.png}
+            \end{center}
+            \caption{Row (a) is our proposed HBS, row (b) is shape context, row (c) is boundary moments and row (d) is conformal welding.For each row, the left is MDS result, the middle is $k$-medoids classification result and the right is confusion matrix of classification.}
             \label{mds2}
@@
 
+        \begin{table}[]
+        \centering
+        \begin{tabular}{|c|c|c|c|c|}
+        \hline
+        Algorithm & our HBS & Shape Context & Boundary Moments & Conformal Welding \\ \hline
+        Accuracy  & 94.83\% & 93.10\% & 46.55\% & 34.48\% \\ \hline
+        \end{tabular}
+        \caption{Multi-class classification accuracy for our HBS, shape context, boundary moments and conformal welding.}
+        \label{acc table}
+        \end{table}
+
     \section{Conclusion}\label{conclusion}
         In this paper, we propose a novel shape representation for 2D bounded simply-connected objects called Harmonic Beltrami signature.
-The proposed signature is based on conformal welding but overcome a key shortcoming that it can be uniquely determined by the given shape.
-What's more exciting is that the proposed representation is invariance under scaling, translation and rotation.
+The proposed signature is based on conformal welding but overcome a key shortcoming and it can be uniquely determined by the given shape.
+What's more exciting is that the proposed representation is invariant under scaling, translation and rotation.
 For slight deformation and distortion, HBS keeps robust and only changes within a reasonable small range.
-Therefore, there are reasons to believe the it does have ability to represent some invariant geometrical features.
+Conversely, if two HBS are alike, their corresponding domains are similar.
+Therefore, we have every reason to believe the it does have ability to represent some invariant geometrical features.
 The experimental results also confirm that the HBS has excellent performance in multi-classification tasks.
@@
         Although our work has achieved relatively good results, the proposed representation still have some limitations.
-Firstly, the HBS is only applicable to simply-connected shapes currently, but as a matter of fact, multi connected images are the majority in the real world.
-So we are eager for a feasible method to extend our HBS to multi connected situation.
+Firstly, the HBS is only applicable to simply-connected shapes currently, but as a matter of fact, multi-connected images are the majority in the real world.
+So we are eager for a feasible method to extend our HBS to multi-connected situation.
 Secondly, the traditional algorithm to compute the Beltrami coefficient is inevitably dependent on triangular mesh, which consumes a lot of time.
 Therefore, a fast algorithm to obtain this signature avoiding dense mesh is of high priority in our future work.
-Thirdly, when normalizing the conformal mapping $\Phi_2$ from exterior of unit disk to exterior of the domain, the position where the derivation of $\Phi_2$ reaches the maximum value is used to adjust the rotation.
-We trust this point in the original image has a certain geometric meaning, whereas it is not clear at present.
 
@@
 \end{document}
-% end of file template.tex
-
-\subsection{Reconstruction}\label{reconstruction}
-    The above theorems show that our Harmonic Beltrami signature can be uniquely defined by the given shape and is invariant under translation, scaling and rotation.
-Conversely, we will further demonstrate the method to reconstruct the original shape when given a Beltrami signature in this section.
-
-    If $B_\Omega$ is the HBS of some simply-connected domain $\Omega$, according to the process we mentioned at the beginning of Section \ref{main}, there exists conformal mappings $\Phi_1 : \D \rightarrow \Omega$, $\Phi_2: \D^c \rightarrow \Omega^c$, conformal welding $f: \partial \D \rightarrow \partial \D $ and harmonic extension $H$ of $f$, where $\Phi_1$ satisfies equation (\ref{norm phi1}), $\Phi_2$ satisfies equations (\ref{norm phi2 1}), $f = \Phi_1^{-1} \circ \Phi_2$, $\mu_H = B_\Omega$ and $B_\Omega$ satisfies (\ref{arg integral B is 0}).
-
-    Given a Harmonic Beltrami signature $B_\Omega$, define
-    \begin{equation}
-        g(z) = \begin{cases}
-            B_\Omega(z), z \in \D \\
-            0, z \in \D^c
-        \end{cases}
-    \end{equation}
-    According to Theorem \ref{Measurable Riemannian Mapping Theorem}, we can find mapping $G: \overline{\C} \rightarrow \overline{\C}$ such that
-    \begin{align}
-        &\mu_G = \frac{G_{\overline{z}}}{G_z} = g \nonumber\\
-        &G(\infty) = \infty\label{Ginfty}
-    \end{align}
-    where $G$ is uniquely determined up to Mobi\"us transformation $M$.
-
-    Claim that $\Omega' = G(\D)$ is the reconstructed domain satisfying $\Omega' = T(\Omega)$, where $T$ is composed by rotation, scaling and translation. Note that
-    \begin{equation}
-        G_0(z) = \begin{cases}
-            \Phi_1 \circ H(z), z \in \D\\
-            \Phi_2(z), z \in \D^c
-        \end{cases}
-    \end{equation}
-    is one solution of (\ref{Ginfty}) since $\mu_{\Phi_1 \circ H} = \mu_H = B_\Omega$ inside $\D$, $\mu_{\Phi_2} = 0$ outside $\D$ and $\Phi_2(\infty) = \infty$. Therefore, we have 
-    \begin{equation}
-        G = M \circ G_0 \text{ and } M(\infty) = \infty.
-    \end{equation}
-    By the properties of Mobi\"us transformation, we have $M(z) = az+b$ where $a, b \in \C$.
-
-    On the other side, $H$ is a harmonic mapping from $\D$ onto itself, so $G_0(\D) = \Phi_1 \circ H(\D) = \Omega$, then $\Omega' = G(\D) = M(\Omega) = a \Omega + b$, which show the claim is correct.
-
-    That means the map between Harmonic Beltrami signatures and shapes is also a bijection, up to transformation, scaling and rotation.
-In the theorem \ref{one to one equivalence class} tells us that there exists a one-to-one relationship between HBS equivalence classes and shapes and now such bijection can be extended to a special HBS, i.e.
-the unique representative of equivalence class.
-    \begin{theorem}
-        Let $\Omega_1, \Omega_2$ be two different simply-connected domains and $B_{\Omega_1}, B_{\Omega_2}$ are the corresponding HBS, then $B_{\Omega_1} = B_{\Omega_2}$ if and only is $\Omega_1 = T(\Omega_2)$, where $T$ is composed by rotation, scaling and translation.
-    \end{theorem}
-
-    \begin{proof}
-        The direction from signatures to shapes is proved in this section, and another direction is derived from theorem \ref{invariance theorem}.
-    \end{proof}
